### 2016-08-14 Documents/SM.tex
Restructured /Documents.

\documentclass[11pt]{article}

\usepackage{amsmath}
\usepackage[pdfborder={0 0 0}]{hyperref}
\usepackage[numbers,round,sort&compress]{natbib}
\usepackage{hypernat}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{microtype}
\usepackage[final]{pdfpages}

\usepackage[noblocks]{authblk}
\renewcommand{\Authsep}{, }
\renewcommand{\Authand}{ \& }
\renewcommand{\Authands}{ \& }
\renewcommand{\Affilfont}{\small}

\newcommand{\comment}[1]{\textbf{[#1]}}
\newcommand{\md}{\mathrm{d}}
\newcommand{\mT}{\mathrm{T}}
\renewcommand{\vec}[1]{\mathbf{#1}}
\newcommand{\mat}[1]{\mathbf{#1}}
\newcommand{\me}{\mathrm{e}}

\title{Supporting online material for\\
  \emph{Effectiveness of UNAIDS targets and HIV vaccination across 127
    countries}}

\author[1*]{Jan Medlock}
\author[2]{Abhishek Pandey}
\author[2]{Alyssa S.~Parpia}
\author[2]{Amber Tang}
\author[2]{Laura A.~Skrip}
\author[2]{Alison P.~Galvani}
\affil[1]{Department of Biomedical Sciences, Oregon State University,
  106 Dryden Hall, Corvallis, OR, 97331-4801, USA}
\affil[2]{Center for Infectious Disease Modeling and Analysis, Yale
  School of Public Health, 135 College Street, New Haven, USA}
\affil[*]{To whom correspondence should be addressed.  E-mail:
  \href{mailto:jan.medlock@oregonstate.edu}{
    \texttt{jan.medlock@oregonstate.edu}}}

\begin{document}
\maketitle

\newcommand{\labelPrefix}{S}
\renewcommand{\thesection}{\labelPrefix\arabic{section}}
\renewcommand{\theequation}{\labelPrefix\arabic{equation}}
\renewcommand{\thefigure}{\labelPrefix\arabic{figure}}
\renewcommand{\thetable}{\labelPrefix\arabic{table}}

Model source code: \url{https://github.com/janmedlock/HIV-95-vaccine/}.

\section{Data sources}

Several sources provided information to parameterize our model at the
country level. Demographic data, including population growth rate
\cite{WorldBankpg}, death rate
\cite{World_Development_Indicators2013-ee}, and number of people aged
15--49 years \cite{The_World_Bank2016-fd} were obtained from the World
Bank. Longitudinal HIV incidence and prevalence estimates for the
15--49 age group, spanning from as early as 1990 to 2015, was
primarily derived from the AIDSinfo database produced by UNAIDS
\cite{Unaids2016-an}. Other sources included UNAIDS Country Progress
Reports \cite{Unaids2016-am} published from 2012 to 2016 and AIDS Data
Hub \cite{AIDSdatahub-fg}, which compiles data from UNAIDS, UNICEF,
WHO, and the Asian Development Bank. These sources were also used to
inform the initial conditions for the model: the number of people who
have been diagnosed with HIV, who are on ART, and who have viral
suppression or have been retained on treatment for at least 12
months. Where data were not available from these sources, alternative
resources such as peer-reviewed journal articles and country health
ministry reports were consulted.  We found sufficient data to
parametrize our mathematical modeling for 127 countries.  See
Supplementary Material 2 (SM2)for full information on data sources for
each country.

\section{Mathematical model}
\begin{figure}
  \label{model_diag}
  \begin{center}
    \input{diagram}
    \caption{Model diagram.}
  \end{center}
\end{figure}

Our continuous-time, compartmental model consists of 8 health states:
susceptible to HIV infection, vaccinated against HIV, acute HIV
infection, undiagnosed HIV infection, diagnosed but untreated HIV
infection, treated without achieving viral suppression, achieved viral
suppression, and having AIDS (Figure \ref{model_diag}). Transitions
between states are governed by a series of differential equations
parameterized using rates estimated from other studies and from
incidence and prevalence data (Table \ref{model_param}).

\begin{table}
\begin{center}
  \begin{tabular}{cp{4cm}llc}
\hline
    Symbol & Definition & Value & Sampling Distribution & Source \\ \hline
    $\delta$	& Rate of leaving acute phase of HIV infection & 4.1379/year & T (4.1379, 2, 9.6) & \cite{Hollingsworth2008-iy} \\
    $\sigma$	& Rate of developing AIDS among non-virally suppressed individuals
                       & 0.1064/year & & \cite{Morgan2002-cq} \\
    $\gamma$ & Rate of viral suppression & 1/year & U (0.5, 1.5) & \cite{Currie2009-yz} \\
    $\upsilon$	& Death rate from AIDS & 0.5/year &  & \cite{Morgan2002-cq} \\
    $\omega$	& Reduction in life years for treated PLHIV & 5 & U (5, 8) & \cite{Unaids2014-ue, Samji2013-kf}\\
    $\beta_{A}$	& Transmission probability during acute phase & 0.0082 & T (0.0082, 0.0039, 0.0150) & \cite{Skarbinski2015-ni,Wawer2005-us}\\
    $\beta_{U}$	& Transmission probability after acute phase & 0.0014 & T (0.0014, 0.00077, 0.00251) & \cite{Hughes2012-so}\\
    $\varepsilon$	& Proportional reduction of transmission with treatment & 0.08 & $\beta$ (0.08, 0.002, 0.57)& \cite{Donnell2010-xo}\\
    $n$			& Sex acts per year & 102 & U (96, 108) & \cite{Wawer2005-us,Abdool_Karim2010-cm}\\ \hline
  \end{tabular}
\caption{Parameters used in model. (T: triangular distribution, U:
  uniform distribution, $\beta$: beta distribution).}
\end{center}
\label{model_param}
\end{table}

The PLHIV population was comprised of people in the acutely infected,
undiagnosed, diagnosed, treated, viral suppression and AIDS
compartments. People susceptible to HIV (S) progress to the
acute-infection phase (A) according to the force of infection, which
depends on the HIV transmission rate, estimated from the
country-specific incidence and prevalence data (next section),
adjusted for the current number of acutely infected, untreated or
ineffectively treated, and viral suppression PLHIV.  Acute infection
is characterized by high viral loads and lasts 88 days on average
\cite{Hollingsworth2008-iy}. We assumed that individuals remain
undiagnosed during their acute infection phase and during at least
some of the subsequent period of clinical latency (i.e., the
undiagnosed compartment). Individuals in the undiagnosed class will be
diagnosed at a rate determined by the country's initial diagnosis
level and potential progress towards the UNAIDS targets. Diagnosed
people transition to the treated compartment upon starting ART at a
rate of $\phi$ , and to the virally suppressed class (V) after
achieving viral suppression through treatment retention at a rate of
$\gamma$. The disengagement from treatment moves individuals (T, V) at
a rate of $\omega$ back to the diagnosed class (D). Rates of movement
between the undiagnosed (U), diagnosed (D), treated (T) and virally
suppressed classes (V) are determined by the proportions of PLHIV
diagnosed ($p_{D}$), proportion of diagnosed individuals on ART
($p_{T}$), and the proportion of individuals on ART who have achieved
viral suppression ($p_{V}$). PLHIV in U, D, T, and V classes develop
AIDS (W) after an average duration dependent on viral suppression
status. Individuals who have achieved viral suppression (V) take
longer to develop AIDS ($1/\theta$), than those who are in the other
PLHIV classes ($1/\sigma$). Individuals who are susceptible to HIV can
be vaccinated at a of rate ($\zeta$), and depending on vaccine
efficacy, have a reduced chance of HIV infection. The model equations
are

\begin{equation}
  \label{model_eqns}
  \begin{split}
    \frac{\md S}{\md t} &= B N - \lambda S - \zeta S- \mu S,
    \\
     \frac{\md R}{\md t} & = \zeta S - \rho \lambda R - \mu R,
    \\
    \frac{\md A}{\md t} &= \lambda S +\rho \lambda R - \delta A - \mu A,
    \\
    \frac{\md U}{\md t} &= \delta A - \alpha U - \mu U - \sigma U,
    \\
    \frac{\md D}{\md t} &=  \alpha U + \psi T + \psi V
    - \phi D - \mu D - \sigma D,
    \\
    \frac{\md T}{\md t} &= \phi D - \psi T - \gamma T - \mu T
    - \sigma T,
    \\
    \frac{\md V}{\md t} &= \gamma T - \psi V - \mu V - \theta V,
    \\
    \frac{\md W}{\md t} &= \sigma U + \sigma D + \sigma T + \theta V -
    \nu W,
  \end{split}
\end{equation}
with force of infection
\begin{equation}
  \label{force_of_infection}
  \begin{split}
    \lambda &= \frac{\beta_A A + \beta_U (U + D + T) + \beta_T V}{N},
    \\
    N &= S + R +  A + U + D + T + V,
    \\
    \beta_x &= c \left[1 - (1 - \tau_x)^n\right]
    \text{ for $x \in \{A, U, T\}$},
    \\
    \tau_T &= (1 - \epsilon) \tau_U.
  \end{split}
\end{equation}

The rate of developing AIDS  among those who have acheived
viral suppression ($\theta$) is
\begin{equation}
 \frac{1}{1/\mu-\omega-1/\nu}.
\end{equation}

The proportion diagnosed is
\begin{equation}
  p_D = \frac{D + T + V + W}{A + U + D + T + V + W},
\end{equation}
the proportion treated is
\begin{equation}
  p_T = \frac{T + V + W}{D + T + V + W},
\end{equation}
and the proportion with viral suppression is
\begin{equation}
  p_V = \frac{V}{T + V}.
\end{equation}

The targets for the proportions $p_D$, $p_T$, and $p_V$ in the achievement of 90---90---90
all operate under the following assumption:
if the initial level $p_x(0)$ is less than $90\%$, the proportion will increase
linearly in the first 5 years and then stay at $90\%$ for the
remaining time; and if the initial level is at $90\%$ or above, the proportion
will remain constant for the duration of the study:
\begin{equation}
  p_x^*(t)
  = p_x(0) + \left[
    \max\left\{0.9, p_x(0)\right\} - p_x(0)
  \right]
  \min\left\{\frac{t}{5}, 1\right\},
\end{equation}
for $x \in \{D, T, V\}$.

Similarly, the proportion of people vaccinated is
\begin{equation}
P_{V} = \frac{R}{S+R},
\end{equation}

We can implement the vaccination compartment in the same way as the other controls. When we begin
vaccination in 2020/2025, the initial vaccination level is 0\%. This
coverage will increase linearly to $50\%$ within first 2 or 5
years. The coverage will continue to increase linearly till it reaches
the desired coverage ($50\%,70\%,90\%$) and then stay constant for the
remainder of the projections.

95---95---95 goal is implemented subsequently after meeting
90---90---90 by2020 by  increasing $p_D$, $p_T$, and $p_V$ to
95---95---95 levels by 2030 linearly. \comment{@Jan, We use the
  Heaveside function here too?}

\subsection{Rates that are on when $p_x < p^*_x$}

The rates are applied when the proportions of $p_D$, $p_T$, and $p_V$ are below the target levels:
\begin{equation}
  \begin{split}
    \alpha(t) &= \alpha_{\max} H\left(p_D^*(t) - p_D(t)\right),
    \\
    \phi(t) &= \phi_{\max} H\left(p_T^*(t) - p_T(t)\right),
    \\
    \psi(t) &= \psi_{\max} H\left(p_V(t) - p_V^*(t)\right),
    \\
    \zeta(t) &= \zeta_{max} H\left(P^{*}_{V}(t)-P_{V}(t)\right),
  \end{split}
\end{equation}
where $H(x)$ is the Heaviside function
\begin{equation}
  H(x) =
  \begin{cases}
    0 & \text{if $x < 0$},
    \\
    1 & \text{if $x > 0$}.
  \end{cases}
\end{equation}

The discontinuity of the Heaviside function makes numerical solution
difficult.  Instead, replace $H$ with the continuous piecewise linear
function
\begin{equation}
  H(x) =
  \begin{cases}
    0 & \text{if $x < 0$},
    \\
    x / \chi & \text{if $0 \leq x \leq \chi$},
    \\
    1 & \text{if $x > \chi$},
  \end{cases}
\end{equation}
with some small value of $\chi$.

\section{Model fitting}
\label{model_fitting}
We first estimated country-specific rates of HIV transmission for each
of the available historical data point for incidence and
prevalence. The calculation involved a simplified force of infection
that initially assumed no differences in transmission risk among
acute, unsuppressed, suppressed, and AIDS classes due to the general
lack of historical data on diagnosis and treatment. We calculated a
time-independent aggregate transmission rate by taking an exponential
weighted mean of the historical (i.e., time-dependent) transmission
rates for each given country (\ref{transmission_rate}). The aggregate
transmission rate was then combined with estimated HIV transmission
risk by stage of HIV infection \cite{Hollingsworth2008-iy} and
treatment status \cite{Wawer2005-us} to calculate separate
transmission rates for unsuppressed, acute, and viral-suppression
people. These rates were used to simulate model projections through
2035.

{We calibrated longitudinal HIV incidence and prevalence data from
  1990 to 2015 incidence in addition to data on $p_{D}$, $p_{T}$ and
  $p_{V}$ levels in 2015 to estimate the rate of transmission for each
  country. The calculation involved a simplified force of infection:}

\begin{align}
  \label{foi}
  \begin{split}
  \lambda(t) &  =    \frac{\beta_{A} A + \beta_{U}(U+D+T)+\beta_{V}V+0
               W}{N} \\
             &  =  \beta \frac{I}{N},
             \end{split}
\end{align}
where $\beta$ is the estimated time-independent aggregate transmission rate under the
assumption that there is no difference in transmission risk among acute, unsuppressed, suppressed, and AIDS classes.

$I = A+U+D+T+V+W$ is the total number of people living with HIV. Therefore, the per-capita
incidence is
\begin{equation}
i(t) = \lambda(t) \frac{S(t)}{N(t)}
= \beta(t) \frac{I(t)}{N(t)} \frac{S(t)}{N(t)} =\beta(t) p(t) (1-p(t)),
\end{equation}
where $p(t)$ is the prevalence. Thus, we can estimate the
transmission rate at each historical time point using the incidence
and prevalence data,
\begin{equation}
  \label{trans_rate}
  \beta(t) = \frac{i(t)}{p(t)(1-p(t))}
\end{equation}

We estimated the time-independent aggregated transmission rate ($\beta$)
by taking the exponential weighted mean of transmission rates
(\ref{trans_rate}).

Rearranging equation (\ref{foi}), the transmission rate for PLHIV
without viral suppression can be written as
\begin{equation}
\label{betaU}
  \beta_{U} = \frac{\beta I}{\frac{\beta_{A}}{\beta_{U}}A +
    U+D+T+\frac{\beta_{V}}{\beta_{U}}V}
\end{equation}

Next, we assumed that the relative risk of acute HIV transmission
($\beta_{AU} = \beta_{A}/\beta_{U}$) and virally suppressed HIV
transmission ($\beta_{VU} = \beta_{V}/\beta_{U}$) with respect to the
unsuppressed transmission remains constant worldwide and calculated
these values using the data from Rakai, Uganda \cite{Wawer2005-us}. The aggregate
rate of transmission ($\beta$) can then be combined with equations \ref{betaU} to calculate transmission
rates for unsuppressed PLHIV, acute PLHIV and suppressed PLHIV as,
\begin{align}
  \beta_{U} & = \frac{\beta I}{\beta_{AU}A +
              U+D+T+\beta_{VU}V}, \\
  \beta_{A} & = \beta_{AU}\beta, \\
  \beta_{V} & = \beta_{VU} \beta.
\end{align}
that we use to simulate our model forward and project results up to 2035.
\\

\comment{Need to add stuff about how we generate distribution of
  transmission rates}

\section{Analysis}
We evaluated the global and country-specific impacts of meeting the
UNAIDS targets and vaccine deployment on four outcome measures: HIV
incidence, PLHIV, number of people with AIDS, and AIDS-related deaths
between 2015 and 2035. Calibrating our model to historical data on
prevalence and incidence, we projected the anticipated trajectories of
the outcomes using country-specific transmission rates across the
intervention scenarios outlined below.  Our base-case scenario assumed
maintenance of the status quo: that 2015 levels of the proportion of
PLHIV diagnosed ($p_{D}$), proportion of those diagnosed on ART
($p_{T}$), and proportion of those on treatment who have achieved
viral suppression ($p_{V}$) continue unchanged until 2035.  The
intervention scenarios were (1.) the attainment of the 90--90--90
target by linear increases in $p_{D}$, $p_{T}$, and $p_{V}$ until 2020
followed by maintenance of those levels until 2035, and (2.) linear
increase in the diagnosis and treatment levels to the 90--90--90
targets by 2020, a linear increase from 90--90--90 to the 95--95--95
target by 2030, and maintenance of the 95--95--95 levels to 2035. (For
90--90--90, if any initial level was above 90\%, it was kept constant
going forward so that the intervention did not worsen coverage.
Likewise, for 95--95--95, any initial level above 95\% was kept
constant.)  For vaccination, we assumed deployment of a vaccine with
50\% efficacy in 2020 with coverage increasing linearly from 0\% to
50\% at 2 years post-rollout and maintaining constant coverage after
reaching 70\%. The added benefit of vaccination was considered in the
context of status quo diagnosis and treatment, achieving the UNAIDS
90–90–90 goal by 2020 followed by maintenance, and achieving the
95–95–95 goal by 2030 followed by maintenance.  Projections were
generated through model simulations based on published parameter
distributions (\autoref{model_param}) and country-specific estimated
transmission rate distributions. The parameters were sampled using
latin hypercube sampling \cite{} and the variance reduction technique
of running different interventions with random parameter values
\cite{}.

We calculated partial rank correlation coefficients (PRCC) to measure
the independent effect of each parameter on model projections of HIV
incidence. Furthermore, due to uncertainty surrounding the prospective
vaccine, we obtained model projections using six additional vaccine
scenarios by considering alternative estimates of efficacy (30\%,
70\%), coverage (50\%, 90\%), time to 50\% coverage (2 years, 5
years), and first year of availability (2025).

\section{Results}

\subsection{Medians and distributions for country-specific
  transmission rates}
\label{transmission_rate}
Country-specific transmission rates were calculated based on the
relative contributions of individuals with acute infection,
unsuppressed viral load or suppressed viral load to overall
transmission (\autoref{model_fitting}). The estimates were calibrated
to data on country-level incidence and/or prevalence to account for
variation in historical incidence while accurately reflecting recent
HIV rates.
\includepdf[]{../../Codes/plots/transmission_rate}

\subsection{Effectiveness of HIV interventions globally, regionally
  and for each of 127 countries}

Model outcomes were projected until 2035 for each of the 127 countries
with sufficient data on status quo rates of diagnosis and treatment
and on historical incidence or prevalence. The median estimates with
interquartile ranges are presented between 2015 and 2035 for number of
PLHIV, annual incidence (per million population), number of people
with AIDS, and number of HIV-related deaths under the status quo and
five intervention scenarios: vaccination only, attainment of the
UNAIDS 90-90-90 target, 90-90-90 target and vaccination, attainment of
the UNAIDS 95-95-95 target, and 95-95-95 target and vaccination.  The
country-specific projections as well as aggregated projections at the
regional and global levels follow:

\bibliographystyle{science_nat}

\bibliography{SM}

\end{document}

### 2016-08-14 Codes/plots/drive_upload.py

@@ -11,8 +11,8 @@ import drive
 
 
 files = (
-    '../../Documents/Latex/diagram_standalone.pdf',
-    '../../Documents/Latex/diagram_standalone.png',
+    '../../Documents/diagram_standalone.pdf',
+    '../../Documents/diagram_standalone.png',
     'effectiveness.pdf',
     'effectiveness.png',
     'effectiveness_all.pdf',

### 2016-08-15 Documents/supplementary_text.tex
Working on supplement.

--- 2016-08-14 Documents/SM.tex
@@
 \usepackage{amsmath}
-\usepackage[pdfborder={0 0 0}]{hyperref}
-\usepackage[numbers,round,sort&compress]{natbib}
-\usepackage{hypernat}
 \usepackage{geometry}
@@
 \usepackage{tikz}
+\usepackage[utf8x]{inputenc}
 \usepackage{microtype}
 \usepackage[final]{pdfpages}
+\usepackage{float}
+\usepackage{longtable}
+\usepackage[pdfborder={0 0 0}]{hyperref}
+\usepackage[numbers,round,sort&compress]{natbib}
+\usepackage{hypernat}
 
@@
 \newcommand{\me}{\mathrm{e}}
+
+\renewcommand{\figurename}{Fig.}
 
@@
 parametrize our mathematical modeling for 127 countries.  See
-Supplementary Material 2 (SM2)for full information on data sources for
-each country.
+\autoref{data_source_treatment_cascade}--\ref{data_source_regions} for
+full information on data sources for each country.
+
+\begin{table}
+  \centering
+  \tiny
+  \input{treatment_cascade.tex}
+  \caption{Data sources on the treatment cascade.}
+  \label{data_source_treatment_cascade}
+\end{table}
 
 \section{Mathematical model}
+
 \begin{figure}
-  \label{model_diag}
-  \begin{center}
+  \centering
   \input{diagram}
   \caption{Model diagram.}
-  \end{center}
+  \label{model_diag}
 \end{figure}
@@
 weighted mean of the historical (i.e., time-dependent) transmission
-rates for each given country (\ref{transmission_rate}). The aggregate
-transmission rate was then combined with estimated HIV transmission
-risk by stage of HIV infection \cite{Hollingsworth2008-iy} and
-treatment status \cite{Wawer2005-us} to calculate separate
-transmission rates for unsuppressed, acute, and viral-suppression
-people. These rates were used to simulate model projections through
-2035.
+rates for each given country (\autoref{transmission_rate}). The
+aggregate transmission rate was then combined with estimated HIV
+transmission risk by stage of HIV infection
+\cite{Hollingsworth2008-iy} and treatment status \cite{Wawer2005-us}
+to calculate separate transmission rates for unsuppressed, acute, and
+viral-suppression people. These rates were used to simulate model
+projections through 2035.
 
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width = \textwidth]{../Codes/plots/transmission_rate}
+  \caption{Country-specific transmission rates were calculated based
+    on the relative contributions of individuals with acute infection,
+    unsuppressed viral load or suppressed viral load to overall
+    transmission (\autoref{model_fitting}). The estimates were
+    calibrated to data on country-level incidence and/or prevalence to
+    account for variation in historical incidence while accurately
+    reflecting recent HIV rates.}
+  \label{transmission_rate}
+\end{figure}
+
 \section{Analysis}
+
 We evaluated the global and country-specific impacts of meeting the
@@
 transmission rate distributions. The parameters were sampled using
-latin hypercube sampling \cite{} and the variance reduction technique
-of running different interventions with random parameter values
-\cite{}.
+latin hypercube sampling \cite{}
+and the variance reduction technique of running different
+interventions with random parameter values \cite{}.
 
@@
 the independent effect of each parameter on model projections of HIV
-incidence. Furthermore, due to uncertainty surrounding the prospective
-vaccine, we obtained model projections using six additional vaccine
-scenarios by considering alternative estimates of efficacy (30\%,
-70\%), coverage (50\%, 90\%), time to 50\% coverage (2 years, 5
-years), and first year of availability (2025).
+incidence (\autoref{PRCCs}). Furthermore, due to uncertainty
+surrounding the prospective vaccine, we obtained model projections
+using six additional vaccine scenarios by considering alternative
+estimates of efficacy (30\%, 70\%), coverage (50\%, 90\%), time to
+50\% coverage (2 years, 5 years), and first year of availability
+(2025).
 
-\section{Results}
-
-\subsection{Medians and distributions for country-specific
-  transmission rates}
-\label{transmission_rate}
-Country-specific transmission rates were calculated based on the
-relative contributions of individuals with acute infection,
-unsuppressed viral load or suppressed viral load to overall
-transmission (\autoref{model_fitting}). The estimates were calibrated
-to data on country-level incidence and/or prevalence to account for
-variation in historical incidence while accurately reflecting recent
-HIV rates.
-\includepdf[]{../../Codes/plots/transmission_rate}
+\begin{figure}
+  \centering
+  \includegraphics{../Codes/plots/prcc.pdf}
+  \caption{Parameter sensitivity of model global infections averted
+    from 2015 to 2035.}
+  \label{PRCCs}
+\end{figure}
 
@@
 five intervention scenarios: vaccination only, attainment of the
-UNAIDS 90-90-90 target, 90-90-90 target and vaccination, attainment of
-the UNAIDS 95-95-95 target, and 95-95-95 target and vaccination.  The
+UNAIDS 90--90--90 target, 90--90--90 target and vaccination, attainment of
+the UNAIDS 95--95--95 target, and 95--95--95 target and vaccination.  The
 country-specific projections as well as aggregated projections at the
@@
 
-\bibliography{SM}
+\bibliography{supplementary_text}
+
+\clearpage
+\input{../Codes/plots/effectiveness_all/all}
 

### 2016-08-15 Documents/treatment_cascade.tex
Working on supplement.

\begin{longtable}{lrrrl}
  \hline
  & & & \multicolumn{1}{c}{Viral} \\
  Country & \multicolumn{1}{l}{Diagnosed}
  & \multicolumn{1}{l}{Treated} & \multicolumn{1}{l}{suppression}
  & References \\
  \hline
  Afghanistan & 5.0\% & 100.0\% & 84.0\% & \cite{Unaids2016-an} \\
  Algeria & 93.0\% & 91.7\% & 50.0\% & \cite{Unaids2016-an} \\
  Angola & 26.0\% & 100.0\% & 92.0\% & \cite{Unaids2016-an}, 2013a \\
  Argentina & 79.0\% & 79.3\% & 66.0\% & \cite{Unaids2016-an}, 2015a \\
  Armenia & 46.0\% & 55.4\% & 77.0\% & \cite{Unaids2016-an} \\
  Australia & 90.0\% & 99.4\% & 92.5\% & \cite{Unaids2016-an}, \url{https://kirby.unsw.edu.au/sites/default/files/hiv/resources/HIVASRsuppl2014_online.pdf} \\
  Austria & 80.0\% & 86.8\% & 63.0\% & 28th Report of the Austrian HIV Cohort Study (Innsbruck, September 30th, 2015), \url{https://www.google.com/url?sa=t&rct=j&q=&esrc=s&source=web&cd=12&ved=0ahUKEwjQkqHwwtLNAhXG0h4KHYxYDdM4ChAWCB0wAQ&url=http%3A%2F%2Fdermatologie.tirol-kliniken.at%2Fdata.cfm%3Fvpath%3Ddokumente%2F2015-hiv-kohortenbericht&usg=AFQjCNH9LyCKkigHECw7oYAEq_NBfRHjKw&sig2=eywFWu8eQN6aWf_QwHNLlw&bvm=bv.125801520,d.dmo&cad=rja} \\
  Azerbaijan & 35.0\% & 76.9\% & 67.0\% & \cite{Unaids2016-an} \\
  Bahamas & 37.0\% & 98.2\% & 69.0\% & \cite{Unaids2016-an} \\
  Bangladesh & 36.0\% & 41.6\% & 31.0\% & \cite{Unaids2016-an} \\
  Barbados & 85.0\% & 50.6\% & 88.0\% & \cite{Unaids2016-an} \\
  Belarus & 20.0\% & 100.0\% & 71.0\% & \cite{Unaids2016-an}, 2015b \\
  Belgium & 80.0\% & 74.5\% & 91.0\% & \cite{Unaids2016-an}, \url{http://ec.europa.eu/chafea/documents/health/hiv-cluster-meeting-material/presentations-pharis-s3_en.pdf}, 2015a \\
  Belize & 46.0\% & 99.0\% & 47.0\% & \cite{Unaids2016-an}, 2014b \\
  Benin & 48.0\% & 100.0\% & 93.0\% & \cite{Unaids2016-an}, 2011a \\
  Bhutan & 40.3\% & 41.4\% & 87.0\% & \cite{Unaids2016-an, Unaids2016-am}, 2014b \\
  Bolivia & 29.0\% & 97.7\% & 69.0\% & \cite{Unaids2016-an} \\
  Botswana & 80.0\% & 97.2\% & 90.0\% & \cite{Unaids2016-an} \\
  Brazil & 55.0\% & 100.0\% & 77.0\% & \cite{Unaids2016-an}, 2014b \\
  Bulgaria & 21.8\% & 72.7\% & 81.6\% & \cite{Unaids2016-an, Unaids2016-am}\\
  Burkina Faso & 83.0\% & 66.3\% & 79.0\% & \cite{Unaids2016-an}, 2013? \\
  Burundi & 54.0\% & 100.0\% & 90.0\% & \cite{Unaids2016-an}, 2015b \\
  Cambodia & 82.0\% & 89.0\% & 94.0\% & \cite{Unaids2016-an} \\
  Cameroon & 27.0\% & 100.0\% & 60.0\% & \cite{Unaids2016-an}, 2015a \\
  Canada & 79.0\% & 64.6\% & 68.6\% & \url{http://www.catie.ca/sites/default/files/2014-HIV-Estimates-in-Canada-EN.pdf}, \url{http://www.catie.ca/en/catienews/2014-02-19/gaps-british-columbia-s-hiv-treatment-cascade} \\
  Cape Verde & 29.0\% & 100.0\% & 95.0\% & \cite{Unaids2016-an}, 2015b \\
  Central African Republic & 24.0\% & 98.1\% & 91.0\% & \cite{Unaids2016-an}, 2013? \\
  Chad & 36.0\% & 100.0\% & 91.0\% & \cite{Unaids2016-an}, 2013? \\
  Chile & 90.0\% & 96.7\% & 95.0\% & \cite{Unaids2016-an}, 2015b \\
  China & 64.2\% & 59.0\% & 91.0\% & \cite{Unaids2016-an, AIDSdatahub-fg}, \url{http://www.avert.org/professionals/hiv-around-world/asia-pacific/china} \\
  Colombia & 45.0\% & 73.0\% & 70.0\% & \url{http://ecdc.europa.eu/en/publications/Publications/dublin-declaration-continuum-of-care-2014.pdf} \\
  Republic of Congo & 37.4\% & 50.5\% & 79.4\% & \cite{Unaids2016-am} \\
  Costa Rica & 56.0\% & 100.0\% & 60.7\% & \cite{Unaids2016-an} \\
  Cuba & 64.0\% & 100.0\% & 59.0\% & \cite{Unaids2016-an} \\
  Côte d'Ivoire & 51.0\% & 68.7\% & 69.0\% & \cite{Unaids2016-an}, 2014b \\
  DR Congo & 33.0\% & 100.0\% & 86.0\% & \cite{Unaids2016-an}, 2015a \\
  Denmark & 85.0\% & 72.9\% & 95.2\% & \url{http://www.aidsmap.com/Australia-performs-best-in-HIV-treatment-cascade-62-with-undetectable-viral-load/page/2919074/} \\
  Djibouti & 70.0\% & 31.4\% & 86.0\% & \cite{Unaids2016-an}, 2015b \\
  Dominican Republic & 47.0\% & 98.4\% & 95.0\% & \cite{Unaids2016-an}, 2015b \\
  Ecuador & 53.0\% & 97.4\% & 85.0\% & \cite{Unaids2016-an}, 2012b \\
  Egypt & 40.6\% & 56.5\% & 80.0\% & \url{http://english.alarabiya.net/en/perspective/analysis/2014/08/28/Registered-HIV-AIDS-cases-rising-in-Egypt-U-N-.html}, 2015b \\
  El Salvador & 54.0\% & 100.0\% & 83.0\% & \cite{Unaids2016-an}, 2015b \\
  Equatorial Guinea & 31.0\% & 100.0\% & 82.0\% & \cite{Unaids2016-an} \\
  Eritrea & 60.0\% & 100.0\% & 77.0\% & \cite{Unaids2016-an}, 2015b \\
  Estonia & 87.0\% & 33.3\% & 65.5\% & \url{https://www.sm.ee/sites/default/files/content-editors/eesmargid_ja_tegevused/Tervis/Tervislik_eluviis/who_raport_hiv_aids_treatment_and_care_in_estonia.pdf} \\
  Ethiopia & 71.5\% & 70.0\% & 82.0\% & \cite{Unaids2016-am}, \url{https://dhsprogram.com/pubs/pdf/CR30/CR30.pdf}, 2012b \\
  France & 81.0\% & 91.4\% & 70.3\% & \url{http://www.aidsmap.com/Australia-performs-best-in-HIV-treatment-cascade-62-with-undetectable-viral-load/page/2919074/} \\
  Gabon & 85.0\% & 68.6\% & 64.0\% & \cite{Unaids2016-an}, 2014b \\
  Gambia & 24.0\% & 100.0\% & 83.0\% & \cite{Unaids2016-an}, 2015a \\
  Georgia & 43.0\% & 72.5\% & 84.0\% & \cite{Unaids2016-an} \\
  Ghana & 34.0\% & 100.0\% & 92.0\% & \cite{Unaids2016-an}, 2014b \\
  Greece & 90.2\% & 52.8\% & 95.0\% & \cite{Unaids2016-an, Unaids2016-am}, 2015b \\
  Guatemala & 38.0\% & 76.8\% & 83.0\% & \cite{Unaids2016-an} \\
  Guinea & 32.0\% & 90.9\% & 65.0\% & \cite{Unaids2016-an} \\
  Guyana & 58.0\% & 99.7\% & 80.0\% & \cite{Unaids2016-an} \\
  Haiti & 54.0\% & 96.3\% & 76.0\% & \cite{Unaids2016-an}, 2013b \\
  Honduras & 56.0\% & 92.9\% & 83.0\% & \cite{Unaids2016-an}, 2015b \\
  India & 95.2\% & 41.5\% & 73.0\% & \cite{AIDSdatahub-fg}, 2014b \\
  Indonesia & 9.0\% & 98.6\% & 71.0\% & \cite{Unaids2016-an}, 2014a \\
  Iran & 31.0\% & 28.4\% & 67.0\% & \cite{Unaids2016-an} \\
  Italy & 70.0\% & 87.6\% & 62.4\% & \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4348082/} \\
  Jamaica & 33.0\% & 95.1\% & 67.0\% & \cite{Unaids2016-an} \\
  Kazakhstan & 72.0\% & 35.7\% & 60.0\% & \cite{Unaids2016-an} \\
  Kenya & 58.0\% & 100.0\% & 84.0\% & \cite{Unaids2016-an} \\
  Kyrgyzstan & 50.0\% & 43.0\% & 62.0\% & \cite{Unaids2016-an} \\
  Laos & 62.0\% & 45.8\% & 83.0\% & \cite{AIDSdatahub-fg}, 2015b \\
  Lebanon & 36.0\% & 100.0\% & 79.0\% & \cite{Unaids2016-an} \\
  Lesotho & 67.0\% & 62.6\% & 68.0\% & \cite{Unaids2016-an} \\
  Liberia & 41.0\% & 65.7\% & 74.0\% & \cite{Unaids2016-an}, 2013b \\
  Madagascar & 4.0\% & 69.2\% & 73.0\% & \cite{Unaids2016-an}, 2012b \\
  Malawi & 61.0\% & 100.0\% & 78.0\% & \cite{Unaids2016-an}, 2012b \\
  Malaysia & 88.1\% & 24.6\% & 85.0\% & \cite{Unaids2016-an, AIDSdatahub-fg} \\
  Mali & 71.0\% & 41.4\% & 72.0\% & \cite{Unaids2016-an}, 2014a \\
  Mauritania & 18.0\% & 100.0\% & 87.0\% & \cite{Unaids2016-an} \\
  Mauritius & 65.0\% & 47.7\% & 82.0\% & \cite{Unaids2016-an}, 2014b \\
  Mexico & 58.0\% & 99.7\% & 85.0\% & \cite{Unaids2016-an}, 2015b \\
  Moldova & 41.0\% & 50.7\% & 78.0\% & \cite{Unaids2016-an} \\
  Mongolia & 41.0\% & 39.8\% & 93.0\% & \cite{Unaids2016-an, Unaids2016-am} \\
  Morocco & 46.0\% & 76.4\% & 82.0\% & \cite{Unaids2016-an}, 2015a \\
  Mozambique & 53.0\% & 99.5\% & 66.0\% & \cite{Unaids2016-an}, 2015b \\
  Myanmar & 47.0\% & 96.1\% & 87.0\% & \cite{Unaids2016-an} \\
  Namibia & 69.0\% & 97.5\% & 85.0\% & \cite{Unaids2016-an}, 2015b \\
  Nepal & 57.0\% & 50.9\% & 91.0\% & \cite{Unaids2016-an} \\
  Netherlands & 73.0\% & 93.2\% & 89.8\% & \url{http://www.aidsmap.com/Australia-performs-best-in-HIV-treatment-cascade-62-with-undetectable-viral-load/page/2919074/} \\
  New Zealand & 85.0\% & 80.0\% & 98.4\% & \cite{Unaids2016-am} \\
  Nicaragua & 47.0\% & 70.2\% & 61.0\% & \cite{Unaids2016-an} \\
  Niger & 28.0\% & 99.4\% & 67.0\% & \cite{Unaids2016-an}, 2015b \\
  Nigeria & 58.0\% & 41.4\% & 81.0\% & \cite{Unaids2016-an}, 2013b \\
  Pakistan & 6.0\% & 100.0\% & 58.0\% & \cite{Unaids2016-an} \\
  Panama & 59.0\% & 100.0\% & 66.0\% & \cite{Unaids2016-an} \\
  Papua New Guinea & 81.0\% & 64.2\% & 90.0\% & \cite{Unaids2016-an}, 2015a \\
  Paraguay & 71.0\% & 44.1\% & 70.0\% & \cite{Unaids2016-an} \\
  Peru & 64.0\% & 87.3\% & 82.0\% & \cite{Unaids2016-an}, 2015b \\
  Philippines & 63.0\% & 42.9\% & 92.0\% & \cite{Unaids2016-an} \\
  Russia & 49.0\% & 23.5\% & 80.0\% & \url{http://www.jiasociety.org/index.php/jias/article/view/19506} \\
  Rwanda & 85.0\% & 92.9\% & 94.0\% & \cite{Unaids2016-an}, 2012b \\
  Saint Lucia & 49.7\% & 70.2\% & 71.0\% & \cite{Unaids2016-an, Unaids2016-am} \\
  Senegal & 56.0\% & 73.2\% & 77.0\% & \cite{Unaids2016-an}, 2015b \\
  Sierra Leone & 27.0\% & 100.0\% & 71.0\% & \cite{Unaids2016-an}, 2014a \\
  Somalia & 8.0\% & 100.0\% & 81.0\% & \cite{Unaids2016-an}, 2015a \\
  South Africa & 57.0\% & 84.0\% & 71.0\% & \cite{Unaids2016-an}, 2013b \\
  South Sudan & 11.0\% & 100.0\% & 76.0\% & \cite{Unaids2016-an}, 2015b \\
  Spain & 74.0\% & 98.7\% & 89.0\% & \cite{Unaids2016-an} \\
  Sri Lanka & 45.0\% & 41.6\% & 81.0\% & \cite{Unaids2016-an}, 2015b \\
  Sudan & 8.0\% & 96.0\% & 90.0\% & \cite{Unaids2016-an}, 2012b \\
  Suriname & 54.0\% & 100.0\% & 76.0\% & \cite{Unaids2016-an}, 2014b \\
  Swaziland & 67.0\% & 100.0\% & 51.0\% & \cite{Unaids2016-an} \\
  Sweden & 90.0\% & 92.1\% & 94.7\% & \url{http://www.croiconference.org/sessions/swedish-hiv-treatement-cascade} \\
  Switzerland & 80.9\% & 87.8\% & 96.3\% & \url{http://www.natap.org/2015/IAS/Jake_IAS_Slides_July20X.pdf} \\
  Tajikistan & 34.0\% & 48.5\% & 77.0\% & \cite{Unaids2016-an} \\
  Tanzania & 53.0\% & 99.9\% & 67.0\% & \cite{Unaids2016-an}, 2015b \\
  Thailand & 83.0\% & 78.3\% & 96.0\% & \cite{Unaids2016-an} \\
  Timor-Leste & 43.8\% & 76.8\% & 82.0\% & \cite{Unaids2016-am} \\
  Togo & 41.0\% & 100.0\% & 87.0\% & \cite{Unaids2016-an}, 2014b \\
  Trinidad and Tobago & 62.0\% & 96.6\% & 90.0\% & \cite{Unaids2016-an}, 2015b \\
  Tunisia & 61.0\% & 44.3\% & 81.0\% & \cite{Unaids2016-an}, 2014b \\
  Uganda & 63.0\% & 87.9\% & 77.0\% & \cite{Unaids2016-an}, 2015b \\
  Ukraine & 27.0\% & 98.2\% & 86.0\% & \cite{Unaids2016-an}, 2015a \\
  United Kingdom & 82.5\% & 89.8\% & 94.7\% & \url{https://www.gov.uk/government/uploads/system/uploads/attachment_data/file/477702/HIV_in_the_UK_2015_report.pdf} \\
  United States & 87.0\% & 52.0\% & 81.9\% & \url{http://www.cdc.gov/hiv/pdf/surveillance_Report_vol_19_no_3.pdf}, \url{http://www.cdc.gov/hiv/statistics/overview/geographicdistribution.html} \\
  Uruguay & 60.0\% & 100.0\% & 93.0\% & \cite{Unaids2016-an}, 2014b \\
  Uzbekistan & 60.0\% & 44.8\% & 88.0\% & \cite{Unaids2016-an}, 2015b \\
  Venezuela & 58.0\% & 97.5\% & 95.0\% & \cite{Unaids2016-an}, 2015a \\
  Vietnam & 80.0\% & 50.8\% & 71.0\% & \cite{Unaids2016-an}, 2014b \\
  Yemen & 14.0\% & 98.6\% & 77.0\% & \cite{Unaids2016-an}, 2013a \\
  Zambia & 73.0\% & 86.3\% & 93.0\% & \cite{Unaids2016-an}, 2015a \\
  Zimbabwe & 64.0\% & 96.9\% & 84.0\% & \cite{Unaids2016-an} \\
  \hline
\end{longtable}
2011a: Viral suppression is 12-month retention on treatment, all ages, for 2011.
2012b: Viral suppression is 12-month retention on treatment, ages 15+, for 2012.
2013a: Viral suppression is 12-month retention on treatment, all ages, for 2013.
2013b: Viral suppression is 12-month retention on treatment, ages 15+, for 2013.
2014a: Viral suppression is 12-month retention on treatment, all ages, for 2014.
2014b: Viral suppression is 12-month retention on treatment, ages 15+, for 2014.
2015a: Viral suppression is 12-month retention on treatment, all ages, for 2015.
2015b: Viral suppression is 12-month retention on treatment, ages 15+, for 2015.

### 2016-08-15 Codes/plots/effectiveness.py

@@ -134,7 +134,7 @@ def _make_legend(fig, **kwargs):
 
 
 def _plot_one(results, country, confidence_level = 0.5, ci_bar = 0.9,
-              figsize = (common.width_3column, 9), **kwargs):
+              figsize = (common.width_2column, 6), **kwargs):
     nrows = len(common.effectiveness_measures)
     ncols = int(numpy.ceil(len(model.targets.all_) / 2))
     fig, axes = pyplot.subplots(nrows, ncols,
@@ -142,7 +142,7 @@ def _plot_one(results, country, confidence_level = 0.5, ci_bar = 0.9,
                                 sharex = 'all', sharey = 'row')
 
     country_name = common.get_country_label(country)
-    fig.suptitle(country_name, size = 15, va = 'center')
+    fig.suptitle(country_name, size = 10, va = 'center')
 
     CIkey = 'CI{:g}'.format(100 * confidence_level)
     CIBkey = 'CI{:g}'.format(100 * ci_bar)
@@ -187,12 +187,8 @@ def _plot_one(results, country, confidence_level = 0.5, ci_bar = 0.9,
                        scale = info.scale, units = info.units,
                        **kwargs)
 
-            ax.tick_params(labelsize = 11)
-            ax.tick_params(axis = 'x', pad = 8)
-            ax.yaxis.get_label().set_size(12)
-
     with seaborn.color_palette(common.colors_paired):
-        _make_legend(fig, fontsize = 11, columnspacing = 5)
+        _make_legend(fig)
 
     fig.tight_layout(rect = (0, 0.055, 1, 0.985))
 

### 2016-08-15 Codes/plots/effectiveness_all.py

@@ -16,22 +16,61 @@ sys.path.append('..')
 import model
 
 
-def plot_all(**kwargs):
-    with model.results.samples.stats.open_() as results:
-        filename = '{}.pdf'.format(common.get_filebase())
-        with backend_pdf.PdfPages(filename) as pdf:
-            for region_or_country in common.all_regions_and_countries:
-                print(region_or_country)
-                fig = effectiveness._plot_one(results,
-                                              region_or_country,
-                                              **kwargs)
-                pdf.savefig(fig)
-                pyplot.close(fig)
+# [H] requires \usepackage{float}
+template = r'''
+\begin{{figure}}[H]
+  \centering
+  \includegraphics{{{figfile:}}}
+  \caption{{{region_or_country:} model outcomes under the different
+    diagnosis, treatment, and vaccination scenarios.  The model was run
+    with 1000 samples from the parameter distributions: central curves
+    show the medians over the model runs, shaded regions show the 1st
+    and 3rd quartiles (i.e., 25th and 75th percentiles), and vertical
+    bars to the right of each axis show the 5th and 95th percentiles
+    at the end time, 2035.  Regional and global outcomes were aggregated
+    from the country-level model outcomes.}}
+  \label{{effectiveness_{base:}}}
+\end{{figure}}
+'''
 
-    common.pdfoptimize(filename)
-    # Use pdftk to add author etc.
-    common.pdf_add_info(filename, Author = common.author)
+
+def plot_all(**kwargs):
+    path = common.get_filebase()
+    with model.results.samples.stats.open_() as results:
+        for region_or_country in common.all_regions_and_countries:
+            print(region_or_country)
+            fig = effectiveness._plot_one(results,
+                                          region_or_country,
+                                          **kwargs)
+            filebase = os.path.join(path, region_or_country.replace(' ', '_'))
+            filename = '{}.pdf'.format(filebase)
+            label = common.get_country_label(region_or_country)
+            common.savefig(fig, filename,
+                           title = '{} effectiveness'.format(label))
+            pyplot.close(fig)
+
+
+def combine(prefix = '../Codes/plots'):
+    path = common.get_filebase()
+    outfile = os.path.join(path, 'all.tex')
+    with open(outfile, 'w') as fd:
+        isfirst = True
+        for region_or_country in common.all_regions_and_countries:
+            filebase = region_or_country.replace(' ', '_')
+            filename = os.path.join(prefix, path,
+                                    '{}.pdf'.format(filebase))
[…]

### 2016-08-15 Documents/supplementary_text.tex
Added stubs for other 3 data tables.

@@
 
-Model source code: \url{https://github.com/janmedlock/HIV-95-vaccine/}.
+\section*{To do}
+
+\begin{itemize}
+\item Finish tables
+\item Reformat transmission rate figure
+\end{itemize}
+
+We developed a continuous-time, compartmental model consisting of 8
+health states: susceptible to HIV infection, vaccinated against HIV,
+acute HIV infection, undiagnosed HIV infection, diagnosed but
+untreated HIV infection, treated without achieving viral suppression,
+achieved viral suppression, and having AIDS (Supplementary text). We
+found sufficient country-level demographic data, as well as estimates
+of longitudinal HIV incidence and prevalence for the 15–49 age group,
+spanning from as early as 1990 to 2015 to parameterize our model for
+127 countries. See Supporting text for information on data sources.
+
+Using available historical data for incidence and prevalence, and
+published transmission estimates (13), we estimated transmission rates
+for people with acute infection, unsuppressed viral load and
+suppressed viral load. Our calibration method provided a recent
+snapshot of country-specific transmission, while using historical data
+to smooth out variations. See Supporting text for detailed information
+on estimating the transmission rate.
+
+Projections were generated for each country through model simulations
+using 1000 random samples from published parameter distributions
+(table S1, Supplementary text) and the country-specific estimated
+distribution of the transmission rate. We evaluated the global and
+country-level impacts of meeting the UNAIDS targets and vaccine
+deployment on four outcome measures: HIV incidence, PLHIV, PLAIDS, and
+AIDS-related deaths between 2015 and 2035. Our base-case scenario
+assumed maintenance of the status quo: that 2015 levels of the
+proportion of PLHIV diagnosed (pD), proportion of those diagnosed on
+ART (pT), and proportion of those on treatment who have achieved viral
+suppression (pV) continue unchanged until 2035. The intervention
+scenarios were (1.) the attainment of the 90–90–90 target by linear
+increases in pD, pT, and pV until 2020 followed by maintenance of
+those levels until 2035, and (2.) linear increase in the diagnosis and
+treatment levels to the 90–90–90 target by 2020, a linear increase
+from 90–90–90 to the 95–95–95 target by 2030, and maintenance of the
+95–95–95 levels to 2035. (For 90–90–90, if any initial level was above
+90\%, it was kept constant going forward so that the intervention did
+not worsen coverage.  Likewise, for 95–95–95, any initial level above
+95\% was kept constant.)  For vaccination, we assumed deployment of a
+vaccine with 50\% efficacy in 2020 with coverage increasing linearly
+from 0\% to 50\% at 2 years post-rollout, continuing on the same
+linear trend to 70\% at 2.8 years post-rollout, and maintaining
+constant 70\% coverage thereafter. We also performed a partial rank
+correlation coefficient (PRCC) sensitivity analysis for each model
+parameter and a scenario analysis to account for uncertainty in the
+profile of the prospective vaccine. See Supplementary text for more
+details.
+
+\section{Source code}
+
+The source code for the model and analysis tools is available at
+\url{https://github.com/janmedlock/HIV-95-vaccine/}.
 
@@
 parametrize our mathematical modeling for 127 countries.  See
-\autoref{data_source_treatment_cascade}--\ref{data_source_regions} for
+\hyperref[data_source_treatment_cascade]{Tables
+  \ref*{data_source_treatment_cascade}}--\ref{data_source_regions} for
 full information on data sources for each country.
@@
   \tiny
-  \input{treatment_cascade.tex}
-  \caption{Data sources on the treatment cascade.}
+  \input{treatment_cascade}
+  \caption{Data used for the treatment cascade.}
   \label{data_source_treatment_cascade}
+\end{table}
+
+\begin{table}
+  \centering
+  \tiny
+  % \input{prevalence}
+  \caption{Data sources for prevalence.}
+  \label{data_source_prevalence}
+\end{table}
+
+\begin{table}
+  \centering
+  \tiny
+  % \input{incidence}
+  \caption{Data sources for prevalence.}
+  \label{data_source_incidence}
+\end{table}
+
+\begin{table}
+  \centering
+  \tiny
+  % \input{regions}
+  \caption{Countries by UNAIDS region.}
+  \label{data_source_regions}
 \end{table}
@@
       uniform distribution, $\beta$: beta distribution).}
+    \label{model_param}
   \end{center}
-\label{model_param}
 \end{table}
@@
 
-The targets for the proportions $p_D$, $p_T$, and $p_V$ in the achievement of 90---90---90
+The targets for the proportions $p_D$, $p_T$, and $p_V$ in the achievement of 90--90--90
 all operate under the following assumption:
@@
 
-95---95---95 goal is implemented subsequently after meeting
-90---90---90 by2020 by  increasing $p_D$, $p_T$, and $p_V$ to
-95---95---95 levels by 2030 linearly. \comment{@Jan, We use the
-  Heaveside function here too?}
+95--95--95 goal is implemented subsequently after meeting 90--90--90
+by 2020 by increasing $p_D$, $p_T$, and $p_V$ to 95--95--95 levels by
+2030 linearly. \comment{@Jan, We use the Heaveside function here too?}
 

### 2016-08-15 Documents/treatment_cascade.tex
Add references for treatment cascade table

@@
   Armenia & 46.0\% & 55.4\% & 77.0\% & \cite{Unaids2016-an} \\
-  Australia & 90.0\% & 99.4\% & 92.5\% & \cite{Unaids2016-an}, \url{https://kirby.unsw.edu.au/sites/default/files/hiv/resources/HIVASRsuppl2014_online.pdf} \\
-  Austria & 80.0\% & 86.8\% & 63.0\% & 28th Report of the Austrian HIV Cohort Study (Innsbruck, September 30th, 2015), \url{https://www.google.com/url?sa=t&rct=j&q=&esrc=s&source=web&cd=12&ved=0ahUKEwjQkqHwwtLNAhXG0h4KHYxYDdM4ChAWCB0wAQ&url=http%3A%2F%2Fdermatologie.tirol-kliniken.at%2Fdata.cfm%3Fvpath%3Ddokumente%2F2015-hiv-kohortenbericht&usg=AFQjCNH9LyCKkigHECw7oYAEq_NBfRHjKw&sig2=eywFWu8eQN6aWf_QwHNLlw&bvm=bv.125801520,d.dmo&cad=rja} \\
+  Australia & 90.0\% & 99.4\% & 92.5\% & \cite{Unaids2016-an, kirby2014}  \\
+  Austria & 80.0\% & 86.8\% & 63.0\% & \cite{ahivcos2015} \\
   Azerbaijan & 35.0\% & 76.9\% & 67.0\% & \cite{Unaids2016-an} \\
@@
   Belarus & 20.0\% & 100.0\% & 71.0\% & \cite{Unaids2016-an}, 2015b \\
-  Belgium & 80.0\% & 74.5\% & 91.0\% & \cite{Unaids2016-an}, \url{http://ec.europa.eu/chafea/documents/health/hiv-cluster-meeting-material/presentations-pharis-s3_en.pdf}, 2015a \\
+  Belgium & 80.0\% & 74.5\% & 91.0\% & \cite{Unaids2016-an,europa2012}, 2015a \\
   Belize & 46.0\% & 99.0\% & 47.0\% & \cite{Unaids2016-an}, 2014b \\
@@
   Cameroon & 27.0\% & 100.0\% & 60.0\% & \cite{Unaids2016-an}, 2015a \\
-  Canada & 79.0\% & 64.6\% & 68.6\% & \url{http://www.catie.ca/sites/default/files/2014-HIV-Estimates-in-Canada-EN.pdf}, \url{http://www.catie.ca/en/catienews/2014-02-19/gaps-british-columbia-s-hiv-treatment-cascade} \\
+  Canada & 79.0\% & 64.6\% & 68.6\% & \cite{catie2014a,catie2014b} \\
   Cape Verde & 29.0\% & 100.0\% & 95.0\% & \cite{Unaids2016-an}, 2015b \\
@@
   Chile & 90.0\% & 96.7\% & 95.0\% & \cite{Unaids2016-an}, 2015b \\
-  China & 64.2\% & 59.0\% & 91.0\% & \cite{Unaids2016-an, AIDSdatahub-fg}, \url{http://www.avert.org/professionals/hiv-around-world/asia-pacific/china} \\
-  Colombia & 45.0\% & 73.0\% & 70.0\% & \url{http://ecdc.europa.eu/en/publications/Publications/dublin-declaration-continuum-of-care-2014.pdf} \\
+  China & 64.2\% & 59.0\% & 91.0\% & \cite{Unaids2016-an, AIDSdatahub-fg, avert2013} \\
+  Colombia & 45.0\% & 73.0\% & 70.0\% & \cite{ecdc2014} \\
   Republic of Congo & 37.4\% & 50.5\% & 79.4\% & \cite{Unaids2016-am} \\
@@
   DR Congo & 33.0\% & 100.0\% & 86.0\% & \cite{Unaids2016-an}, 2015a \\
-  Denmark & 85.0\% & 72.9\% & 95.2\% & \url{http://www.aidsmap.com/Australia-performs-best-in-HIV-treatment-cascade-62-with-undetectable-viral-load/page/2919074/} \\
+  Denmark & 85.0\% & 72.9\% & 95.2\% & \cite{aid2014} \\
   Djibouti & 70.0\% & 31.4\% & 86.0\% & \cite{Unaids2016-an}, 2015b \\
@@
   Ecuador & 53.0\% & 97.4\% & 85.0\% & \cite{Unaids2016-an}, 2012b \\
-  Egypt & 40.6\% & 56.5\% & 80.0\% & \url{http://english.alarabiya.net/en/perspective/analysis/2014/08/28/Registered-HIV-AIDS-cases-rising-in-Egypt-U-N-.html}, 2015b \\
+  Egypt & 40.6\% & 56.5\% & 80.0\% & \cite{alarab2014} 2015b \\
   El Salvador & 54.0\% & 100.0\% & 83.0\% & \cite{Unaids2016-an}, 2015b \\
@@
   Eritrea & 60.0\% & 100.0\% & 77.0\% & \cite{Unaids2016-an}, 2015b \\
-  Estonia & 87.0\% & 33.3\% & 65.5\% & \url{https://www.sm.ee/sites/default/files/content-editors/eesmargid_ja_tegevused/Tervis/Tervislik_eluviis/who_raport_hiv_aids_treatment_and_care_in_estonia.pdf} \\
-  Ethiopia & 71.5\% & 70.0\% & 82.0\% & \cite{Unaids2016-am}, \url{https://dhsprogram.com/pubs/pdf/CR30/CR30.pdf}, 2012b \\
-  France & 81.0\% & 91.4\% & 70.3\% & \url{http://www.aidsmap.com/Australia-performs-best-in-HIV-treatment-cascade-62-with-undetectable-viral-load/page/2919074/} \\
+  Estonia & 87.0\% & 33.3\% & 65.5\% & \cite{chip2014}  \\
+  Ethiopia & 71.5\% & 70.0\% & 82.0\% & \cite{Unaids2016-am, usaid2013}, 2012b \\
+  France & 81.0\% & 91.4\% & 70.3\% & \cite{aid2014} \\
   Gabon & 85.0\% & 68.6\% & 64.0\% & \cite{Unaids2016-an}, 2014b \\
@@
   Iran & 31.0\% & 28.4\% & 67.0\% & \cite{Unaids2016-an} \\
-  Italy & 70.0\% & 87.6\% & 62.4\% & \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4348082/} \\
+  Italy & 70.0\% & 87.6\% & 62.4\% & \cite{camoni2015estimating}  \\
   Jamaica & 33.0\% & 95.1\% & 67.0\% & \cite{Unaids2016-an} \\
@@
   Nepal & 57.0\% & 50.9\% & 91.0\% & \cite{Unaids2016-an} \\
-  Netherlands & 73.0\% & 93.2\% & 89.8\% & \url{http://www.aidsmap.com/Australia-performs-best-in-HIV-treatment-cascade-62-with-undetectable-viral-load/page/2919074/} \\
+  Netherlands & 73.0\% & 93.2\% & 89.8\% & \cite{aid2014} \\
   New Zealand & 85.0\% & 80.0\% & 98.4\% & \cite{Unaids2016-am} \\
@@
   Philippines & 63.0\% & 42.9\% & 92.0\% & \cite{Unaids2016-an} \\
-  Russia & 49.0\% & 23.5\% & 80.0\% & \url{http://www.jiasociety.org/index.php/jias/article/view/19506} \\
+  Russia & 49.0\% & 23.5\% & 80.0\% & \cite{pokrovskaya2014cascade} \\
   Rwanda & 85.0\% & 92.9\% & 94.0\% & \cite{Unaids2016-an}, 2012b \\
@@
   Swaziland & 67.0\% & 100.0\% & 51.0\% & \cite{Unaids2016-an} \\
-  Sweden & 90.0\% & 92.1\% & 94.7\% & \url{http://www.croiconference.org/sessions/swedish-hiv-treatement-cascade} \\
-  Switzerland & 80.9\% & 87.8\% & 96.3\% & \url{http://www.natap.org/2015/IAS/Jake_IAS_Slides_July20X.pdf} \\
+  Sweden & 90.0\% & 92.1\% & 94.7\% & \cite{croi2016} \\
+  Switzerland & 80.9\% & 87.8\% & 96.3\% & \cite{ias2015} \\
   Tajikistan & 34.0\% & 48.5\% & 77.0\% & \cite{Unaids2016-an} \\
@@
   Ukraine & 27.0\% & 98.2\% & 86.0\% & \cite{Unaids2016-an}, 2015a \\
-  United Kingdom & 82.5\% & 89.8\% & 94.7\% & \url{https://www.gov.uk/government/uploads/system/uploads/attachment_data/file/477702/HIV_in_the_UK_2015_report.pdf} \\
-  United States & 87.0\% & 52.0\% & 81.9\% & \url{http://www.cdc.gov/hiv/pdf/surveillance_Report_vol_19_no_3.pdf}, \url{http://www.cdc.gov/hiv/statistics/overview/geographicdistribution.html} \\
+  United Kingdom & 82.5\% & 89.8\% & 94.7\% & \cite{ukhIv2015} \\
+ United States & 87.0\% & 52.0\% & 81.9\% & \cite{cdc2012a,cdc2014} \\
   Uruguay & 60.0\% & 100.0\% & 93.0\% & \cite{Unaids2016-an}, 2014b \\

### 2016-08-15 Documents/prevalence.tex
Working on supplement tables.

\begin{longtable}{lrrrrrrrrrrrrrrrrrrrrrrrrrrl}
  \caption{prevalence.}
  \label{data_source_prevalence}
  \\[-2ex]
  \hline
  Country & 1990 & 1991 & 1992 & 1993 & 1994 & 1995 & 1996 & 1997 & 1998 & 1999 & 2000 & 2001 & 2002 & 2003 & 2004 & 2005 & 2006 & 2007 & 2008 & 2009 & 2010 & 2011 & 2012 & 2013 & 2014 & 2015 & References\\
  \hline
  \endfirsthead
  \caption{(continued)}
  \\[-2ex]
  \hline
  Country & 1990 & 1991 & 1992 & 1993 & 1994 & 1995 & 1996 & 1997 & 1998 & 1999 & 2000 & 2001 & 2002 & 2003 & 2004 & 2005 & 2006 & 2007 & 2008 & 2009 & 2010 & 2011 & 2012 & 2013 & 2014 & 2015 & References\\
  \hline
  \endhead
  \hline
  \endfoot
  \endlastfoot
  Afghanistan & 0.0077\% & 0.0095\% & 0.01\% & 0.012\% & 0.013\% & 0.014\% & 0.014\% & 0.015\% & 0.016\% & 0.017\% & 0.018\% & 0.019\% & 0.02\% & 0.02\% & 0.022\% & 0.023\% & 0.025\% & 0.027\% & 0.028\% & 0.03\% & 0.032\% & 0.033\% & 0.034\% & 0.035\% & 0.036\% & --- & \url{http://www.unaids.org/sites/default/files/country/documents/AFG_narrative_report_2014.pdf }, Estimated PLHIV (total) / Population (total)\\
  Algeria & --- & --- & --- & --- & 0.0079\% & 0.0083\% & 0.0094\% & 0.01\% & 0.011\% & 0.013\% & 0.014\% & 0.015\% & 0.017\% & 0.018\% & 0.02\% & 0.021\% & 0.023\% & 0.026\% & 0.028\% & 0.03\% & 0.033\% & 0.035\% & 0.037\% & 0.038\% & 0.039\% & 0.04\% & \url{http://aidsinfo.unaids.org/}, PLHIV 15+ / population 15-49\\
  Angola & 0.5\% & 0.5\% & 0.6\% & 0.7\% & 0.8\% & 0.9\% & 1.1\% & 1.2\% & 1.3\% & 1.4\% & 1.5\% & 1.6\% & 1.7\% & 1.8\% & 1.8\% & 1.9\% & 2.0\% & 2.0\% & 2.1\% & 2.1\% & 2.1\% & 2.2\% & 2.2\% & 2.2\% & 2.2\% & 2.2\% & \url{http://aidsinfo.unaids.org/}\\
  Argentina & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & \url{http://aidsinfo.unaids.org/}\\
  Armenia & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & \url{http://aidsinfo.unaids.org/}\\
  Australia & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & \url{http://aidsinfo.unaids.org/}\\
  Austria & --- & --- & --- & --- & --- & --- & --- & 0.062\% & 0.076\% & 0.093\% & 0.11\% & 0.13\% & 0.16\% & 0.19\% & 0.22\% & 0.24\% & 0.28\% & 0.31\% & 0.35\% & 0.39\% & 0.4\% & 0.44\% & 0.47\% & --- & --- & --- & \url{http://www.unaids.org/en/resources/campaigns/globalreport2013/globalreport}\\
  Azerbaijan & --- & --- & --- & --- & --- & --- & --- & --- & 0.025\% & 0.032\% & 0.04\% & 0.048\% & 0.055\% & 0.062\% & 0.071\% & 0.08\% & 0.09\% & 0.1\% & 0.11\% & 0.13\% & 0.14\% & 0.15\% & 0.17\% & 0.18\% & 0.21\% & --- & \url{http://aidsinfo.unaids.org/}, PLHIV 15+ / population 15-49\\
  Bahamas & 1.6\% & 1.8\% & 2.0\% & 2.3\% & 2.5\% & 2.7\% & 2.8\% & 2.9\% & 3.0\% & 3.0\% & 3.1\% & 3.1\% & 3.1\% & 3.1\% & 3.1\% & 3.1\% & 3.1\% & 3.1\% & 3.2\% & 3.2\% & 3.2\% & 3.2\% & 3.2\% & 3.2\% & 3.2\% & 3.2\% & \url{http://aidsinfo.unaids.org/}\\
  Bangladesh & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & 0.0016\% & 0.0022\% & 0.003\% & 0.0038\% & 0.0048\% & 0.0058\% & 0.0065\% & 0.0074\% & 0.0083\% & 0.009\% & 0.0097\% & 0.01\% & 0.01\% & 0.011\% & 0.011\% & 0.011\% & \url{http://aidsinfo.unaids.org/}, Estimated PLHIV (adult) / Population (15-49)\\
  Barbados & 0.2\% & 0.2\% & 0.2\% & 0.3\% & 0.3\% & 0.4\% & 0.4\% & 0.5\% & 0.5\% & 0.6\% & 0.7\% & 0.7\% & 0.8\% & 0.8\% & 0.9\% & 1\% & 1\% & 1.1\% & 1.2\% & 1.3\% & 1.3\% & 1.4\% & 1.4\% & 1.5\% & 1.5\% & 1.6\% & \url{http://aidsinfo.unaids.org/}\\
  Belarus & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & 0.1\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.4\% & 0.4\% & 0.4\% & 0.5\% & 0.6\% & 0.6\% & \url{http://aidsinfo.unaids.org/}\\
  Belgium & --- & --- & 0.045\% & 0.057\% & 0.072\% & 0.084\% & 0.097\% & 0.11\% & 0.12\% & 0.14\% & 0.16\% & 0.18\% & 0.19\% & 0.21\% & 0.23\% & 0.25\% & 0.28\% & 0.3\% & 0.33\% & 0.34\% & 0.36\% & 0.38\% & 0.41\% & --- & --- & --- & \url{http://www.unaids.org/en/resources/campaigns/globalreport2013/globalreport}, Estimated PLHIV (total) / Population (15-49)\\
  Belize & $<$0.1\% & $<$0.1\% & $<$0.1\% & 0.1\% & 0.2\% & 0.2\% & 0.3\% & 0.5\% & 0.6\% & 0.9\% & 1.1\% & 1.4\% & 1.7\% & 1.9\% & 2.0\% & 2.0\% & 1.9\% & 1.9\% & 1.8\% & 1.7\% & 1.7\% & 1.7\% & 1.6\% & 1.6\% & 1.6\% & 1.5\% & \url{http://aidsinfo.unaids.org/}\\
  Benin & 0.2\% & 0.3\% & 0.4\% & 0.6\% & 0.8\% & 0.9\% & 1.1\% & 1.2\% & 1.3\% & 1.4\% & 1.5\% & 1.5\% & 1.5\% & 1.5\% & 1.4\% & 1.4\% & 1.3\% & 1.3\% & 1.2\% & 1.2\% & 1.2\% & 1.2\% & 1.1\% & 1.1\% & 1.1\% & 1.1\% & \url{http://aidsinfo.unaids.org/}\\
  Bhutan & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.13\% & --- & --- & \url{https://www.cia.gov/library/publications/the-world-factbook/rankorder/2155rank.html}, \url{http://www.unaids.org/en/resources/campaigns/globalreport2013/globalreport}\\
  Bolivia & 0.2\% & 0.2\% & 0.2\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & \url{http://aidsinfo.unaids.org/}\\
  Botswana & 6.0\% & 8.4\% & 11.2\% & 14.2\% & 17.2\% & 19.9\% & 22.2\% & 24.0\% & 25.1\% & 25.8\% & 26.0\% & 26.0\% & 25.7\% & 25.3\% & 24.9\% & 24.6\% & 24.3\% & 24.1\% & 23.9\% & 23.6\% & 23.5\% & 23.3\% & 23.1\% & 22.8\% & 22.5\% & 22.2\% & \url{http://aidsinfo.unaids.org/}\\
  Brazil & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.6\% & 0.6\% & 0.6\% & 0.6\% & \url{http://aidsinfo.unaids.org/}\\
  Bulgaria & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & 0.042\% & 0.051\% & 0.058\% & 0.065\% & 0.073\% & 0.081\% & 0.09\% & 0.097\% & 0.1\% & 0.11\% & 0.12\% & 0.12\% & --- & --- & --- & \url{http://www.unaids.org/en/resources/campaigns/globalreport2013/globalreport}\\
  Burkina Faso & 3.4\% & 3.6\% & 3.7\% & 3.8\% & 3.7\% & 3.6\% & 3.4\% & 3.2\% & 2.9\% & 2.7\% & 2.4\% & 2.2\% & 1.9\% & 1.7\% & 1.6\% & 1.4\% & 1.3\% & 1.2\% & 1.1\% & 1.1\% & 1\% & 1\% & 0.9\% & 0.9\% & 0.9\% & 0.8\% & \url{http://aidsinfo.unaids.org/}\\
  Burundi & 0.9\% & 1.1\% & 1.4\% & 1.8\% & 2.1\% & 2.5\% & 2.7\% & 2.9\% & 3.1\% & 3.2\% & 3.2\% & 3.1\% & 2.9\% & 2.7\% & 2.5\% & 2.3\% & 2.2\% & 2.0\% & 1.8\% & 1.6\% & 1.5\% & 1.4\% & 1.3\% & 1.2\% & 1.1\% & 1\% & \url{http://aidsinfo.unaids.org/}\\
  Cambodia & --- & 0.1\% & 0.3\% & 0.6\% & 1\% & 1.4\% & 1.7\% & 1.8\% & 1.9\% & 1.8\% & 1.8\% & 1.6\% & 1.5\% & 1.4\% & 1.2\% & 1.1\% & 1.1\% & 1\% & 0.9\% & 0.9\% & 0.8\% & 0.8\% & 0.7\% & 0.7\% & 0.7\% & 0.6\% & \url{http://aidsinfo.unaids.org/}\\
  Cameroon & 2.0\% & 2.5\% & 3.0\% & 3.5\% & 3.9\% & 4.3\% & 4.7\% & 5.0\% & 5.2\% & 5.3\% & 5.4\% & 5.4\% & 5.4\% & 5.3\% & 5.3\% & 5.2\% & 5.1\% & 5.0\% & 4.9\% & 4.9\% & 4.8\% & 4.8\% & 4.7\% & 4.6\% & 4.6\% & 4.5\% & \url{http://aidsinfo.unaids.org/}\\
  Canada & 0.22\% & 0.22\% & 0.24\% & 0.24\% & 0.25\% & 0.25\% & 0.25\% & 0.26\% & 0.27\% & 0.27\% & 0.28\% & 0.29\% & 0.3\% & 0.32\% & 0.33\% & 0.34\% & 0.35\% & 0.36\% & 0.38\% & 0.39\% & 0.4\% & 0.43\% & --- & --- & 0.45\% & --- & \url{http://www.phac-aspc.gc.ca/aids-sida/publication/epi/2010/1-eng.php#a0502}, Estimated \# HIV infections (total) / Population (15-49)\\
  Cape Verde & 0.8\% & 0.9\% & 1\% & 1.1\% & 1.2\% & 1.3\% & 1.4\% & 1.5\% & 1.5\% & 1.6\% & 1.6\% & 1.6\% & 1.5\% & 1.5\% & 1.4\% & 1.3\% & 1.3\% & 1.2\% & 1.2\% & 1.1\% & 1.1\% & 1\% & 1\% & 1\% & 1\% & 1\% & \url{http://aidsinfo.unaids.org/}\\
  Central African Republic & 4.0\% & 4.8\% & 5.6\% & 6.4\% & 7.2\% & 7.8\% & 8.3\% & 8.7\% & 8.8\% & 8.8\% & 8.7\% & 8.4\% & 8.0\% & 7.5\% & 7.0\% & 6.5\% & 6.1\% & 5.7\% & 5.3\% & 5.0\% & 4.8\% & 4.5\% & 4.3\% & 4.1\% & 3.9\% & 3.7\% & \url{http://aidsinfo.unaids.org/}\\
  Chad & 1.2\% & 1.3\% & 1.5\% & 1.7\% & 1.9\% & 2.1\% & 2.4\% & 2.6\% & 2.8\% & 3.0\% & 3.2\% & 3.3\% & 3.4\% & 3.4\% & 3.4\% & 3.3\% & 3.2\% & 3.1\% & 3.0\% & 2.8\% & 2.7\% & 2.6\% & 2.4\% & 2.3\% & 2.2\% & 2.0\% & \url{http://aidsinfo.unaids.org/}\\
  Chile & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.3\% & 0.3\% & 0.3\% & \url{http://aidsinfo.unaids.org/}\\
  China & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & 0.086\% & --- & 0.091\% & --- & 0.095\% & --- & 0.1\% & --- & 0.11\% & 0.066\% & --- & \url{http://www.unaids.org/sites/default/files/country/documents/CHN_narrative_report_2015.pdf}, \url{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4730421/pdf/ijerph-13-00030.pdf}\\
  Colombia & 0.1\% & 0.1\% & 0.1\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.5\% & 0.5\% & \url{http://aidsinfo.unaids.org/}\\
  Congo & 3.9\% & 4.3\% & 4.8\% & 5.1\% & 5.4\% & 5.5\% & 5.6\% & 5.7\% & 5.6\% & 5.5\% & 5.4\% & 5.2\% & 4.9\% & 4.7\% & 4.4\% & 4.1\% & 3.9\% & 3.7\% & 3.5\% & 3.3\% & 3.2\% & 3.1\% & 3.0\% & 2.9\% & 2.8\% & --- & \url{http://www.who.int/gho/database/en/}\\
  Costa Rica & $<$0.1\% & $<$0.1\% & $<$0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & \url{http://aidsinfo.unaids.org/}\\
  Cuba & --- & --- & --- & --- & 0.016\% & 0.02\% & 0.023\% & 0.026\% & 0.03\% & 0.034\% & 0.039\% & 0.046\% & 0.054\% & 0.062\% & 0.073\% & 0.085\% & 0.098\% & 0.11\% & 0.13\% & 0.15\% & 0.18\% & 0.2\% & 0.24\% & 0.29\% & 0.33\% & 0.39\% & \url{http://aidsinfo.unaids.org/}, PLHIV 15+/ Population 15-49\\
  Côte d'Ivoire & 3.0\% & 3.5\% & 3.9\% & 4.3\% & 4.7\% & 5.1\% & 5.4\% & 5.6\% & 5.7\% & 5.7\% & 5.6\% & 5.5\% & 5.3\% & 5.1\% & 4.9\% & 4.6\% & 4.4\% & 4.2\% & 4.1\% & 3.9\% & 3.8\% & 3.7\% & 3.6\% & 3.4\% & 3.3\% & 3.2\% & \url{http://aidsinfo.unaids.org/}\\
  DR Congo & 1.7\% & 1.7\% & 1.7\% & 1.7\% & 1.7\% & 1.8\% & 1.8\% & 1.9\% & 1.9\% & 1.9\% & 1.9\% & 1.9\% & 1.9\% & 1.8\% & 1.8\% & 1.7\% & 1.6\% & 1.5\% & 1.4\% & 1.3\% & 1.2\% & 1.1\% & 1\% & 1\% & 0.9\% & 0.8\% & \url{http://aidsinfo.unaids.org/}\\
  Denmark & 0.049\% & 0.056\% & 0.06\% & 0.066\% & 0.071\% & 0.077\% & 0.085\% & 0.09\% & 0.1\% & 0.11\% & 0.13\% & 0.14\% & 0.15\% & 0.16\% & 0.17\% & 0.18\% & 0.19\% & 0.2\% & 0.21\% & 0.22\% & 0.23\% & 0.24\% & 0.26\% & --- & --- & --- & \url{http://www.unaids.org/en/resources/campaigns/globalreport2013/globalreport}\\
  Djibouti & 0.2\% & 0.3\% & 0.5\% & 0.8\% & 1.1\% & 1.5\% & 1.8\% & 2.2\% & 2.4\% & 2.7\% & 2.8\% & 2.8\% & 2.8\% & 2.7\% & 2.6\% & 2.5\% & 2.3\% & 2.2\% & 2.1\% & 1.9\% & 1.9\% & 1.8\% & 1.7\% & 1.6\% & 1.6\% & 1.6\% & \url{http://aidsinfo.unaids.org/}\\
  Dominican Republic & 0.6\% & 0.8\% & 1\% & 1.2\% & 1.5\% & 1.7\% & 1.9\% & 2.1\% & 2.2\% & 2.3\% & 2.3\% & 2.3\% & 2.2\% & 2.1\% & 2.0\% & 1.9\% & 1.8\% & 1.7\% & 1.5\% & 1.4\% & 1.4\% & 1.3\% & 1.2\% & 1.1\% & 1.1\% & 1\% & \url{http://aidsinfo.unaids.org/}\\
  Ecuador & 0.2\% & 0.2\% & 0.2\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & \url{http://aidsinfo.unaids.org/}\\
  Egypt & --- & --- & --- & --- & --- & --- & --- & 0.0035\% & 0.0037\% & 0.0043\% & 0.005\% & 0.0054\% & 0.0058\% & 0.0065\% & 0.007\% & 0.0079\% & 0.0085\% & 0.0093\% & 0.01\% & 0.011\% & 0.012\% & 0.013\% & 0.014\% & --- & 0.02\% & --- & \url{https://www.cia.gov/library/publications/the-world-factbook/rankorder/2155rank.html}, Estimated PLHIV (total) / Population (15-49)\\
  El Salvador & 0.1\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.3\% & 0.3\% & 0.3\% & 0.4\% & 0.4\% & 0.4\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.6\% & 0.6\% & 0.6\% & 0.6\% & 0.6\% & 0.6\% & 0.6\% & 0.5\% & 0.5\% & 0.5\% & \url{http://aidsinfo.unaids.org/}\\
  Equatorial Guinea & 0.7\% & 0.7\% & 0.8\% & 0.9\% & 1\% & 1.1\% & 1.3\% & 1.5\% & 1.8\% & 2.1\% & 2.5\% & 3.0\% & 3.5\% & 4.1\% & 4.6\% & 5.2\% & 5.7\% & 6.1\% & 6.4\% & 6.5\% & 6.5\% & 6.3\% & 6.0\% & 5.6\% & 5.3\% & 4.9\% & \url{http://aidsinfo.unaids.org/}\\
  Eritrea & 0.5\% & 0.6\% & 0.8\% & 1\% & 1.2\% & 1.3\% & 1.5\% & 1.5\% & 1.6\% & 1.6\% & 1.6\% & 1.5\% & 1.4\% & 1.3\% & 1.2\% & 1.1\% & 1\% & 0.9\% & 0.9\% & 0.8\% & 0.8\% & 0.7\% & 0.7\% & 0.7\% & 0.6\% & 0.6\% & \url{http://aidsinfo.unaids.org/}\\
  Estonia & --- & --- & --- & --- & --- & --- & --- & --- & 0.56\% & 0.73\% & 0.98\% & 1.3\% & 1.6\% & 1.8\% & 2.0\% & 2.2\% & 2.4\% & 2.5\% & 2.6\% & 2.6\% & 2.8\% & 2.9\% & 2.9\% & --- & --- & --- & \url{http://www.unaids.org/en/resources/campaigns/globalreport2013/globalreport}\\
  Ethiopia & 1.3\% & 1.7\% & 2.1\% & 2.5\% & 2.8\% & 3.1\% & 3.3\% & 3.4\% & 3.4\% & 3.4\% & 3.2\% & 3.1\% & 2.8\% & 2.6\% & 2.4\% & 2.1\% & 1.9\% & 1.7\% & 1.6\% & 1.5\% & 1.4\% & 1.3\% & 1.3\% & 1.2\% & 1.2\% & --- & \url{https://www.cia.gov/library/publications/the-world-factbook/rankorder/2155rank.html}, \url{http://data.worldbank.org/indicator/SH.DYN.AIDS.ZS}\\
  France & 0.31\% & 0.31\% & 0.3\% & 0.29\% & 0.29\% & 0.29\% & 0.29\% & 0.32\% & 0.33\% & 0.36\% & 0.36\% & 0.38\% & 0.39\% & 0.39\% & 0.42\% & 0.42\% & 0.44\% & 0.44\% & 0.46\% & 0.48\% & 0.49\% & 0.51\% & --- & --- & 0.51\% & --- & \url{http://www.aidsmap.com/Australia-performs-best-in-HIV-treatment-cascade-62-with-undetectable-viral-load/page/2919074/}, \url{http://www.unaids.org/en/resources/campaigns/globalreport2013/globalreport}\\
  Gabon & 0.9\% & 1.2\% & 1.5\% & 1.9\% & 2.3\% & 2.8\% & 3.3\% & 3.7\% & 4.2\% & 4.6\% & 5.0\% & 5.2\% & 5.4\% & 5.4\% & 5.5\% & 5.4\% & 5.4\% & 5.2\% & 5.0\% & 4.8\% & 4.6\% & 4.4\% & 4.2\% & 4.0\% & 3.9\% & 3.8\% & \url{http://aidsinfo.unaids.org/}\\
  Gambia & 0.2\% & 0.2\% & 0.3\% & 0.4\% & 0.5\% & 0.6\% & 0.8\% & 1\% & 1.3\% & 1.5\% & 1.7\% & 1.9\% & 2.0\% & 2.1\% & 2.2\% & 2.2\% & 2.2\% & 2.2\% & 2.2\% & 2.1\% & 2.1\% & 2.0\% & 2.0\% & 1.9\% & 1.9\% & 1.8\% & \url{http://aidsinfo.unaids.org/}\\
  Georgia & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.3\% & 0.3\% & 0.3\% & 0.4\% & 0.4\% & \url{http://aidsinfo.unaids.org/}\\
  Ghana & 1.5\% & 1.7\% & 1.9\% & 2.2\% & 2.4\% & 2.6\% & 2.7\% & 2.8\% & 2.9\% & 2.9\% & 2.9\% & 2.8\% & 2.7\% & 2.6\% & 2.5\% & 2.4\% & 2.3\% & 2.2\% & 2.1\% & 2.0\% & 1.9\% & 1.9\% & 1.8\% & 1.7\% & 1.7\% & 1.6\% & \url{http://aidsinfo.unaids.org/}\\
  Greece & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.3\% & \url{http://aidsinfo.unaids.org/}\\
  Guatemala & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & 0.1\% & 0.2\% & 0.2\% & 0.2\% & 0.3\% & 0.3\% & 0.4\% & 0.4\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.6\% & 0.6\% & 0.6\% & 0.6\% & 0.6\% & 0.6\% & 0.6\% & \url{http://aidsinfo.unaids.org/}\\
  Guinea & 0.5\% & 0.6\% & 0.8\% & 1.1\% & 1.3\% & 1.5\% & 1.6\% & 1.7\% & 1.8\% & 1.8\% & 1.8\% & 1.8\% & 1.8\% & 1.7\% & 1.7\% & 1.7\% & 1.7\% & 1.6\% & 1.6\% & 1.6\% & 1.6\% & 1.6\% & 1.6\% & 1.6\% & 1.6\% & 1.6\% & \url{http://aidsinfo.unaids.org/}\\
  Guyana & --- & 0.1\% & 0.2\% & 0.3\% & 0.4\% & 0.5\% & 0.7\% & 0.8\% & 0.9\% & 0.9\% & 1\% & 1.1\% & 1.1\% & 1.2\% & 1.2\% & 1.3\% & 1.4\% & 1.4\% & 1.4\% & 1.5\% & 1.5\% & 1.5\% & 1.5\% & 1.5\% & 1.5\% & 1.5\% & \url{http://aidsinfo.unaids.org/}\\
  Haiti & 2.2\% & 2.7\% & 3.2\% & 3.7\% & 4.2\% & 4.6\% & 5.0\% & 5.2\% & 5.4\% & 5.5\% & 5.5\% & 5.4\% & 5.2\% & 5.0\% & 4.7\% & 4.4\% & 4.0\% & 3.6\% & 3.3\% & 3.0\% & 2.8\% & 2.5\% & 2.3\% & 2.0\% & 1.9\% & 1.7\% & \url{http://aidsinfo.unaids.org/}\\
  Honduras & 1.8\% & 1.9\% & 1.9\% & 2.0\% & 1.9\% & 1.9\% & 1.8\% & 1.7\% & 1.5\% & 1.4\% & 1.3\% & 1.1\% & 1\% & 0.9\% & 0.8\% & 0.8\% & 0.7\% & 0.6\% & 0.6\% & 0.5\% & 0.5\% & 0.5\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & \url{http://aidsinfo.unaids.org/}\\
  India & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & 0.1\% & 0.2\% & 0.2\% & 0.3\% & 0.3\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & --- & --- & --- & \url{http://www.unaids.org/en/resources/campaigns/globalreport2013/globalreport}\\
  Indonesia & --- & --- & --- & --- & 0.0017\% & 0.0034\% & 0.0063\% & 0.011\% & 0.017\% & 0.024\% & 0.035\% & 0.052\% & 0.079\% & 0.12\% & 0.15\% & 0.19\% & 0.23\% & 0.26\% & 0.3\% & 0.33\% & 0.37\% & 0.39\% & 0.42\% & 0.44\% & 0.46\% & 0.49\% & \url{http://aidsinfo.unaids.org/}, PLHIV 15+/ Population 15-49\\
  Iran & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & \url{http://aidsinfo.unaids.org/}\\
  Italy & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & 0.1\% & 0.2\% & 0.2\% & 0.2\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & \url{http://aidsinfo.unaids.org/}\\
  Jamaica & 0.9\% & 1.2\% & 1.5\% & 1.7\% & 1.9\% & 2.0\% & 2.1\% & 2.2\% & 2.2\% & 2.3\% & 2.2\% & 2.2\% & 2.2\% & 2.1\% & 2.0\% & 2.0\% & 1.9\% & 1.9\% & 1.8\% & 1.8\% & 1.7\% & 1.7\% & 1.7\% & 1.7\% & 1.6\% & 1.6\% & \url{http://aidsinfo.unaids.org/}\\
  Kazakhstan & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.2\% & 0.2\% & 0.2\% & \url{http://aidsinfo.unaids.org/}\\
  Kenya & 6.4\% & 8.0\% & 9.5\% & 10.9\% & 11.9\% & 12.6\% & 12.8\% & 12.7\% & 12.2\% & 11.6\% & 10.7\% & 9.9\% & 9.0\% & 8.3\% & 7.6\% & 7.0\% & 6.6\% & 6.4\% & 6.2\% & 6.1\% & 6.1\% & 6.0\% & 6.0\% & 6.0\% & 6.0\% & 5.9\% & \url{http://aidsinfo.unaids.org/}\\
  Kyrgyzstan & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & \url{http://aidsinfo.unaids.org/}\\
  Laos & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & --- & \url{http://data.worldbank.org/indicator/SH.DYN.AIDS.ZS}\\
  Lebanon & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & 0.056\% & 0.059\% & 0.061\% & 0.063\% & 0.061\% & 0.064\% & 0.063\% & 0.067\% & 0.069\% & 0.071\% & 0.074\% & 0.081\% & 0.085\% & 0.092\% & 0.094\% & \url{http://aidsinfo.unaids.org/}, PLHIV 15+/ Population 15-49\\
  Lesotho & 2.6\% & 3.6\% & 4.9\% & 6.8\% & 9.0\% & 11.5\% & 13.7\% & 15.6\% & 17.3\% & 18.7\% & 19.9\% & 20.9\% & 21.7\% & 22.2\% & 22.6\% & 22.8\% & 23.0\% & 23.1\% & 23.2\% & 23.2\% & 23.1\% & 23.1\% & 23.0\% & 22.9\% & 22.8\% & 22.7\% & \url{http://aidsinfo.unaids.org/}\\
  Liberia & 0.7\% & 0.9\% & 1.1\% & 1.4\% & 1.6\% & 1.8\% & 2.0\% & 2.2\% & 2.4\% & 2.4\% & 2.5\% & 2.5\% & 2.4\% & 2.3\% & 2.2\% & 2.1\% & 1.9\% & 1.8\% & 1.7\% & 1.5\% & 1.4\% & 1.3\% & 1.3\% & 1.2\% & 1.1\% & 1.1\% & \url{http://aidsinfo.unaids.org/}\\
  Madagascar & $<$0.1\% & $<$0.1\% & $<$0.1\% & 0.1\% & 0.2\% & 0.2\% & 0.3\% & 0.4\% & 0.5\% & 0.5\% & 0.6\% & 0.6\% & 0.6\% & 0.6\% & 0.5\% & 0.5\% & 0.5\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.4\% & \url{http://aidsinfo.unaids.org/}\\
  Malawi & 8.8\% & 10.4\% & 12.0\% & 13.3\% & 14.5\% & 15.4\% & 16.0\% & 16.5\% & 16.7\% & 16.7\% & 16.6\% & 16.3\% & 15.8\% & 15.2\% & 14.5\% & 13.9\% & 13.2\% & 12.6\% & 12.1\% & 11.6\% & 11.2\% & 10.8\% & 10.3\% & 9.9\% & 9.5\% & 9.1\% & \url{http://aidsinfo.unaids.org/}\\
  Malaysia & $<$0.1\% & 0.3\% & 0.4\% & 0.5\% & 0.6\% & 0.6\% & 0.6\% & 0.7\% & 0.7\% & 0.7\% & 0.7\% & 0.7\% & 0.7\% & 0.7\% & 0.6\% & 0.6\% & 0.6\% & 0.6\% & 0.6\% & 0.6\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.4\% & 0.4\% & \url{http://aidsinfo.unaids.org/}\\
  Mali & 1.8\% & 2.0\% & 2.1\% & 2.2\% & 2.2\% & 2.2\% & 2.1\% & 2.0\% & 1.9\% & 1.8\% & 1.7\% & 1.6\% & 1.5\% & 1.5\% & 1.4\% & 1.4\% & 1.3\% & 1.3\% & 1.3\% & 1.3\% & 1.3\% & 1.3\% & 1.3\% & 1.3\% & 1.3\% & 1.3\% & \url{http://aidsinfo.unaids.org/}\\
  Mauritania & 0.3\% & 0.3\% & 0.4\% & 0.4\% & 0.5\% & 0.6\% & 0.6\% & 0.7\% & 0.7\% & 0.8\% & 0.8\% & 0.9\% & 0.9\% & 0.9\% & 0.9\% & 0.9\% & 0.9\% & 0.8\% & 0.8\% & 0.8\% & 0.7\% & 0.7\% & 0.7\% & 0.6\% & 0.6\% & 0.6\% & \url{http://aidsinfo.unaids.org/}\\
  Mauritius & --- & --- & --- & 0.1\% & 0.2\% & 0.3\% & 0.4\% & 0.6\% & 0.7\% & 0.9\% & 1\% & 1.1\% & 1.1\% & 1.2\% & 1.2\% & 1.2\% & 1.2\% & 1.2\% & 1.2\% & 1.1\% & 1.1\% & 1\% & 1\% & 1\% & 0.9\% & 0.9\% & \url{http://aidsinfo.unaids.org/}\\
  Mexico & 0.1\% & 0.2\% & 0.2\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & \url{http://aidsinfo.unaids.org/}\\
  Mongolia & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & 0.019\% & 0.025\% & 0.033\% & 0.04\% & 0.054\% & 0.067\% & 0.081\% & 0.097\% & 0.11\% & --- & \url{https://www.cia.gov/library/publications/the-world-factbook/rankorder/2155rank.html}, Reported \# HIV cases (total) / Population (15-49)\\
  Morocco & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & \url{http://aidsinfo.unaids.org/}\\
  Mozambique & 1.6\% & 2.0\% & 2.4\% & 2.9\% & 3.5\% & 4.1\% & 4.8\% & 5.5\% & 6.3\% & 7.1\% & 7.8\% & 8.6\% & 9.2\% & 9.8\% & 10.2\% & 10.5\% & 10.8\% & 10.9\% & 11.1\% & 11.2\% & 11.2\% & 11.1\% & 11.0\% & 10.9\% & 10.7\% & 10.5\% & \url{http://aidsinfo.unaids.org/}\\
  Myanmar & --- & 0.1\% & 0.2\% & 0.3\% & 0.3\% & 0.4\% & 0.4\% & 0.5\% & 0.6\% & 0.7\% & 0.8\% & 0.8\% & 0.9\% & 0.9\% & 0.9\% & 0.9\% & 0.9\% & 0.9\% & 0.9\% & 0.9\% & 0.8\% & 0.8\% & 0.8\% & 0.8\% & 0.8\% & 0.8\% & \url{http://aidsinfo.unaids.org/}\\
  Namibia & 1.4\% & 2.2\% & 3.3\% & 4.8\% & 6.8\% & 9.1\% & 11.4\% & 13.5\% & 15.1\% & 16.3\% & 17.1\% & 17.4\% & 17.4\% & 17.2\% & 16.8\% & 16.3\% & 15.9\% & 15.5\% & 15.3\% & 15.0\% & 14.7\% & 14.4\% & 14.1\% & 13.8\% & 13.6\% & 13.3\% & \url{http://aidsinfo.unaids.org/}\\
  Nepal & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.2\% & 0.2\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.2\% & 0.2\% & 0.2\% & \url{http://aidsinfo.unaids.org/}\\
  Netherlands & 0.095\% & 0.12\% & 0.14\% & 0.17\% & 0.19\% & 0.19\% & 0.2\% & 0.21\% & 0.22\% & 0.22\% & 0.24\% & 0.24\% & 0.25\% & 0.26\% & 0.27\% & 0.28\% & 0.29\% & 0.31\% & 0.31\% & 0.31\% & 0.33\% & 0.34\% & 0.35\% & --- & --- & --- & \url{http://www.unaids.org/en/resources/campaigns/globalreport2013/globalreport}\\
  New Zealand & 0.06\% & 0.06\% & 0.06\% & 0.06\% & 0.06\% & 0.06\% & 0.06\% & 0.06\% & 0.06\% & 0.05\% & 0.05\% & 0.05\% & 0.05\% & 0.05\% & 0.05\% & 0.05\% & 0.05\% & 0.05\% & --- & --- & --- & --- & --- & --- & 0.091\% & 0.15\% & \url{http://dnmeds.otago.ac.nz/departments/psm/research/aids/pdf/75%20AIDS-NZ%20May%202016.pdf}, Estimated PLHIV (total) / Population (15-49)\\
  Nicaragua & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & \url{http://aidsinfo.unaids.org/}\\
  Niger & 0.2\% & 0.3\% & 0.4\% & 0.5\% & 0.6\% & 0.7\% & 0.9\% & 1\% & 1.1\% & 1.2\% & 1.2\% & 1.2\% & 1.2\% & 1.2\% & 1.2\% & 1.1\% & 1\% & 0.9\% & 0.8\% & 0.8\% & 0.7\% & 0.6\% & 0.6\% & 0.5\% & 0.5\% & 0.5\% & \url{http://aidsinfo.unaids.org/}\\
  Nigeria & 1.4\% & 1.6\% & 1.9\% & 2.2\% & 2.5\% & 2.9\% & 3.2\% & 3.5\% & 3.7\% & 3.8\% & 3.9\% & 4.0\% & 4.0\% & 4.0\% & 3.9\% & 3.8\% & 3.8\% & 3.7\% & 3.6\% & 3.5\% & 3.5\% & 3.4\% & 3.3\% & 3.2\% & 3.2\% & 3.1\% & \url{http://aidsinfo.unaids.org/}\\
  Pakistan & 0.0047\% & 0.0054\% & 0.0063\% & 0.007\% & 0.0076\% & 0.0083\% & 0.0089\% & 0.0098\% & 0.011\% & 0.012\% & 0.013\% & 0.015\% & 0.016\% & 0.018\% & 0.022\% & 0.025\% & 0.028\% & 0.032\% & 0.037\% & 0.046\% & 0.054\% & 0.063\% & 0.072\% & 0.082\% & 0.092\% & 0.1\% & \url{http://aidsinfo.unaids.org/}, PLHIV 15+/ Population 15-49\\
  Panama & 0.3\% & 0.4\% & 0.5\% & 0.6\% & 0.7\% & 0.7\% & 0.7\% & 0.7\% & 0.7\% & 0.7\% & 0.7\% & 0.7\% & 0.7\% & 0.6\% & 0.6\% & 0.6\% & 0.6\% & 0.6\% & 0.7\% & 0.7\% & 0.7\% & 0.7\% & 0.7\% & 0.7\% & 0.7\% & 0.7\% & \url{http://aidsinfo.unaids.org/}\\
  Papua New Guinea & $<$0.1\% & $<$0.1\% & 0.1\% & 0.2\% & 0.3\% & 0.3\% & 0.4\% & 0.5\% & 0.6\% & 0.7\% & 0.8\% & 0.9\% & 0.9\% & 0.9\% & 0.9\% & 0.9\% & 0.9\% & 0.9\% & 0.9\% & 0.8\% & 0.8\% & 0.8\% & 0.8\% & 0.8\% & 0.8\% & 0.8\% & \url{http://aidsinfo.unaids.org/}\\
  Paraguay & 0.1\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & \url{http://aidsinfo.unaids.org/}\\
  Peru & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & \url{http://aidsinfo.unaids.org/}\\
  Philippines & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & 0.006\% & 0.0071\% & 0.0085\% & 0.01\% & 0.012\% & 0.014\% & 0.017\% & 0.02\% & 0.024\% & 0.03\% & 0.039\% & 0.047\% & 0.063\% & 0.071\% & --- & \url{http://www.unaids.org/sites/default/files/country/documents//PHL_narrative_report_2014.pdf}, Projected PLHIV / Population (15-49)\\
  Moldova & --- & --- & --- & --- & --- & --- & 0.1\% & 0.1\% & 0.2\% & 0.2\% & 0.3\% & 0.3\% & 0.3\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.5\% & 0.5\% & 0.5\% & 0.6\% & 0.6\% & 0.6\% & 0.6\% & 0.6\% & \url{http://aidsinfo.unaids.org/}\\
  Russia & --- & --- & --- & --- & --- & --- & --- & 0.0069\% & 0.012\% & 0.038\% & 0.12\% & 0.23\% & 0.3\% & 0.35\% & 0.4\% & 0.45\% & 0.51\% & 0.57\% & 0.63\% & --- & --- & *1.385 & --- & --- & --- & 2.2\% & \url{http://data.unaids.org/pub/Report/2008/russia_2008_country_progress_report_en.pdf}, \url{http://www.hivrussia.ru/skm/info_en.shtml}, \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4247269/table/T1/}, \url{http://www.unaids.org/sites/default/files/country/documents/RUS_narrative_report_2015.pdf}\\
  Rwanda & 5.2\% & 5.7\% & 6.1\% & 6.3\% & 6.3\% & 6.3\% & 6.1\% & 5.9\% & 5.6\% & 5.3\% & 4.9\% & 4.6\% & 4.2\% & 3.9\% & 3.6\% & 3.4\% & 3.3\% & 3.3\% & 3.2\% & 3.2\% & 3.1\% & 3.1\% & 3.1\% & 3.0\% & 3.0\% & 2.9\% & \url{http://aidsinfo.unaids.org/}\\
  Saint Lucia & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & 0.28\% & --- & --- & 0.56\% & 0.46\% & --- & 0.69\% & --- & \url{http://www.unaids.org/sites/default/files/country/documents/file,68394,es..pdf}, \url{http://www.unaids.org/sites/default/files/country/documents/LCA_narrative_report_2015.pdf}\\
  Senegal & 0.2\% & 0.2\% & 0.2\% & 0.3\% & 0.3\% & 0.4\% & 0.4\% & 0.5\% & 0.6\% & 0.7\% & 0.7\% & 0.8\% & 0.9\% & 0.9\% & 0.9\% & 0.9\% & 0.8\% & 0.8\% & 0.8\% & 0.7\% & 0.7\% & 0.7\% & 0.6\% & 0.6\% & 0.6\% & 0.5\% & \url{http://aidsinfo.unaids.org/}\\
  Sierra Leone & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.2\% & 0.3\% & 0.4\% & 0.6\% & 0.7\% & 0.9\% & 1.1\% & 1.3\% & 1.4\% & 1.5\% & 1.6\% & 1.7\% & 1.7\% & 1.7\% & 1.7\% & 1.6\% & 1.6\% & 1.5\% & 1.5\% & 1.4\% & 1.3\% & \url{http://aidsinfo.unaids.org/}\\
  Somalia & $<$0.1\% & 0.1\% & 0.2\% & 0.2\% & 0.3\% & 0.4\% & 0.4\% & 0.5\% & 0.6\% & 0.6\% & 0.6\% & 0.6\% & 0.6\% & 0.6\% & 0.6\% & 0.6\% & 0.6\% & 0.6\% & 0.6\% & 0.6\% & 0.6\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & \url{http://aidsinfo.unaids.org/}\\
  South Africa & 1\% & 1.6\% & 2.6\% & 3.9\% & 5.7\% & 7.9\% & 10.3\% & 12.8\% & 15.1\% & 17.1\% & 18.7\% & 19.9\% & 20.6\% & 21.0\% & 21.0\% & 20.8\% & 20.4\% & 19.9\% & 19.5\% & 19.2\% & 18.9\% & 18.8\% & 18.8\% & 18.9\% & 19.0\% & 19.2\% & \url{http://aidsinfo.unaids.org/}\\
  South Sudan & 0.1\% & 0.3\% & 0.4\% & 0.6\% & 0.9\% & 1.1\% & 1.4\% & 1.6\% & 1.9\% & 2.2\% & 2.4\% & 2.6\% & 2.8\% & 2.9\% & 2.9\% & 2.9\% & 2.9\% & 2.8\% & 2.8\% & 2.8\% & 2.7\% & 2.7\% & 2.6\% & 2.6\% & 2.5\% & 2.5\% & \url{http://aidsinfo.unaids.org/}\\
  Spain & 0.4\% & 0.4\% & 0.4\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & \url{http://aidsinfo.unaids.org/}\\
  Sri Lanka & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & 0.038\% & --- & 0.028\% & --- & 0.023\% & 0.027\% & 0.029\% & 0.032\% & --- & \url{http://www.unaids.org/sites/default/files/country/documents/LKA_narrative_report_2016.pdf}, Estimated \# PLHIV (total) / Population (15-49)\\
  Sudan & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.3\% & 0.3\% & \url{http://aidsinfo.unaids.org/}\\
  Suriname & 0.1\% & 0.2\% & 0.3\% & 0.3\% & 0.4\% & 0.5\% & 0.6\% & 0.8\% & 0.9\% & 1\% & 1.1\% & 1.2\% & 1.3\% & 1.3\% & 1.3\% & 1.3\% & 1.3\% & 1.2\% & 1.2\% & 1.2\% & 1.2\% & 1.2\% & 1.1\% & 1.1\% & 1.1\% & 1.1\% & \url{http://aidsinfo.unaids.org/}\\
  Swaziland & 2.2\% & 4.0\% & 6.5\% & 9.4\% & 12.6\% & 15.7\% & 18.5\% & 20.9\% & 22.7\% & 24.0\% & 24.8\% & 25.4\% & 25.6\% & 25.7\% & 25.7\% & 25.7\% & 25.8\% & 26.1\% & 26.4\% & 26.7\% & 27.2\% & 27.6\% & 28.0\% & 28.4\% & 28.7\% & 28.8\% & \url{http://aidsinfo.unaids.org/}\\
  Sweden & 0.089\% & 0.11\% & 0.13\% & 0.14\% & 0.15\% & 0.16\% & 0.17\% & 0.17\% & 0.18\% & 0.18\% & 0.19\% & 0.19\% & 0.19\% & 0.21\% & 0.21\% & 0.21\% & 0.22\% & 0.22\% & 0.22\% & 0.23\% & 0.23\% & 0.23\% & 0.23\% & --- & --- & --- & \url{http://www.unaids.org/en/resources/campaigns/globalreport2013/globalreport}\\
  Switzerland & 0.26\% & 0.29\% & 0.31\% & 0.33\% & 0.34\% & 0.34\% & 0.33\% & 0.35\% & 0.36\% & 0.37\% & 0.38\% & 0.39\% & 0.4\% & 0.43\% & 0.44\% & 0.46\% & 0.46\% & 0.48\% & 0.49\% & 0.51\% & 0.52\% & 0.53\% & 0.56\% & --- & --- & --- & \url{http://www.unaids.org/en/resources/campaigns/globalreport2013/globalreport}\\
  Tajikistan & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & 0.1\% & 0.1\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & \url{http://aidsinfo.unaids.org/}\\
  Thailand & 0.5\% & 0.9\% & 1.3\% & 1.6\% & 1.8\% & 1.9\% & 2.0\% & 1.9\% & 1.9\% & 1.8\% & 1.7\% & 1.7\% & 1.6\% & 1.5\% & 1.4\% & 1.4\% & 1.4\% & 1.3\% & 1.3\% & 1.3\% & 1.3\% & 1.3\% & 1.2\% & 1.2\% & 1.2\% & 1.1\% & \url{http://aidsinfo.unaids.org/}\\
  Timor-Leste & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & 0.013\% & --- & --- & --- & --- & --- & --- & --- & --- & --- & 0.085\% & 0.097\% & \url{http://www.hivpolicy.org/Library/HPP000476.pdf}, Estimated \# PLHIV (total) / Population (15-49)\\
  Togo & 1.2\% & 1.5\% & 1.9\% & 2.3\% & 2.8\% & 3.2\% & 3.6\% & 4.0\% & 4.4\% & 4.6\% & 4.8\% & 4.9\% & 4.9\% & 4.8\% & 4.6\% & 4.4\% & 4.1\% & 3.9\% & 3.6\% & 3.3\% & 3.1\% & 2.9\% & 2.8\% & 2.6\% & 2.5\% & 2.4\% & \url{http://aidsinfo.unaids.org/}\\
  Trinidad and Tobago & 0.4\% & 0.5\% & 0.5\% & 0.6\% & 0.7\% & 0.8\% & 0.8\% & 0.9\% & 0.9\% & 1\% & 1\% & 1\% & 1.1\% & 1.1\% & 1.1\% & 1.1\% & 1.2\% & 1.2\% & 1.2\% & 1.2\% & 1.2\% & 1.2\% & 1.2\% & 1.2\% & 1.2\% & 1.2\% & \url{http://aidsinfo.unaids.org/}\\
  Tunisia & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & 0.019\% & 0.022\% & 0.024\% & 0.027\% & 0.03\% & 0.033\% & 0.037\% & 0.04\% & 0.043\% & \url{http://aidsinfo.unaids.org/}, PLHIV 15+/ Population 15-49\\
  Uganda & 13.1\% & 13.3\% & 13.1\% & 12.7\% & 12.1\% & 11.4\% & 10.6\% & 9.8\% & 9.0\% & 8.4\% & 7.8\% & 7.3\% & 7.0\% & 6.7\% & 6.5\% & 6.5\% & 6.6\% & 6.6\% & 6.7\% & 6.9\% & 7.0\% & 7.1\% & 7.2\% & 7.2\% & 7.1\% & 7.1\% & \url{http://aidsinfo.unaids.org/}\\
  Ukraine & --- & --- & --- & 0.1\% & 0.1\% & 0.2\% & 0.3\% & 0.3\% & 0.4\% & 0.6\% & 0.7\% & 0.8\% & 0.8\% & 0.9\% & 0.9\% & 1\% & 1\% & 0.9\% & 0.9\% & 0.9\% & 0.9\% & 0.8\% & 0.8\% & 0.8\% & 0.8\% & 0.9\% & \url{http://aidsinfo.unaids.org/}\\
  United Kingdom & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & 0.096\% & 0.11\% & 0.12\% & 0.13\% & 0.15\% & 0.16\% & 0.17\% & 0.17\% & 0.18\% & 0.19\% & 0.19\% & 0.2\% & --- & --- & \url{https://www.gov.uk/government/uploads/system/uploads/attachment_data/file/335452/HIV_annual_report_2012.pdf}, Estimated \# PLHIV (15-49) / Population (15-49)\\
  Tanzania & 5.1\% & 5.8\% & 6.4\% & 7.0\% & 7.4\% & 7.7\% & 7.9\% & 8.0\% & 7.9\% & 7.8\% & 7.7\% & 7.5\% & 7.3\% & 7.1\% & 6.8\% & 6.5\% & 6.3\% & 6.1\% & 6.0\% & 5.8\% & 5.6\% & 5.4\% & 5.2\% & 5.1\% & 4.9\% & 4.7\% & \url{http://aidsinfo.unaids.org/}\\
  United States & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & --- & 0.21\% & 0.22\% & 0.23\% & 0.24\% & 0.25\% & 0.26\% & 0.26\% & 0.37\% & 0.37\% & 0.37\% & 0.37\% & 0.37\% & --- & --- & --- & \url{http://www.cdc.gov/hiv/library/reports/surveillance/pastissues.html}, Estimated \# PLHIV (15-49) / Population (15-49)\\
  Uruguay & 0.1\% & 0.1\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.4\% & 0.4\% & 0.4\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & \url{http://aidsinfo.unaids.org/}\\
  Uzbekistan & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & 0.1\% & 0.2\% & 0.2\% & 0.3\% & 0.3\% & 0.4\% & 0.4\% & 0.4\% & 0.3\% & 0.3\% & 0.3\% & 0.3\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & 0.2\% & \url{http://aidsinfo.unaids.org/}\\
  Venezuela & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & $<$0.1\% & 0.1\% & 0.2\% & 0.2\% & 0.3\% & 0.3\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & \url{http://aidsinfo.unaids.org/}\\
  Viet Nam & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.1\% & 0.2\% & 0.2\% & 0.3\% & 0.3\% & 0.3\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.4\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & 0.5\% & \url{http://aidsinfo.unaids.org/}\\
  Yemen & --- & 0.022\% & 0.024\% & 0.026\% & 0.028\% & 0.032\% & 0.032\% & 0.034\% & 0.034\% & 0.036\% & 0.037\% & 0.039\% & 0.04\% & 0.042\% & 0.043\% & 0.044\% & 0.047\% & 0.048\% & 0.05\% & 0.052\% & 0.054\% & 0.056\% & 0.058\% & 0.06\% & 0.063\% & 0.065\% & \url{http://aidsinfo.unaids.org/}, PLHIV 15+/ Population 15-49\\
  Zambia & 12.4\% & 13.5\% & 14.3\% & 14.9\% & 15.3\% & 15.6\% & 15.7\% & 15.8\% & 15.7\% & 15.6\% & 15.4\% & 15.2\% & 14.9\% & 14.6\% & 14.4\% & 14.1\% & 13.8\% & 13.6\% & 13.6\% & 13.5\% & 13.5\% & 13.4\% & 13.3\% & 13.2\% & 13.1\% & 12.9\% & \url{http://aidsinfo.unaids.org/}\\
  Zimbabwe & 15.0\% & 17.7\% & 20.3\% & 22.5\% & 24.2\% & 25.3\% & 26.0\% & 26.0\% & 25.7\% & 24.9\% & 24.0\% & 22.8\% & 21.6\% & 20.4\% & 19.2\% & 18.1\% & 17.2\% & 16.5\% & 16.0\% & 15.7\% & 15.5\% & 15.3\% & 15.2\% & 15.0\% & 14.9\% & 14.7\% & \url{http://aidsinfo.unaids.org/}\\
  \hline
  \multicolumn{1}{l}{NOTES}
\end{longtable}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "supplementary_text"
%%% End:

### 2016-08-15 Documents/supplementary_text.tex
Long table works- but not wihin table enviornment
Working on supplement tables.

@@
 \usepackage{longtable}
+\usepackage[labelsep = period, singlelinecheck = off, labelfont = {bf}]{caption}
+
+% Load hyperref after the other stuff above.
 \usepackage[pdfborder={0 0 0}]{hyperref}
@@
 parametrize our mathematical modeling for 127 countries.  See
-\hyperref[data_source_treatment_cascade]{Tables
-  \ref*{data_source_treatment_cascade}}--\ref{data_source_regions} for
-full information on data sources for each country.
-
-\begin{table}
-  \centering
-  \tiny
-  \input{treatment_cascade}
-  \caption{Data used for the treatment cascade.}
-  \label{data_source_treatment_cascade}
-\end{table}
-
-\begin{table}
-  \centering
-  \tiny
-  % \input{prevalence}
-  \caption{Data sources for prevalence.}
-  \label{data_source_prevalence}
-\end{table}
-
-\begin{table}
-  \centering
-  \tiny
-  % \input{incidence}
-  \caption{Data sources for prevalence.}
-  \label{data_source_incidence}
-\end{table}
-
-\begin{table}
-  \centering
-  \tiny
-  % \input{regions}
-  \caption{Countries by UNAIDS region.}
-  \label{data_source_regions}
-\end{table}
+Supplemental data files for full information on data sources for each
+country.
 
@@
   \centering
-  \includegraphics[width = \textwidth]{../Codes/plots/transmission_rate}
+  \includegraphics{../Codes/plots/transmission_rate}
   \caption{Country-specific transmission rates were calculated based
@@
 
+\appendix
 \clearpage
+\section{Model results by region and country}
+
 \input{../Codes/plots/effectiveness_all/all}

### 2016-08-15 Documents/treatment_cascade.tex
Long table works- but not wihin table enviornment
Working on supplement tables.

@@
 \begin{longtable}{lrrrl}
+  \caption{The treatment cascade.}
+  \label{data_source_treatment_cascade}
+  \\[-2ex]
   \hline  
@@
   \hline
+  \endfirsthead
+  \caption{(continued)}
+  \\[-2ex]
+  \hline  
+  & & & \multicolumn{1}{c}{Viral} \\
+  Country & \multicolumn{1}{l}{Diagnosed}
+  & \multicolumn{1}{l}{Treated} & \multicolumn{1}{l}{suppression}
+  & References \\
+  \hline
+  \endhead
+  \hline
+  \endfoot
+  \endlastfoot
   Afghanistan & 5.0\% & 100.0\% & 84.0\% & \cite{Unaids2016-an} \\
@@
   \hline
+  \multicolumn{5}{l}{2011a: Viral suppression is 12-month retention on
+  treatment, all ages, for 2011.} \\
+  \multicolumn{5}{l}{2012b: Viral suppression is 12-month retention on
+  treatment, ages 15+, for 2012.} \\
+  \multicolumn{5}{l}{2013a: Viral suppression is 12-month retention on
+  treatment, all ages, for 2013.} \\
+  \multicolumn{5}{l}{2013b: Viral suppression is 12-month retention on
+  treatment, ages 15+, for 2013.} \\
+  \multicolumn{5}{l}{2014a: Viral suppression is 12-month retention on
+  treatment, all ages, for 2014.} \\
+  \multicolumn{5}{l}{2014b: Viral suppression is 12-month retention on
+  treatment, ages 15+, for 2014.} \\
+  \multicolumn{5}{l}{2015a: Viral suppression is 12-month retention on
+  treatment, all ages, for 2015.} \\
+  \multicolumn{5}{l}{2015b: Viral suppression is 12-month retention on
+  treatment, ages 15+, for 2015.}
 \end{longtable}
-2011a: Viral suppression is 12-month retention on treatment, all ages, for 2011.
-2012b: Viral suppression is 12-month retention on treatment, ages 15+, for 2012.
-2013a: Viral suppression is 12-month retention on treatment, all ages, for 2013.
-2013b: Viral suppression is 12-month retention on treatment, ages 15+, for 2013.
-2014a: Viral suppression is 12-month retention on treatment, all ages, for 2014.
-2014b: Viral suppression is 12-month retention on treatment, ages 15+, for 2014.
-2015a: Viral suppression is 12-month retention on treatment, all ages, for 2015.
-2015b: Viral suppression is 12-month retention on treatment, ages 15+, for 2015.
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "supplementary_text"
+%%% End:

### 2016-08-15 Documents/supplementary_text.tex
Working on supplementary figures.

@@
 \usepackage{microtype}
-\usepackage[final]{pdfpages}
-\usepackage{float}
-\usepackage{longtable}
-\usepackage[labelsep = period, singlelinecheck = off, labelfont = {bf}]{caption}
+\usepackage[font = {sf}, labelfont = {bf},
+  labelsep = period, singlelinecheck = off]{caption}
+\usepackage[font = {sf}]{floatrow}
 
@@
 \usepackage[pdfborder={0 0 0}]{hyperref}
-\usepackage[numbers,round,sort&compress]{natbib}
+\usepackage[numbers, round, sort&compress]{natbib}
 \usepackage{hypernat}
@@
 \renewcommand{\thetable}{\labelPrefix\arabic{table}}
-
-\section*{To do}
-
-\begin{itemize}
-\item Finish tables
-\item Reformat transmission rate figure
-\end{itemize}
 
@@
 
-The source code for the model and analysis tools is available at
-\url{https://github.com/janmedlock/HIV-95-vaccine/}.
+The source code for the model and analysis tools is publicly available
+at \url{https://github.com/janmedlock/HIV-95-vaccine/}
+\cite{medlock2016-git}.
 
@@
 Supplemental data files for full information on data sources for each
-country.
+country.  The data files are also available in the public source-code
+repository \cite{medlock2016-git}.
 
@@
   \centering
-  \includegraphics{../Codes/plots/transmission_rate}
+  \includegraphics{../Codes/plots/transmission_rate.pdf}
   \caption{Country-specific transmission rates were calculated based
@@
 
+\clearpage
 \bibliographystyle{science_nat}
-
 \bibliography{supplementary_text}
@@
 \appendix
-\clearpage
+\newpage
+\vspace*{3in}
 \section{Model results by region and country}
-
+\newpage
 \input{../Codes/plots/effectiveness_all/all}

### 2016-08-15 Codes/plots/prcc.py

@@ -77,7 +77,7 @@ def tornados():
     # times = (2025, 2035)
     times = (2035, )
 
-    figsize = (common.width_2column, 5)
+    figsize = (5.95, 6.5)
     palette = 'Dark2'
 
     parameter_samples = model.samples.load()
@@ -96,30 +96,33 @@ def tornados():
 
         nrows = 1
         ncols = len(times)
-        fig, axes = pyplot.subplots(nrows, ncols,
-                                    figsize = figsize,
-                                    sharex = 'all')
+        with seaborn.axes_style('whitegrid'):
+            fig, axes = pyplot.subplots(nrows, ncols,
+                                        figsize = figsize,
+                                        sharex = 'all')
 
-        if isinstance(axes, pyplot.Axes):
-            axes = [axes]
+            if isinstance(axes, pyplot.Axes):
+                axes = [axes]
 
-        for (ax, t) in zip(axes, times):
-            if ax.is_first_col():
-                ylabels = 'left'
-            elif ax.is_last_col():
-                ylabels = 'right'
-            else:
-                ylabels = 'none'
-            tornado(ax, results, country, targets, outcome, t,
-                    parameter_samples, colors,
-                    parameter_names = parameter_names,
-                    ylabels = ylabels)
-            ax.set_xlabel('PRCC')
-            # Make x-axis limits symmetric.
-            xmin, xmax = ax.get_xlim()
-            xabs = max(abs(xmin), abs(xmax))
-            ax.set_xlim(- xabs, xabs)
-            # ax.set_title(t)
+            for (ax, t) in zip(axes, times):
+                seaborn.despine(ax = ax, top = True, bottom = True)
+                ax.tick_params(labelsize = pyplot.rcParams['font.size'])
+                if ax.is_first_col():
+                    ylabels = 'left'
+                elif ax.is_last_col():
+                    ylabels = 'right'
+                else:
+                    ylabels = 'none'
+                tornado(ax, results, country, targets, outcome, t,
+                        parameter_samples, colors,
+                        parameter_names = parameter_names,
+                        ylabels = ylabels)
+                ax.set_xlabel('PRCC')
+                # Make x-axis limits symmetric.
+                xmin, xmax = ax.get_xlim()
+                xabs = max(abs(xmin), abs(xmax))
+                ax.set_xlim(- xabs, xabs)
+                # ax.set_title(t)
 
     fig.tight_layout(pad = 0)
 

### 2016-08-16 Documents/supplementary_text.tex
A little work.

@@
 vaccine with 50\% efficacy in 2020 with coverage increasing linearly
-from 0\% to 50\% at 2 years post-rollout, continuing on the same
-linear trend to 70\% at 2.8 years post-rollout, and maintaining
-constant 70\% coverage thereafter. We also performed a partial rank
-correlation coefficient (PRCC) sensitivity analysis for each model
-parameter and a scenario analysis to account for uncertainty in the
-profile of the prospective vaccine. See Supplementary text for more
-details.
+by 25\% per year, continuing up to 70\% at 2.8 years post-rollout, and
+maintaining constant 70\% coverage thereafter.  We also performed a
+partial rank correlation coefficient (PRCC) sensitivity analysis for
+each model parameter and a scenario analysis to account for
+uncertainty in the profile of the prospective vaccine.
 
@@
 undiagnosed, diagnosed, treated, viral suppression and AIDS
-compartments. People susceptible to HIV (S) progress to the
-acute-infection phase (A) according to the force of infection, which
+compartments. People susceptible to HIV ($S$) progress to the
+acute-infection phase ($A$) according to the force of infection, which
 depends on the HIV transmission rate, estimated from the
-country-specific incidence and prevalence data (next section),
-adjusted for the current number of acutely infected, untreated or
-ineffectively treated, and viral suppression PLHIV.  Acute infection
-is characterized by high viral loads and lasts 88 days on average
-\cite{Hollingsworth2008-iy}. We assumed that individuals remain
-undiagnosed during their acute infection phase and during at least
-some of the subsequent period of clinical latency (i.e., the
-undiagnosed compartment). Individuals in the undiagnosed class will be
-diagnosed at a rate determined by the country's initial diagnosis
+country-specific incidence and prevalence data
+(\autoref{model_fitting}), adjusted for the current number of acutely
+infected, untreated or ineffectively treated, and viral suppression
+PLHIV.  Acute infection is characterized by high viral loads and lasts
+88 [XX, YY] days \cite{Hollingsworth2008-iy}. We assumed that people
+remain undiagnosed during their acute infection phase and during at
+least some of the subsequent period of clinical latency (i.e., the
+undiagnosed compartment). After acute infection, people move into the
+chronic undiagnosed class ($U$).  People in the undiagnosed class will
+be diagnosed at a rate determined by the country's initial diagnosis
 level and potential progress towards the UNAIDS targets.  Diagnosed
-people transition to the treated compartment upon starting ART at a
-rate of $\phi$ , and to the virally suppressed class (V) after
-achieving viral suppression through treatment retention at a rate of
-$\gamma$. The disengagement from treatment moves individuals (T, V) at
-a rate of $\omega$ back to the diagnosed class (D). Rates of movement
-between the undiagnosed (U), diagnosed (D), treated (T) and virally
-suppressed classes (V) are determined by the proportions of PLHIV
-diagnosed ($p_{D}$), proportion of diagnosed individuals on ART
-($p_{T}$), and the proportion of individuals on ART who have achieved
-viral suppression ($p_{V}$). PLHIV in U, D, T, and V classes develop
-AIDS (W) after an average duration dependent on viral suppression
-status. Individuals who have achieved viral suppression (V) take
-longer to develop AIDS ($1/\theta$), than those who are in the other
-PLHIV classes ($1/\sigma$). Individuals who are susceptible to HIV can
-be vaccinated at a of rate ($\zeta$), and depending on vaccine
-efficacy, have a reduced chance of HIV infection. The model equations
+people (compartment $D$) transition to the treated compartment ($T$)
+upon starting ART at a rate of $\phi$ , and then to the
+viral-suppression class ($V$) after achieving viral suppression
+through treatment retention at a rate of $\gamma$. The disengagement
+from treatment moves people from treated ($T$) and viral suppression
+($V$) at a rate of $\omega$ back to the diagnosed class ($D$). Rates
+of movement between the undiagnosed ($U$), diagnosed ($D$), treated
+($T$) and viral-suppression classes ($V$) are determined by the
+proportions of PLHIV diagnosed ($p_{D}$), proportion of diagnosed
+people on ART ($p_{T}$), and the proportion of people on ART who have
+achieved viral suppression ($p_{V}$). PLHIV in $U$, $D$, $T$, and $V$
+classes develop AIDS (compartment $W$) after an average duration
+dependent on viral suppression status. People who have achieved viral
+suppression ($V$) take longer to develop AIDS ($1/\theta$), than those
+who are in the other PLHIV classes ($1/\sigma$). People who are
+susceptible to HIV are vaccinated at rate $\zeta$, transitioning into
+the vaccinated compartment ($R$), where the vaccine reduces their
+force of infection by the efficacy factor $\rho$.  The model equations
 are
-
 \begin{equation}
@@
     \\
-     \frac{\md R}{\md t} & = \zeta S - \rho \lambda R - \mu R,
+    \frac{\md R}{\md t} & = \zeta S - (1 - \rho) \lambda R - \mu R,
     \\
-    \frac{\md A}{\md t} &= \lambda S +\rho \lambda R - \delta A - \mu A,
+    \frac{\md A}{\md t} &= \lambda S + (1 - \rho) \lambda R - \delta A - \mu A,
     \\
@@
 \end{equation}
-
-The rate of developing AIDS  among those who have acheived
-viral suppression ($\theta$) is
+The rate of developing AIDS among those who have acheived viral
+suppression is
 \begin{equation}
- \frac{1}{1/\mu-\omega-1/\nu}.
+ \theta = \frac{1}{1/\mu-\omega-1/\nu}.
 \end{equation}
@@
 \end{equation}
-and the proportion with viral suppression is
+the proportion with viral suppression is
 \begin{equation}
-  p_V = \frac{V}{T + V}.
+  p_V = \frac{V}{T + V},
+\end{equation}
+and the proportion of people vaccinated is
+\begin{equation}
+  P_{V} = \frac{R}{S+R}.
 \end{equation}
 
-The targets for the proportions $p_D$, $p_T$, and $p_V$ in the achievement of 90--90--90
-all operate under the following assumption:
-if the initial level $p_x(0)$ is less than $90\%$, the proportion will increase
-linearly in the first 5 years and then stay at $90\%$ for the
-remaining time; and if the initial level is at $90\%$ or above, the proportion
-will remain constant for the duration of the study:
+The targets for the proportions $p_D$, $p_T$, and $p_V$ in the
+achievement of 90--90--90 all operate under the following assumption:
+if the initial level $p_x(0)$ is less than $90\%$, the proportion will
+increase linearly in the first 5 years and then stay at $90\%$ for the
+remaining time; and if the initial level is at $90\%$ or above, the
+proportion will remain constant for the duration of the study:
 \begin{equation}
@@
 
-Similarly, the proportion of people vaccinated is
-\begin{equation}
-P_{V} = \frac{R}{S+R},
-\end{equation}
-
-We can implement the vaccination compartment in the same way as the other controls. When we begin
-vaccination in 2020/2025, the initial vaccination level is 0\%. This
-coverage will increase linearly to $50\%$ within first 2 or 5
-years. The coverage will continue to increase linearly till it reaches
-the desired coverage ($50\%,70\%,90\%$) and then stay constant for the
-remainder of the projections.
+We can implement the vaccination compartment in the same way as the
+other controls. When we begin vaccination in 2020 (also 2025 in
+scenario analysis), the initial vaccination level is 0\%. The coverage
+will increase linearly by 25\% per year (also 10\% per year in
+scenario analysis). The coverage will continue to increase linearly
+until it reaches 70\% coverage (50\% \& 90\% in scenario analysis) and
+then stay constant for the remainder of the time period.
 
@@
 by 2020 by increasing $p_D$, $p_T$, and $p_V$ to 95--95--95 levels by
-2030 linearly. \comment{@Jan, We use the Heaveside function here too?}
+2030 linearly. \comment{@Jan, We use the Heaveside function here too?
+JM: Yes.  I'll write it at some point.}
 
-\subsection{Rates that are on when $p_x < p^*_x$}
-
-The rates are applied when the proportions of $p_D$, $p_T$, and $p_V$ are below the target levels:
+The rates are applied when the proportions of $p_D$, $p_T$, and $p_V$
+are below the target levels:
 \begin{equation}
@@
 \label{model_fitting}
+
 We first estimated country-specific rates of HIV transmission for each
@@
   \caption{Country-specific transmission rates were calculated based
-    on the relative contributions of individuals with acute infection,
+    on the relative contributions of people with acute infection,
     unsuppressed viral load or suppressed viral load to overall
@@
 viral suppression ($p_{V}$) continue unchanged until 2035.  The
-intervention scenarios were (1.) the attainment of the 90--90--90
+intervention scenarios were 1.) the attainment of the 90--90--90
 target by linear increases in $p_{D}$, $p_{T}$, and $p_{V}$ until 2020
-followed by maintenance of those levels until 2035, and (2.) linear
+followed by maintenance of those levels until 2035, and 2.) linear
 increase in the diagnosis and treatment levels to the 90--90--90
@@
 
-We calculated partial rank correlation coefficients (PRCC) to measure
-the independent effect of each parameter on model projections of HIV
-incidence (\autoref{PRCCs}). Furthermore, due to uncertainty
-surrounding the prospective vaccine, we obtained model projections
-using six additional vaccine scenarios by considering alternative
-estimates of efficacy (30\%, 70\%), coverage (50\%, 90\%), time to
-50\% coverage (2 years, 5 years), and first year of availability
-(2025).
+Model outcomes were projected until 2035 for each of the 127 countries
+with sufficient data on status quo rates of diagnosis and treatment
+and on historical incidence or prevalence
+(\hyperref[effectiveness_Global]{\autoref*{effectiveness_Global}}--\ref{effectiveness_Zimbabwe}). The
+median estimates with interquartile ranges are presented between 2015
+and 2035 for number of PLHIV, per-capita incidence, PLAIDS, and number
+of HIV-related deaths under the status quo and five intervention
+scenarios: vaccination only, attaining the UNAIDS 90--90--90 target,
+attaining the 90--90--90 target and vaccination, attaining the UNAIDS
+95--95--95 target, and attaining the 95--95--95 target and
+vaccination.  The results from the country were aggregated to the
+regional and global levels by adding the numbers of people in each
+compartment over time and then PLHIV, per-capita incidence, PLAIDS,
+and HIV-related deaths were calculated from the aggregates.
+
+We calculated partial rank correlation coefficients (PRCC) \cite{}
+to measure the independent effect of each parameter on model
+projections of HIV incidence (\autoref{PRCCs}). Furthermore, due to
+uncertainty surrounding the prospective vaccine, we obtained model
+projections using six additional vaccine scenarios by considering
+alternative estimates of efficacy (30\%, 70\%), coverage (50\%, 90\%),
+speed of scale up (10\% coverage per year), and first year of
+availability (2025).
 
@@
 \end{figure}
-
-\subsection{Effectiveness of HIV interventions globally, regionally
-  and for each of 127 countries}
-
-Model outcomes were projected until 2035 for each of the 127 countries
-with sufficient data on status quo rates of diagnosis and treatment
-and on historical incidence or prevalence. The median estimates with
-interquartile ranges are presented between 2015 and 2035 for number of
-PLHIV, annual incidence (per million population), number of people
-with AIDS, and number of HIV-related deaths under the status quo and
-five intervention scenarios: vaccination only, attainment of the
-UNAIDS 90--90--90 target, 90--90--90 target and vaccination, attainment of
-the UNAIDS 95--95--95 target, and 95--95--95 target and vaccination.  The
-country-specific projections as well as aggregated projections at the
-regional and global levels follow:
 

### 2016-08-18 Documents/supplementary_text.tex
More work on supplement.

@@
 
+\usepackage[utf8x]{inputenc}
+\usepackage{microtype}
+\usepackage{geometry}
+
 \usepackage{amsmath}
-\usepackage{geometry}
-\usepackage{setspace}
 \usepackage{graphicx}
 \usepackage{tikz}
-\usepackage[utf8x]{inputenc}
-\usepackage{microtype}
+
 \usepackage[font = {sf}, labelfont = {bf},
@@
 \usepackage[font = {sf}]{floatrow}
+\usepackage{tabularx}
 
-% Load hyperref after the other stuff above.
-\usepackage[pdfborder={0 0 0}]{hyperref}
 \usepackage[numbers, round, sort&compress]{natbib}
-\usepackage{hypernat}
+\renewcommand{\citenumfont}{\itshape}  % Citations get italics numbers
+\makeatletter
+\renewcommand\NAT@open{(\hspace*{-0.3ex}}   % Tweak spacing.
+\renewcommand\@biblabel[1]{#1.}  % Reference list doesn't use square brackets.
+\makeatother
 
@@
 
+% Load hyperref after the other stuff above.
+\usepackage[pdfborder={0 0 0}]{hyperref}
+\usepackage{hypernat}
+
 \newcommand{\comment}[1]{\textbf{[#1]}}
@@
 \newcommand{\me}{\mathrm{e}}
+\DeclareMathOperator{\Uniform}{Uniform}
+\DeclareMathOperator{\Triangular}{Triangular}
+\DeclareMathOperator{\Lognormal}{Lognormal}
+\DeclareMathOperator{\BetaPERT}{Beta-PERT}
 
+\newcommand{\labelPrefix}{S}
+\renewcommand{\thesection}{\labelPrefix\arabic{section}}
+\renewcommand{\theequation}{\labelPrefix\arabic{equation}}
+\renewcommand{\thefigure}{\labelPrefix\arabic{figure}}
+\renewcommand{\thetable}{\labelPrefix\arabic{table}}
 \renewcommand{\figurename}{Fig.}
+\renewcommand{\sectionautorefname}{Section}
 
@@
 \begin{document}
+
 \maketitle
 
-\newcommand{\labelPrefix}{S}
-\renewcommand{\thesection}{\labelPrefix\arabic{section}}
-\renewcommand{\theequation}{\labelPrefix\arabic{equation}}
-\renewcommand{\thefigure}{\labelPrefix\arabic{figure}}
-\renewcommand{\thetable}{\labelPrefix\arabic{table}}
+\section{Mathematical model}
 
 We developed a continuous-time, compartmental model consisting of 8
-health states: susceptible to HIV infection, vaccinated against HIV,
-acute HIV infection, undiagnosed HIV infection, diagnosed but
-untreated HIV infection, treated without achieving viral suppression,
-achieved viral suppression, and having AIDS (Supplementary text). We
-found sufficient country-level demographic data, as well as estimates
-of longitudinal HIV incidence and prevalence for the 15–49 age group,
-spanning from as early as 1990 to 2015 to parameterize our model for
-127 countries. See Supporting text for information on data sources.
+health states (\autoref{model_diag}): susceptible to HIV infection
+($S$), vaccinated against HIV ($R$), acute HIV infection ($A$),
+undiagnosed HIV infection ($U$), diagnosed but untreated HIV infection
+($D$), treated without viral suppression ($T$), viral suppression
+($V$), and having AIDS ($W$).  Transitions between states are governed
+by a series of differential equations parametrized using rates
+estimated from other studies and from incidence and prevalence data
+(Table \ref{model_param}).  The model is deterministic, but
+uncertainty in the parameters is treated by running the model with
+many different samples from the parameter distributions.
 
-Using available historical data for incidence and prevalence, and
-published transmission estimates (13), we estimated transmission rates
-for people with acute infection, unsuppressed viral load and
-suppressed viral load. Our calibration method provided a recent
-snapshot of country-specific transmission, while using historical data
-to smooth out variations. See Supporting text for detailed information
-on estimating the transmission rate.
+\begin{figure}
+  \centering
+  \input{diagram}
+  \caption{Model diagram.}
+  \label{model_diag}
+\end{figure}
+
+\begin{table}
+  \begin{center}
+    \begin{tabularx}{\textwidth}{lXlll}
+      \hline
+      & Definition & Value & Reference \\
+      \hline
+      $\delta$	& Rate of leaving acute infection
+      & $\Triangular$(2, 4.14, 9.6)\;y$^{-1}$
+      & \cite{Hollingsworth2008-iy} \\
+      $\sigma$	& Rate of developing AIDS without viral suppression
+      & 0.1064\;y$^{-1}$ & \cite{Morgan2002-cq} \\
+      $\theta$ & Rate of developing AIDS with viral suppression
+      & See eq.~(\ref{theta}) & --- \\
+      $\gamma$ & Rate of viral suppression
+      & $\Uniform$(0.5, 1.5)\;y$^{-1}$
+      & \cite{Currie2009-yz} \\
+      $\nu$ & Death rate from AIDS & 0.5\;y$^{-1}$
+      & \cite{Morgan2002-cq} \\
+      $\rho$ & Vaccine efficacy & 50\%\,[30\%, 70\%] & --- \\
+      $\omega$	& Reduction in lifetime with viral suppression
+      & $\Uniform$(5, 8)\;y
+      & \cite{Unaids2014-ue, Samji2013-kf} \\
+      $\tau_{A}$ & Transmissibility during acute phase
+      & $\Triangular$(0.0039, 0.0082, 0.0150)
+      & \cite{Skarbinski2015-ni,Wawer2005-us}\\
+      $\tau_{U}$ & Transmissibility after acute phase
+      & $\Triangular$(0.00077, 0.0014, 0.00251)
+      & \cite{Hughes2012-so} \\
+      $\varepsilon$ & Relative transmissibility with
+      viral suppression & $\BetaPERT$(0.08, 0.002, 0.57)
+      & \cite{Donnell2010-xo} \\
+      $n$ & Sex acts per year & $\Uniform$(96, 108)
+      & \cite{Wawer2005-us,Abdool_Karim2010-cm}\\
+      $\mu$ & Background death rate & Country specific
+      & \cite{World_Development_Indicators2013-ee} \\
+      $B$ & Birth rate & Country specific
+      & \cite{World_Development_Indicators2013-ee, WorldBankpg} \\
+      $\alpha$ & Diagnosis rate & See eqs.~(\ref{target_rates}) & --- \\
+      $\phi$ & Treatment rate & See eqs.~(\ref{target_rates}) & --- \\
+      $\psi$ & Rate of relapse to untreated & See eqs.~(\ref{target_rates})
+      & --- \\
+      $\zeta$ & Vaccination rate & See eqs.~(\ref{target_rates}) & --- \\
+      \hline
+    \end{tabularx}
+    \caption{Model parameters. $\Triangular$, $\Uniform$,
+      and $\BetaPERT$ are sampling distributions: see text for a
+      full description.  For vaccine efficacy, $50\%$ was the
+      baseline, and $30\%$ and $70\%$ were also used in scenario
+      analysis.}
+    \label{model_param}
+  \end{center}
+\end{table}
+
+Birth and death.
+
+People living with HIV (PLHIV) are divided among the acutely infected,
+undiagnosed, diagnosed, treated, viral suppression and AIDS
+compartments. People susceptible to HIV ($S$) progress to the
+acute-infection phase ($A$) according to the force of infection
+($\lambda$), which depends on the HIV transmission rate, estimated
+from the country-specific incidence and prevalence data
+(\autoref{model_fitting}), adjusted for the current number of acutely
+infected, untreated or ineffectively treated, and viral suppression
+PLHIV.  Acute infection is characterized by high viral loads and lasts
+an average of 2.90 [95\% confidence interval 1.23, 6.00]\;months
+\cite{Hollingsworth2008-iy}.  (We converted these durations to rates
+like $1 / 2.90\;\text{month$^{-1}$} \approx 4.14\;\text{y$^{-1}$}$ and
+set the parameter using random samples from
+$\Triangular(2, 4.14, 9.6)\;\text{y$^{-1}$}$ to capture the
+uncertainty in its value.)  We assumed that people remain undiagnosed
+during their acute infection phase and during at least some of the
+subsequent period of clinical latency (i.e., the undiagnosed
+compartment $U$). After acute infection, people move into the chronic
+undiagnosed class ($U$).  People in the undiagnosed class will be
+diagnosed at the rate $\alpha$, which is determined by the country's
+current diagnosis level and its diagnosis target.  Diagnosed people
+($D$) transition to the treated compartment ($T$) upon starting ART at
+the rate $\phi$, dependent on the country's current treatment level
+and its treatment target.  After some time, treated people then to the
+viral-suppression class ($V$), at the rate $\gamma$.  We took $\gamma$
+as a random sample from $\Uniform(0.5, 1.5)\;\text{y$^{-1}$}$, that
+is, viral suppression occurs after between 8 months and 2 years on
+treatment \cite{Currie2009-yz}.  The disengagement from treatment
+moves people from treated ($T$) and viral suppression ($V$) at the
+rate $\psi$, dependent on the current level of viral suppression and
+the country's target, back to the diagnosed class ($D$).
+
+PLHIV without viral suppression (compartments $U$, $D$, and $T$)
+develop AIDS (compartment $W$) after an average duration of 10.4 y
+\cite{Morgan2002-cq}, giving the transition rate
+$\sigma = 0.1064\;\text{y$^{-1}$}$.  People who have achieved viral
+suppression ($V$) develop AIDS at rate $\theta$, slower than PLHIV
+without viral suppression.  People with viral suppression are
+estimated to live 5--8 y shorter lives than the non-HIV infected
+\cite{Unaids2014-ue, Samji2013-kf}, which we quantified by randomly
+sampling the parameter $\omega$ from $\Uniform(5, 8)\;\text{y}$.
+Assuming no relapse to untreated, the duration of viral suppression is
+\begin{equation}
+  \frac{1}{\theta + \mu} = \frac{1}{\mu} - \omega - \frac{1}{\nu}.
+\end{equation}
+The term to the left of the equals sign is the time until leaving
+viral suppression by either progression to AIDS (at rate $\theta$) or
+background mortality (at rate $\mu$).  The term to the right of the
+equals sign is the lifespan of the non-HIV infected, minus the
+reduction in life due to having HIV with viral suppression, minus the
+duration of the AIDS stage.  Solving for $\theta$ gives the rate of
+progression to AIDS with viral suppression as
+\begin{equation}
+  \label{theta}
+  \theta = \frac{1}{1/\mu - \omega - 1/\nu} - \mu.
+\end{equation}
+
+Susceptible people are vaccinated at rate $\zeta$, transitioning into
+the vaccinated compartment ($R$), where the vaccine reduces their
+force of infection by the efficacy factor $\rho$.
+
+Transition rates between the undiagnosed ($U$), diagnosed ($D$),
+treated ($T$), and viral-suppression classes ($V$) are determined by
+the proportion of PLHIV diagnosed
+\begin{equation}
+  p_D = \frac{D + T + V + W}{A + U + D + T + V + W},
+\end{equation}
+the proportion of diagnosed people on ART
+\begin{equation}
+  p_T = \frac{T + V + W}{D + T + V + W},
+\end{equation}
+the proportion of people on ART who have
+achieved viral suppression
+\begin{equation}
+  p_V = \frac{V}{T + V},
+\end{equation}
+and the proportion of susceptible people vaccinated is
+\begin{equation}
+  p_R = \frac{R}{S + R}.
+\end{equation}
+
+We can implement the vaccination compartment in the same way as the
+other controls. When we begin vaccination in 2020 (also 2025 in
+scenario analysis), the initial vaccination level is 0\%. The coverage
+will increase linearly by 25\% per year (also 10\% per year in
+scenario analysis). The coverage will continue to increase linearly
+until it reaches 70\% coverage (50\% \& 90\% in scenario analysis) and
+then stay constant for the remainder of the time period.
+
+95--95--95 goal is implemented subsequently after meeting 90--90--90
+by 2020 by increasing $p_D$, $p_T$, and $p_V$ to 95--95--95 levels by
+2030 linearly. \comment{@Jan, We use the Heaveside function here too?
+JM: Yes.  I'll write it at some point.}
+
+The rates are applied when the proportions of $p_D$, $p_T$, $p_V$, and
+$p_R$ are below the target levels:
+\begin{equation}
+  \label{target_rates}
+  \begin{split}
+    \alpha(t) &= \alpha_{\max} H\left(p_D^*(t) - p_D(t)\right),
+    \\
+    \phi(t) &= \phi_{\max} H\left(p_T^*(t) - p_T(t)\right),
+    \\
+    \psi(t) &= \psi_{\max} H\left(p_V(t) - p_V^*(t)\right),
+    \\
+    \zeta(t) &= \zeta_{\max} H\left(p^{*}_{R}(t) - p_{W}(t)\right),
+  \end{split}
+\end{equation}
+where $H(x)$ is the Heaviside function
+\begin{equation}
+  H(x) =
+  \begin{cases}
+    0 & \text{if $x < 0$},
+    \\
+    1 & \text{if $x > 0$}.
+  \end{cases}
+\end{equation}
+
+The discontinuity of the Heaviside function makes numerical solution
+difficult.  Instead, replace $H$ with the continuous piecewise linear
+function
+\begin{equation}
+  H(x) =
+  \begin{cases}
+    0 & \text{if $x < 0$},
+    \\
+    x / \chi & \text{if $0 \leq x \leq \chi$},
+    \\
+    1 & \text{if $x > \chi$},
+  \end{cases}
+\end{equation}
+with some small value of $\chi$.
+
+The model equations are
+\begin{equation}
+  \label{model_eqns}
+  \begin{split}
+    \frac{\md S}{\md t} &= B N - \lambda S - \zeta S- \mu S,
+    \\
+    \frac{\md R}{\md t} & = \zeta S - (1 - \rho) \lambda R - \mu R,
+    \\
+    \frac{\md A}{\md t} &= \lambda S + (1 - \rho) \lambda R - \delta A - \mu A,
+    \\
+    \frac{\md U}{\md t} &= \delta A - \alpha U - \mu U - \sigma U,
+    \\
+    \frac{\md D}{\md t} &=  \alpha U + \psi T + \psi V
+    - \phi D - \mu D - \sigma D,
+    \\
+    \frac{\md T}{\md t} &= \phi D - \psi T - \gamma T - \mu T
+    - \sigma T,
+    \\
+    \frac{\md V}{\md t} &= \gamma T - \psi V - \mu V - \theta V,
+    \\
+    \frac{\md W}{\md t} &= \sigma U + \sigma D + \sigma T + \theta V -
+    \nu W,
+  \end{split}
+\end{equation}
+with force of infection
+\begin{equation}
+  \label{force_of_infection}
+  \begin{split}
+    \lambda &= \frac{\beta_A A + \beta_U (U + D + T) + \beta_T V}{N},
+    \\
+    N &= S + R +  A + U + D + T + V,
+    \\
+    \beta_x &= T \left[1 - (1 - \tau_x)^n\right]
+    \text{ for $x \in \{A, U, T\}$},
+    \\
+    \tau_T &= \varepsilon \tau_U.
+  \end{split}
+\end{equation}
+
+The targets for the proportions $p_D$, $p_T$, and $p_V$ in the
+achievement of 90--90--90 all operate under the following assumption:
+if the initial level $p_x(0)$ is less than $90\%$, the proportion will
+increase linearly in the first 5 years and then stay at $90\%$ for the
+remaining time; and if the initial level is at $90\%$ or above, the
+proportion will remain constant for the duration of the study:
+\begin{equation}
+  p_x^*(t)
+  = p_x(0) + \left[
+    \max\left\{0.9, p_x(0)\right\} - p_x(0)
+  \right]
+  \min\left\{\frac{t}{5}, 1\right\},
+\end{equation}
+for $x \in \{D, T, V\}$.
+
+$\Uniform(a, b)$ is the uniform random variable with minimum $a$
+and maximum $b$: it has density function
+\begin{equation}
+  \label{uniform}
+  p_{\Uniform}(x) =
+  \begin{cases}
+    \frac{1}{b - a} & \text{if $a \leq x \leq b$,}
+    \\
+    0 & \text{otherwise.}
+  \end{cases}
+\end{equation}
+We defined the mode for the uniform distribution to be the midpoint
+$\frac{b - a}{2}$.
+%
+$\Triangular(a, b, c)$ is the triangular random variable
+distribution with minimum $a$, mode $b$, and maximum $c$: it has
+density function
+\begin{equation}
+  \label{triangular}
+  p_{\Triangular}(x) =
+  \begin{cases}
+    \frac{2 (x - a)}{(c - a)(b - a)} & \text{if $a \leq x \leq b$,}
+    \\
+    \frac{2 (c - x)}{(c - a)(c - b)} & \text{if $b \leq x \leq c$,}
+    \\
+    0 & \text{otherwise.}
+  \end{cases}
+\end{equation}
+$\BetaPERT(a, b, c)$ is the beta-PERT probability distribution
+\cite{malcom1959} with minimum $a$, mode $b$, and maximum $c$: it has
+density function
+\begin{equation}
+  \label{betaPERT}
+  p_{\BetaPERT}(x) =
+  \begin{cases}
+    \frac{(x - a)^{v - 1} (c - x)^{w - 1}}{(c - a)^{v + w - 2} B(v, w)}
+    & \text{if $a \leq x \leq c$,}
+    \\
+    0 & \text{otherwise,}
+  \end{cases}
+\end{equation}
+where
+\begin{equation}
+  \begin{split}
+    \mu &= \frac{a + \lambda b + c}{\lambda + 2},
+    \\
+    v &= \frac{(\mu - a)(2 b - a - c)}{(b - \mu) (c - a)},
+    \\
+    w &= \frac{v (a - \mu)}{\mu - c},
+  \end{split}
+\end{equation}
+and $B(v, w)$ is the standard beta function \cite[\S 6.2]{davis1972}.
+We used the standard value of $\lambda = 4$.
+%
+$\Lognormal(\mu, \sigma^2)$ is the lognormal random variable: it has
+density function
+\begin{equation}
+  p_{\Lognormal}(x) = \frac{1}{x \sigma \sqrt{2 \pi}}
+  \exp\left(- \frac{\left(\log x - \mu\right)^2}{2 \sigma^2}\right).
+\end{equation}
 
@@
 \section{Data sources}
+\label{data_sources}
+
+For 127 countries, we found sufficient data to parametrize our model:
+these data consisted of estimates of longitudinal HIV incidence and
+prevalence for ages 15–49 years starting as early as 1990 in some
+countries and running through 2015, along with basic demographics
+(\autoref{data_sources}).
 
@@
 
-\section{Mathematical model}
-
-\begin{figure}
-  \centering
-  \input{diagram}
-  \caption{Model diagram.}
-  \label{model_diag}
-\end{figure}
-
-Our continuous-time, compartmental model consists of 8 health states:
-susceptible to HIV infection, vaccinated against HIV, acute HIV
-infection, undiagnosed HIV infection, diagnosed but untreated HIV
-infection, treated without achieving viral suppression, achieved viral
-suppression, and having AIDS (Figure \ref{model_diag}). Transitions
-between states are governed by a series of differential equations
-parameterized using rates estimated from other studies and from
-incidence and prevalence data (Table \ref{model_param}).
-
-\begin{table}
-  \begin{center}
-    \begin{tabular}{cp{4cm}llc}
-      \hline
-      Symbol & Definition & Value & Sampling Distribution & Source \\ \hline
-      $\delta$	& Rate of leaving acute phase of HIV infection & 4.1379/year & T (4.1379, 2, 9.6) & \cite{Hollingsworth2008-iy} \\
-      $\sigma$	& Rate of developing AIDS among non-virally suppressed individuals
-                          & 0.1064/year & & \cite{Morgan2002-cq} \\
-      $\gamma$ & Rate of viral suppression & 1/year & U (0.5, 1.5) & \cite{Currie2009-yz} \\
-      $\upsilon$	& Death rate from AIDS & 0.5/year &  & \cite{Morgan2002-cq} \\
-      $\omega$	& Reduction in life years for treated PLHIV & 5 & U (5, 8) & \cite{Unaids2014-ue, Samji2013-kf}\\
-      $\beta_{A}$	& Transmission probability during acute phase & 0.0082 & T (0.0082, 0.0039, 0.0150) & \cite{Skarbinski2015-ni,Wawer2005-us}\\
-      $\beta_{U}$	& Transmission probability after acute phase & 0.0014 & T (0.0014, 0.00077, 0.00251) & \cite{Hughes2012-so}\\
-      $\varepsilon$	& Proportional reduction of transmission with treatment & 0.08 & $\beta$ (0.08, 0.002, 0.57)& \cite{Donnell2010-xo}\\
-      $n$			& Sex acts per year & 102 & U (96, 108) & \cite{Wawer2005-us,Abdool_Karim2010-cm}\\ \hline
-    \end{tabular}
-    \caption{Parameters used in model. (T: triangular distribution, U:
-      uniform distribution, $\beta$: beta distribution).}
-    \label{model_param}
-  \end{center}
-\end{table}
-
-The PLHIV population was comprised of people in the acutely infected,
-undiagnosed, diagnosed, treated, viral suppression and AIDS
-compartments. People susceptible to HIV ($S$) progress to the
-acute-infection phase ($A$) according to the force of infection, which
-depends on the HIV transmission rate, estimated from the
-country-specific incidence and prevalence data
-(\autoref{model_fitting}), adjusted for the current number of acutely
-infected, untreated or ineffectively treated, and viral suppression
-PLHIV.  Acute infection is characterized by high viral loads and lasts
-88 [XX, YY] days \cite{Hollingsworth2008-iy}. We assumed that people
-remain undiagnosed during their acute infection phase and during at
-least some of the subsequent period of clinical latency (i.e., the
-undiagnosed compartment). After acute infection, people move into the
-chronic undiagnosed class ($U$).  People in the undiagnosed class will
-be diagnosed at a rate determined by the country's initial diagnosis
-level and potential progress towards the UNAIDS targets.  Diagnosed
-people (compartment $D$) transition to the treated compartment ($T$)
-upon starting ART at a rate of $\phi$ , and then to the
-viral-suppression class ($V$) after achieving viral suppression
-through treatment retention at a rate of $\gamma$. The disengagement
-from treatment moves people from treated ($T$) and viral suppression
-($V$) at a rate of $\omega$ back to the diagnosed class ($D$). Rates
-of movement between the undiagnosed ($U$), diagnosed ($D$), treated
-($T$) and viral-suppression classes ($V$) are determined by the
-proportions of PLHIV diagnosed ($p_{D}$), proportion of diagnosed
-people on ART ($p_{T}$), and the proportion of people on ART who have
-achieved viral suppression ($p_{V}$). PLHIV in $U$, $D$, $T$, and $V$
-classes develop AIDS (compartment $W$) after an average duration
-dependent on viral suppression status. People who have achieved viral
-suppression ($V$) take longer to develop AIDS ($1/\theta$), than those
-who are in the other PLHIV classes ($1/\sigma$). People who are
-susceptible to HIV are vaccinated at rate $\zeta$, transitioning into
-the vaccinated compartment ($R$), where the vaccine reduces their
-force of infection by the efficacy factor $\rho$.  The model equations
-are
-\begin{equation}
-  \label{model_eqns}
-  \begin{split}
-    \frac{\md S}{\md t} &= B N - \lambda S - \zeta S- \mu S,
-    \\
-    \frac{\md R}{\md t} & = \zeta S - (1 - \rho) \lambda R - \mu R,
-    \\
-    \frac{\md A}{\md t} &= \lambda S + (1 - \rho) \lambda R - \delta A - \mu A,
-    \\
-    \frac{\md U}{\md t} &= \delta A - \alpha U - \mu U - \sigma U,
-    \\
-    \frac{\md D}{\md t} &=  \alpha U + \psi T + \psi V
-    - \phi D - \mu D - \sigma D,
-    \\
-    \frac{\md T}{\md t} &= \phi D - \psi T - \gamma T - \mu T
-    - \sigma T,
-    \\
-    \frac{\md V}{\md t} &= \gamma T - \psi V - \mu V - \theta V,
-    \\
-    \frac{\md W}{\md t} &= \sigma U + \sigma D + \sigma T + \theta V -
-    \nu W,
-  \end{split}
-\end{equation}
-with force of infection
-\begin{equation}
-  \label{force_of_infection}
-  \begin{split}
-    \lambda &= \frac{\beta_A A + \beta_U (U + D + T) + \beta_T V}{N},
-    \\
-    N &= S + R +  A + U + D + T + V,
-    \\
-    \beta_x &= c \left[1 - (1 - \tau_x)^n\right]
-    \text{ for $x \in \{A, U, T\}$},
-    \\
-    \tau_T &= (1 - \epsilon) \tau_U.
-  \end{split}
-\end{equation}
-The rate of developing AIDS among those who have acheived viral
-suppression is
-\begin{equation}
- \theta = \frac{1}{1/\mu-\omega-1/\nu}.
-\end{equation}
-
-The proportion diagnosed is
-\begin{equation}
-  p_D = \frac{D + T + V + W}{A + U + D + T + V + W},
-\end{equation}
-the proportion treated is
-\begin{equation}
-  p_T = \frac{T + V + W}{D + T + V + W},
-\end{equation}
-the proportion with viral suppression is
-\begin{equation}
-  p_V = \frac{V}{T + V},
-\end{equation}
-and the proportion of people vaccinated is
-\begin{equation}
-  P_{V} = \frac{R}{S+R}.
-\end{equation}
-
-The targets for the proportions $p_D$, $p_T$, and $p_V$ in the
-achievement of 90--90--90 all operate under the following assumption:
-if the initial level $p_x(0)$ is less than $90\%$, the proportion will
-increase linearly in the first 5 years and then stay at $90\%$ for the
-remaining time; and if the initial level is at $90\%$ or above, the
-proportion will remain constant for the duration of the study:
-\begin{equation}
-  p_x^*(t)
-  = p_x(0) + \left[
-    \max\left\{0.9, p_x(0)\right\} - p_x(0)
-  \right]
-  \min\left\{\frac{t}{5}, 1\right\},
-\end{equation}
-for $x \in \{D, T, V\}$.
-
-We can implement the vaccination compartment in the same way as the
-other controls. When we begin vaccination in 2020 (also 2025 in
-scenario analysis), the initial vaccination level is 0\%. The coverage
-will increase linearly by 25\% per year (also 10\% per year in
-scenario analysis). The coverage will continue to increase linearly
-until it reaches 70\% coverage (50\% \& 90\% in scenario analysis) and
-then stay constant for the remainder of the time period.
-
-95--95--95 goal is implemented subsequently after meeting 90--90--90
-by 2020 by increasing $p_D$, $p_T$, and $p_V$ to 95--95--95 levels by
-2030 linearly. \comment{@Jan, We use the Heaveside function here too?
-JM: Yes.  I'll write it at some point.}
-
-The rates are applied when the proportions of $p_D$, $p_T$, and $p_V$
-are below the target levels:
-\begin{equation}
-  \begin{split}
-    \alpha(t) &= \alpha_{\max} H\left(p_D^*(t) - p_D(t)\right),
-    \\
-    \phi(t) &= \phi_{\max} H\left(p_T^*(t) - p_T(t)\right),
-    \\
-    \psi(t) &= \psi_{\max} H\left(p_V(t) - p_V^*(t)\right),
-    \\
-    \zeta(t) &= \zeta_{max} H\left(P^{*}_{V}(t)-P_{V}(t)\right),
-  \end{split}
-\end{equation}
-where $H(x)$ is the Heaviside function
-\begin{equation}
-  H(x) =
-  \begin{cases}
-    0 & \text{if $x < 0$},
-    \\
-    1 & \text{if $x > 0$}.
-  \end{cases}
-\end{equation}
-
-The discontinuity of the Heaviside function makes numerical solution
-difficult.  Instead, replace $H$ with the continuous piecewise linear
-function
-\begin{equation}
-  H(x) =
-  \begin{cases}
-    0 & \text{if $x < 0$},
-    \\
-    x / \chi & \text{if $0 \leq x \leq \chi$},
-    \\
-    1 & \text{if $x > \chi$},
-  \end{cases}
-\end{equation}
-with some small value of $\chi$.
-
 \section{Model fitting}
 \label{model_fitting}
+
+Using available historical data for incidence and prevalence, and
+published transmission estimates, we estimated transmission rates for
+people with acute infection, unsuppressed viral load and suppressed
+viral load. Our calibration method provided a recent snapshot of
+country-specific transmission, while using historical data to smooth
+out variations.
 
@@
 transmission rate distributions. The parameters were sampled using
-latin hypercube sampling \cite{}
-and the variance reduction technique of running different
-interventions with random parameter values \cite{}.
+latin hypercube sampling \cite{blower1994} and the variance reduction
+technique of running different interventions with random parameter
+values \cite{shechter2006}.
 
@@
 
-We calculated partial rank correlation coefficients (PRCC) \cite{}
-to measure the independent effect of each parameter on model
-projections of HIV incidence (\autoref{PRCCs}). Furthermore, due to
-uncertainty surrounding the prospective vaccine, we obtained model
-projections using six additional vaccine scenarios by considering
-alternative estimates of efficacy (30\%, 70\%), coverage (50\%, 90\%),
-speed of scale up (10\% coverage per year), and first year of
-availability (2025).
+We calculated partial rank correlation coefficients (PRCC)
+\cite{blower1994} to measure the independent effect of each parameter
+on model projections of HIV incidence (\autoref{PRCCs}). Furthermore,
+due to uncertainty surrounding the prospective vaccine, we obtained
+model projections using six additional vaccine scenarios by
+considering alternative estimates of efficacy (30\%, 70\%), coverage
+(50\%, 90\%), speed of scale up (10\% coverage per year), and first
+year of availability (2025).
 

### 2016-08-18 Documents/supplementary_text.tex
More hacking on supplement.

@@
 
-We developed a continuous-time, compartmental model consisting of 8
-health states (\autoref{model_diag}): susceptible to HIV infection
-($S$), vaccinated against HIV ($R$), acute HIV infection ($A$),
-undiagnosed HIV infection ($U$), diagnosed but untreated HIV infection
-($D$), treated without viral suppression ($T$), viral suppression
-($V$), and having AIDS ($W$).  Transitions between states are governed
-by a series of differential equations parametrized using rates
-estimated from other studies and from incidence and prevalence data
-(Table \ref{model_param}).  The model is deterministic, but
-uncertainty in the parameters is treated by running the model with
-many different samples from the parameter distributions.
+We developed a continuous-time, compartmental model that divides
+people aged 15 years and older into 8 health states
+(\autoref{model_diag}): susceptible to HIV infection ($S$), vaccinated
+against HIV ($R$), acute HIV infection ($A$), undiagnosed HIV
+infection ($U$), diagnosed but untreated HIV infection ($D$), treated
+without viral suppression ($T$), viral suppression ($V$), and having
+AIDS ($W$).  We chose to consider only people aged 15 years and older
+because they are the vast majority of PLHIV (93\% in 2014
+\cite{UNICEF}).  Transitions between states are governed by a series
+of differential equations parametrized using rates estimated from
+other studies and from incidence and prevalence data (Table
+\ref{model_param}).  The model is deterministic, but uncertainty in
+the parameters is treated by running the model with many different
+samples from the parameter distributions and summarizing the model
+outcomes using the median, 1st and 3rd quartiles (i.e., 25th and 75th
+percentiles), and 5th and 95th percentiles.
 
@@
       \hline
+      $\mu$ & Background death rate & Country specific
+      & \cite{World_Development_Indicators2013-ee} \\
+      $B$ & Recruitment rate & Country specific
+      & \cite{World_Development_Indicators2013-ee, WorldBankpg} \\
       $\delta$	& Rate of leaving acute infection
@@
       & \cite{Wawer2005-us,Abdool_Karim2010-cm}\\
-      $\mu$ & Background death rate & Country specific
-      & \cite{World_Development_Indicators2013-ee} \\
-      $B$ & Birth rate & Country specific
-      & \cite{World_Development_Indicators2013-ee, WorldBankpg} \\
       $\alpha$ & Diagnosis rate & See eqs.~(\ref{target_rates}) & --- \\
@@
 
-Birth and death.
+The background mortality rate ($\mu$) in each of the 127 countries was
+collected from published estimates
+\cite{World_Development_Indicators2013-ee}.  The recruitment rate into
+the 15 age group was 
+including population
+growth rate \cite{WorldBankpg}, death rate
+\cite{World_Development_Indicators2013-ee}, and number of people aged
+15--49 years \cite{The_World_Bank2016-fd}
 

### 2016-08-19 Documents/supplementary_text.tex
More hacking on supplement.

@@
 
-\usepackage[utf8x]{inputenc}
+\usepackage[utf8]{inputenc}
 \usepackage{microtype}
@@
 
-\usepackage[numbers, round, sort&compress]{natbib}
-\renewcommand{\citenumfont}{\itshape}  % Citations get italics numbers
-\makeatletter
-\renewcommand\NAT@open{(\hspace*{-0.3ex}}   % Tweak spacing.
-\renewcommand\@biblabel[1]{#1.}  % Reference list doesn't use square brackets.
-\makeatother
-
 \usepackage[noblocks]{authblk}
@@
 
-% Load hyperref after the other stuff above.
 \usepackage[pdfborder={0 0 0}]{hyperref}
-\usepackage{hypernat}
+
+\usepackage[style = science, article-title = true, maxnames = 100]{biblatex}
+\addbibresource{supplementary_text.bib}
+\newcommand{\labeltitlepunc}{}
+\DeclareBibliographyDriver{incollection}{%
+  \usebibmacro{bibindex}%
+  \usebibmacro{begentry}%
+  \usebibmacro{author/translator+others}%
+  \setunit{\labelnamepunct}\newblock
+  \printlist{language}%
+  \newunit\newblock
+  \usebibmacro{byauthor}%
+  \newunit\newblock
+  \usebibmacro{title}%
+  \usebibmacro{in:}%
+  \usebibmacro{maintitle+booktitle}%
+  \newunit\newblock
+  \usebibmacro{byeditor+others}%
+  \newunit\newblock
+  \printfield{volumes}%
+  \newunit\newblock
+  \printfield{note}%
+  \newunit\newblock
+  \usebibmacro{publisher+location+date}%
+  \newunit\newblock
+  \printfield{volume}
+  \newunit
+  \usebibmacro{chapter+pages}%
+  \newunit\newblock
+  \iftoggle{bbx:isbn}
+    {\printfield{isbn}}
+    {}%
+  \newunit\newblock
+  \usebibmacro{doi+eprint+url}%
+  \newunit\newblock
+  \usebibmacro{addendum+pubstate}%
+  \setunit{\bibpagerefpunct}\newblock
+  \usebibmacro{pageref}%
+  \newunit\newblock
+  \usebibmacro{related}%
+  \usebibmacro{finentry}%
+}
 
@@
 We developed a continuous-time, compartmental model that divides
-people aged 15 years and older into 8 health states
+people aged $15\;\text{y}$ and older into 8 health states
 (\autoref{model_diag}): susceptible to HIV infection ($S$), vaccinated
@@
 without viral suppression ($T$), viral suppression ($V$), and having
-AIDS ($W$).  We chose to consider only people aged 15 years and older
-because they are the vast majority of PLHIV (93\% in 2014
-\cite{UNICEF}).  Transitions between states are governed by a series
-of differential equations parametrized using rates estimated from
-other studies and from incidence and prevalence data (Table
-\ref{model_param}).  The model is deterministic, but uncertainty in
-the parameters is treated by running the model with many different
-samples from the parameter distributions and summarizing the model
-outcomes using the median, 1st and 3rd quartiles (i.e., 25th and 75th
-percentiles), and 5th and 95th percentiles.
+AIDS ($W$).  We chose to consider only people aged $15\;\text{y}$ and
+older because they are the vast majority of PLHIV, 93\% in 2014
+\cite{UNICEF}, and because HIV and demographic data are often
+stratified into these ages \cite[e.g.,][]{Unaids2016-an}.  Transitions
+between model states are governed by a series of differential
+equations parametrized using rates estimated from other studies and
+from incidence and prevalence data (Table \ref{model_param}).  The
+model is deterministic, but uncertainty in the parameters is treated
+by running the model with many different samples from the parameter
+distributions and summarizing the model outcomes using the median, 1st
+and 3rd quartiles (i.e., 25th and 75th percentiles), and 5th and 95th
+percentiles.
 
@@
 
-The background mortality rate ($\mu$) in each of the 127 countries was
-collected from published estimates
-\cite{World_Development_Indicators2013-ee}.  The recruitment rate into
-the 15 age group was 
-including population
-growth rate \cite{WorldBankpg}, death rate
-\cite{World_Development_Indicators2013-ee}, and number of people aged
-15--49 years \cite{The_World_Bank2016-fd}
-
 People living with HIV (PLHIV) are divided among the acutely infected,
@@
 \end{equation}
+
+The background mortality rate ($\mu$) in each of the 127 countries was
+collected from published estimates
+\cite{World_Development_Indicators2013-ee}.  The recruitment rate into
+ages $15\;\text{y}$ and older group ($B$) was set by the difference
+between the population growth rate \cite{WorldBankpg} and the
+background mortality rate \cite{World_Development_Indicators2013-ee}.
+\comment{Add mortality and population growth to data sources.}
+
+The number of people aged 15--49 years \cite{The_World_Bank2016-fd}
 
@@
 \clearpage
-\bibliographystyle{science_nat}
-\bibliography{supplementary_text}
+\printbibliography
 

### 2016-08-19 Documents/supplementary_text.tex
Working on supplement.

@@
 \renewcommand{\figurename}{Fig.}
-\renewcommand{\sectionautorefname}{Section}
 
@@
 We developed a continuous-time, compartmental model that divides
-people aged $15\;\text{y}$ and older into 8 health states
-(\autoref{model_diag}): susceptible to HIV infection ($S$), vaccinated
+people aged $15$\;y and older into non-overlapping HIV states.  We
+chose to consider only these ages because they are the vast majority
+of PLHIV, 93\% in 2014 \cite{UNICEF}, and because HIV and demographic
+data are often stratified into these ages, although some data used to
+parametrize the model was only available for ages $15$--$49$ rather
+than for ages $15$ and older.  The background mortality rate ($\mu$)
+in each of the 127 countries was collected from published estimates
+\cite{World_Development_Indicators2013-ee}.  The recruitment rate into
+ages $15\;\text{y}$ and older group ($B$) was set by the difference
+between the country's population growth rate \cite{WorldBankpg} and
+its background mortality rate
+\cite{World_Development_Indicators2013-ee}, as would be true if the
+population was at its stable age structure.
+
+Our model has 8 HIV states (\autoref{model_diag}): susceptible to HIV
+infection ($S$ is the number of people susceptible), vaccinated
 against HIV ($R$), acute HIV infection ($A$), undiagnosed HIV
@@
 without viral suppression ($T$), viral suppression ($V$), and having
-AIDS ($W$).  We chose to consider only people aged $15\;\text{y}$ and
-older because they are the vast majority of PLHIV, 93\% in 2014
-\cite{UNICEF}, and because HIV and demographic data are often
-stratified into these ages \cite[e.g.,][]{Unaids2016-an}.  Transitions
-between model states are governed by a series of differential
-equations parametrized using rates estimated from other studies and
-from incidence and prevalence data (Table \ref{model_param}).  The
-model is deterministic, but uncertainty in the parameters is treated
-by running the model with many different samples from the parameter
-distributions and summarizing the model outcomes using the median, 1st
-and 3rd quartiles (i.e., 25th and 75th percentiles), and 5th and 95th
-percentiles.
+AIDS ($W$).  Transitions between model states are governed by a series
+of differential equations parametrized using values estimated from
+other studies and from incidence and prevalence data
+(\autoref{model_param}).  The model is deterministic, but uncertainty
+in the parameters is treated by running the model many times with
+samples from the parameter distributions and summarizing the model
+outcomes using the median, 1st and 3rd quartiles (i.e., 25th and 75th
+percentiles), and 5th and 95th percentiles.
 
@@
       \hline
-      $\mu$ & Background death rate & Country specific
+      $\mu$ & Background death rate & Country specific, see Table S2
       & \cite{World_Development_Indicators2013-ee} \\
-      $B$ & Recruitment rate & Country specific
+      $B$ & Recruitment rate & Country specific, see Table S2
       & \cite{World_Development_Indicators2013-ee, WorldBankpg} \\
@@
       & \cite{Donnell2010-xo} \\
-      $n$ & Sex acts per year & $\Uniform$(96, 108)
+      $n$ & Coital acts per year & $\Uniform$(96, 108)
       & \cite{Wawer2005-us,Abdool_Karim2010-cm}\\
-      $\alpha$ & Diagnosis rate & See eqs.~(\ref{target_rates}) & --- \\
-      $\phi$ & Treatment rate & See eqs.~(\ref{target_rates}) & --- \\
-      $\psi$ & Rate of relapse to untreated & See eqs.~(\ref{target_rates})
+      $\alpha$ & Diagnosis rate & See eq.~(\ref{diagnosis_rate}) & --- \\
+      $\phi$ & Treatment rate & See eq.~(\ref{treatment_rate}) & --- \\
+      $\psi$ & Rate of relapse to untreated & See eq.~(\ref{relapse_rate})
       & --- \\
-      $\zeta$ & Vaccination rate & See eqs.~(\ref{target_rates}) & --- \\
+      $\zeta$ & Vaccination rate & See eqs.~(\ref{vaccination_rate}) & --- \\
       \hline
     \end{tabularx}
-    \caption{Model parameters. $\Triangular$, $\Uniform$,
-      and $\BetaPERT$ are sampling distributions: see text for a
-      full description.  For vaccine efficacy, $50\%$ was the
-      baseline, and $30\%$ and $70\%$ were also used in scenario
-      analysis.}
+    \caption{Model parameters. $\Triangular$, $\Uniform$, and
+      $\BetaPERT$ are sampling distributions: see
+      \autoref{uncertainty} for a full description.  For vaccine
+      efficacy, $50\%$ was the baseline, and $30\%$ and $70\%$ were
+      also used in scenario analysis.}
     \label{model_param}
@@
 
-People living with HIV (PLHIV) are divided among the acutely infected,
-undiagnosed, diagnosed, treated, viral suppression and AIDS
-compartments. People susceptible to HIV ($S$) progress to the
-acute-infection phase ($A$) according to the force of infection
-($\lambda$), which depends on the HIV transmission rate, estimated
-from the country-specific incidence and prevalence data
-(\autoref{model_fitting}), adjusted for the current number of acutely
-infected, untreated or ineffectively treated, and viral suppression
-PLHIV.  Acute infection is characterized by high viral loads and lasts
-an average of 2.90 [95\% confidence interval 1.23, 6.00]\;months
-\cite{Hollingsworth2008-iy}.  (We converted these durations to rates
-like $1 / 2.90\;\text{month$^{-1}$} \approx 4.14\;\text{y$^{-1}$}$ and
-set the parameter using random samples from
+People susceptible to HIV ($S$) progress to acute infection ($A$)
+according to the force of infection ($\lambda$,
+eq.~\eqref{force_of_infection}), which depends on the HIV transmission
+rate, estimated from the country-specific incidence and prevalence
+data (\autoref{model_fitting}), adjusted for the current number of
+acutely infected, untreated or ineffectively treated, and viral
+suppression PLHIV.  Acute infection is characterized by high viral
+loads and lasts an average of 2.90 [95\% confidence interval 1.23,
+6.00]\;months \cite{Hollingsworth2008-iy}.  (We converted these
+durations to rates like $1 / 2.90\;\text{month$^{-1}$} \approx
+4.14\;\text{y$^{-1}$}$ and set the parameter using random samples from
 $\Triangular(2, 4.14, 9.6)\;\text{y$^{-1}$}$ to capture the
-uncertainty in its value.)  We assumed that people remain undiagnosed
-during their acute infection phase and during at least some of the
-subsequent period of clinical latency (i.e., the undiagnosed
-compartment $U$). After acute infection, people move into the chronic
-undiagnosed class ($U$).  People in the undiagnosed class will be
-diagnosed at the rate $\alpha$, which is determined by the country's
-current diagnosis level and its diagnosis target.  Diagnosed people
+uncertainty in its value.  See \autoref{uncertainty} for the
+definition of $\Triangular(a, b, c)$ and other distributions.)  We
+assumed that people remain undiagnosed during their acute infection
+phase. After acute infection, people move into the chronic undiagnosed
+class ($U$).  People in the undiagnosed class will be diagnosed at the
+rate $\alpha$, which is determined by the country's current diagnosis
+level and its diagnosis target (\autoref{targets}).  Diagnosed people
 ($D$) transition to the treated compartment ($T$) upon starting ART at
 the rate $\phi$, dependent on the country's current treatment level
-and its treatment target.  After some time, treated people then to the
-viral-suppression class ($V$), at the rate $\gamma$.  We took $\gamma$
-as a random sample from $\Uniform(0.5, 1.5)\;\text{y$^{-1}$}$, that
-is, viral suppression occurs after between 8 months and 2 years on
-treatment \cite{Currie2009-yz}.  The disengagement from treatment
-moves people from treated ($T$) and viral suppression ($V$) at the
-rate $\psi$, dependent on the current level of viral suppression and
-the country's target, back to the diagnosed class ($D$).
+and its treatment target (\autoref{targets}).  After some time,
+treated people then transition to the viral-suppression class ($V$),
+at the rate $\gamma$.  We took $\gamma$ as a random sample from
+$\Uniform(0.5, 1.5)\;\text{y$^{-1}$}$, that is, viral suppression
+occurs after between 8 months and 2 years on treatment
+\cite{Currie2009-yz}.  The disengagement from treatment moves people
+from treated ($T$) and viral suppression ($V$) at the rate $\psi$,
+dependent on the current level of viral suppression and the country's
+target (\autoref{targets}), back to the diagnosed class ($D$).
 
@@
 develop AIDS (compartment $W$) after an average duration of 10.4 y
-\cite{Morgan2002-cq}, giving the transition rate
+\cite{Morgan2002-cq}, i.e., with transition rate
 $\sigma = 0.1064\;\text{y$^{-1}$}$.  People who have achieved viral
@@
 without viral suppression.  People with viral suppression are
-estimated to live 5--8 y shorter lives than the non-HIV infected
+estimated to live $5$--$8$\;y shorter lives than the non-HIV infected
 \cite{Unaids2014-ue, Samji2013-kf}, which we quantified by randomly
@@
 
-The background mortality rate ($\mu$) in each of the 127 countries was
-collected from published estimates
-\cite{World_Development_Indicators2013-ee}.  The recruitment rate into
-ages $15\;\text{y}$ and older group ($B$) was set by the difference
-between the population growth rate \cite{WorldBankpg} and the
-background mortality rate \cite{World_Development_Indicators2013-ee}.
-\comment{Add mortality and population growth to data sources.}
-
-The number of people aged 15--49 years \cite{The_World_Bank2016-fd}
-
-Susceptible people are vaccinated at rate $\zeta$, transitioning into
-the vaccinated compartment ($R$), where the vaccine reduces their
-force of infection by the efficacy factor $\rho$.
-
-Transition rates between the undiagnosed ($U$), diagnosed ($D$),
-treated ($T$), and viral-suppression classes ($V$) are determined by
-the proportion of PLHIV diagnosed
-\begin{equation}
-  p_D = \frac{D + T + V + W}{A + U + D + T + V + W},
-\end{equation}
-the proportion of diagnosed people on ART
-\begin{equation}
-  p_T = \frac{T + V + W}{D + T + V + W},
-\end{equation}
-the proportion of people on ART who have
-achieved viral suppression
-\begin{equation}
-  p_V = \frac{V}{T + V},
-\end{equation}
-and the proportion of susceptible people vaccinated is
-\begin{equation}
-  p_R = \frac{R}{S + R}.
-\end{equation}
-
-We can implement the vaccination compartment in the same way as the
-other controls. When we begin vaccination in 2020 (also 2025 in
-scenario analysis), the initial vaccination level is 0\%. The coverage
-will increase linearly by 25\% per year (also 10\% per year in
-scenario analysis). The coverage will continue to increase linearly
-until it reaches 70\% coverage (50\% \& 90\% in scenario analysis) and
-then stay constant for the remainder of the time period.
-
-95--95--95 goal is implemented subsequently after meeting 90--90--90
-by 2020 by increasing $p_D$, $p_T$, and $p_V$ to 95--95--95 levels by
-2030 linearly. \comment{@Jan, We use the Heaveside function here too?
-JM: Yes.  I'll write it at some point.}
-
-The rates are applied when the proportions of $p_D$, $p_T$, $p_V$, and
-$p_R$ are below the target levels:
-\begin{equation}
-  \label{target_rates}
-  \begin{split}
-    \alpha(t) &= \alpha_{\max} H\left(p_D^*(t) - p_D(t)\right),
-    \\
-    \phi(t) &= \phi_{\max} H\left(p_T^*(t) - p_T(t)\right),
-    \\
-    \psi(t) &= \psi_{\max} H\left(p_V(t) - p_V^*(t)\right),
-    \\
-    \zeta(t) &= \zeta_{\max} H\left(p^{*}_{R}(t) - p_{W}(t)\right),
-  \end{split}
-\end{equation}
-where $H(x)$ is the Heaviside function
-\begin{equation}
-  H(x) =
-  \begin{cases}
-    0 & \text{if $x < 0$},
-    \\
-    1 & \text{if $x > 0$}.
-  \end{cases}
-\end{equation}
-
-The discontinuity of the Heaviside function makes numerical solution
-difficult.  Instead, replace $H$ with the continuous piecewise linear
-function
-\begin{equation}
-  H(x) =
-  \begin{cases}
-    0 & \text{if $x < 0$},
-    \\
-    x / \chi & \text{if $0 \leq x \leq \chi$},
-    \\
-    1 & \text{if $x > \chi$},
-  \end{cases}
-\end{equation}
-with some small value of $\chi$.
+In scenarios with vaccine, susceptible people are vaccinated at rate
+$\zeta$, depending on the country's current vaccination coverage and
+its coverage target (\autoref{targets}), transitioning into the
+vaccinated compartment ($R$), where the vaccine reduces their force of
+infection by the efficacy factor $\rho$.  Without vaccine,
+$\zeta = 0$.
 
@@
     \\
-    \beta_x &= T \left[1 - (1 - \tau_x)^n\right]
+    \beta_x &= \eta \left[1 - (1 - \tau_x)^n\right]
     \text{ for $x \in \{A, U, T\}$},
     \\
-    \tau_T &= \varepsilon \tau_U.
+    \tau_T &= \varepsilon \tau_U,
   \end{split}
 \end{equation}
+where $\eta$ is the transmission rate (\autoref{model_fitting}).
+
+\comment{Describe transmissibilities.}
+
+\comment{Initial conditions.}
+The number of people aged 15--49 years \cite{The_World_Bank2016-fd}
+and the proportion diagnosed, treated, and with viral suppression
+(\autoref{data_sources}) were used to initialize the model for year
+2015.  Due to a lack of data on acute infections, and since the acute
+phase is so much shorter than the other stages, we assumed that
+initially there were no acute infections.
+
+\section{Target rates}
+\label{targets}
+
+The current proportion of PLHIV who know their diagnosis is
+\begin{equation}
+  p_D(t) = \frac{D(t) + T(t) + V(t) + W(t)}
+  {A(t) + U(t) + D(t) + T(t) + V(t) + W(t)},
+\end{equation}
+and the desired target for the current level of diagnosis is
+$p_D^*(t)$.  For the rate of new diagnosis, we used the function
+\begin{equation}
+  \label{diagnosis_rate}
+  \alpha(t) = \alpha_{\max} H\!\left(p_D^*(t) - p_D(t)\right),
+\end{equation}
+where $H(x)$ is the Heaviside-like function
+\begin{equation}
+  H(x) =
+  \begin{cases}
+    0 & \text{if $x < 0$},
+    \\
+    x / \chi & \text{if $0 \leq x \leq \chi$},
+    \\
+    1 & \text{if $x > \chi$},
+  \end{cases}
+\end{equation}
+with $\chi = 0.001$.  The linear segment connecting $H = 0$ and
+$H = 1$ was used to avoid difficulties in computing numerical
+solutions that occur when using a discontinuous function.  This
+function allows new diagnoses ($\alpha(t) > 0$) when the current
+diagnosis level is below the target (i.e., when $p_D^*(t) > p_D(t)$),
+and stops new diagnoses ($\alpha(t) = 0$) when the current diagnosis
+level is at or above target.  We took
+$\alpha_{\max} = 1\;\text{y$^{-1}$}$.
+
+The proportion of diagnosed people who are treated is
+\begin{equation}
+  p_T(t) = \frac{T(t) + V(t) + W(t)}{D(t) + T(t) + V(t) + W(t)}.
+\end{equation}
+Like the rate of new diagnosis, the rate of enrolling new people in
+treatment is
+\begin{equation}
+  \label{treatment_rate}
+  \phi(t) = \phi_{\max} H\!\left(p_T^*(t) - p_T(t)\right),
+\end{equation}
+with $\phi_{\max} = 10$, allowing new treatment ($\phi(t) > 0$) when
+the current treatment level is below the target ($p_T^*(t) > p_T(t)$)
+and stopping new treatment ($\phi(t) = 0$) when the current treatment
+level is at or above target.
+
+The proportion of people on ART who have achieved viral suppression is
+\begin{equation}
+  p_V(t) = \frac{V(t)}{T(t) + V(t)}.
+\end{equation}
+The rate of people relapsing to untreated is
+\begin{equation}
+  \label{relapse_rate}
+  \psi(t) = \psi_{\max} H\!\left(p_V(t) - p_V^*(t)\right),
+\end{equation}
+with $\psi_{\max} = 1$, which, unlike diagnosis and treatment rates,
+prevents relapses ($\psi(t) = 0$) when the current level of viral
+suppression is below the target ($p_V^*(t) > p_V(t)$) and allows
+relapses ($\psi(t) > 0$) when the current level of viral suppression
+is at or above target.  We chose to vary the relapse rate to achieve
+the desired level of viral suppression because achieving viral
+suppression seems to depend on the time on treatment (parametrized by
+our rate $\gamma$), while relapse rates are difficult to estimate.
+
+The proportion of susceptible people vaccinated is
+\begin{equation}
+  p_R(t) = \frac{R(t)}{S(t) + R(t)}.
+\end{equation}
+Like diagnosis and treatment, the vaccination rate is
+\begin{equation}
+  \label{vaccination_rate}
+  \zeta(t) = \zeta_{\max} H\!\left(p_R^*(t) - p_R(t)\right),
+\end{equation}
+with $\zeta_{\max} = 1$, allowing vaccination ($\zeta(t) > 0$) when
+the current vaccine coverage level is below the target
+($p_R^*(t) > p_R(t)$) and stopping vaccination ($\zeta(t) = 0$) when
+the current vaccine coverage is at or above target.
 
@@
 for $x \in \{D, T, V\}$.
+
+We can implement the vaccination compartment in the same way as the
+other controls. When we begin vaccination in 2020 (also 2025 in
+scenario analysis), the initial vaccination level is 0\%. The coverage
+will increase linearly by 25\% per year (also 10\% per year in
+scenario analysis). The coverage will continue to increase linearly
+until it reaches 70\% coverage (50\% \& 90\% in scenario analysis) and
+then stay constant for the remainder of the time period.  95--95--95
+goal is implemented subsequently after meeting 90--90--90 by 2020 by
+increasing $p_D$, $p_T$, and $p_V$ to 95--95--95 levels by 2030
+linearly.
+
+\section{Uncertainty analysis}
+\label{uncertainty}
+
+Projections were generated for each country through model simulations
+using 1000 random samples from published parameter distributions
+(table S1, Supplementary text) and the country-specific estimated
+distribution of the transmission rate. We evaluated the global and
+country-level impacts of meeting the UNAIDS targets and vaccine
+deployment on four outcome measures: HIV incidence, PLHIV, PLAIDS, and
+AIDS-related deaths between 2015 and 2035. Our base-case scenario
+assumed maintenance of the status quo: that 2015 levels of the
+proportion of PLHIV diagnosed (pD), proportion of those diagnosed on
+ART (pT), and proportion of those on treatment who have achieved viral
+suppression (pV) continue unchanged until 2035. The intervention
+scenarios were (1.) the attainment of the 90–90–90 target by linear
+increases in pD, pT, and pV until 2020 followed by maintenance of
+those levels until 2035, and (2.) linear increase in the diagnosis and
+treatment levels to the 90–90–90 target by 2020, a linear increase
+from 90–90–90 to the 95–95–95 target by 2030, and maintenance of the
+95–95–95 levels to 2035. (For 90–90–90, if any initial level was above
+90\%, it was kept constant going forward so that the intervention did
+not worsen coverage.  Likewise, for 95–95–95, any initial level above
+95\% was kept constant.)  For vaccination, we assumed deployment of a
+vaccine with 50\% efficacy in 2020 with coverage increasing linearly
+by 25\% per year, continuing up to 70\% at 2.8 years post-rollout, and
+maintaining constant 70\% coverage thereafter.  We also performed a
+partial rank correlation coefficient (PRCC) sensitivity analysis for
+each model parameter and a scenario analysis to account for
+uncertainty in the profile of the prospective vaccine.
 
@@
 
-Projections were generated for each country through model simulations
-using 1000 random samples from published parameter distributions
-(table S1, Supplementary text) and the country-specific estimated
-distribution of the transmission rate. We evaluated the global and
-country-level impacts of meeting the UNAIDS targets and vaccine
-deployment on four outcome measures: HIV incidence, PLHIV, PLAIDS, and
-AIDS-related deaths between 2015 and 2035. Our base-case scenario
-assumed maintenance of the status quo: that 2015 levels of the
-proportion of PLHIV diagnosed (pD), proportion of those diagnosed on
-ART (pT), and proportion of those on treatment who have achieved viral
-suppression (pV) continue unchanged until 2035. The intervention
-scenarios were (1.) the attainment of the 90–90–90 target by linear
-increases in pD, pT, and pV until 2020 followed by maintenance of
-those levels until 2035, and (2.) linear increase in the diagnosis and
-treatment levels to the 90–90–90 target by 2020, a linear increase
-from 90–90–90 to the 95–95–95 target by 2030, and maintenance of the
-95–95–95 levels to 2035. (For 90–90–90, if any initial level was above
-90\%, it was kept constant going forward so that the intervention did
-not worsen coverage.  Likewise, for 95–95–95, any initial level above
-95\% was kept constant.)  For vaccination, we assumed deployment of a
-vaccine with 50\% efficacy in 2020 with coverage increasing linearly
-by 25\% per year, continuing up to 70\% at 2.8 years post-rollout, and
-maintaining constant 70\% coverage thereafter.  We also performed a
-partial rank correlation coefficient (PRCC) sensitivity analysis for
-each model parameter and a scenario analysis to account for
-uncertainty in the profile of the prospective vaccine.
-
 \section{Source code}
@@
 prevalence for ages 15–49 years starting as early as 1990 in some
-countries and running through 2015, along with basic demographics
-(\autoref{data_sources}).
+countries and running through 2015, along with basic demographics.
 
@@
 by taking the exponential weighted mean of transmission rates
-(\ref{trans_rate}).
+\eqref{trans_rate}.
 
-Rearranging equation (\ref{foi}), the transmission rate for PLHIV
+Rearranging equation \eqref{foi}, the transmission rate for PLHIV
 without viral suppression can be written as
@@
 unsuppressed transmission remains constant worldwide and calculated
-these values using the data from Rakai, Uganda \cite{Wawer2005-us}. The aggregate
-rate of transmission ($\beta$) can then be combined with equations \ref{betaU} to calculate transmission
+these values using the data from Rakai, Uganda
+\cite{Wawer2005-us}. The aggregate rate of transmission ($\beta$) can
+then be combined with eqs.~\eqref{betaU} to calculate transmission
 rates for unsuppressed PLHIV, acute PLHIV and suppressed PLHIV as,
@@
   \includegraphics{../Codes/plots/prcc.pdf}
-  \caption{Parameter sensitivity of model global infections averted
-    from 2015 to 2035.}
+  \caption{Parameter sensitivity of global infections averted from
+    2015 to 2035.  Left is the parameter sensitivity of infections
+    averted by 95--95--95, relative to status quo.  Right is the
+    parameter sensitivity of vaccination with status quo levels of
+    diagnosis and treatment, relative to status quo.  Sensitivity is
+    measured by the partial rank correlation coefficient (PRCC).}
   \label{PRCCs}

### 2016-08-20 Documents/supplementary_text.tex
Hacking on supplement.

@@
-\documentclass[11pt]{article}
+\documentclass{article}
 
@@
 \cite{World_Development_Indicators2013-ee}.  The recruitment rate into
-ages $15\;\text{y}$ and older group ($B$) was set by the difference
+ages $15\;\text{y}$ and older group ($\kappa$) was set by the difference
 between the country's population growth rate \cite{WorldBankpg} and
@@
       \hline
-      $\mu$ & Background death rate & Country specific, see Table S2
+      $\mu$ & Background death rate & Country specific, Table S2
       & \cite{World_Development_Indicators2013-ee} \\
-      $B$ & Recruitment rate & Country specific, see Table S2
+      $\kappa$ & Recruitment rate & Country specific, Table S2
       & \cite{World_Development_Indicators2013-ee, WorldBankpg} \\
@@
       $\theta$ & Rate of developing AIDS with viral suppression
-      & See eq.~(\ref{theta}) & --- \\
+      & Eq.~(\ref{theta}) & --- \\
       $\gamma$ & Rate of viral suppression
@@
 occurs after between 8 months and 2 years on treatment
-\cite{Currie2009-yz}.  The disengagement from treatment moves people
-from treated ($T$) and viral suppression ($V$) at the rate $\psi$,
+\cite{Currie2009-yz}.  Disengagement from treatment moves people from
+treated ($T$) and viral suppression ($V$) at the rate $\psi$,
 dependent on the current level of viral suppression and the country's
@@
 vaccinated compartment ($R$), where the vaccine reduces their force of
-infection by the efficacy factor $\rho$.  Without vaccine,
-$\zeta = 0$.
+infection by the efficacy factor $\rho$.  We took the base-case
+efficacy to be $50\%$ and varied it to $30\%$ and $70\%$ in analyzing
+vaccination scenarios (\autoref{uncertainty}).  We did not model
+specific vaccine dose regime, such that implicit in our efficacy
+parameter is the assumption that boosters will be used to maintain
+efficacy over time.  Without vaccine, $\zeta = 0$.
+
+We also added differential equations to track the cumulative number of
+new infections ($Y$) and AIDS deaths ($Z$) over the model period.
 
@@
   \begin{split}
-    \frac{\md S}{\md t} &= B N - \lambda S - \zeta S- \mu S,
+    \frac{\md S}{\md t} &= \kappa N - \lambda S - \zeta S- \mu S,
     \\
@@
     \nu W,
+    \\
+    \frac{\md Y}{\md t} &= \lambda \big[S + (1 - \rho) R\big],
+    \\
+    \frac{\md Z}{\md t} &= \nu W,
   \end{split}
@@
   \begin{split}
-    \lambda &= \frac{\beta_A A + \beta_U (U + D + T) + \beta_T V}{N},
+    \lambda &= \frac{\beta_A A + \beta_U (U + D + T) + \beta_V V}{N},
     \\
@@
     \\
-    \beta_x &= \eta \left[1 - (1 - \tau_x)^n\right]
-    \text{ for $x \in \{A, U, T\}$},
+    \beta_A &= \eta \left[1 - (1 - \tau_A)^n\right]
     \\
-    \tau_T &= \varepsilon \tau_U,
+    \beta_U &= \eta \left[1 - (1 - \tau_U)^n\right]
+    \\
+    \beta_V &= \eta \left[1 - (1 - \tau_V)^n\right]
+    \\
+    \tau_V &= \varepsilon \tau_U,
   \end{split}
 \end{equation}
-where $\eta$ is the transmission rate (\autoref{model_fitting}).
+where the $\tau$'s are the relative transmissibility of people with
+acute ($A$), unsuppressed ($U$ and $T$), and suppressed ($V$)
+infections, $n$ is the annual number of coital acts, and $\eta$ is the
+country-specific transmission rate (\autoref{model_fitting}).  For
+transmissibility during the acute phase, we sampled from
+$\Triangular$(0.0039, 0.0082, 0.0150)
+\cite{Skarbinski2015-ni,Wawer2005-us}, whereas, for transmissibility
+for unsuppressed people, we sampled from
+$\Triangular(0.00077, 0.0014, 0.00251)$ \cite{Hughes2012-so}.  The
+transmissibility of people with viral suppression relative to those
+without suppression has been estimated at 0.08 (95\% confidence
+interval 0.002, 0.57) \cite{Donnell2010-xo}: because of the extremely
+long left tail, we chose to sample the relative transmissibility
+$\varepsilon$ from $\BetaPERT(0.08, 0.002, 0.57)$ rather than a
+$\Triangular$ distribution.  (See \autoref{uncertainty} for a full
+description of $\BetaPERT(a, b, c)$.)  The annual number of coital $n$
+was sampled from $\Uniform(96, 108)$
+\cite{Wawer2005-us,Abdool_Karim2010-cm}.
 
-\comment{Describe transmissibilities.}
-
-\comment{Initial conditions.}
-The number of people aged 15--49 years \cite{The_World_Bank2016-fd}
-and the proportion diagnosed, treated, and with viral suppression
-(\autoref{data_sources}) were used to initialize the model for year
-2015.  Due to a lack of data on acute infections, and since the acute
-phase is so much shorter than the other stages, we assumed that
-initially there were no acute infections.
+For year 2015, the number of people aged 15--49 years, $M(2015)$; the
+prevalence, $p_I(2015)$; the proportion diagnosed, $p_D(2015)$; the
+proportion treated, $p_T(2015)$; and proportion with viral
+suppression, $p_V(2015)$ (\autoref{data_sources}) were used to
+initialize the model.  Due to a lack of data on acute infections, and
+since the acute phase is so much shorter than the other stages, we
+assumed that initially there were no acute infections.  Due to a lack
+of comprehensive data on PLAIDS in each country, we assumed that the
+proportion of diagnosed, untreated people ($D + W$) who have AIDS
+($W$) in year 2015 was
+\begin{equation}
+  p_A = \frac{\sigma}{\sigma + \nu},
+\end{equation}
+which is the equilibrium fraction of diagnosed people ($D + W$) who
+have AIDS ($W$) in the absence of treatment and background mortality.
+The number initially vaccinated was set to 0.  The initial cumulative
+number of new infections and AIDS deaths were set to 0.  Thus, the
+model initial conditions are
+\begin{equation}
+  \label{initial_conditions}
+  \begin{split}
+    S(2015) &= \big(1 - p_I(2015)\big) M(2015), \\
+    R(2015) &= 0, \\
+    A(2015) &= 0, \\
+    U(2015) &= \big(1 - p_D(2015)\big) p_I(2015) M(2015), \\
+    D(2015) &= \big(1 - p_A\big) p_D(2015) \big(1 - p_T(2015)\big)
+    p_I(2015) M(2015), \\
+    T(2015) &= p_D(2015) p_T(2015) \big(1 - p_V(2015)\big)
+    p_I(2015) M(2015), \\
+    V(2015) &= p_D(2015) p_T(2015) p_V(2015) p_I(2015) M(2015), \\
+    W(2015) &= p_A p_D(2015) \big(1 - p_T(2015)\big) p_I(2015) M(2015), \\
+    Y(2015) &= 0, \\
+    Z(2015) &= 0.
+  \end{split}
+\end{equation}
 
@@
   \label{diagnosis_rate}
-  \alpha(t) = \alpha_{\max} H\!\left(p_D^*(t) - p_D(t)\right),
+  \alpha(t) = \alpha_{\max} H\big(p_D^*(t) - p_D(t)\big),
 \end{equation}
@@
 \end{equation}
-with $\chi = 0.001$.  The linear segment connecting $H = 0$ and
+with $\chi = 0.001$, which rapidly switches from $H = 0$ when $x < 0$
+to $H = 1$ when $x > 0$.  The linear segment connecting $H = 0$ and
 $H = 1$ was used to avoid difficulties in computing numerical
-solutions that occur when using a discontinuous function.  This
-function allows new diagnoses ($\alpha(t) > 0$) when the current
-diagnosis level is below the target (i.e., when $p_D^*(t) > p_D(t)$),
-and stops new diagnoses ($\alpha(t) = 0$) when the current diagnosis
-level is at or above target.  We took
-$\alpha_{\max} = 1\;\text{y$^{-1}$}$.
+solutions that occur when using a discontinuous function.  The
+function for the rate of new diagnoses \eqref{diagnosis_rate} allows
+new diagnoses ($\alpha(t) > 0$) when the current diagnosis level is
+below the target ($p_D^*(t) > p_D(t)$), and stops new
+diagnoses ($\alpha(t) = 0$) when the current diagnosis level is at or
+above target.  We took $\alpha_{\max} = 1\;\text{y$^{-1}$}$.
 
@@
   \label{treatment_rate}
-  \phi(t) = \phi_{\max} H\!\left(p_T^*(t) - p_T(t)\right),
+  \phi(t) = \phi_{\max} H\big(p_T^*(t) - p_T(t)\big),
 \end{equation}
@@
   \label{relapse_rate}
-  \psi(t) = \psi_{\max} H\!\left(p_V(t) - p_V^*(t)\right),
+  \psi(t) = \psi_{\max} H\big(p_V(t) - p_V^*(t)\big),
 \end{equation}
@@
 the desired level of viral suppression because achieving viral
-suppression seems to depend on the time on treatment (parametrized by
-our rate $\gamma$), while relapse rates are difficult to estimate.
+suppression seems to depend on the time on treatment (i.e.,
+$1 / \gamma$), while relapse rates are difficult to estimate.
 
@@
   \label{vaccination_rate}
-  \zeta(t) = \zeta_{\max} H\!\left(p_R^*(t) - p_R(t)\right),
+  \zeta(t) = \zeta_{\max} H\big(p_R^*(t) - p_R(t)\big),
 \end{equation}
@@
 
-The targets for the proportions $p_D$, $p_T$, and $p_V$ in the
-achievement of 90--90--90 all operate under the following assumption:
-if the initial level $p_x(0)$ is less than $90\%$, the proportion will
-increase linearly in the first 5 years and then stay at $90\%$ for the
-remaining time; and if the initial level is at $90\%$ or above, the
-proportion will remain constant for the duration of the study:
+We modeled 3 different targets for the proportion diagnosed ($p_D$), the
+proportion treated ($p_T$), and the proportion with viral suppression ($p_V$).
+\begin{description}
+\item[Status quo] Given initial proportions $p_D(2015)$, $p_T(2015)$,
+  and $p_V(2015)$, the targets are for the proportion to remain fixed
+  at that level for all times:
   \begin{equation}
-  p_x^*(t)
-  = p_x(0) + \left[
-    \max\left\{0.9, p_x(0)\right\} - p_x(0)
-  \right]
-  \min\left\{\frac{t}{5}, 1\right\},
+    \label{status_quo_target}
+    \begin{split}
+      p_D^*(t) &= p_D(2015), \\
+      p_T^*(t) &= p_T(2015), \\
+      p_V^*(t) &= p_V(2015).
+    \end{split}
   \end{equation}
-for $x \in \{D, T, V\}$.
 
-We can implement the vaccination compartment in the same way as the
-other controls. When we begin vaccination in 2020 (also 2025 in
-scenario analysis), the initial vaccination level is 0\%. The coverage
-will increase linearly by 25\% per year (also 10\% per year in
-scenario analysis). The coverage will continue to increase linearly
-until it reaches 70\% coverage (50\% \& 90\% in scenario analysis) and
-then stay constant for the remainder of the time period.  95--95--95
-goal is implemented subsequently after meeting 90--90--90 by 2020 by
-increasing $p_D$, $p_T$, and $p_V$ to 95--95--95 levels by 2030
-linearly.
+\item[UNAIDS 90--90--90] The UNAIDS 90--90--90 target is for $p_D$,
+  $p_T$, and $p_V$ to all be raised to $90\%$ by 2020.  We implemented
+  this target as linear increases from the 2015 levels, each up to
+  $90\%$ in 2020, and constant at $90\%$ from 2020 to 2035, except if
+  an initial level is above $90\%$ then it remains constant from 2015
+  to 2035 so that meeting the UNAIDS target does not worsen any aspect
+  of the treatment cascade.  That is,
+  \begin{equation}
+    \label{unaids90_targets}
+    \begin{split}
+      p_D^*(t) &=
+      \begin{cases}
+        F\big(t, 2015, p_D(2015), 2020, 0.9\big)
+        & \text{if $p_D(2015) < 0.9$},
+        \\
+        p_D(2015) & \text{if $p_D(2015) \geq 0.9$}.
+      \end{cases}
+      \\
+      p_T^*(t) &=
+      \begin{cases}
+        F\big(t, 2015, p_T(2015), 2020, 0.9\big)
+        & \text{if $p_T(2015) < 0.9$},
+        \\
+        p_T(2015) & \text{if $p_T(2015) \geq 0.9$}.
+      \end{cases}
+      \\
+      p_V^*(t) &=
+      \begin{cases}
+        F\big(t, 2015, p_V(2015), 2020, 0.9\big)
+        & \text{if $p_V(2015) < 0.9$},
+        \\
+        p_V(2015) & \text{if $p_V(2015) \geq 0.9$}.
+      \end{cases}
+    \end{split}
+  \end{equation}
+  where
+  \begin{equation}
+    \label{F}
+    F(t, t_0, x_0, t_1, x_1) =
+    \begin{cases}
+      x_0 & \text{if $t < t_0$},
+      \\
+      x_0 + (x_1 - x_0) \frac{t - t_0}{t_1 - t_0} &
+      \text{if $t_0 \leq t < t_1$},
+      \\
+      x_1 & \text{if $t \geq t_1$},
+    \end{cases}
+  \end{equation}
+  is constant at $x_0$ for $t < t_0$, linearly connects $x_0$ at
+  $t_0$ to $x_1$ at $t_1$ for $t_0 \leq t < t_1$, and is constant at
+  $x_1$ for $t \geq t_1$.
+
+\item[UNAIDS 95--95--95] The UNAIDS 95--95--95 target is to achieve
+  90--90--90 by 2020 and then for $p_D$, $p_T$, and $p_V$ to all be
+  raised to $95\%$ by 2030.  We implemented this target as for
+  90--90--90 from 2015 to 2020, and then linear increases from the
+  2020 levels up to $95\%$ in 2030, again with the exception that if
+  an initial level is above $95\%$ then it remains constant from 2015
+  to 2035.  That is,
+  \begin{equation}
+    \label{unaids95_targets}
+    \begin{split}
+      p_D^*(t) &=
+      \begin{cases}
+        G\big(t, 2015, p_D(2015), 2020, 0.9, 2030, 0.95\big)
+        & \text{if $p_D(2015) < 0.9$},
+        \\
+        F\big(t, 2020, p_D(2015), 2030, 0.95\big)
+        & \text{if $0.9 \leq p_D(2015) < 0.95$},
+        \\
+        p_D(2015) & \text{if $p_D(2015) \geq 0.95$},
+      \end{cases}
+      \\
+      p_T^*(t) &=
+      \begin{cases}
+        G\big(t, 2015, p_T(2015), 2020, 0.9, 2030, 0.95\big)
+        & \text{if $p_T(2015) < 0.9$},
+        \\
+        F\big(t, 2020, p_T(2015), 2030, 0.95\big)
+        & \text{if $0.9 \leq p_T(2015) < 0.95$},
+        \\
+        p_T(2015) & \text{if $p_T(2015) \geq 0.95$},
+      \end{cases}
+      \\
+      p_V^*(t) &=
+      \begin{cases}
+        G\big(t, 2015, p_V(2015), 2020, 0.9, 2030, 0.95\big)
+        & \text{if $p_V(2015) < 0.9$},
+        \\
+        F\big(t, 2020, p_V(2015), 2030, 0.95\big)
+        & \text{if $0.9 \leq p_V(2015) < 0.95$},
+        \\
+        p_V(2015) & \text{if $p_V(2015) \geq 0.95$},
+      \end{cases}
+    \end{split}
+  \end{equation}
+  where
+  \begin{equation}
+    G(t, t_0, x_0, t_1, x_1, t_2, x_2) =
+    \begin{cases}
+      x_0 & \text{if $t < t_0$},
+      \\
+      x_0 + (x_1 - x_0) \frac{t - t_0}{t_1 - t_0} &
+      \text{if $t_0 \leq t < t_1$},
+      \\
+      x_1 + (x_2 - x_1) \frac{t - t_1}{t_2 - t_1} &
+      \text{if $t_1 \leq t < t_2$},
+      \\
+      x_2 & \text{if $t \geq t_2$},
+    \end{cases}
+  \end{equation}
+  is constant at $x_0$ for $t < t_0$, linearly connects $x_0$ at $t_0$
+  to $x_1$ at $t_1$ for $t_0 \leq t < t_1$, linearly connects $x_1$ at
+  $t_1$ to $x_2$ at $t_2$ for $t_1 \leq t < t_2$, and is constant at
+  $x_2$ for $t \geq t_2$, and $F$ is as in \eqref{F}.
+
+\end{description}
+
+For vaccination, we assume that vaccination rollout begins in year
+$t_V = 2020$ (or $t_V = 2025$ in vaccine scenario analysis,
+\autoref{uncertainty}), that rollout linearly increases the proportion
+of non-infected population covered from 0\% by $r_V = 25\%$ per year
+(or $r_V = 10\%$ per year) up to $c_V = 70\%$ (or $c_V = 50\%$ or
+$c_V = 90\%$) and staying constant thereafter.  Thus, the vaccination
+target is
+\begin{equation}
+  \label{vaccination_target}
+  p_R^*(t) =
+  \begin{cases}
+    0 & \text{if $t < t_V$},
+    \\
+    r_V (t - t_V) & \text{if $t_V \leq t < T_V$},
+    \\
+    c_V & \text{if $t \geq T_V$},
+  \end{cases}
+\end{equation}
+where $T_V = t_V + c_V / r_V$ is the time when rollout reaches
+the full coverage $c_V$.
+
+\section{Numerical solution}
+
+For accuracy and speed in numerically solving differential equations
+\eqref{model_eqns}, the variables $S$, $U$, $D$, $T$, $V$, and
+$W$---i.e., those that are not initially $0$---were log transformed
+and the differential equations were written in terms of
+the new log variables:
+\begin{equation}
+  \label{model_eqns_log}
+  \begin{split}
+    \frac{\md \log S}{\md t} &= \kappa N \me^{- \log S} - \lambda - \zeta - \mu,
+    \\
+    \frac{\md R}{\md t} & = \zeta \me^{\log S} - (1 - \rho) \lambda R - \mu R,
+    \\
+    \frac{\md A}{\md t} &= \lambda \me^{\log S} + (1 - \rho) \lambda R
+    - \delta A - \mu A,
+    \\
+    \frac{\md \log U}{\md t} &= \delta A \me^{- \log U} - \alpha - \mu - \sigma,
+    \\
+    \frac{\md \log D}{\md t} &=  \alpha \me^{\log U - \log D}
+    + \psi \me^{\log T - \log D} + \psi \me^{\log V - \log D} - \phi - \mu - \sigma,
+    \\
+    \frac{\md \log T}{\md t} &= \phi \me^{\log D - \log T} - \psi - \gamma - \mu
+    - \sigma,
+    \\
+    \frac{\md \log V}{\md t} &= \gamma \me^{\log T - \log V} - \psi
+    - \mu  - \theta,
+    \\
+    \frac{\md \log W}{\md t} &= \sigma \me^{\log U - \log W}
+    + \sigma \me^{\log D - \log W} + \sigma \me^{\log T - \log W}
+    + \theta \me^{\log V - \log W} - \nu,
+    \\
+    \frac{\md Y}{\md t} &= \lambda \left[\me^{\log S} + (1 - \rho) R\right],
+    \\
+    \frac{\md Z}{\md t} &= \nu \me^{\log W}.
+  \end{split}
+\end{equation}
+
+The model simulation and analysis tools, written in Python, are
+publicly available at
+\url{https://github.com/janmedlock/HIV-95-vaccine/}
+\cite{medlock2016-git}.  The differential equations were solved using
+\texttt{scipy.integrate.odeint()} \cite{scipy}.  See the source code
+for full details.
 
@@
 using 1000 random samples from published parameter distributions
-(table S1, Supplementary text) and the country-specific estimated
-distribution of the transmission rate. We evaluated the global and
-country-level impacts of meeting the UNAIDS targets and vaccine
-deployment on four outcome measures: HIV incidence, PLHIV, PLAIDS, and
-AIDS-related deaths between 2015 and 2035. Our base-case scenario
-assumed maintenance of the status quo: that 2015 levels of the
-proportion of PLHIV diagnosed (pD), proportion of those diagnosed on
-ART (pT), and proportion of those on treatment who have achieved viral
-suppression (pV) continue unchanged until 2035. The intervention
-scenarios were (1.) the attainment of the 90–90–90 target by linear
-increases in pD, pT, and pV until 2020 followed by maintenance of
-those levels until 2035, and (2.) linear increase in the diagnosis and
-treatment levels to the 90–90–90 target by 2020, a linear increase
-from 90–90–90 to the 95–95–95 target by 2030, and maintenance of the
-95–95–95 levels to 2035. (For 90–90–90, if any initial level was above
-90\%, it was kept constant going forward so that the intervention did
-not worsen coverage.  Likewise, for 95–95–95, any initial level above
-95\% was kept constant.)  For vaccination, we assumed deployment of a
-vaccine with 50\% efficacy in 2020 with coverage increasing linearly
-by 25\% per year, continuing up to 70\% at 2.8 years post-rollout, and
+(table S1) and the country-specific estimated distribution of the
+transmission rate. We evaluated the global and country-level impacts
+of meeting the UNAIDS targets and vaccine deployment on four outcome
+measures: HIV incidence, PLHIV, PLAIDS, and AIDS-related deaths
+between 2015 and 2035. Our base-case scenario assumed maintenance of
+the status quo: that 2015 levels of the proportion of PLHIV diagnosed
+(pD), proportion of those diagnosed on ART (pT), and proportion of
+those on treatment who have achieved viral suppression (pV) continue
+unchanged until 2035. The intervention scenarios were (1.) the
+attainment of the 90–90–90 target by linear increases in pD, pT, and
+pV until 2020 followed by maintenance of those levels until 2035, and
+(2.) linear increase in the diagnosis and treatment levels to the
+90–90–90 target by 2020, a linear increase from 90–90–90 to the
+95–95–95 target by 2030, and maintenance of the 95–95–95 levels to
+2035. (For 90–90–90, if any initial level was above 90\%, it was kept
+constant going forward so that the intervention did not worsen
+coverage.  Likewise, for 95–95–95, any initial level above 95\% was
+kept constant.)  For vaccination, we assumed deployment of a vaccine
+with 50\% efficacy in 2020 with coverage increasing linearly by 25\%
+per year, continuing up to 70\% at 2.8 years post-rollout, and
 maintaining constant 70\% coverage thereafter.  We also performed a
@@
 
-\section{Source code}
-
-The source code for the model and analysis tools is publicly available
-at \url{https://github.com/janmedlock/HIV-95-vaccine/}
-\cite{medlock2016-git}.
+\comment{Vaccine scenarios.}
 
@@
 repository \cite{medlock2016-git}.
+
+A few countries—e.g., Bulgaria, Timor-Leste, and Yemen—currently have
+low HIV prevalence but relatively high incidence, resulting in large
+estimated transmission rates, leading to rapid projected growth of
+their HIV epidemics by 2035. The apparent low prevalence and high
+incidence may, at least in part, be due to the resolution in UNAIDS
+data (0.1\% for prevalence, 0.01\% for annual per-capita incidence).
+Results for such countries should be considered in light of this
+limitation.
 
@@
 
-\appendix
+\clearpage
 \newpage

### 2016-08-20 Documents/supplementary_text.tex
Removed section on log variables.

@@
 
-\section{Numerical solution}
-
-For accuracy and speed in numerically solving differential equations
-\eqref{model_eqns}, the variables $S$, $U$, $D$, $T$, $V$, and
-$W$---i.e., those that are not initially $0$---were log transformed
-and the differential equations were written in terms of
-the new log variables:
-\begin{equation}
-  \label{model_eqns_log}
-  \begin{split}
-    \frac{\md \log S}{\md t} &= \kappa N \me^{- \log S} - \lambda - \zeta - \mu,
-    \\
-    \frac{\md R}{\md t} & = \zeta \me^{\log S} - (1 - \rho) \lambda R - \mu R,
-    \\
-    \frac{\md A}{\md t} &= \lambda \me^{\log S} + (1 - \rho) \lambda R
-    - \delta A - \mu A,
-    \\
-    \frac{\md \log U}{\md t} &= \delta A \me^{- \log U} - \alpha - \mu - \sigma,
-    \\
-    \frac{\md \log D}{\md t} &=  \alpha \me^{\log U - \log D}
-    + \psi \me^{\log T - \log D} + \psi \me^{\log V - \log D} - \phi - \mu - \sigma,
-    \\
-    \frac{\md \log T}{\md t} &= \phi \me^{\log D - \log T} - \psi - \gamma - \mu
-    - \sigma,
-    \\
-    \frac{\md \log V}{\md t} &= \gamma \me^{\log T - \log V} - \psi
-    - \mu  - \theta,
-    \\
-    \frac{\md \log W}{\md t} &= \sigma \me^{\log U - \log W}
-    + \sigma \me^{\log D - \log W} + \sigma \me^{\log T - \log W}
-    + \theta \me^{\log V - \log W} - \nu,
-    \\
-    \frac{\md Y}{\md t} &= \lambda \left[\me^{\log S} + (1 - \rho) R\right],
-    \\
-    \frac{\md Z}{\md t} &= \nu \me^{\log W}.
-  \end{split}
-\end{equation}
-
-The model simulation and analysis tools, written in Python, are
-publicly available at
-\url{https://github.com/janmedlock/HIV-95-vaccine/}
-\cite{medlock2016-git}.  The differential equations were solved using
-\texttt{scipy.integrate.odeint()} \cite{scipy}.  See the source code
-for full details.
-
 \section{Uncertainty analysis}
@@
 
+\section{Source code}
+
+The model simulation and analysis tools, written in Python, are
+publicly available at
+\url{https://github.com/janmedlock/HIV-95-vaccine/}
+\cite{medlock2016-git}.
+
 \section{Analysis}

### 2016-08-21 Documents/supplementary_text.tex
More work on supplement.

@@
 
-\usepackage[font = {sf}, labelfont = {bf},
-  labelsep = period, singlelinecheck = off]{caption}
-\usepackage[font = {sf}]{floatrow}
+\usepackage[font={sf}, labelfont={bf},
+  labelsep=period, singlelinecheck=off]{caption}
+\usepackage[font={sf}]{floatrow}
 \usepackage{tabularx}
@@
 
-\usepackage[style = science, article-title = true, maxnames = 100]{biblatex}
+\usepackage[style=science, article-title=true, maxnames=100]{biblatex}
 \addbibresource{supplementary_text.bib}
@@
 
+The model simulation and analysis tools, written in Python, are
+publicly available at\\
+\url{https://github.com/janmedlock/HIV-95-vaccine/}
+\cite{medlock2016-git}.
+
 \section{Mathematical model}
@@
 chose to consider only these ages because they are the vast majority
-of PLHIV, 93\% in 2014 \cite{UNICEF}, and because HIV and demographic
-data are often stratified into these ages, although some data used to
-parametrize the model was only available for ages $15$--$49$ rather
-than for ages $15$ and older.  The background mortality rate ($\mu$)
-in each of the 127 countries was collected from published estimates
-\cite{World_Development_Indicators2013-ee}.  The recruitment rate into
-ages $15\;\text{y}$ and older group ($\kappa$) was set by the difference
-between the country's population growth rate \cite{WorldBankpg} and
-its background mortality rate
+of PLHIV---93\% in 2014 \cite{UNICEF}---and because HIV and
+demographic data are often stratified into these ages, although some
+data used to parametrize the model was only available for ages
+$15$--$49$ rather than for ages $15$ and older.  The background
+mortality rate ($\mu$) in each of the 127 countries was collected from
+published estimates \cite{World_Development_Indicators2013-ee}.  The
+recruitment rate ($\kappa$) into the age $15\;\text{y}$ and older
+group was set by the difference between the country's population
+growth rate \cite{WorldBankpg} and its background mortality rate
 \cite{World_Development_Indicators2013-ee}, as would be true if the
@@
 \begin{description}
-\item[Status quo] Given initial proportions $p_D(2015)$, $p_T(2015)$,
-  and $p_V(2015)$, the targets are for the proportion to remain fixed
-  at that level for all times:
+\item[Status quo] The status quo target is for the proportions $p_D$,
+  $p_T$, and $p_V$ to remain fixed at their initial levels going
+  forward:
   \begin{equation}
@@
 
-For vaccination, we assume that vaccination rollout begins in year
-$t_V = 2020$ (or $t_V = 2025$ in vaccine scenario analysis,
-\autoref{uncertainty}), that rollout linearly increases the proportion
-of non-infected population covered from 0\% by $r_V = 25\%$ per year
-(or $r_V = 10\%$ per year) up to $c_V = 70\%$ (or $c_V = 50\%$ or
-$c_V = 90\%$) and staying constant thereafter.  Thus, the vaccination
-target is
+For vaccination, we assume that rollout begins in year $t_V = 2020$
+(or $t_V = 2025$ in vaccine scenario analysis, \autoref{uncertainty}),
+that rollout linearly increases the proportion of the non-infected
+population covered from 0\% by $r_V = 25\%$ per year (or $r_V = 10\%$
+per year) up to $c_V = 70\%$ (or $c_V = 50\%$ or $c_V = 90\%$) and
+staying constant thereafter.  Thus, the vaccination target is
 \begin{equation}
@@
 where $T_V = t_V + c_V / r_V$ is the time when rollout reaches
-the full coverage $c_V$.
+the ultimate coverage $c_V$.
 
-\section{Uncertainty analysis}
-\label{uncertainty}
-
-Projections were generated for each country through model simulations
-using 1000 random samples from published parameter distributions
-(table S1) and the country-specific estimated distribution of the
-transmission rate. We evaluated the global and country-level impacts
-of meeting the UNAIDS targets and vaccine deployment on four outcome
-measures: HIV incidence, PLHIV, PLAIDS, and AIDS-related deaths
-between 2015 and 2035. Our base-case scenario assumed maintenance of
-the status quo: that 2015 levels of the proportion of PLHIV diagnosed
-(pD), proportion of those diagnosed on ART (pT), and proportion of
-those on treatment who have achieved viral suppression (pV) continue
-unchanged until 2035. The intervention scenarios were (1.) the
-attainment of the 90–90–90 target by linear increases in pD, pT, and
-pV until 2020 followed by maintenance of those levels until 2035, and
-(2.) linear increase in the diagnosis and treatment levels to the
-90–90–90 target by 2020, a linear increase from 90–90–90 to the
-95–95–95 target by 2030, and maintenance of the 95–95–95 levels to
-2035. (For 90–90–90, if any initial level was above 90\%, it was kept
-constant going forward so that the intervention did not worsen
-coverage.  Likewise, for 95–95–95, any initial level above 95\% was
-kept constant.)  For vaccination, we assumed deployment of a vaccine
-with 50\% efficacy in 2020 with coverage increasing linearly by 25\%
-per year, continuing up to 70\% at 2.8 years post-rollout, and
-maintaining constant 70\% coverage thereafter.  We also performed a
-partial rank correlation coefficient (PRCC) sensitivity analysis for
-each model parameter and a scenario analysis to account for
-uncertainty in the profile of the prospective vaccine.
-
-$\Uniform(a, b)$ is the uniform random variable with minimum $a$
-and maximum $b$: it has density function
-\begin{equation}
-  \label{uniform}
-  p_{\Uniform}(x) =
-  \begin{cases}
-    \frac{1}{b - a} & \text{if $a \leq x \leq b$,}
-    \\
-    0 & \text{otherwise.}
-  \end{cases}
-\end{equation}
-We defined the mode for the uniform distribution to be the midpoint
-$\frac{b - a}{2}$.
-%
-$\Triangular(a, b, c)$ is the triangular random variable
-distribution with minimum $a$, mode $b$, and maximum $c$: it has
-density function
-\begin{equation}
-  \label{triangular}
-  p_{\Triangular}(x) =
-  \begin{cases}
-    \frac{2 (x - a)}{(c - a)(b - a)} & \text{if $a \leq x \leq b$,}
-    \\
-    \frac{2 (c - x)}{(c - a)(c - b)} & \text{if $b \leq x \leq c$,}
-    \\
-    0 & \text{otherwise.}
-  \end{cases}
-\end{equation}
-$\BetaPERT(a, b, c)$ is the beta-PERT probability distribution
-\cite{malcom1959} with minimum $a$, mode $b$, and maximum $c$: it has
-density function
-\begin{equation}
-  \label{betaPERT}
-  p_{\BetaPERT}(x) =
-  \begin{cases}
-    \frac{(x - a)^{v - 1} (c - x)^{w - 1}}{(c - a)^{v + w - 2} B(v, w)}
-    & \text{if $a \leq x \leq c$,}
-    \\
-    0 & \text{otherwise,}
-  \end{cases}
-\end{equation}
-where
-\begin{equation}
-  \begin{split}
-    \mu &= \frac{a + \lambda b + c}{\lambda + 2},
-    \\
-    v &= \frac{(\mu - a)(2 b - a - c)}{(b - \mu) (c - a)},
-    \\
-    w &= \frac{v (a - \mu)}{\mu - c},
-  \end{split}
-\end{equation}
-and $B(v, w)$ is the standard beta function \cite[\S 6.2]{davis1972}.
-We used the standard value of $\lambda = 4$.
-%
-$\Lognormal(\mu, \sigma^2)$ is the lognormal random variable: it has
-density function
-\begin{equation}
-  p_{\Lognormal}(x) = \frac{1}{x \sigma \sqrt{2 \pi}}
-  \exp\left(- \frac{\left(\log x - \mu\right)^2}{2 \sigma^2}\right).
-\end{equation}
-
-\comment{Vaccine scenarios.}
+Target strategies were one of the three diagnosis and treatment
+targets (status quo, 90--90--90, or 95--95--95) combined with either
+no vaccination ($p_R^*(t) = 0$) or vaccination at some level of
+efficacy, ultimate coverage, start date of rollout, and speed of
+rollout.
 
@@
 
-For 127 countries, we found sufficient data to parametrize our model:
-these data consisted of estimates of longitudinal HIV incidence and
-prevalence for ages 15–49 years starting as early as 1990 in some
-countries and running through 2015, along with basic demographics.
-
-Several sources provided information to parameterize our model at the
-country level. Demographic data, including population growth rate
-\cite{WorldBankpg}, death rate
-\cite{World_Development_Indicators2013-ee}, and number of people aged
-15--49 years \cite{The_World_Bank2016-fd} were obtained from the World
-Bank. Longitudinal HIV incidence and prevalence estimates for the
-15--49 age group, spanning from as early as 1990 to 2015, was
-primarily derived from the AIDSinfo database produced by UNAIDS
+For 127 countries, we found sufficient data to parametrize our model.
+Demographic data, including population growth rate \cite{WorldBankpg},
+death rate \cite{World_Development_Indicators2013-ee}, and number of
+people aged 15--49 years \cite{The_World_Bank2016-fd} were obtained
+from the World Bank. Longitudinal HIV incidence and prevalence
+estimates for ages 15--49, spanning from as early as 1990 to 2015,
+were primarily derived from the AIDSinfo database produced by UNAIDS
 \cite{Unaids2016-an}. Other sources included UNAIDS Country Progress
@@
 WHO, and the Asian Development Bank. These sources were also used to
-inform the initial conditions for the model: the number of people who
-have been diagnosed with HIV, who are on ART, and who have viral
+inform the initial conditions for the model: the number of people
+diagnosed with HIV, the number on ART, and the number who have viral
 suppression or have been retained on treatment for at least 12
@@
 resources such as peer-reviewed journal articles and country health
-ministry reports were consulted.  We found sufficient data to
-parametrize our mathematical modeling for 127 countries.  See
-Supplemental data files for full information on data sources for each
-country.  The data files are also available in the public source-code
-repository \cite{medlock2016-git}.
-
-A few countries—e.g., Bulgaria, Timor-Leste, and Yemen—currently have
-low HIV prevalence but relatively high incidence, resulting in large
-estimated transmission rates, leading to rapid projected growth of
-their HIV epidemics by 2035. The apparent low prevalence and high
-incidence may, at least in part, be due to the resolution in UNAIDS
-data (0.1\% for prevalence, 0.01\% for annual per-capita incidence).
-Results for such countries should be considered in light of this
-limitation.
+ministry reports were consulted.  See Tables S2--S6 for full
+information on data sources for each country.  The data tables are
+also available in the public source-code repository
+\cite{medlock2016-git}.
 
@@
 
+A few countries—e.g., Bulgaria, Timor-Leste, and Yemen—currently have
+low HIV prevalence but relatively high incidence, resulting in large
+estimated transmission rates, leading to rapid projected growth of
+their HIV epidemics by 2035. The apparent low prevalence and high
+incidence may, at least in part, be due to the resolution in UNAIDS
+data (0.1\% for prevalence, 0.01\% for annual per-capita incidence).
+Results for such countries should be considered in light of this
+limitation.
+
 \begin{figure}
@@
 
-\section{Source code}
+\section{Uncertainty analysis}
+\label{uncertainty}
 
-The model simulation and analysis tools, written in Python, are
-publicly available at
-\url{https://github.com/janmedlock/HIV-95-vaccine/}
-\cite{medlock2016-git}.
+Projections were generated for each country through model simulations
+using 1000 random samples from published parameter distributions
+(\autoref{model_param}) and the country-specific estimated
+distribution of the transmission rate (\autoref{model_fitting}). We
+evaluated the global and country-level impacts of meeting the UNAIDS
+targets and vaccine deployment on four outcome measures: HIV
+incidence, PLHIV, PLAIDS, and AIDS-related deaths between 2015 and
+2035. Our base-case scenario assumed maintenance of the status quo:
+that 2015 levels of the proportion of PLHIV diagnosed (pD), proportion
+of those diagnosed on ART (pT), and proportion of those on treatment
+who have achieved viral suppression (pV) continue unchanged until
+2035. The intervention scenarios were (1.) the attainment of the
+90–90–90 target by linear increases in pD, pT, and pV until 2020
+followed by maintenance of those levels until 2035, and (2.) linear
+increase in the diagnosis and treatment levels to the 90–90–90 target
+by 2020, a linear increase from 90–90–90 to the 95–95–95 target by
+2030, and maintenance of the 95–95–95 levels to 2035. (For 90–90–90,
+if any initial level was above 90\%, it was kept constant going
+forward so that the intervention did not worsen coverage.  Likewise,
+for 95–95–95, any initial level above 95\% was kept constant.)  For
+vaccination, we assumed deployment of a vaccine with 50\% efficacy in
+2020 with coverage increasing linearly by 25\% per year, continuing up
+to 70\% at 2.8 years post-rollout, and maintaining constant 70\%
+coverage thereafter.  We also performed a partial rank correlation
+coefficient (PRCC) sensitivity analysis for each model parameter and a
+scenario analysis to account for uncertainty in the profile of the
+prospective vaccine.
+
+$\Uniform(a, b)$ is the uniform random variable with minimum $a$
+and maximum $b$: it has density function
+\begin{equation}
+  \label{uniform}
+  p_{\Uniform}(x) =
+  \begin{cases}
+    \frac{1}{b - a} & \text{if $a \leq x \leq b$,}
+    \\
+    0 & \text{otherwise.}
+  \end{cases}
+\end{equation}
+We defined the mode for the uniform distribution to be the midpoint
+$\frac{b - a}{2}$.
+%
+$\Triangular(a, b, c)$ is the triangular random variable
+distribution with minimum $a$, mode $b$, and maximum $c$: it has
+density function
+\begin{equation}
+  \label{triangular}
+  p_{\Triangular}(x) =
+  \begin{cases}
+    \frac{2 (x - a)}{(c - a)(b - a)} & \text{if $a \leq x \leq b$,}
+    \\
+    \frac{2 (c - x)}{(c - a)(c - b)} & \text{if $b \leq x \leq c$,}
+    \\
+    0 & \text{otherwise.}
+  \end{cases}
+\end{equation}
+$\BetaPERT(a, b, c)$ is the beta-PERT probability distribution
+\cite{malcom1959} with minimum $a$, mode $b$, and maximum $c$: it has
+density function
+\begin{equation}
+  \label{betaPERT}
+  p_{\BetaPERT}(x) =
+  \begin{cases}
+    \frac{(x - a)^{v - 1} (c - x)^{w - 1}}{(c - a)^{v + w - 2} B(v, w)}
+    & \text{if $a \leq x \leq c$,}
+    \\
+    0 & \text{otherwise,}
+  \end{cases}
+\end{equation}
+where
+\begin{equation}
+  \begin{split}
+    \mu &= \frac{a + \lambda b + c}{\lambda + 2},
+    \\
+    v &= \frac{(\mu - a)(2 b - a - c)}{(b - \mu) (c - a)},
+    \\
+    w &= \frac{v (a - \mu)}{\mu - c},
+  \end{split}
+\end{equation}
+and $B(v, w)$ is the standard beta function \cite[\S 6.2]{davis1972}.
+We used the standard value of $\lambda = 4$.
+%
+$\Lognormal(\mu, \sigma^2)$ is the lognormal random variable: it has
+density function
+\begin{equation}
+  p_{\Lognormal}(x) = \frac{1}{x \sigma \sqrt{2 \pi}}
+  \exp\left(- \frac{\left(\log x - \mu\right)^2}{2 \sigma^2}\right).
+\end{equation}
+
+\comment{Vaccine scenarios.}
 

### 2016-08-21 Documents/supplementary_text.tex
Jan finished supplement.

@@
 \usepackage{tikz}
+
+\usepackage{enumitem}
+\setlist{topsep=1ex}
 
@@
 \section{Mathematical model}
+\label{model}
 
-We developed a continuous-time, compartmental model that divides
-people aged $15$\;y and older into non-overlapping HIV states.  We
-chose to consider only these ages because they are the vast majority
-of PLHIV---93\% in 2014 \cite{UNICEF}---and because HIV and
+We developed a country-level continuous-time, compartmental model that
+divides people aged $15$\;y and older into non-overlapping HIV states.
+We chose to consider only these ages because they are the vast
+majority of PLHIV---93\% in 2014 \cite{UNICEF}---and because HIV and
 demographic data are often stratified into these ages, although some
@@
 without viral suppression ($T$), viral suppression ($V$), and having
-AIDS ($W$).  Transitions between model states are governed by a series
-of differential equations parametrized using values estimated from
-other studies and from incidence and prevalence data
+AIDS ($W$).  Viral suppression is defined as a viral load of less than
+1000 viral RNA copies per mL of blood.  Viral suppression not only
+extends survival but also dramatically reduces transmission
+\cite{vernazza2000, ioannidis2001, attia2009, May2014-gp}.
+Transitions between model states are governed by a series of
+differential equations parametrized using values estimated from other
+studies and from incidence and prevalence data
 (\autoref{model_param}).  The model is deterministic, but uncertainty
 in the parameters is treated by running the model many times with
-samples from the parameter distributions and summarizing the model
-outcomes using the median, 1st and 3rd quartiles (i.e., 25th and 75th
-percentiles), and 5th and 95th percentiles.
+samples from the parameter distributions (\autoref{uncertainty}) and
+summarizing the model outcomes using the median, 1st and 3rd quartiles
+(i.e., 25th and 75th percentiles), and 5th and 95th percentiles.  Each
+country was modeled separately
+(\hyperref[effectiveness_Afghanistan]{Figures
+  \ref*{effectiveness_Afghanistan}}--\ref{effectiveness_Zimbabwe}) and
+the country simulations were aggregated to calculate global and
+regional outcomes
+(\hyperref[effectiveness_Global]{Figures
+  \ref*{effectiveness_Global}}--\ref{effectiveness_Western_Europe}).
 
@@
       & $\Uniform$(5, 8)\;y
-      & \cite{Unaids2014-ue, Samji2013-kf} \\
+      & \cite{Samji2013-kf, Unaids2014-ue} \\
       $\tau_{A}$ & Transmissibility during acute phase
       & $\Triangular$(0.0039, 0.0082, 0.0150)
-      & \cite{Skarbinski2015-ni,Wawer2005-us}\\
+      & \cite{Wawer2005-us, Skarbinski2015-ni}\\
       $\tau_{U}$ & Transmissibility after acute phase
@@
       $n$ & Coital acts per year & $\Uniform$(96, 108)
-      & \cite{Wawer2005-us,Abdool_Karim2010-cm}\\
+      & \cite{Wawer2005-us, Abdool_Karim2010-cm}\\
       $\alpha$ & Diagnosis rate & See eq.~(\ref{diagnosis_rate}) & --- \\
@@
 estimated to live $5$--$8$\;y shorter lives than the non-HIV infected
-\cite{Unaids2014-ue, Samji2013-kf}, which we quantified by randomly
+\cite{Samji2013-kf, Unaids2014-ue}, which we quantified by randomly
 sampling the parameter $\omega$ from $\Uniform(5, 8)\;\text{y}$.
@@
   \label{force_of_infection}
+  \lambda =
+  \frac{\eta \big[\beta_A A + \beta_U (U + D + T) + \beta_V V\big]}{N},
+\end{equation}
+sexually active population size $N = S + R + A + U + D + T + V$.  We
+assumed that people with AIDS ($W$) are too sick to be sexually
+active.
+
+The relative transmission rates of acute, unsuppressed, and suppressed
+infected people are
+\begin{equation}
+  \label{betas}
   \begin{split}
-    \lambda &= \frac{\beta_A A + \beta_U (U + D + T) + \beta_V V}{N},
+    \beta_A &= 1 - (1 - \tau_A)^n,
     \\
-    N &= S + R +  A + U + D + T + V,
+    \beta_U &= 1 - (1 - \tau_U)^n,
     \\
-    \beta_A &= \eta \left[1 - (1 - \tau_A)^n\right]
-    \\
-    \beta_U &= \eta \left[1 - (1 - \tau_U)^n\right]
-    \\
-    \beta_V &= \eta \left[1 - (1 - \tau_V)^n\right]
-    \\
-    \tau_V &= \varepsilon \tau_U,
+    \beta_V &= 1 - (1 - \varepsilon \tau_U)^n,
   \end{split}
 \end{equation}
-where the $\tau$'s are the relative transmissibility of people with
+where the $\tau$'s are the relative transmissibilities of people with
 acute ($A$), unsuppressed ($U$ and $T$), and suppressed ($V$)
@@
 country-specific transmission rate (\autoref{model_fitting}).  For
-transmissibility during the acute phase, we sampled from
+transmissibility during the acute phase, we sampled $\tau_A$ from
 $\Triangular$(0.0039, 0.0082, 0.0150)
-\cite{Skarbinski2015-ni,Wawer2005-us}, whereas, for transmissibility
-for unsuppressed people, we sampled from
+\cite{Wawer2005-us, Skarbinski2015-ni}, whereas, for transmissibility
+for unsuppressed people, we sampled $\tau_U$ from
 $\Triangular(0.00077, 0.0014, 0.00251)$ \cite{Hughes2012-so}.  The
@@
 $\Triangular$ distribution.  (See \autoref{uncertainty} for a full
-description of $\BetaPERT(a, b, c)$.)  The annual number of coital $n$
-was sampled from $\Uniform(96, 108)$
-\cite{Wawer2005-us,Abdool_Karim2010-cm}.
+description of $\BetaPERT(a, b, c)$.)  The annual number of coital
+acts $n$ was sampled from $\Uniform(96, 108)$
+\cite{Wawer2005-us, Abdool_Karim2010-cm}.
 
@@
 proportion treated, $p_T(2015)$; and proportion with viral
-suppression, $p_V(2015)$ (\autoref{data_sources}) were used to
-initialize the model.  Due to a lack of data on acute infections, and
-since the acute phase is so much shorter than the other stages, we
+suppression, $p_V(2015)$ were used to initialize the model
+(\autoref{data_sources}).  Due to a lack of data on acute infections,
+and since the acute phase is so much shorter than the other stages, we
 assumed that initially there were no acute infections.  Due to a lack
@@
 \end{equation}
+
+The parametrized differential equations were solved numerically
+\cite[see][]{medlock2016-git} and five effectiveness outcomes were
+computed from the solutions.
+\begin{description}
+\item[New infections] New infections from 2015 to time $t$ are given
+  by $Y(t)$.
+
+\item[Per-capita incidence] At each solution time point, the
+  per-capita incidence was calculated as
+  \begin{equation}
+    i(t_j) = \frac{Y(t_j) - Y(t_{j - 1})}{M(t_j) (t_j - t_{j - 1})},
+  \end{equation}
+  where
+  \begin{equation}
+    M(t) = S(t) + R(t) + A(t) + U(t) + D(t) + T(t) + V(t) + W(t)
+  \end{equation}
+  is the total population size at time $t$.  The per-capita incidence
+  at the first time point was undefined.
+
+\item[PLHIV] At each solution time point, PLHIV was given by
+  \begin{equation}
+    A(t) + U(t) + D(t) + T(t) + V(t) + W(t).
+  \end{equation}
+
+\item[PLAIDS] PLAIDS is given by $W(t)$.
+
+\item[AIDS-related deaths] AIDS-related deaths from 2015 to time $t$
+  are given by $Z(t)$.
+
+\end{description}
+
+The results from the country simulations were aggregated to the
+regional and global levels by adding the numbers of people in each
+compartment over time and then new infections, per-capita incidence,
+PLHIV, PLAIDS, and HIV-related deaths were calculated from the
+aggregates.  (See Table S6 for the definitions of UNAIDS regions.)
 
@@
 \item[Status quo] The status quo target is for the proportions $p_D$,
-  $p_T$, and $p_V$ to remain fixed at their initial levels going
-  forward:
+  $p_T$, and $p_V$ to remain fixed at their initial levels (Table S5)
+  going forward:
   \begin{equation}
@@
 people aged 15--49 years \cite{The_World_Bank2016-fd} were obtained
-from the World Bank. Longitudinal HIV incidence and prevalence
-estimates for ages 15--49, spanning from as early as 1990 to 2015,
-were primarily derived from the AIDSinfo database produced by UNAIDS
-\cite{Unaids2016-an}. Other sources included UNAIDS Country Progress
-Reports \cite{Unaids2016-am} published from 2012 to 2016 and AIDS Data
-Hub \cite{AIDSdatahub-fg}, which compiles data from UNAIDS, UNICEF,
-WHO, and the Asian Development Bank. These sources were also used to
-inform the initial conditions for the model: the number of people
-diagnosed with HIV, the number on ART, and the number who have viral
-suppression or have been retained on treatment for at least 12
-months. Where data were not available from these sources, alternative
-resources such as peer-reviewed journal articles and country health
-ministry reports were consulted.  See Tables S2--S6 for full
-information on data sources for each country.  The data tables are
-also available in the public source-code repository
-\cite{medlock2016-git}.
+from the World Bank (Table S2). Longitudinal HIV prevalence (Table S3)
+and incidence (Table S4) estimates for ages 15--49, spanning from as
+early as 1990 to 2015, were primarily derived from the AIDSinfo
+database produced by UNAIDS \cite{Unaids2016-an}. Other sources
+included UNAIDS Country Progress Reports \cite{Unaids2016-am}
+published from 2012 to 2016 and AIDS Data Hub \cite{AIDSdatahub-fg},
+which compiles data from UNAIDS, UNICEF, WHO, and the Asian
+Development Bank. These sources were also used to inform the initial
+conditions for the model: the number of people diagnosed with HIV, the
+number on ART, and the number who have viral suppression or have been
+retained on treatment for at least 12 months (Table S5). Where data
+were not available from these sources, alternative resources such as
+peer-reviewed journal articles and country health ministry reports
+were consulted.  See Tables S2--S6 for full information on data
+sources for each country.  The data tables are also available in the
+public source-code repository \cite{medlock2016-git}.
 
@@
 
-Using available historical data for incidence and prevalence, and
-published transmission estimates, we estimated transmission rates for
-people with acute infection, unsuppressed viral load and suppressed
-viral load. Our calibration method provided a recent snapshot of
-country-specific transmission, while using historical data to smooth
-out variations.
+Using available historical country-level data for prevalence and
+incidence (Tables S3 and S4), and published transmissibility estimates
+\cite{Wawer2005-us,Donnell2010-xo,Hughes2012-so,Skarbinski2015-ni}, we
+estimated an average country-specific transmission rate, which then
+informs the acute, unsuppressed, and suppressed transmission rates.
+This calibration method provided a recent snapshot of country-specific
+transmission, while using historical data to smooth out short-term
+variations.
 
-We first estimated country-specific rates of HIV transmission for each
-of the available historical data point for incidence and
-prevalence. The calculation involved a simplified force of infection
-that initially assumed no differences in transmission risk among
-acute, unsuppressed, suppressed, and AIDS classes due to the general
-lack of historical data on diagnosis and treatment. We calculated a
-time-independent aggregate transmission rate by taking an exponential
-weighted mean of the historical (i.e., time-dependent) transmission
-rates for each given country (\autoref{transmission_rate}). The
-aggregate transmission rate was then combined with estimated HIV
-transmission risk by stage of HIV infection
-\cite{Hollingsworth2008-iy} and treatment status \cite{Wawer2005-us}
-to calculate separate transmission rates for unsuppressed, acute, and
-viral-suppression people. These rates were used to simulate model
-projections through 2035.
-
-{We calibrated longitudinal HIV incidence and prevalence data from
-  1990 to 2015 incidence in addition to data on $p_{D}$, $p_{T}$ and
-  $p_{V}$ levels in 2015 to estimate the rate of transmission for each
-  country. The calculation involved a simplified force of infection:}
-
+For each country, we first estimated rates of HIV transmission for
+each of the available historical data points for prevalence and
+incidence.  The calculation involved approximating the simplified
+force of infection
 \begin{align}
@@
   \begin{split}
-  \lambda(t) &  =    \frac{\beta_{A} A + \beta_{U}(U+D+T)+\beta_{V}V+0
-               W}{N} \\
-             &  =  \beta \frac{I}{N},
+    \lambda(t) &= \frac{\eta \left[\beta_{A} A(t)
+        + \beta_{U} \big(U(t) + D(t) + T(t)\big) +
+        \beta_{V} V(t)\right]}{N(t)}
+    \approx  \beta(t) \frac{I(t)}{N(t)},
   \end{split}
 \end{align}
-where $\beta$ is the estimated time-independent aggregate transmission rate under the
-assumption that there is no difference in transmission risk among acute, unsuppressed, suppressed, and AIDS classes.
-
-$I = A+U+D+T+V+W$ is the total number of people living with HIV. Therefore, the per-capita
-incidence is
+where $\beta$ is the estimated time-independent aggregate transmission
+rate under the approximation that there is no difference in
+transmission risk among acute, unsuppressed, suppressed, and AIDS
+classes, and $I = A + U + D + T + V + W$ is the total number of
+PLHIV.  Therefore, the per-capita incidence is
 \begin{equation}
 i(t) = \lambda(t) \frac{S(t)}{N(t)}
-= \beta(t) \frac{I(t)}{N(t)} \frac{S(t)}{N(t)} =\beta(t) p(t) (1-p(t)),
+\approx \beta(t) \frac{I(t)}{N(t)} \frac{S(t)}{N(t)} =\beta(t) p(t) (1-p(t)),
 \end{equation}
-where $p(t)$ is the prevalence. Thus, we can estimate the
-transmission rate at each historical time point using the incidence
-and prevalence data,
+where $p(t)$ is the prevalence. Thus, we estimated the transmission
+rate at each historical time point using the incidence and prevalence
+data by
 \begin{equation}
   \label{trans_rate}
-  \beta(t) = \frac{i(t)}{p(t)(1-p(t))}
+  \beta(t) \approx \frac{i(t)}{p(t)(1-p(t))}.
 \end{equation}
 
-We estimated the time-independent aggregated transmission rate ($\beta$)
-by taking the exponential weighted mean of transmission rates
-\eqref{trans_rate}.
-
-Rearranging equation \eqref{foi}, the transmission rate for PLHIV
-without viral suppression can be written as
+To capture the uncertainty in $\beta(t)$, we assumed that it follows a
+lognormal distribution (\autoref{uncertainty}).  To capture the recent
+transmission behavior while still allowing for the use of less-recent
+data to smooth short-term variations, for the parameters $\mu$ and
+$\sigma^2$ of the lognormal distribution we used the exponentially
+weighted mean and variance \cite{holt2004} over time, with half-life
+1\;y, of $\log \beta(t)$ for the year 2015
+(\autoref{transmission_rate}).  That is,
 \begin{equation}
-\label{betaU}
-  \beta_{U} = \frac{\beta I}{\frac{\beta_{A}}{\beta_{U}}A +
-    U+D+T+\frac{\beta_{V}}{\beta_{U}}V}
+  \begin{split}
+    \mu &= \frac{\sum_{i = 1}^n  0.5^{2015 - t_i} \log \beta(t_i)}
+    {\sum_{i = 1}^n 0.5^{2015 - t_i}},
+    \\
+    \sigma^2 &= \frac{\left[\sum_{i = 1}^n 0.5^{2015 - t_i}\right]
+      \left[\sum_{i = 1}^n  0.5^{2015 - t_i}
+        \big(\log \beta(t_i) - \mu\big)^2\right]}
+    {\left[\sum_{i = 1}^n 0.5^{2015 - t_i}\right]^2
+      - \sum_{i = 1}^n \left(0.5^{2015 - t_i}\right)^2}.
+  \end{split}
 \end{equation}
 
-Next, we assumed that the relative risk of acute HIV transmission
-($\beta_{AU} = \beta_{A}/\beta_{U}$) and virally suppressed HIV
-transmission ($\beta_{VU} = \beta_{V}/\beta_{U}$) with respect to the
-unsuppressed transmission remains constant worldwide and calculated
-these values using the data from Rakai, Uganda
-\cite{Wawer2005-us}. The aggregate rate of transmission ($\beta$) can
-then be combined with eqs.~\eqref{betaU} to calculate transmission
-rates for unsuppressed PLHIV, acute PLHIV and suppressed PLHIV as,
-\begin{align}
-  \beta_{U} & = \frac{\beta I}{\beta_{AU}A +
-              U+D+T+\beta_{VU}V}, \\
-  \beta_{A} & = \beta_{AU}\beta, \\
-  \beta_{V} & = \beta_{VU} \beta.
-\end{align}
-that we use to simulate our model forward and project results up to 2035.
-\\
+\begin{figure}
+  \centering
+  \includegraphics{../Codes/plots/transmission_rate.pdf}
+  \caption{Country-specific distributions of transmission rate,
+    $\beta$, calculated based on historical country prevalence and
+    incidence.  See \autoref{model_fitting}.}
+  \label{transmission_rate}
+\end{figure}
 
-\comment{Need to add stuff about how we generate distribution of
-  transmission rates}
+For each of the 1000 model parameter samples, the country-level
+aggregate transmission rate $\beta$ was sampled, along with the
+transmissibilities for acute and unsuppressed infected people,
+$\tau_A$ and $\tau_U$; the transmission reduction by suppression,
+$\varepsilon$; and the annual number of coital acts, $n$
+(\autoref{model}).  From the latter samples, the relative transmission
+rates for the acute phase ($\beta_A$), for unsuppressed chronic
+infections ($\beta_U$), and for chronic infections with viral
+suppression ($\beta_V$) were calculated by
+eqs.~\eqref{force_of_infection}.  The sample value of the
+country-level transmission rate was then computed by
+\begin{equation}
+  \label{eta}
+  \eta = \frac{\beta I(2015)}{
+    \beta_A A(2015) + \beta_U \big(U(2015) + D(2015) + T(2015)\big)
+    + \beta_V V(2015)},
+\end{equation}
+derived by rearranging eq.~\eqref{foi}, and uses the model initial
+conditions eq.~\eqref{initial_conditions}.
 
@@
 
-\begin{figure}
-  \centering
-  \includegraphics{../Codes/plots/transmission_rate.pdf}
-  \caption{Country-specific transmission rates were calculated based
-    on the relative contributions of people with acute infection,
-    unsuppressed viral load or suppressed viral load to overall
-    transmission (\autoref{model_fitting}). The estimates were
-    calibrated to data on country-level incidence and/or prevalence to
-    account for variation in historical incidence while accurately
-    reflecting recent HIV rates.}
-  \label{transmission_rate}
-\end{figure}
-
 \section{Uncertainty analysis}
@@
 (\autoref{model_param}) and the country-specific estimated
-distribution of the transmission rate (\autoref{model_fitting}). We
-evaluated the global and country-level impacts of meeting the UNAIDS
-targets and vaccine deployment on four outcome measures: HIV
-incidence, PLHIV, PLAIDS, and AIDS-related deaths between 2015 and
-2035. Our base-case scenario assumed maintenance of the status quo:
-that 2015 levels of the proportion of PLHIV diagnosed (pD), proportion
-of those diagnosed on ART (pT), and proportion of those on treatment
-who have achieved viral suppression (pV) continue unchanged until
-2035. The intervention scenarios were (1.) the attainment of the
-90–90–90 target by linear increases in pD, pT, and pV until 2020
-followed by maintenance of those levels until 2035, and (2.) linear
-increase in the diagnosis and treatment levels to the 90–90–90 target
-by 2020, a linear increase from 90–90–90 to the 95–95–95 target by
-2030, and maintenance of the 95–95–95 levels to 2035. (For 90–90–90,
-if any initial level was above 90\%, it was kept constant going
-forward so that the intervention did not worsen coverage.  Likewise,
-for 95–95–95, any initial level above 95\% was kept constant.)  For
-vaccination, we assumed deployment of a vaccine with 50\% efficacy in
-2020 with coverage increasing linearly by 25\% per year, continuing up
-to 70\% at 2.8 years post-rollout, and maintaining constant 70\%
-coverage thereafter.  We also performed a partial rank correlation
-coefficient (PRCC) sensitivity analysis for each model parameter and a
-scenario analysis to account for uncertainty in the profile of the
-prospective vaccine.
+distribution of the transmission rate (\autoref{model_fitting}). The
+parameters were sampled using Latin hypercube sampling
+\cite{blower1994}.  We also used the variance reduction technique of
+running different interventions with the same parameter samples, i.e.,
+one set of sample parameter values is drawn, status quo and
+intervention scenarios are all run with those sample values and
+compared, and this process is repeated for each of the 1000 sample
+sets of parameters \cite{shechter2006}.
 
-$\Uniform(a, b)$ is the uniform random variable with minimum $a$
-and maximum $b$: it has density function
+The model outcomes were summarized using the median, 1st and 3rd
+quartiles (i.e., 25th and 75th percentiles), and 5th and 95th
+percentiles.  We calculated partial rank correlation coefficients
+(PRCC) \cite{blower1994} to measure the independent effect of each
+non-vaccine parameter on model projections of global new HIV
+infections from 2015 to 2035 (\autoref{PRCCs}).
+
+\begin{figure}
+  \centering
+  \includegraphics{../Codes/plots/prcc.pdf}
+  \caption{Sensitivity of global infections averted from 2015 to 2035
+    to model parameters.  Left is the sensitivity of infections
+    averted by 95--95--95, relative to status quo.  Right is the
+    sensitivity of vaccination with status quo levels of diagnosis and
+    treatment, relative to status quo.  Sensitivity is measured by the
+    partial rank correlation coefficient (PRCC).}
+  \label{PRCCs}
+\end{figure}
+
+Given that vaccine parameters have not yet been quantified, we chose
+plausible baseline values (efficacy 50\%, ultimate coverage 70\%,
+speed of rollout 25\% per year, year vaccine is first available 2020)
+and examined uncertainty by simulating 6 additional vaccine scenarios,
+varying efficacy (30\%, 70\%), ultimate coverage (50\%, 90\%), speed
+of rollout (10\% coverage per year), and first year of availability
+(2025; Figure 4).  The vaccine scenario analysis was done using the
+modes from the parameter distributions, not samples from these
+distributions, to reduce the computation time.
+
+We used several probability distributions to quantify the parameters.
+\begin{description}
+\item[Uniform] $\Uniform(a, b)$ is the uniform random variable with
+  minimum $a$ and maximum $b$, which has density function
   \begin{equation}
     \label{uniform}
-  p_{\Uniform}(x) =
+    f_{\Uniform}(x) =
     \begin{cases}
@@
   $\frac{b - a}{2}$.
-%
-$\Triangular(a, b, c)$ is the triangular random variable
-distribution with minimum $a$, mode $b$, and maximum $c$: it has
-density function
+
+\item [Triangular] $\Triangular(a, b, c)$ is the triangular random
+  variable distribution with minimum $a$, mode $b$, and maximum $c$.
+  It has density function
   \begin{equation}
     \label{triangular}
-  p_{\Triangular}(x) =
+    f_{\Triangular}(x) =
     \begin{cases}
@@
   \end{equation}
-$\BetaPERT(a, b, c)$ is the beta-PERT probability distribution
-\cite{malcom1959} with minimum $a$, mode $b$, and maximum $c$: it has
-density function
+
+\item[Beta-PERT] $\BetaPERT(a, b, c)$ is the Beta-PERT probability
+  distribution \cite{malcom1959} with minimum $a$, mode $b$, and
+  maximum $c$.  It has density function
   \begin{equation}
-  \label{betaPERT}
-  p_{\BetaPERT}(x) =
+    \label{BetaPERT}
+    f_{\BetaPERT}(x) =
     \begin{cases}
@@
   We used the standard value of $\lambda = 4$.
-%
-$\Lognormal(\mu, \sigma^2)$ is the lognormal random variable: it has
-density function
+
+\item[Lognormal] $\Lognormal(\mu, \sigma^2)$ is the lognormal random
+  variable, which has density function
   \begin{equation}
-  p_{\Lognormal}(x) = \frac{1}{x \sigma \sqrt{2 \pi}}
+    f_{\Lognormal}(x) = \frac{1}{x \sigma \sqrt{2 \pi}}
     \exp\left(- \frac{\left(\log x - \mu\right)^2}{2 \sigma^2}\right).
   \end{equation}
-
-\comment{Vaccine scenarios.}
-
-\section{Analysis}
-
-We evaluated the global and country-specific impacts of meeting the
-UNAIDS targets and vaccine deployment on four outcome measures: HIV
-incidence, PLHIV, number of people with AIDS, and AIDS-related deaths
-between 2015 and 2035. Calibrating our model to historical data on
-prevalence and incidence, we projected the anticipated trajectories of
-the outcomes using country-specific transmission rates across the
-intervention scenarios outlined below.  Our base-case scenario assumed
-maintenance of the status quo: that 2015 levels of the proportion of
-PLHIV diagnosed ($p_{D}$), proportion of those diagnosed on ART
-($p_{T}$), and proportion of those on treatment who have achieved
-viral suppression ($p_{V}$) continue unchanged until 2035.  The
-intervention scenarios were 1.) the attainment of the 90--90--90
-target by linear increases in $p_{D}$, $p_{T}$, and $p_{V}$ until 2020
-followed by maintenance of those levels until 2035, and 2.) linear
-increase in the diagnosis and treatment levels to the 90--90--90
-targets by 2020, a linear increase from 90--90--90 to the 95--95--95
-target by 2030, and maintenance of the 95--95--95 levels to 2035. (For
-90--90--90, if any initial level was above 90\%, it was kept constant
-going forward so that the intervention did not worsen coverage.
-Likewise, for 95--95--95, any initial level above 95\% was kept
-constant.)  For vaccination, we assumed deployment of a vaccine with
-50\% efficacy in 2020 with coverage increasing linearly from 0\% to
-50\% at 2 years post-rollout and maintaining constant coverage after
-reaching 70\%. The added benefit of vaccination was considered in the
-context of status quo diagnosis and treatment, achieving the UNAIDS
-90–90–90 goal by 2020 followed by maintenance, and achieving the
-95–95–95 goal by 2030 followed by maintenance.  Projections were
-generated through model simulations based on published parameter
-distributions (\autoref{model_param}) and country-specific estimated
-transmission rate distributions. The parameters were sampled using
-latin hypercube sampling \cite{blower1994} and the variance reduction
-technique of running different interventions with random parameter
-values \cite{shechter2006}.
-
-Model outcomes were projected until 2035 for each of the 127 countries
-with sufficient data on status quo rates of diagnosis and treatment
-and on historical incidence or prevalence
-(\hyperref[effectiveness_Global]{\autoref*{effectiveness_Global}}--\ref{effectiveness_Zimbabwe}). The
-median estimates with interquartile ranges are presented between 2015
-and 2035 for number of PLHIV, per-capita incidence, PLAIDS, and number
-of HIV-related deaths under the status quo and five intervention
-scenarios: vaccination only, attaining the UNAIDS 90--90--90 target,
-attaining the 90--90--90 target and vaccination, attaining the UNAIDS
-95--95--95 target, and attaining the 95--95--95 target and
-vaccination.  The results from the country were aggregated to the
-regional and global levels by adding the numbers of people in each
-compartment over time and then PLHIV, per-capita incidence, PLAIDS,
-and HIV-related deaths were calculated from the aggregates.
-
-We calculated partial rank correlation coefficients (PRCC)
-\cite{blower1994} to measure the independent effect of each parameter
-on model projections of HIV incidence (\autoref{PRCCs}). Furthermore,
-due to uncertainty surrounding the prospective vaccine, we obtained
-model projections using six additional vaccine scenarios by
-considering alternative estimates of efficacy (30\%, 70\%), coverage
-(50\%, 90\%), speed of scale up (10\% coverage per year), and first
-year of availability (2025).
-
-\begin{figure}
-  \centering
-  \includegraphics{../Codes/plots/prcc.pdf}
-  \caption{Parameter sensitivity of global infections averted from
-    2015 to 2035.  Left is the parameter sensitivity of infections
-    averted by 95--95--95, relative to status quo.  Right is the
-    parameter sensitivity of vaccination with status quo levels of
-    diagnosis and treatment, relative to status quo.  Sensitivity is
-    measured by the partial rank correlation coefficient (PRCC).}
-  \label{PRCCs}
-\end{figure}
+\end{description}
 
@@
 \vspace*{3in}
-\section{Model results by region and country}
+\section{Global, regional, and per-country effectiveness}
 \newpage

### 2016-08-22 Documents/supplementary_text.tex
A few tweaks to supplement.

@@
 We chose to consider only these ages because they are the vast
-majority of PLHIV---93\% in 2014 \cite{UNICEF}---and because HIV and
-demographic data are often stratified into these ages, although some
-data used to parametrize the model was only available for ages
-$15$--$49$ rather than for ages $15$ and older.  The background
-mortality rate ($\mu$) in each of the 127 countries was collected from
-published estimates \cite{World_Development_Indicators2013-ee}.  The
-recruitment rate ($\kappa$) into the age $15\;\text{y}$ and older
-group was set by the difference between the country's population
-growth rate \cite{WorldBankpg} and its background mortality rate
+majority of global PLHIV---93\% in 2014 \cite{UNICEF}, because HIV and
+demographic data are often stratified into ages $15$--$49$, and to
+capture the continuing burden of infections in people ages $50$ and
+older.
+
+The background mortality rate ($\mu$) in each of the
+127 countries was collected from published estimates
+\cite{World_Development_Indicators2013-ee}.  The recruitment rate
+($\kappa$) into the age $15\;\text{y}$ and older group was set by the
+difference between the country's population growth rate
+\cite{WorldBankpg} and its background mortality rate
 \cite{World_Development_Indicators2013-ee}, as would be true if the
@@
 peer-reviewed journal articles and country health ministry reports
-were consulted.  See Tables S2--S6 for full information on data
+were consulted.  See Tables S2--S5 for full information on data
 sources for each country.  The data tables are also available in the

### 2016-08-22 Documents/cover_letter.tex
* Add cover_letter.tex
* Add Makefile to build diagram_standalone.png and others.

* Add delay in drive_upload.py for too-fast responses from Google.

* Save png at high resolution.

\documentclass{jpmletter}

\begin{document}
  \begin{letter}{}

    \opening{Dear Editorial Board of Science,}

    Please find enclosed our manuscript ``Effectiveness of UNAIDS
    targets and HIV vaccination across 127 countries,'' which we are
    submitting to Science as a Report.

    An estimated 37 million people are currently living with HIV. To
    promote higher rates of diagnosis, treatment, and viral
    suppression, the Joint United Nations Programme on HIV/AIDS
    (UNAIDS) has established the 90–90–90 and 95–95–95
    targets. Additionally, recent advances in the development of an
    HIV vaccine have been promising. To evaluate the effectiveness of
    the UNAIDS goals and HIV vaccination, both individually and in
    combination, to turning the tide on the HIV pandemic, we developed
    a mathematical model of HIV progression, transmission, and
    intervention, which we tailored to each of 127 countries that
    collectively harbor over 99\% of HIV infections worldwide.

    This is the first modeling analysis to evaluate the 95–95–95
    UNAIDS target as well as the first assessment of the global impact
    of potential HIV vaccination programs. Our results show that,
    relative to maintaining status quo rates of diagnosis and
    treatment, cumulative global HIV incidence in 2035 would be 54\%
    and 67\% lower upon meeting the 90–90–90 and 95–95–95 targets,
    respectively. The addition of a 50\%-efficacy vaccine in 2020
    gradually scaled up to 70\% coverage, could achieve a further 26\%
    reduction by 2035 beyond the 95–95–95 target alone.

    Our results also demonstrate the importance of evaluating
    country-level as well as global intervention effectiveness in the
    prioritization of interventions for country-specific policies. In
    many countries, including the US, Uganda, and Nigeria, the UNAIDS
    goals, as ambitious as they are, would be insufficient to reverse
    the growth of PLHIV without at least a partially efficacious
    vaccine. Even in countries for which UNAIDS goals are sufficient
    to turn the tide on the HIV epidemic, such as India, Tanzania, and
    Ethiopia, vaccination would greatly accelerate elimination, saving
    millions of lives annually.

    Thank you for your consideration. We look forward to hearing from
    you.

    \closing{Sincerely,}

  \end{letter}

\end{document}

### 2016-08-22 Codes/plots/drive_upload.py

@@ -5,6 +5,7 @@ Upload figures etc to Google Drive.
 
 import os.path
 import sys
+import time
 
 sys.path.append('..')
 import drive
@@ -31,7 +32,12 @@ folderId = '0B_53qFSHU3XKNjc0d3lTV2s4cWM'
 
 
 if __name__ == '__main__':
+    first = True
     with drive.Driver(parent = folderId) as d:
+        if not first:
+            time.sleep(1)
+        else:
+            first = False
         for f in files:
             try:
                 d.upload_if_newer(f)

### 2016-08-22 Documents/supplementary_text.tex
Final tweak to exponentially weighted formulas.
One more final tweak to exponentially weighted formulas.
Add SI edits from Laura and Abhi

@@
 (\autoref{model_param}).  The model is deterministic, but uncertainty
-in the parameters is treated by running the model many times with
+in the parameters is treated by running the model 1000 times with
 samples from the parameter distributions (\autoref{uncertainty}) and
@@
       & --- \\
-      $\zeta$ & Vaccination rate & See eqs.~(\ref{vaccination_rate}) & --- \\
+      $\zeta$ & Vaccination rate & See eq.~(\ref{vaccination_rate}) & --- \\
       \hline
@@
       efficacy, $50\%$ was the baseline, and $30\%$ and $70\%$ were
-      also used in scenario analysis.}
+      also used in a scenario analysis.}
     \label{model_param}
@@
 acute ($A$), unsuppressed ($U$ and $T$), and suppressed ($V$)
-infections, $n$ is the annual number of coital acts, and $\eta$ is the
-country-specific transmission rate (\autoref{model_fitting}).  For
+infections, $n$ is the annual number of coital acts, and $\epsilon$ is the
+relative transmissibility with viral suppression.  For
 transmissibility during the acute phase, we sampled $\tau_A$ from
@@
 without suppression has been estimated at 0.08 (95\% confidence
-interval 0.002, 0.57) \cite{Donnell2010-xo}: because of the extremely
+interval 0.002, 0.57) \cite{Donnell2010-xo}: due to the extremely
 long left tail, we chose to sample the relative transmissibility
@@
 suppression, $p_V(2015)$ were used to initialize the model
-(\autoref{data_sources}).  Due to a lack of data on acute infections,
+(\autoref{data_sources}). Although the initial population fell in the 15--49 age group
+to account for available data, model projections allowed for analysis of aging beyond 50 years.
+Due to a lack of data on acute infections,
 and since the acute phase is so much shorter than the other stages, we
@@
   $p_T$, and $p_V$ to remain fixed at their initial levels (Table S5)
-  going forward:
+  going forward. That is,
   \begin{equation}
@@
 informs the acute, unsuppressed, and suppressed transmission rates.
-This calibration method provided a recent snapshot of country-specific
-transmission, while using historical data to smooth out short-term
-variations.
 
@@
 
-To capture the uncertainty in $\beta(t)$, we assumed that it follows a
-lognormal distribution (\autoref{uncertainty}).  To capture the recent
+To reflect the uncertainty in $\beta(t)$, we assumed that it follows a
+lognormal distribution (\autoref{uncertainty}). For the parameters $\mu$ and
+$\sigma^2$ of the lognormal distribution we used the exponentially
+weighted mean and variance \cite{holt2004} over time (with half-life
+1\;y) of $\log \beta(t)$ for the year 2015. The approach captured the recent
 transmission behavior while still allowing for the use of less-recent
-data to smooth short-term variations, for the parameters $\mu$ and
-$\sigma^2$ of the lognormal distribution we used the exponentially
-weighted mean and variance \cite{holt2004} over time, with half-life
-1\;y, of $\log \beta(t)$ for the year 2015
+data to smooth short-term variations,
 (\autoref{transmission_rate}).  That is,
@@
   \begin{split}
-    \mu &= \frac{\sum_{i = 1}^n  0.5^{2015 - t_i} \log \beta(t_i)}
-    {\sum_{i = 1}^n 0.5^{2015 - t_i}},
+    \mu &= \frac{\sum_{i = 1}^n  2^{t_i}
+      \log \beta(t_i)}
+    {\sum_{i = 1}^n 2^{t_i}},
     \\
-    \sigma^2 &= \frac{\left[\sum_{i = 1}^n 0.5^{2015 - t_i}\right]
-      \left[\sum_{i = 1}^n  0.5^{2015 - t_i}
+    \sigma^2 &= \frac{\big(\sum_{i = 1}^n 2^{t_i}\big)
+      \left[\sum_{i = 1}^n  2^{t_i}
         \big(\log \beta(t_i) - \mu\big)^2\right]}
-    {\left[\sum_{i = 1}^n 0.5^{2015 - t_i}\right]^2
-      - \sum_{i = 1}^n \left(0.5^{2015 - t_i}\right)^2}.
+    {\big(\sum_{i = 1}^n 2^{t_i}\big)^2
+      - \sum_{i = 1}^n 2^{2 t_i}}.
   \end{split}
@@
 Projections were generated for each country through model simulations
-using 1000 random samples from published parameter distributions
+using 1000 random draws from published parameter distributions
 (\autoref{model_param}) and the country-specific estimated
@@
 intervention scenarios are all run with those sample values and
-compared, and this process is repeated for each of the 1000 sample
-sets of parameters \cite{shechter2006}.
+compared, and this process is repeated for each of the 1000
+parameter sets \cite{shechter2006}.
 
@@
 
-Given that vaccine parameters have not yet been quantified, we chose
-plausible baseline values (efficacy 50\%, ultimate coverage 70\%,
-speed of rollout 25\% per year, year vaccine is first available 2020)
-and examined uncertainty by simulating 6 additional vaccine scenarios,
-varying efficacy (30\%, 70\%), ultimate coverage (50\%, 90\%), speed
-of rollout (10\% coverage per year), and first year of availability
-(2025; Figure 4).  The vaccine scenario analysis was done using the
-modes from the parameter distributions, not samples from these
-distributions, to reduce the computation time.
+Given that vaccine parameters have not yet been quantified, we
+restricted the number of unknowns by keeping vaccine efficacy constant
+over time. This assumption is based on proposed vaccine regimens that
+include boosters for sustaining immunogenicity. We chose plausible
+baseline values for the included vaccine parameters (efficacy 50\%,
+ultimate coverage 70\%, speed of rollout 25\% per year, year vaccine
+is first available 2020) and examined uncertainty by simulating 6
+additional vaccine scenarios, varying efficacy (30\%, 70\%), ultimate
+coverage (50\%, 90\%), speed of rollout (10\% coverage per year), and
+first year of availability (2025; Figure 4). The vaccine scenario
+analysis was done using the modes from the parameter distributions,
+not samples from these distributions, to reduce the computation time.
 

### 2016-08-22 Documents/supplementary_text.tex
Final tweaks to supplement.

@@
 acute ($A$), unsuppressed ($U$ and $T$), and suppressed ($V$)
-infections, $n$ is the annual number of coital acts, and $\epsilon$ is the
-relative transmissibility with viral suppression.  For
+infections, $n$ is the annual number of coital acts, and $\varepsilon$
+is the relative transmissibility with viral suppression.  For
 transmissibility during the acute phase, we sampled $\tau_A$ from
@@
 without suppression has been estimated at 0.08 (95\% confidence
-interval 0.002, 0.57) \cite{Donnell2010-xo}: due to the extremely
-long left tail, we chose to sample the relative transmissibility
+interval 0.002, 0.57) \cite{Donnell2010-xo}: due to the extremely long
+left tail, we chose to sample the relative transmissibility
 $\varepsilon$ from $\BetaPERT(0.08, 0.002, 0.57)$ rather than a
@@
 acts $n$ was sampled from $\Uniform(96, 108)$
-\cite{Wawer2005-us, Abdool_Karim2010-cm}.
+\cite{Wawer2005-us, Abdool_Karim2010-cm}.  The country-specific
+transmission rate $\eta$ was estimated from each country's
+longitudinal HIV prevalence and incidence (\autoref{model_fitting}).
 
@@
 suppression, $p_V(2015)$ were used to initialize the model
-(\autoref{data_sources}). Although the initial population fell in the 15--49 age group
-to account for available data, model projections allowed for analysis of aging beyond 50 years.
-Due to a lack of data on acute infections,
-and since the acute phase is so much shorter than the other stages, we
-assumed that initially there were no acute infections.  Due to a lack
-of comprehensive data on PLAIDS in each country, we assumed that the
-proportion of diagnosed, untreated people ($D + W$) who have AIDS
-($W$) in year 2015 was
+(\autoref{data_sources}).  Although the initial population used ages
+15--49 due to data availability, model projections allowed for
+analysis of infected people aging beyond age 50.  Due to a lack of
+data on acute infections, and since the acute phase is so much shorter
+than the other stages, we assumed that initially there were no acute
+infections.  Due to a lack of comprehensive data on PLAIDS in each
+country, we assumed that the proportion of diagnosed, untreated people
+($D + W$) who have AIDS ($W$) in year 2015 was
 \begin{equation}
@@
 informs the acute, unsuppressed, and suppressed transmission rates.
+This calibration method provided a recent estimate of country-specific
+transmission, while using historical data to smooth out short-term
+variations.
 
@@
 To reflect the uncertainty in $\beta(t)$, we assumed that it follows a
-lognormal distribution (\autoref{uncertainty}). For the parameters $\mu$ and
-$\sigma^2$ of the lognormal distribution we used the exponentially
-weighted mean and variance \cite{holt2004} over time (with half-life
-1\;y) of $\log \beta(t)$ for the year 2015. The approach captured the recent
-transmission behavior while still allowing for the use of less-recent
-data to smooth short-term variations,
-(\autoref{transmission_rate}).  That is,
+lognormal distribution (\autoref{uncertainty}). For the parameters
+$\mu$ and $\sigma^2$ of the lognormal distribution we used the
+exponentially weighted mean and variance \cite{holt2004} over time
+(with half-life 1\;y) of $\log \beta(t)$ for the year 2015.  That is,
 \begin{equation}
@@
 \end{equation}
+A half-life of 1\;y means that the estimate of the transmission rate
+from year $i$ is weighted half as much as the estimate from year
+$i + 1$, a quarter as much as the estimate from year $i + 2$, and so
+on.  This approach captured the recent country-level transmission
+behavior while still allowing for the use of less-recent data to
+smooth short-term variations (\autoref{transmission_rate}).
 
@@
 Projections were generated for each country through model simulations
-using 1000 random draws from published parameter distributions
+using 1000 random samples from published parameter distributions
 (\autoref{model_param}) and the country-specific estimated
@@
 intervention scenarios are all run with those sample values and
-compared, and this process is repeated for each of the 1000
-parameter sets \cite{shechter2006}.
+compared, and this process is repeated for each of the 1000 sample
+sets of parameters \cite{shechter2006}.
 

### 2016-10-12 Documents/supplementary_text.tex
One last tweak to supplement.
Edits to supplement.

@@
 We chose to consider only these ages because they are the vast
-majority of global PLHIV---93\% in 2014 \cite{UNICEF}, because HIV and
-demographic data are often stratified into ages $15$--$49$, and to
-capture the continuing burden of infections in people ages $50$ and
-older.
+majority of global PLHIV, 93\% in 2014 \cite{UNICEF}; because
+population-level HIV estimates and demographic data are often
+stratified into ages $15$--$49$; and to capture the continuing burden
+of infections in people ages $50$ and older.
 
@@
 Transitions between model states are governed by a series of
-differential equations parametrized using values estimated from other
-studies and from incidence and prevalence data
-(\autoref{model_param}).  The model is deterministic, but uncertainty
-in the parameters is treated by running the model 1000 times with
-samples from the parameter distributions (\autoref{uncertainty}) and
-summarizing the model outcomes using the median, 1st and 3rd quartiles
-(i.e., 25th and 75th percentiles), and 5th and 95th percentiles.  Each
-country was modeled separately
+differential equations parametrized using values found in other
+studies, along with transmission rates derived from UNAIDS estimates
+of incidence and prevalence (\autoref{model_param}).  The model is
+deterministic, but uncertainty in the parameters is treated by running
+the model 1000 times with samples from the parameter distributions
+(\autoref{uncertainty}) and summarizing the model outcomes using the
+median, 1st and 3rd quartiles (i.e., 25th and 75th percentiles), and
+5th and 95th percentiles.  Each country was modeled separately
 (\hyperref[effectiveness_Afghanistan]{Figures
@@
 definition of $\Triangular(a, b, c)$ and other distributions.)  We
-assumed that people remain undiagnosed during their acute infection
+assumed that people remain undiagnosed during their acute-infection
 phase. After acute infection, people move into the chronic undiagnosed
@@
 \cite{Wawer2005-us, Abdool_Karim2010-cm}.  The country-specific
-transmission rate $\eta$ was estimated from each country's
-longitudinal HIV prevalence and incidence (\autoref{model_fitting}).
+transmission rate $\eta$ was derived from UNAIDS estimates of each
+country's longitudinal HIV prevalence and incidence
+(\autoref{model_fitting}).
 
-For year 2015, the number of people aged 15--49 years, $M(2015)$; the
-prevalence, $p_I(2015)$; the proportion diagnosed, $p_D(2015)$; the
-proportion treated, $p_T(2015)$; and proportion with viral
-suppression, $p_V(2015)$ were used to initialize the model
+For year 2015, estimates of the number of people aged 15--49 years,
+$M(2015)$; the prevalence, $p_I(2015)$; the proportion diagnosed,
+$p_D(2015)$; the proportion treated, $p_T(2015)$; and proportion with
+viral suppression, $p_V(2015)$ were used to initialize the model
 (\autoref{data_sources}).  Although the initial population used ages
-15--49 due to data availability, model projections allowed for
-analysis of infected people aging beyond age 50.  Due to a lack of
-data on acute infections, and since the acute phase is so much shorter
-than the other stages, we assumed that initially there were no acute
-infections.  Due to a lack of comprehensive data on PLAIDS in each
+15--49 due to the availability of published estimates, model
+projections allowed for analysis of infected people aging beyond age
+50.  Due to a lack of published estimates of acute infections, and
+since the acute phase is so much shorter than the other stages, we
+assumed that initially there were no acute infections.  Due to a lack
+of comprehensive estimates of the number of people with AIDS in each
 country, we assumed that the proportion of diagnosed, untreated people
@@
 The parametrized differential equations were solved numerically
-\cite[see][]{medlock2016-git} and five effectiveness outcomes were
+\cite[see][]{medlock2016-git} and four effectiveness outcomes were
 computed from the solutions.
@@
 
-\item[PLAIDS] PLAIDS is given by $W(t)$.
-
 \item[AIDS-related deaths] AIDS-related deaths from 2015 to time $t$
@@
 compartment over time and then new infections, per-capita incidence,
-PLHIV, PLAIDS, and HIV-related deaths were calculated from the
-aggregates.  (See Table S6 for the definitions of UNAIDS regions.)
+PLHIV, and HIV-related deaths were calculated from the aggregates.
+(See Table S6 for the definitions of UNAIDS regions.)
 
@@
   $t_1$ to $x_2$ at $t_2$ for $t_1 \leq t < t_2$, and is constant at
-  $x_2$ for $t \geq t_2$, and $F$ is as in \eqref{F}.
+  $x_2$ for $t \geq t_2$, and $F$ is as in eq.~\eqref{F}.
 
@@
 Target strategies were one of the three diagnosis and treatment
-targets (status quo, 90--90--90, or 95--95--95) combined with either
+targets (status quo, 90--90--90, or 95--95--95), combined with either
 no vaccination ($p_R^*(t) = 0$) or vaccination at some level of
@@
 
-For 127 countries, we found sufficient data to parametrize our model.
-Demographic data, including population growth rate \cite{WorldBankpg},
-death rate \cite{World_Development_Indicators2013-ee}, and number of
-people aged 15--49 years \cite{The_World_Bank2016-fd} were obtained
-from the World Bank (Table S2). Longitudinal HIV prevalence (Table S3)
-and incidence (Table S4) estimates for ages 15--49, spanning from as
-early as 1990 to 2015, were primarily derived from the AIDSinfo
-database produced by UNAIDS \cite{Unaids2016-an}. Other sources
-included UNAIDS Country Progress Reports \cite{Unaids2016-am}
-published from 2012 to 2016 and AIDS Data Hub \cite{AIDSdatahub-fg},
-which compiles data from UNAIDS, UNICEF, WHO, and the Asian
-Development Bank. These sources were also used to inform the initial
-conditions for the model: the number of people diagnosed with HIV, the
-number on ART, and the number who have viral suppression or have been
-retained on treatment for at least 12 months (Table S5). Where data
-were not available from these sources, alternative resources such as
-peer-reviewed journal articles and country health ministry reports
-were consulted.  See Tables S2--S5 for full information on data
-sources for each country.  The data tables are also available in the
-public source-code repository \cite{medlock2016-git}.
+For 127 countries, we found sufficient published estimates and data to
+parametrize our model.  Demographic data, including population growth
+rate \cite{WorldBankpg}, death rate
+\cite{World_Development_Indicators2013-ee}, and number of people aged
+15--49 years \cite{The_World_Bank2016-fd} were obtained from the World
+Bank (Table S2). Longitudinal HIV prevalence (Table S3) and incidence
+(Table S4) estimates for ages 15--49, spanning from as early as 1990
+to 2015, were primarily obtained from the AIDSinfo database produced
+by UNAIDS \cite{Unaids2016-an}. Other sources included UNAIDS Country
+Progress Reports \cite{Unaids2016-am} published from 2012 to 2016 and
+AIDS Data Hub \cite{AIDSdatahub-fg}, which compiles data from UNAIDS,
+UNICEF, WHO, and the Asian Development Bank. These sources were also
+used to inform the initial conditions for the model: the number of
+people diagnosed with HIV, the number on ART, and the number who have
+viral suppression or have been retained on treatment for at least 12
+months (Table S5). Where estimates or data were not available from
+these sources, alternative resources such as peer-reviewed journal
+articles and country health ministry reports were consulted.  See
+Tables S2--S5 for full information on the sources used for each
+country.  These source tables are also available in the public
+source-code repository \cite{medlock2016-git}.
 
@@
 
-Using available historical country-level data for prevalence and
-incidence (Tables S3 and S4), and published transmissibility estimates
+Using available historical country-level estimates of prevalence and
+incidence (Tables S3 and S4), and published estimates of
+transmissibility
 \cite{Wawer2005-us,Donnell2010-xo,Hughes2012-so,Skarbinski2015-ni}, we
-estimated an average country-specific transmission rate, which then
+derived an average country-specific transmission rate, which then
 informs the acute, unsuppressed, and suppressed transmission rates.
@@
 
-For each country, we first estimated rates of HIV transmission for
-each of the available historical data points for prevalence and
-incidence.  The calculation involved approximating the simplified
-force of infection
+For each country, we first derived time-dependent rates of HIV
+transmission for each of the available points in the historical
+estimates of prevalence and incidence.  The calculation involved
+approximating the simplified force of infection
 \begin{align}
@@
 \end{align}
-where $\beta$ is the estimated time-independent aggregate transmission
+where $\beta$ is the estimated time-dependent aggregate transmission
 rate under the approximation that there is no difference in
 transmission risk among acute, unsuppressed, suppressed, and AIDS
-classes, and $I = A + U + D + T + V + W$ is the total number of
-PLHIV.  Therefore, the per-capita incidence is
+classes, and $I = A + U + D + T + V + W$ is the total number of PLHIV.
+Therefore, the per-capita incidence is
 \begin{equation}
@@
 \end{equation}
-where $p(t)$ is the prevalence. Thus, we estimated the transmission
+where $p(t)$ is the prevalence. Thus, we calculated the transmission
 rate at each historical time point using the incidence and prevalence
-data by
+estimates by
 \begin{equation}
@@
 \begin{equation}
+  \label{lognormal_params}
   \begin{split}
@@
 on.  This approach captured the recent country-level transmission
-behavior while still allowing for the use of less-recent data to
+behavior while still allowing for the use of less-recent estimates to
 smooth short-term variations (\autoref{transmission_rate}).
@@
   \caption{Country-specific distributions of transmission rate,
-    $\beta$, calculated based on historical country prevalence and
-    incidence.  See \autoref{model_fitting}.}
+    $\bar{\beta}$, calculated based on UNAIDS historical estimates of
+    country prevalence and incidence.  See \autoref{model_fitting}.}
   \label{transmission_rate}
@@
 For each of the 1000 model parameter samples, the country-level
-aggregate transmission rate $\beta$ was sampled, along with the
+aggregate transmission rate $\bar{\beta}$ was sampled from
+$\Lognormal(\mu, \sigma^2)$ with the parameters given by
+eqs.~\eqref{lognormal_params}, and samples were also drawn for the
 transmissibilities for acute and unsuppressed infected people,
@@
 infections ($\beta_U$), and for chronic infections with viral
-suppression ($\beta_V$) were calculated by
-eqs.~\eqref{force_of_infection}.  The sample value of the
-country-level transmission rate was then computed by
+suppression ($\beta_V$) were calculated by eqs.~\eqref{betas}.  The
+sample value of the country-level transmission rate was then computed
+by
 \begin{equation}
   \label{eta}
-  \eta = \frac{\beta I(2015)}{
+  \eta = \frac{\bar{\beta} I(2015)}{
     \beta_A A(2015) + \beta_U \big(U(2015) + D(2015) + T(2015)\big)
@@
 derived by rearranging eq.~\eqref{foi}, and uses the model initial
-conditions eq.~\eqref{initial_conditions}.
+conditions eq.~\eqref{initial_conditions}.  This estimate of $\eta$ is
+derived for the 2015 estimates of the proportion of PLHIV divided
+among acute infections; undiagnosed, diagnosed, or treated infections;
+and virally suppressed infections.  Using the estimate of $\eta$ in
+projections for future times, when these proportions may change, may
+introduce bias.
 
-A few countries—e.g., Bulgaria, Timor-Leste, and Yemen—currently have
-low HIV prevalence but relatively high incidence, resulting in large
-estimated transmission rates, leading to rapid projected growth of
-their HIV epidemics by 2035. The apparent low prevalence and high
-incidence may, at least in part, be due to the resolution in UNAIDS
-data (0.1\% for prevalence, 0.01\% for annual per-capita incidence).
-Results for such countries should be considered in light of this
-limitation.
+A few countries—e.g., Bulgaria, Timor-Leste, and Yemen—are currently
+estimated by UNAIDS to have low HIV prevalence but relatively high
+incidence, resulting in large estimated transmission rates, leading to
+rapid projected growth of their HIV epidemics by 2035. The apparent
+low prevalence and high incidence may, at least in part, be due to the
+resolution in UNAIDS estimates (0.1\% for prevalence, 0.01\% for
+annual per-capita incidence).  Results for such countries should be
+considered in light of this limitation.
 
@@
 
-\clearpage
 \printbibliography

### 2016-10-17 Documents/supplementary_text.tex
Added some references.

@@
       viral suppression & $\BetaPERT$(0.08, 0.002, 0.57)
-      & \cite{Donnell2010-xo} \\
+      & \cite{Donnell2010-xo, attia_2009, wilson_2012, jia_2013,
+        rodger_2016} \\
       $n$ & Coital acts per year & $\Uniform$(96, 108)

### 2016-10-19 Documents/cover_letter.tex
Minor changes for Nature.

@@
 
-    \opening{Dear Editorial Board of Science,}
+    \opening{Dear Editorial Board of Nature,}
 
@@
     targets and HIV vaccination across 127 countries,'' which we are
-    submitting to Science as a Report.
+    submitting to \textit{Nature} as a Letter.
 
@@
     This is the first modeling analysis to evaluate the 95–95–95
-    UNAIDS target as well as the first assessment of the global impact
-    of potential HIV vaccination programs. Our results show that,
-    relative to maintaining status quo rates of diagnosis and
-    treatment, cumulative global HIV incidence in 2035 would be 54\%
-    and 67\% lower upon meeting the 90–90–90 and 95–95–95 targets,
-    respectively. The addition of a 50\%-efficacy vaccine in 2020
-    gradually scaled up to 70\% coverage, could achieve a further 26\%
-    reduction by 2035 beyond the 95–95–95 target alone.
+    UNAIDS target as well as the first broad-scale assessment of the
+    global impact of potential HIV vaccination programs. Our results
+    show that, relative to maintaining status quo rates of diagnosis
+    and treatment, cumulative global HIV incidence in 2035 would be
+    54\% and 67\% lower upon meeting the 90–90–90 and 95–95–95
+    targets, respectively. The addition of a 50\%-efficacy vaccine in
+    2020 gradually scaled up to 70\% coverage, could achieve a further
+    26\% reduction by 2035 beyond the 95–95–95 target alone.
 
@@
 
+    We believe our letter will be approximately 4 pages when
+    formatted.
+
     Thank you for your consideration. We look forward to hearing from

### 2016-10-19 Codes/plots/drive_upload.py

@@ -12,7 +12,7 @@ import drive
 
 
 files = (
-    '../../Documents/supplementary_text.pdf',
+    '../../Documents/supplementary_information.pdf',
     '../../Documents/diagram_standalone.pdf',
     '../../Documents/diagram_standalone.png',
     'effectiveness.pdf',

### 2016-10-19 Documents/extended_data_fig_2.tex
More changes for Nature.

--- 2016-08-22 Documents/supplementary_text.tex
@@
 
-\usepackage{amsmath}
 \usepackage{graphicx}
-\usepackage{tikz}
-
-\usepackage{enumitem}
-\setlist{topsep=1ex}
 
 \usepackage[font={sf}, labelfont={bf},
-  labelsep=period, singlelinecheck=off]{caption}
+            labelsep=space, singlelinecheck=off]{caption}
 \usepackage[font={sf}]{floatrow}
-\usepackage{tabularx}
-
-\usepackage[noblocks]{authblk}
-\renewcommand{\Authsep}{, }
-\renewcommand{\Authand}{ \& }
-\renewcommand{\Authands}{ \& }
-\renewcommand{\Affilfont}{\small}
 
@@
 
-\usepackage[style=science, article-title=true, maxnames=100]{biblatex}
-\addbibresource{supplementary_text.bib}
-\newcommand{\labeltitlepunc}{}
-\DeclareBibliographyDriver{incollection}{%
-  \usebibmacro{bibindex}%
-  \usebibmacro{begentry}%
-  \usebibmacro{author/translator+others}%
-  \setunit{\labelnamepunct}\newblock
-  \printlist{language}%
-  \newunit\newblock
-  \usebibmacro{byauthor}%
-  \newunit\newblock
-  \usebibmacro{title}%
-  \usebibmacro{in:}%
-  \usebibmacro{maintitle+booktitle}%
-  \newunit\newblock
-  \usebibmacro{byeditor+others}%
-  \newunit\newblock
-  \printfield{volumes}%
-  \newunit\newblock
-  \printfield{note}%
-  \newunit\newblock
-  \usebibmacro{publisher+location+date}%
-  \newunit\newblock
-  \printfield{volume}
-  \newunit
-  \usebibmacro{chapter+pages}%
-  \newunit\newblock
-  \iftoggle{bbx:isbn}
-    {\printfield{isbn}}
-    {}%
-  \newunit\newblock
-  \usebibmacro{doi+eprint+url}%
-  \newunit\newblock
-  \usebibmacro{addendum+pubstate}%
-  \setunit{\bibpagerefpunct}\newblock
-  \usebibmacro{pageref}%
-  \newunit\newblock
-  \usebibmacro{related}%
-  \usebibmacro{finentry}%
-}
-
-\newcommand{\comment}[1]{\textbf{[#1]}}
-\newcommand{\md}{\mathrm{d}}
-\newcommand{\mT}{\mathrm{T}}
-\renewcommand{\vec}[1]{\mathbf{#1}}
-\newcommand{\mat}[1]{\mathbf{#1}}
-\newcommand{\me}{\mathrm{e}}
-\DeclareMathOperator{\Uniform}{Uniform}
-\DeclareMathOperator{\Triangular}{Triangular}
-\DeclareMathOperator{\Lognormal}{Lognormal}
-\DeclareMathOperator{\BetaPERT}{Beta-PERT}
-
-\newcommand{\labelPrefix}{S}
-\renewcommand{\thesection}{\labelPrefix\arabic{section}}
-\renewcommand{\theequation}{\labelPrefix\arabic{equation}}
-\renewcommand{\thefigure}{\labelPrefix\arabic{figure}}
-\renewcommand{\thetable}{\labelPrefix\arabic{table}}
-\renewcommand{\figurename}{Fig.}
-
-\title{Supporting online material for\\
-  \emph{Effectiveness of UNAIDS targets and HIV vaccination across 127
-    countries}}
-
-\author[1*]{Jan Medlock}
-\author[2]{Abhishek Pandey}
-\author[2]{Alyssa S.~Parpia}
-\author[2]{Amber Tang}
-\author[2]{Laura A.~Skrip}
-\author[2]{Alison P.~Galvani}
-\affil[1]{Department of Biomedical Sciences, Oregon State University,
-  106 Dryden Hall, Corvallis, OR, 97331-4801, USA}
-\affil[2]{Center for Infectious Disease Modeling and Analysis, Yale
-  School of Public Health, 135 College Street, New Haven, USA}
-\affil[*]{To whom correspondence should be addressed.  E-mail:
-  \href{mailto:jan.medlock@oregonstate.edu}{
-    \texttt{jan.medlock@oregonstate.edu}}}
+\renewcommand{\figurename}{Extended Data Fig.}
+\setcounter{figure}{1}
 
 \begin{document}
-
-\maketitle
-
-The model simulation and analysis tools, written in Python, are
-publicly available at\\
-\url{https://github.com/janmedlock/HIV-95-vaccine/}
-\cite{medlock2016-git}.
-
-\section{Mathematical model}
-\label{model}
-
-We developed a country-level continuous-time, compartmental model that
-divides people aged $15$\;y and older into non-overlapping HIV states.
-We chose to consider only these ages because they are the vast
-majority of global PLHIV---93\% in 2014 \cite{UNICEF}, because HIV and
-demographic data are often stratified into ages $15$--$49$, and to
-capture the continuing burden of infections in people ages $50$ and
-older.
-
-The background mortality rate ($\mu$) in each of the
-127 countries was collected from published estimates
-\cite{World_Development_Indicators2013-ee}.  The recruitment rate
-($\kappa$) into the age $15\;\text{y}$ and older group was set by the
-difference between the country's population growth rate
-\cite{WorldBankpg} and its background mortality rate
-\cite{World_Development_Indicators2013-ee}, as would be true if the
-population was at its stable age structure.
-
-Our model has 8 HIV states (\autoref{model_diag}): susceptible to HIV
-infection ($S$ is the number of people susceptible), vaccinated
-against HIV ($R$), acute HIV infection ($A$), undiagnosed HIV
-infection ($U$), diagnosed but untreated HIV infection ($D$), treated
-without viral suppression ($T$), viral suppression ($V$), and having
-AIDS ($W$).  Viral suppression is defined as a viral load of less than
-1000 viral RNA copies per mL of blood.  Viral suppression not only
-extends survival but also dramatically reduces transmission
-\cite{vernazza2000, ioannidis2001, attia2009, May2014-gp}.
-Transitions between model states are governed by a series of
-differential equations parametrized using values estimated from other
-studies and from incidence and prevalence data
-(\autoref{model_param}).  The model is deterministic, but uncertainty
-in the parameters is treated by running the model 1000 times with
-samples from the parameter distributions (\autoref{uncertainty}) and
-summarizing the model outcomes using the median, 1st and 3rd quartiles
-(i.e., 25th and 75th percentiles), and 5th and 95th percentiles.  Each
-country was modeled separately
-(\hyperref[effectiveness_Afghanistan]{Figures
-  \ref*{effectiveness_Afghanistan}}--\ref{effectiveness_Zimbabwe}) and
-the country simulations were aggregated to calculate global and
-regional outcomes
-(\hyperref[effectiveness_Global]{Figures
-  \ref*{effectiveness_Global}}--\ref{effectiveness_Western_Europe}).
-
-\begin{figure}
-  \centering
-  \input{diagram}
-  \caption{Model diagram.}
-  \label{model_diag}
-\end{figure}
-
-\begin{table}
-  \begin{center}
-    \begin{tabularx}{\textwidth}{lXlll}
-      \hline
-      & Definition & Value & Reference \\
-      \hline
-      $\mu$ & Background death rate & Country specific, Table S2
-      & \cite{World_Development_Indicators2013-ee} \\
-      $\kappa$ & Recruitment rate & Country specific, Table S2
-      & \cite{World_Development_Indicators2013-ee, WorldBankpg} \\
-      $\delta$	& Rate of leaving acute infection
-      & $\Triangular$(2, 4.14, 9.6)\;y$^{-1}$
-      & \cite{Hollingsworth2008-iy} \\
-      $\sigma$	& Rate of developing AIDS without viral suppression
-      & 0.1064\;y$^{-1}$ & \cite{Morgan2002-cq} \\
-      $\theta$ & Rate of developing AIDS with viral suppression
-      & Eq.~(\ref{theta}) & --- \\
-      $\gamma$ & Rate of viral suppression
-      & $\Uniform$(0.5, 1.5)\;y$^{-1}$
-      & \cite{Currie2009-yz} \\
-      $\nu$ & Death rate from AIDS & 0.5\;y$^{-1}$
-      & \cite{Morgan2002-cq} \\
-      $\rho$ & Vaccine efficacy & 50\%\,[30\%, 70\%] & --- \\
-      $\omega$	& Reduction in lifetime with viral suppression
-      & $\Uniform$(5, 8)\;y
-      & \cite{Samji2013-kf, Unaids2014-ue} \\
-      $\tau_{A}$ & Transmissibility during acute phase
-      & $\Triangular$(0.0039, 0.0082, 0.0150)
-      & \cite{Wawer2005-us, Skarbinski2015-ni}\\
-      $\tau_{U}$ & Transmissibility after acute phase
-      & $\Triangular$(0.00077, 0.0014, 0.00251)
-      & \cite{Hughes2012-so} \\
-      $\varepsilon$ & Relative transmissibility with
-      viral suppression & $\BetaPERT$(0.08, 0.002, 0.57)
-      & \cite{Donnell2010-xo} \\
-      $n$ & Coital acts per year & $\Uniform$(96, 108)
-      & \cite{Wawer2005-us, Abdool_Karim2010-cm}\\
-      $\alpha$ & Diagnosis rate & See eq.~(\ref{diagnosis_rate}) & --- \\
-      $\phi$ & Treatment rate & See eq.~(\ref{treatment_rate}) & --- \\
-      $\psi$ & Rate of relapse to untreated & See eq.~(\ref{relapse_rate})
-      & --- \\
-      $\zeta$ & Vaccination rate & See eq.~(\ref{vaccination_rate}) & --- \\
-      \hline
-    \end{tabularx}
-    \caption{Model parameters. $\Triangular$, $\Uniform$, and
-      $\BetaPERT$ are sampling distributions: see
-      \autoref{uncertainty} for a full description.  For vaccine
-      efficacy, $50\%$ was the baseline, and $30\%$ and $70\%$ were
-      also used in a scenario analysis.}
-    \label{model_param}
-  \end{center}
-\end{table}
-
-People susceptible to HIV ($S$) progress to acute infection ($A$)
-according to the force of infection ($\lambda$,
-eq.~\eqref{force_of_infection}), which depends on the HIV transmission
-rate, estimated from the country-specific incidence and prevalence
-data (\autoref{model_fitting}), adjusted for the current number of
-acutely infected, untreated or ineffectively treated, and viral
-suppression PLHIV.  Acute infection is characterized by high viral
-loads and lasts an average of 2.90 [95\% confidence interval 1.23,
-6.00]\;months \cite{Hollingsworth2008-iy}.  (We converted these
-durations to rates like $1 / 2.90\;\text{month$^{-1}$} \approx
-4.14\;\text{y$^{-1}$}$ and set the parameter using random samples from
-$\Triangular(2, 4.14, 9.6)\;\text{y$^{-1}$}$ to capture the
-uncertainty in its value.  See \autoref{uncertainty} for the
-definition of $\Triangular(a, b, c)$ and other distributions.)  We
-assumed that people remain undiagnosed during their acute infection
-phase. After acute infection, people move into the chronic undiagnosed
-class ($U$).  People in the undiagnosed class will be diagnosed at the
-rate $\alpha$, which is determined by the country's current diagnosis
-level and its diagnosis target (\autoref{targets}).  Diagnosed people
-($D$) transition to the treated compartment ($T$) upon starting ART at
-the rate $\phi$, dependent on the country's current treatment level
-and its treatment target (\autoref{targets}).  After some time,
-treated people then transition to the viral-suppression class ($V$),
-at the rate $\gamma$.  We took $\gamma$ as a random sample from
-$\Uniform(0.5, 1.5)\;\text{y$^{-1}$}$, that is, viral suppression
-occurs after between 8 months and 2 years on treatment
-\cite{Currie2009-yz}.  Disengagement from treatment moves people from
-treated ($T$) and viral suppression ($V$) at the rate $\psi$,
-dependent on the current level of viral suppression and the country's
-target (\autoref{targets}), back to the diagnosed class ($D$).
-
-PLHIV without viral suppression (compartments $U$, $D$, and $T$)
-develop AIDS (compartment $W$) after an average duration of 10.4 y
-\cite{Morgan2002-cq}, i.e., with transition rate
-$\sigma = 0.1064\;\text{y$^{-1}$}$.  People who have achieved viral
-suppression ($V$) develop AIDS at rate $\theta$, slower than PLHIV
-without viral suppression.  People with viral suppression are
-estimated to live $5$--$8$\;y shorter lives than the non-HIV infected
-\cite{Samji2013-kf, Unaids2014-ue}, which we quantified by randomly
-sampling the parameter $\omega$ from $\Uniform(5, 8)\;\text{y}$.
-Assuming no relapse to untreated, the duration of viral suppression is
-\begin{equation}
-  \frac{1}{\theta + \mu} = \frac{1}{\mu} - \omega - \frac{1}{\nu}.
-\end{equation}
-The term to the left of the equals sign is the time until leaving
-viral suppression by either progression to AIDS (at rate $\theta$) or
-background mortality (at rate $\mu$).  The term to the right of the
-equals sign is the lifespan of the non-HIV infected, minus the
-reduction in life due to having HIV with viral suppression, minus the
-duration of the AIDS stage.  Solving for $\theta$ gives the rate of
-progression to AIDS with viral suppression as
-\begin{equation}
-  \label{theta}
-  \theta = \frac{1}{1/\mu - \omega - 1/\nu} - \mu.
-\end{equation}
-
-In scenarios with vaccine, susceptible people are vaccinated at rate
-$\zeta$, depending on the country's current vaccination coverage and
-its coverage target (\autoref{targets}), transitioning into the
-vaccinated compartment ($R$), where the vaccine reduces their force of
-infection by the efficacy factor $\rho$.  We took the base-case
-efficacy to be $50\%$ and varied it to $30\%$ and $70\%$ in analyzing
-vaccination scenarios (\autoref{uncertainty}).  We did not model
-specific vaccine dose regime, such that implicit in our efficacy
-parameter is the assumption that boosters will be used to maintain
-efficacy over time.  Without vaccine, $\zeta = 0$.
-
-We also added differential equations to track the cumulative number of
-new infections ($Y$) and AIDS deaths ($Z$) over the model period.
-
-The model equations are
-\begin{equation}
-  \label{model_eqns}
-  \begin{split}
-    \frac{\md S}{\md t} &= \kappa N - \lambda S - \zeta S- \mu S,
-    \\
-    \frac{\md R}{\md t} & = \zeta S - (1 - \rho) \lambda R - \mu R,
-    \\
-    \frac{\md A}{\md t} &= \lambda S + (1 - \rho) \lambda R - \delta A - \mu A,
-    \\
-    \frac{\md U}{\md t} &= \delta A - \alpha U - \mu U - \sigma U,
-    \\
-    \frac{\md D}{\md t} &=  \alpha U + \psi T + \psi V
-    - \phi D - \mu D - \sigma D,
-    \\
-    \frac{\md T}{\md t} &= \phi D - \psi T - \gamma T - \mu T
-    - \sigma T,
-    \\
-    \frac{\md V}{\md t} &= \gamma T - \psi V - \mu V - \theta V,
-    \\
-    \frac{\md W}{\md t} &= \sigma U + \sigma D + \sigma T + \theta V -
-    \nu W,
-    \\
-    \frac{\md Y}{\md t} &= \lambda \big[S + (1 - \rho) R\big],
-    \\
-    \frac{\md Z}{\md t} &= \nu W,
-  \end{split}
-\end{equation}
-with force of infection
-\begin{equation}
-  \label{force_of_infection}
-  \lambda =
-  \frac{\eta \big[\beta_A A + \beta_U (U + D + T) + \beta_V V\big]}{N},
-\end{equation}
-sexually active population size $N = S + R + A + U + D + T + V$.  We
-assumed that people with AIDS ($W$) are too sick to be sexually
-active.
-
-The relative transmission rates of acute, unsuppressed, and suppressed
-infected people are
-\begin{equation}
-  \label{betas}
-  \begin{split}
-    \beta_A &= 1 - (1 - \tau_A)^n,
-    \\
-    \beta_U &= 1 - (1 - \tau_U)^n,
-    \\
-    \beta_V &= 1 - (1 - \varepsilon \tau_U)^n,
-  \end{split}
-\end{equation}
-where the $\tau$'s are the relative transmissibilities of people with
-acute ($A$), unsuppressed ($U$ and $T$), and suppressed ($V$)
-infections, $n$ is the annual number of coital acts, and $\varepsilon$
-is the relative transmissibility with viral suppression.  For
-transmissibility during the acute phase, we sampled $\tau_A$ from
-$\Triangular$(0.0039, 0.0082, 0.0150)
-\cite{Wawer2005-us, Skarbinski2015-ni}, whereas, for transmissibility
-for unsuppressed people, we sampled $\tau_U$ from
-$\Triangular(0.00077, 0.0014, 0.00251)$ \cite{Hughes2012-so}.  The
-transmissibility of people with viral suppression relative to those
-without suppression has been estimated at 0.08 (95\% confidence
-interval 0.002, 0.57) \cite{Donnell2010-xo}: due to the extremely long
-left tail, we chose to sample the relative transmissibility
-$\varepsilon$ from $\BetaPERT(0.08, 0.002, 0.57)$ rather than a
-$\Triangular$ distribution.  (See \autoref{uncertainty} for a full
-description of $\BetaPERT(a, b, c)$.)  The annual number of coital
-acts $n$ was sampled from $\Uniform(96, 108)$
-\cite{Wawer2005-us, Abdool_Karim2010-cm}.  The country-specific
-transmission rate $\eta$ was estimated from each country's
-longitudinal HIV prevalence and incidence (\autoref{model_fitting}).
-
-For year 2015, the number of people aged 15--49 years, $M(2015)$; the
-prevalence, $p_I(2015)$; the proportion diagnosed, $p_D(2015)$; the
-proportion treated, $p_T(2015)$; and proportion with viral
-suppression, $p_V(2015)$ were used to initialize the model
-(\autoref{data_sources}).  Although the initial population used ages
-15--49 due to data availability, model projections allowed for
-analysis of infected people aging beyond age 50.  Due to a lack of
-data on acute infections, and since the acute phase is so much shorter
-than the other stages, we assumed that initially there were no acute
-infections.  Due to a lack of comprehensive data on PLAIDS in each
-country, we assumed that the proportion of diagnosed, untreated people
-($D + W$) who have AIDS ($W$) in year 2015 was
-\begin{equation}
-  p_A = \frac{\sigma}{\sigma + \nu},
-\end{equation}
-which is the equilibrium fraction of diagnosed people ($D + W$) who
-have AIDS ($W$) in the absence of treatment and background mortality.
-The number initially vaccinated was set to 0.  The initial cumulative
-number of new infections and AIDS deaths were set to 0.  Thus, the
-model initial conditions are
-\begin{equation}
-  \label{initial_conditions}
-  \begin{split}
-    S(2015) &= \big(1 - p_I(2015)\big) M(2015), \\
-    R(2015) &= 0, \\
-    A(2015) &= 0, \\
-    U(2015) &= \big(1 - p_D(2015)\big) p_I(2015) M(2015), \\
-    D(2015) &= \big(1 - p_A\big) p_D(2015) \big(1 - p_T(2015)\big)
-    p_I(2015) M(2015), \\
-    T(2015) &= p_D(2015) p_T(2015) \big(1 - p_V(2015)\big)
-    p_I(2015) M(2015), \\
-    V(2015) &= p_D(2015) p_T(2015) p_V(2015) p_I(2015) M(2015), \\
-    W(2015) &= p_A p_D(2015) \big(1 - p_T(2015)\big) p_I(2015) M(2015), \\
-    Y(2015) &= 0, \\
-    Z(2015) &= 0.
-  \end{split}
-\end{equation}
-
-The parametrized differential equations were solved numerically
-\cite[see][]{medlock2016-git} and five effectiveness outcomes were
-computed from the solutions.
-\begin{description}
-\item[New infections] New infections from 2015 to time $t$ are given
-  by $Y(t)$.
-
-\item[Per-capita incidence] At each solution time point, the
-  per-capita incidence was calculated as
-  \begin{equation}
-    i(t_j) = \frac{Y(t_j) - Y(t_{j - 1})}{M(t_j) (t_j - t_{j - 1})},
-  \end{equation}
-  where
-  \begin{equation}
-    M(t) = S(t) + R(t) + A(t) + U(t) + D(t) + T(t) + V(t) + W(t)
-  \end{equation}
-  is the total population size at time $t$.  The per-capita incidence
-  at the first time point was undefined.
-
-\item[PLHIV] At each solution time point, PLHIV was given by
-  \begin{equation}
-    A(t) + U(t) + D(t) + T(t) + V(t) + W(t).
-  \end{equation}
-
-\item[PLAIDS] PLAIDS is given by $W(t)$.
-
-\item[AIDS-related deaths] AIDS-related deaths from 2015 to time $t$
-  are given by $Z(t)$.
-
-\end{description}
-
-The results from the country simulations were aggregated to the
-regional and global levels by adding the numbers of people in each
-compartment over time and then new infections, per-capita incidence,
-PLHIV, PLAIDS, and HIV-related deaths were calculated from the
-aggregates.  (See Table S6 for the definitions of UNAIDS regions.)
-
-\section{Target rates}
-\label{targets}
-
-The current proportion of PLHIV who know their diagnosis is
-\begin{equation}
-  p_D(t) = \frac{D(t) + T(t) + V(t) + W(t)}
-  {A(t) + U(t) + D(t) + T(t) + V(t) + W(t)},
-\end{equation}
-and the desired target for the current level of diagnosis is
-$p_D^*(t)$.  For the rate of new diagnosis, we used the function
-\begin{equation}
-  \label{diagnosis_rate}
-  \alpha(t) = \alpha_{\max} H\big(p_D^*(t) - p_D(t)\big),
-\end{equation}
-where $H(x)$ is the Heaviside-like function
-\begin{equation}
-  H(x) =
-  \begin{cases}
-    0 & \text{if $x < 0$},
-    \\
-    x / \chi & \text{if $0 \leq x \leq \chi$},
-    \\
-    1 & \text{if $x > \chi$},
-  \end{cases}
-\end{equation}
-with $\chi = 0.001$, which rapidly switches from $H = 0$ when $x < 0$
-to $H = 1$ when $x > 0$.  The linear segment connecting $H = 0$ and
-$H = 1$ was used to avoid difficulties in computing numerical
-solutions that occur when using a discontinuous function.  The
-function for the rate of new diagnoses \eqref{diagnosis_rate} allows
-new diagnoses ($\alpha(t) > 0$) when the current diagnosis level is
-below the target ($p_D^*(t) > p_D(t)$), and stops new
-diagnoses ($\alpha(t) = 0$) when the current diagnosis level is at or
-above target.  We took $\alpha_{\max} = 1\;\text{y$^{-1}$}$.
-
-The proportion of diagnosed people who are treated is
-\begin{equation}
-  p_T(t) = \frac{T(t) + V(t) + W(t)}{D(t) + T(t) + V(t) + W(t)}.
-\end{equation}
-Like the rate of new diagnosis, the rate of enrolling new people in
-treatment is
-\begin{equation}
-  \label{treatment_rate}
-  \phi(t) = \phi_{\max} H\big(p_T^*(t) - p_T(t)\big),
-\end{equation}
-with $\phi_{\max} = 10$, allowing new treatment ($\phi(t) > 0$) when
-the current treatment level is below the target ($p_T^*(t) > p_T(t)$)
-and stopping new treatment ($\phi(t) = 0$) when the current treatment
-level is at or above target.
-
-The proportion of people on ART who have achieved viral suppression is
-\begin{equation}
-  p_V(t) = \frac{V(t)}{T(t) + V(t)}.
-\end{equation}
-The rate of people relapsing to untreated is
-\begin{equation}
-  \label{relapse_rate}
-  \psi(t) = \psi_{\max} H\big(p_V(t) - p_V^*(t)\big),
-\end{equation}
-with $\psi_{\max} = 1$, which, unlike diagnosis and treatment rates,
-prevents relapses ($\psi(t) = 0$) when the current level of viral
-suppression is below the target ($p_V^*(t) > p_V(t)$) and allows
-relapses ($\psi(t) > 0$) when the current level of viral suppression
-is at or above target.  We chose to vary the relapse rate to achieve
-the desired level of viral suppression because achieving viral
-suppression seems to depend on the time on treatment (i.e.,
-$1 / \gamma$), while relapse rates are difficult to estimate.
-
-The proportion of susceptible people vaccinated is
-\begin{equation}
-  p_R(t) = \frac{R(t)}{S(t) + R(t)}.
-\end{equation}
-Like diagnosis and treatment, the vaccination rate is
-\begin{equation}
-  \label{vaccination_rate}
-  \zeta(t) = \zeta_{\max} H\big(p_R^*(t) - p_R(t)\big),
-\end{equation}
-with $\zeta_{\max} = 1$, allowing vaccination ($\zeta(t) > 0$) when
-the current vaccine coverage level is below the target
-($p_R^*(t) > p_R(t)$) and stopping vaccination ($\zeta(t) = 0$) when
-the current vaccine coverage is at or above target.
-
-We modeled 3 different targets for the proportion diagnosed ($p_D$), the
-proportion treated ($p_T$), and the proportion with viral suppression ($p_V$).
-\begin{description}
-\item[Status quo] The status quo target is for the proportions $p_D$,
-  $p_T$, and $p_V$ to remain fixed at their initial levels (Table S5)
-  going forward. That is,
-  \begin{equation}
-    \label{status_quo_target}
-    \begin{split}
-      p_D^*(t) &= p_D(2015), \\
-      p_T^*(t) &= p_T(2015), \\
-      p_V^*(t) &= p_V(2015).
-    \end{split}
-  \end{equation}
-
-\item[UNAIDS 90--90--90] The UNAIDS 90--90--90 target is for $p_D$,
-  $p_T$, and $p_V$ to all be raised to $90\%$ by 2020.  We implemented
-  this target as linear increases from the 2015 levels, each up to
-  $90\%$ in 2020, and constant at $90\%$ from 2020 to 2035, except if
-  an initial level is above $90\%$ then it remains constant from 2015
-  to 2035 so that meeting the UNAIDS target does not worsen any aspect
-  of the treatment cascade.  That is,
-  \begin{equation}
-    \label{unaids90_targets}
-    \begin{split}
-      p_D^*(t) &=
-      \begin{cases}
-        F\big(t, 2015, p_D(2015), 2020, 0.9\big)
-        & \text{if $p_D(2015) < 0.9$},
-        \\
-        p_D(2015) & \text{if $p_D(2015) \geq 0.9$}.
-      \end{cases}
-      \\
-      p_T^*(t) &=
-      \begin{cases}
-        F\big(t, 2015, p_T(2015), 2020, 0.9\big)
-        & \text{if $p_T(2015) < 0.9$},
-        \\
-        p_T(2015) & \text{if $p_T(2015) \geq 0.9$}.
-      \end{cases}
-      \\
-      p_V^*(t) &=
-      \begin{cases}
-        F\big(t, 2015, p_V(2015), 2020, 0.9\big)
-        & \text{if $p_V(2015) < 0.9$},
-        \\
-        p_V(2015) & \text{if $p_V(2015) \geq 0.9$}.
-      \end{cases}
-    \end{split}
-  \end{equation}
-  where
-  \begin{equation}
-    \label{F}
-    F(t, t_0, x_0, t_1, x_1) =
-    \begin{cases}
-      x_0 & \text{if $t < t_0$},
-      \\
-      x_0 + (x_1 - x_0) \frac{t - t_0}{t_1 - t_0} &
-      \text{if $t_0 \leq t < t_1$},
-      \\
-      x_1 & \text{if $t \geq t_1$},
-    \end{cases}
-  \end{equation}
-  is constant at $x_0$ for $t < t_0$, linearly connects $x_0$ at
-  $t_0$ to $x_1$ at $t_1$ for $t_0 \leq t < t_1$, and is constant at
-  $x_1$ for $t \geq t_1$.
-
-\item[UNAIDS 95--95--95] The UNAIDS 95--95--95 target is to achieve
-  90--90--90 by 2020 and then for $p_D$, $p_T$, and $p_V$ to all be
-  raised to $95\%$ by 2030.  We implemented this target as for
-  90--90--90 from 2015 to 2020, and then linear increases from the
-  2020 levels up to $95\%$ in 2030, again with the exception that if
-  an initial level is above $95\%$ then it remains constant from 2015
-  to 2035.  That is,
-  \begin{equation}
-    \label{unaids95_targets}
-    \begin{split}
-      p_D^*(t) &=
-      \begin{cases}
-        G\big(t, 2015, p_D(2015), 2020, 0.9, 2030, 0.95\big)
-        & \text{if $p_D(2015) < 0.9$},
-        \\
-        F\big(t, 2020, p_D(2015), 2030, 0.95\big)
-        & \text{if $0.9 \leq p_D(2015) < 0.95$},
-        \\
-        p_D(2015) & \text{if $p_D(2015) \geq 0.95$},
-      \end{cases}
-      \\
-      p_T^*(t) &=
-      \begin{cases}
-        G\big(t, 2015, p_T(2015), 2020, 0.9, 2030, 0.95\big)
-        & \text{if $p_T(2015) < 0.9$},
-        \\
-        F\big(t, 2020, p_T(2015), 2030, 0.95\big)
-        & \text{if $0.9 \leq p_T(2015) < 0.95$},
-        \\
-        p_T(2015) & \text{if $p_T(2015) \geq 0.95$},
-      \end{cases}
-      \\
-      p_V^*(t) &=
-      \begin{cases}
-        G\big(t, 2015, p_V(2015), 2020, 0.9, 2030, 0.95\big)
-        & \text{if $p_V(2015) < 0.9$},
-        \\
-        F\big(t, 2020, p_V(2015), 2030, 0.95\big)
-        & \text{if $0.9 \leq p_V(2015) < 0.95$},
-        \\
-        p_V(2015) & \text{if $p_V(2015) \geq 0.95$},
-      \end{cases}
-    \end{split}
-  \end{equation}
-  where
-  \begin{equation}
-    G(t, t_0, x_0, t_1, x_1, t_2, x_2) =
-    \begin{cases}
-      x_0 & \text{if $t < t_0$},
-      \\
-      x_0 + (x_1 - x_0) \frac{t - t_0}{t_1 - t_0} &
-      \text{if $t_0 \leq t < t_1$},
-      \\
-      x_1 + (x_2 - x_1) \frac{t - t_1}{t_2 - t_1} &
-      \text{if $t_1 \leq t < t_2$},
-      \\
-      x_2 & \text{if $t \geq t_2$},
-    \end{cases}
-  \end{equation}
-  is constant at $x_0$ for $t < t_0$, linearly connects $x_0$ at $t_0$
-  to $x_1$ at $t_1$ for $t_0 \leq t < t_1$, linearly connects $x_1$ at
-  $t_1$ to $x_2$ at $t_2$ for $t_1 \leq t < t_2$, and is constant at
-  $x_2$ for $t \geq t_2$, and $F$ is as in \eqref{F}.
-
-\end{description}
-
-For vaccination, we assume that rollout begins in year $t_V = 2020$
-(or $t_V = 2025$ in vaccine scenario analysis, \autoref{uncertainty}),
-that rollout linearly increases the proportion of the non-infected
-population covered from 0\% by $r_V = 25\%$ per year (or $r_V = 10\%$
-per year) up to $c_V = 70\%$ (or $c_V = 50\%$ or $c_V = 90\%$) and
-staying constant thereafter.  Thus, the vaccination target is
-\begin{equation}
-  \label{vaccination_target}
-  p_R^*(t) =
-  \begin{cases}
-    0 & \text{if $t < t_V$},
-    \\
-    r_V (t - t_V) & \text{if $t_V \leq t < T_V$},
-    \\
-    c_V & \text{if $t \geq T_V$},
-  \end{cases}
-\end{equation}
-where $T_V = t_V + c_V / r_V$ is the time when rollout reaches
-the ultimate coverage $c_V$.
-
-Target strategies were one of the three diagnosis and treatment
-targets (status quo, 90--90--90, or 95--95--95) combined with either
-no vaccination ($p_R^*(t) = 0$) or vaccination at some level of
-efficacy, ultimate coverage, start date of rollout, and speed of
-rollout.
-
-\section{Data sources}
-\label{data_sources}
-
-For 127 countries, we found sufficient data to parametrize our model.
-Demographic data, including population growth rate \cite{WorldBankpg},
-death rate \cite{World_Development_Indicators2013-ee}, and number of
-people aged 15--49 years \cite{The_World_Bank2016-fd} were obtained
-from the World Bank (Table S2). Longitudinal HIV prevalence (Table S3)
-and incidence (Table S4) estimates for ages 15--49, spanning from as
-early as 1990 to 2015, were primarily derived from the AIDSinfo
-database produced by UNAIDS \cite{Unaids2016-an}. Other sources
-included UNAIDS Country Progress Reports \cite{Unaids2016-am}
-published from 2012 to 2016 and AIDS Data Hub \cite{AIDSdatahub-fg},
-which compiles data from UNAIDS, UNICEF, WHO, and the Asian
-Development Bank. These sources were also used to inform the initial
-conditions for the model: the number of people diagnosed with HIV, the
-number on ART, and the number who have viral suppression or have been
-retained on treatment for at least 12 months (Table S5). Where data
-were not available from these sources, alternative resources such as
-peer-reviewed journal articles and country health ministry reports
-were consulted.  See Tables S2--S5 for full information on data
-sources for each country.  The data tables are also available in the
-public source-code repository \cite{medlock2016-git}.
-
-\section{Model fitting}
-\label{model_fitting}
-
-Using available historical country-level data for prevalence and
-incidence (Tables S3 and S4), and published transmissibility estimates
-\cite{Wawer2005-us,Donnell2010-xo,Hughes2012-so,Skarbinski2015-ni}, we
-estimated an average country-specific transmission rate, which then
-informs the acute, unsuppressed, and suppressed transmission rates.
-This calibration method provided a recent estimate of country-specific
-transmission, while using historical data to smooth out short-term
-variations.
-
-For each country, we first estimated rates of HIV transmission for
-each of the available historical data points for prevalence and
-incidence.  The calculation involved approximating the simplified
-force of infection
-\begin{align}
-  \label{foi}
-  \begin{split}
-    \lambda(t) &= \frac{\eta \left[\beta_{A} A(t)
-        + \beta_{U} \big(U(t) + D(t) + T(t)\big) +
-        \beta_{V} V(t)\right]}{N(t)}
-    \approx  \beta(t) \frac{I(t)}{N(t)},
-  \end{split}
-\end{align}
-where $\beta$ is the estimated time-independent aggregate transmission
-rate under the approximation that there is no difference in
-transmission risk among acute, unsuppressed, suppressed, and AIDS
-classes, and $I = A + U + D + T + V + W$ is the total number of
-PLHIV.  Therefore, the per-capita incidence is
-\begin{equation}
-i(t) = \lambda(t) \frac{S(t)}{N(t)}
-\approx \beta(t) \frac{I(t)}{N(t)} \frac{S(t)}{N(t)} =\beta(t) p(t) (1-p(t)),
-\end{equation}
-where $p(t)$ is the prevalence. Thus, we estimated the transmission
-rate at each historical time point using the incidence and prevalence
-data by
-\begin{equation}
-  \label{trans_rate}
-  \beta(t) \approx \frac{i(t)}{p(t)(1-p(t))}.
-\end{equation}
-
-To reflect the uncertainty in $\beta(t)$, we assumed that it follows a
-lognormal distribution (\autoref{uncertainty}). For the parameters
-$\mu$ and $\sigma^2$ of the lognormal distribution we used the
-exponentially weighted mean and variance \cite{holt2004} over time
-(with half-life 1\;y) of $\log \beta(t)$ for the year 2015.  That is,
-\begin{equation}
-  \begin{split}
-    \mu &= \frac{\sum_{i = 1}^n  2^{t_i}
-      \log \beta(t_i)}
-    {\sum_{i = 1}^n 2^{t_i}},
-    \\
-    \sigma^2 &= \frac{\big(\sum_{i = 1}^n 2^{t_i}\big)
-      \left[\sum_{i = 1}^n  2^{t_i}
-        \big(\log \beta(t_i) - \mu\big)^2\right]}
-    {\big(\sum_{i = 1}^n 2^{t_i}\big)^2
-      - \sum_{i = 1}^n 2^{2 t_i}}.
-  \end{split}
-\end{equation}
-A half-life of 1\;y means that the estimate of the transmission rate
-from year $i$ is weighted half as much as the estimate from year
-$i + 1$, a quarter as much as the estimate from year $i + 2$, and so
-on.  This approach captured the recent country-level transmission
-behavior while still allowing for the use of less-recent data to
-smooth short-term variations (\autoref{transmission_rate}).
-
-\begin{figure}
-  \centering
-  \includegraphics{../Codes/plots/transmission_rate.pdf}
-  \caption{Country-specific distributions of transmission rate,
-    $\beta$, calculated based on historical country prevalence and
-    incidence.  See \autoref{model_fitting}.}
-  \label{transmission_rate}
-\end{figure}
-
-For each of the 1000 model parameter samples, the country-level
-aggregate transmission rate $\beta$ was sampled, along with the
-transmissibilities for acute and unsuppressed infected people,
-$\tau_A$ and $\tau_U$; the transmission reduction by suppression,
-$\varepsilon$; and the annual number of coital acts, $n$
-(\autoref{model}).  From the latter samples, the relative transmission
-rates for the acute phase ($\beta_A$), for unsuppressed chronic
-infections ($\beta_U$), and for chronic infections with viral
-suppression ($\beta_V$) were calculated by
-eqs.~\eqref{force_of_infection}.  The sample value of the
-country-level transmission rate was then computed by
-\begin{equation}
-  \label{eta}
-  \eta = \frac{\beta I(2015)}{
-    \beta_A A(2015) + \beta_U \big(U(2015) + D(2015) + T(2015)\big)
-    + \beta_V V(2015)},
-\end{equation}
-derived by rearranging eq.~\eqref{foi}, and uses the model initial
-conditions eq.~\eqref{initial_conditions}.
-
-A few countries—e.g., Bulgaria, Timor-Leste, and Yemen—currently have
-low HIV prevalence but relatively high incidence, resulting in large
-estimated transmission rates, leading to rapid projected growth of
-their HIV epidemics by 2035. The apparent low prevalence and high
-incidence may, at least in part, be due to the resolution in UNAIDS
-data (0.1\% for prevalence, 0.01\% for annual per-capita incidence).
-Results for such countries should be considered in light of this
-limitation.
-
-\section{Uncertainty analysis}
-\label{uncertainty}
-
-Projections were generated for each country through model simulations
-using 1000 random samples from published parameter distributions
-(\autoref{model_param}) and the country-specific estimated
-distribution of the transmission rate (\autoref{model_fitting}). The
-parameters were sampled using Latin hypercube sampling
-\cite{blower1994}.  We also used the variance reduction technique of
-running different interventions with the same parameter samples, i.e.,
-one set of sample parameter values is drawn, status quo and
-intervention scenarios are all run with those sample values and
-compared, and this process is repeated for each of the 1000 sample
-sets of parameters \cite{shechter2006}.
-
-The model outcomes were summarized using the median, 1st and 3rd
-quartiles (i.e., 25th and 75th percentiles), and 5th and 95th
-percentiles.  We calculated partial rank correlation coefficients
-(PRCC) \cite{blower1994} to measure the independent effect of each
-non-vaccine parameter on model projections of global new HIV
-infections from 2015 to 2035 (\autoref{PRCCs}).
 
@@
 
-Given that vaccine parameters have not yet been quantified, we
-restricted the number of unknowns by keeping vaccine efficacy constant
-over time.  This assumption is based on proposed vaccine regimens that
-include boosters for sustaining immunogenicity.  We chose plausible
-baseline values for the included vaccine parameters (efficacy 50\%,
-ultimate coverage 70\%, speed of rollout 25\% per year, year vaccine
-is first available 2020) and examined uncertainty by simulating 6
-additional vaccine scenarios, varying efficacy (30\%, 70\%), ultimate
-coverage (50\%, 90\%), speed of rollout (10\% coverage per year), and
-first year of availability (2025; Figure 4). The vaccine scenario
-analysis was done using the modes from the parameter distributions,
-not samples from these distributions, to reduce the computation time.
-
-We used several probability distributions to quantify the parameters.
-\begin{description}
-\item[Uniform] $\Uniform(a, b)$ is the uniform random variable with
-  minimum $a$ and maximum $b$, which has density function
-  \begin{equation}
-    \label{uniform}
-    f_{\Uniform}(x) =
-    \begin{cases}
-      \frac{1}{b - a} & \text{if $a \leq x \leq b$,}
-      \\
-      0 & \text{otherwise.}
-    \end{cases}
-  \end{equation}
-  We defined the mode for the uniform distribution to be the midpoint
-  $\frac{b - a}{2}$.
-
-\item [Triangular] $\Triangular(a, b, c)$ is the triangular random
-  variable distribution with minimum $a$, mode $b$, and maximum $c$.
-  It has density function
-  \begin{equation}
-    \label{triangular}
-    f_{\Triangular}(x) =
-    \begin{cases}
-      \frac{2 (x - a)}{(c - a)(b - a)} & \text{if $a \leq x \leq b$,}
-      \\
-      \frac{2 (c - x)}{(c - a)(c - b)} & \text{if $b \leq x \leq c$,}
-      \\
-      0 & \text{otherwise.}
-    \end{cases}
-  \end{equation}
-
-\item[Beta-PERT] $\BetaPERT(a, b, c)$ is the Beta-PERT probability
-  distribution \cite{malcom1959} with minimum $a$, mode $b$, and
-  maximum $c$.  It has density function
-  \begin{equation}
-    \label{BetaPERT}
-    f_{\BetaPERT}(x) =
-    \begin{cases}
-      \frac{(x - a)^{v - 1} (c - x)^{w - 1}}{(c - a)^{v + w - 2} B(v, w)}
-      & \text{if $a \leq x \leq c$,}
-      \\
-      0 & \text{otherwise,}
-    \end{cases}
-  \end{equation}
-  where
-  \begin{equation}
-    \begin{split}
-      \mu &= \frac{a + \lambda b + c}{\lambda + 2},
-      \\
-      v &= \frac{(\mu - a)(2 b - a - c)}{(b - \mu) (c - a)},
-      \\
-      w &= \frac{v (a - \mu)}{\mu - c},
-    \end{split}
-  \end{equation}
-  and $B(v, w)$ is the standard beta function \cite[\S 6.2]{davis1972}.
-  We used the standard value of $\lambda = 4$.
-
-\item[Lognormal] $\Lognormal(\mu, \sigma^2)$ is the lognormal random
-  variable, which has density function
-  \begin{equation}
-    f_{\Lognormal}(x) = \frac{1}{x \sigma \sqrt{2 \pi}}
-    \exp\left(- \frac{\left(\log x - \mu\right)^2}{2 \sigma^2}\right).
-  \end{equation}
-\end{description}
-
-\clearpage
-\printbibliography
-
-\clearpage
-\newpage
-\vspace*{3in}
-\section{Global, regional, and per-country effectiveness}
-\newpage
-\input{../Codes/plots/effectiveness_all/all}
-
 \end{document}

### 2016-10-19 Documents/supplementary_information.tex
Minor changes for Nature.
More changes for Nature.

--- 2016-10-12 Documents/supplementary_text.tex
@@
 \usepackage[font={sf}, labelfont={bf},
-  labelsep=period, singlelinecheck=off]{caption}
+            labelsep=space, singlelinecheck=off]{caption}
 \usepackage[font={sf}]{floatrow}
@@
 
-\usepackage[noblocks]{authblk}
+\usepackage[blocks]{authblk}
 \renewcommand{\Authsep}{, }
 \renewcommand{\Authand}{ \& }
-\renewcommand{\Authands}{ \& }
+\renewcommand{\Authands}{, }
 \renewcommand{\Affilfont}{\small}
@@
 
-\usepackage[style=science, article-title=true, maxnames=100]{biblatex}
-\addbibresource{supplementary_text.bib}
-\newcommand{\labeltitlepunc}{}
-\DeclareBibliographyDriver{incollection}{%
-  \usebibmacro{bibindex}%
-  \usebibmacro{begentry}%
-  \usebibmacro{author/translator+others}%
-  \setunit{\labelnamepunct}\newblock
-  \printlist{language}%
-  \newunit\newblock
-  \usebibmacro{byauthor}%
-  \newunit\newblock
-  \usebibmacro{title}%
-  \usebibmacro{in:}%
-  \usebibmacro{maintitle+booktitle}%
-  \newunit\newblock
-  \usebibmacro{byeditor+others}%
-  \newunit\newblock
-  \printfield{volumes}%
-  \newunit\newblock
-  \printfield{note}%
-  \newunit\newblock
-  \usebibmacro{publisher+location+date}%
-  \newunit\newblock
-  \printfield{volume}
-  \newunit
-  \usebibmacro{chapter+pages}%
-  \newunit\newblock
-  \iftoggle{bbx:isbn}
-    {\printfield{isbn}}
-    {}%
-  \newunit\newblock
-  \usebibmacro{doi+eprint+url}%
-  \newunit\newblock
-  \usebibmacro{addendum+pubstate}%
-  \setunit{\bibpagerefpunct}\newblock
-  \usebibmacro{pageref}%
-  \newunit\newblock
-  \usebibmacro{related}%
-  \usebibmacro{finentry}%
-}
+\usepackage[style=nature]{biblatex}
+\addbibresource{supplementary_information.bib}
+
+\usepackage{xr}
+\externaldocument{extended_data_fig_1}
+\externaldocument{extended_data_fig_2}
 
@@
 
-\newcommand{\labelPrefix}{S}
-\renewcommand{\thesection}{\labelPrefix\arabic{section}}
-\renewcommand{\theequation}{\labelPrefix\arabic{equation}}
-\renewcommand{\thefigure}{\labelPrefix\arabic{figure}}
-\renewcommand{\thetable}{\labelPrefix\arabic{table}}
-\renewcommand{\figurename}{Fig.}
+\renewcommand{\thesection}{S\arabic{section}}
+\renewcommand{\figurename}{Supplementary Fig.}
+\renewcommand{\figureautorefname}{\figurename}
+\renewcommand{\tablename}{Supplementary Table}
+\renewcommand{\tableautorefname}{\tablename}
 
-\title{Supporting online material for\\
+\title{Supplementary Methods for\\
   \emph{Effectiveness of UNAIDS targets and HIV vaccination across 127
@@
 
-\author[1*]{Jan Medlock}
-\author[2]{Abhishek Pandey}
-\author[2]{Alyssa S.~Parpia}
-\author[2]{Amber Tang}
-\author[2]{Laura A.~Skrip}
-\author[2]{Alison P.~Galvani}
-\affil[1]{Department of Biomedical Sciences, Oregon State University,
-  106 Dryden Hall, Corvallis, OR, 97331-4801, USA}
-\affil[2]{Center for Infectious Disease Modeling and Analysis, Yale
+\author{Jan Medlock}
+\affil{Department of Biomedical Sciences, Oregon State University, 106
+  Dryden Hall, Corvallis, OR, 97331-4801, USA,
+  \href{mailto:jan.medlock@oregonstate.edu}{\texttt{jan.medlock@oregonstate.edu}}}
+\author{Abhishek Pandey} \author{Alyssa S.~Parpia} \author{Amber Tang}
+\author{Laura A.~Skrip} \author{Alison P.~Galvani}
+\affil{Center for Infectious Disease Modeling and Analysis, Yale
   School of Public Health, 135 College Street, New Haven, USA}
-\affil[*]{To whom correspondence should be addressed.  E-mail:
-  \href{mailto:jan.medlock@oregonstate.edu}{
-    \texttt{jan.medlock@oregonstate.edu}}}
 
@@
 The model simulation and analysis tools, written in Python, are
-publicly available at\\
-\url{https://github.com/janmedlock/HIV-95-vaccine/}
-\cite{medlock2016-git}.
+publicly available \autocite{medlock2016-git}.
 
@@
 We chose to consider only these ages because they are the vast
-majority of global PLHIV, 93\% in 2014 \cite{UNICEF}; because
+majority of global PLHIV \autocite{UNICEF}, 93\% in 2014; because
 population-level HIV estimates and demographic data are often
@@
 127 countries was collected from published estimates
-\cite{World_Development_Indicators2013-ee}.  The recruitment rate
+\autocite{World_Development_Indicators2013-ee}.  The recruitment rate
 ($\kappa$) into the age $15\;\text{y}$ and older group was set by the
 difference between the country's population growth rate
-\cite{WorldBankpg} and its background mortality rate
-\cite{World_Development_Indicators2013-ee}, as would be true if the
+\autocite{WorldBankpg} and its background mortality rate
+\autocite{World_Development_Indicators2013-ee}, as would be true if the
 population was at its stable age structure.
@@
 extends survival but also dramatically reduces transmission
-\cite{vernazza2000, ioannidis2001, attia2009, May2014-gp}.
+\autocite{vernazza2000, ioannidis2001, attia2009, May2014-gp}.
 Transitions between model states are governed by a series of
@@
 5th and 95th percentiles.  Each country was modeled separately
-(\hyperref[effectiveness_Afghanistan]{Figures
-  \ref*{effectiveness_Afghanistan}}--\ref{effectiveness_Zimbabwe}) and
-the country simulations were aggregated to calculate global and
+(\hyperref[effectiveness_Afghanistan]{Extended Data
+  Figs.~\ref*{effectiveness_Afghanistan}}--\ref{effectiveness_Zimbabwe})
+and the country simulations were aggregated to calculate global and
 regional outcomes
-(\hyperref[effectiveness_Global]{Figures
-  \ref*{effectiveness_Global}}--\ref{effectiveness_Western_Europe}).
+(\hyperref[effectiveness_Global]{Extended Data
+  Figs.~\ref*{effectiveness_Global}}--\ref{effectiveness_Western_Europe}).
 
@@
       \hline
-      $\mu$ & Background death rate & Country specific, Table S2
-      & \cite{World_Development_Indicators2013-ee} \\
-      $\kappa$ & Recruitment rate & Country specific, Table S2
-      & \cite{World_Development_Indicators2013-ee, WorldBankpg} \\
+      $\mu$ & Background death rate
+      & Country specific, Supplementary Table 2
+      & \autocite{World_Development_Indicators2013-ee} \\
+      $\kappa$ & Recruitment rate
+      & Country specific, Supplementary Table 2
+      & \autocite{World_Development_Indicators2013-ee, WorldBankpg} \\
       $\delta$	& Rate of leaving acute infection
       & $\Triangular$(2, 4.14, 9.6)\;y$^{-1}$
-      & \cite{Hollingsworth2008-iy} \\
+      & \autocite{Hollingsworth2008-iy} \\
       $\sigma$	& Rate of developing AIDS without viral suppression
-      & 0.1064\;y$^{-1}$ & \cite{Morgan2002-cq} \\
+      & 0.1064\;y$^{-1}$ & \autocite{Morgan2002-cq} \\
       $\theta$ & Rate of developing AIDS with viral suppression
@@
       & $\Uniform$(0.5, 1.5)\;y$^{-1}$
-      & \cite{Currie2009-yz} \\
+      & \autocite{Currie2009-yz} \\
       $\nu$ & Death rate from AIDS & 0.5\;y$^{-1}$
-      & \cite{Morgan2002-cq} \\
+      & \autocite{Morgan2002-cq} \\
       $\rho$ & Vaccine efficacy & 50\%\,[30\%, 70\%] & --- \\
@@
       & $\Uniform$(5, 8)\;y
-      & \cite{Samji2013-kf, Unaids2014-ue} \\
+      & \autocite{Samji2013-kf, Unaids2014-ue} \\
       $\tau_{A}$ & Transmissibility during acute phase
       & $\Triangular$(0.0039, 0.0082, 0.0150)
-      & \cite{Wawer2005-us, Skarbinski2015-ni}\\
+      & \autocite{Wawer2005-us, Skarbinski2015-ni}\\
       $\tau_{U}$ & Transmissibility after acute phase
       & $\Triangular$(0.00077, 0.0014, 0.00251)
-      & \cite{Hughes2012-so} \\
+      & \autocite{Hughes2012-so} \\
       $\varepsilon$ & Relative transmissibility with
       viral suppression & $\BetaPERT$(0.08, 0.002, 0.57)
-      & \cite{Donnell2010-xo} \\
+      & \autocite{Donnell2010-xo, attia_2009, wilson_2012, jia_2013,
+        rodger_2016} \\
       $n$ & Coital acts per year & $\Uniform$(96, 108)
-      & \cite{Wawer2005-us, Abdool_Karim2010-cm}\\
+      & \autocite{Wawer2005-us, Abdool_Karim2010-cm}\\
       $\alpha$ & Diagnosis rate & See eq.~(\ref{diagnosis_rate}) & --- \\
@@
 loads and lasts an average of 2.90 [95\% confidence interval 1.23,
-6.00]\;months \cite{Hollingsworth2008-iy}.  (We converted these
+6.00]\;months \autocite{Hollingsworth2008-iy}.  (We converted these
 durations to rates like $1 / 2.90\;\text{month$^{-1}$} \approx
@@
 occurs after between 8 months and 2 years on treatment
-\cite{Currie2009-yz}.  Disengagement from treatment moves people from
+\autocite{Currie2009-yz}.  Disengagement from treatment moves people from
 treated ($T$) and viral suppression ($V$) at the rate $\psi$,
@@
 PLHIV without viral suppression (compartments $U$, $D$, and $T$)
-develop AIDS (compartment $W$) after an average duration of 10.4 y
-\cite{Morgan2002-cq}, i.e., with transition rate
+develop AIDS (compartment $W$) after an average duration of 10.4 years
+\autocite{Morgan2002-cq}, i.e., with transition rate
 $\sigma = 0.1064\;\text{y$^{-1}$}$.  People who have achieved viral
@@
 estimated to live $5$--$8$\;y shorter lives than the non-HIV infected
-\cite{Samji2013-kf, Unaids2014-ue}, which we quantified by randomly
-sampling the parameter $\omega$ from $\Uniform(5, 8)\;\text{y}$.
-Assuming no relapse to untreated, the duration of viral suppression is
+\autocite{Samji2013-kf, Unaids2014-ue}, which we quantified by
+randomly sampling the parameter $\omega$ from
+$\Uniform(5, 8)\;\text{y}$.  Assuming no relapse to untreated, the
+duration of viral suppression is
 \begin{equation}
@@
 $\Triangular$(0.0039, 0.0082, 0.0150)
-\cite{Wawer2005-us, Skarbinski2015-ni}, whereas, for transmissibility
+\autocite{Wawer2005-us, Skarbinski2015-ni}, whereas, for transmissibility
 for unsuppressed people, we sampled $\tau_U$ from
-$\Triangular(0.00077, 0.0014, 0.00251)$ \cite{Hughes2012-so}.  The
+$\Triangular(0.00077, 0.0014, 0.00251)$ \autocite{Hughes2012-so}.  The
 transmissibility of people with viral suppression relative to those
 without suppression has been estimated at 0.08 (95\% confidence
-interval 0.002, 0.57) \cite{Donnell2010-xo}: due to the extremely long
+interval 0.002, 0.57) \autocite{Donnell2010-xo}: due to the extremely long
 left tail, we chose to sample the relative transmissibility
@@
 acts $n$ was sampled from $\Uniform(96, 108)$
-\cite{Wawer2005-us, Abdool_Karim2010-cm}.  The country-specific
+\autocite{Wawer2005-us, Abdool_Karim2010-cm}.  The country-specific
 transmission rate $\eta$ was derived from UNAIDS estimates of each
@@
 The parametrized differential equations were solved numerically
-\cite[see][]{medlock2016-git} and four effectiveness outcomes were
+\autocite[see][]{medlock2016-git} and four effectiveness outcomes were
 computed from the solutions.
@@
 PLHIV, and HIV-related deaths were calculated from the aggregates.
-(See Table S6 for the definitions of UNAIDS regions.)
+(See Supplementary Table 6 for the definitions of UNAIDS regions.)
 
@@
 \item[Status quo] The status quo target is for the proportions $p_D$,
-  $p_T$, and $p_V$ to remain fixed at their initial levels (Table S5)
-  going forward. That is,
+  $p_T$, and $p_V$ to remain fixed at their initial levels
+  (Supplementary Table 5) going forward. That is,
   \begin{equation}
@@
 parametrize our model.  Demographic data, including population growth
-rate \cite{WorldBankpg}, death rate
-\cite{World_Development_Indicators2013-ee}, and number of people aged
-15--49 years \cite{The_World_Bank2016-fd} were obtained from the World
-Bank (Table S2). Longitudinal HIV prevalence (Table S3) and incidence
-(Table S4) estimates for ages 15--49, spanning from as early as 1990
-to 2015, were primarily obtained from the AIDSinfo database produced
-by UNAIDS \cite{Unaids2016-an}. Other sources included UNAIDS Country
-Progress Reports \cite{Unaids2016-am} published from 2012 to 2016 and
-AIDS Data Hub \cite{AIDSdatahub-fg}, which compiles data from UNAIDS,
-UNICEF, WHO, and the Asian Development Bank. These sources were also
-used to inform the initial conditions for the model: the number of
-people diagnosed with HIV, the number on ART, and the number who have
-viral suppression or have been retained on treatment for at least 12
-months (Table S5). Where estimates or data were not available from
-these sources, alternative resources such as peer-reviewed journal
-articles and country health ministry reports were consulted.  See
-Tables S2--S5 for full information on the sources used for each
-country.  These source tables are also available in the public
-source-code repository \cite{medlock2016-git}.
+rate \autocite{WorldBankpg}, death rate
+\autocite{World_Development_Indicators2013-ee}, and number of people
+aged 15--49 years \autocite{The_World_Bank2016-fd} were obtained from
+the World Bank (Supplementary Table 2). Longitudinal HIV prevalence
+(Supplementary Table 3) and incidence (Supplementary Table 4)
+estimates for ages 15--49, spanning from as early as 1990 to 2015,
+were primarily obtained from the AIDSinfo database produced by UNAIDS
+\autocite{Unaids2016-an}. Other sources included UNAIDS Country
+Progress Reports \autocite{Unaids2016-am} published from 2012 to 2016
+and AIDS Data Hub \autocite{AIDSdatahub-fg}, which compiles data from
+UNAIDS, UNICEF, WHO, and the Asian Development Bank. These sources
+were also used to inform the initial conditions for the model: the
+number of people diagnosed with HIV, the number on ART, and the number
+who have viral suppression or have been retained on treatment for at
+least 12 months (Supplementary Table 5). Where estimates or data were
+not available from these sources, alternative resources such as
+peer-reviewed journal articles and country health ministry reports
+were consulted.  See Supplementary Tables 2--5 for full information on
+the sources used for each country.  These source tables are also
+available in the public source-code repository
+\autocite{medlock2016-git}.
 
@@
 Using available historical country-level estimates of prevalence and
-incidence (Tables S3 and S4), and published estimates of
+incidence (Supplementary Tables 3 and 4), and published estimates of
 transmissibility
-\cite{Wawer2005-us,Donnell2010-xo,Hughes2012-so,Skarbinski2015-ni}, we
-derived an average country-specific transmission rate, which then
+\autocite{Wawer2005-us,Donnell2010-xo,Hughes2012-so,Skarbinski2015-ni},
+we derived an average country-specific transmission rate, which then
 informs the acute, unsuppressed, and suppressed transmission rates.
@@
 $\mu$ and $\sigma^2$ of the lognormal distribution we used the
-exponentially weighted mean and variance \cite{holt2004} over time
+exponentially weighted mean and variance \autocite{holt2004} over time
 (with half-life 1\;y) of $\log \beta(t)$ for the year 2015.  That is,
@@
 parameters were sampled using Latin hypercube sampling
-\cite{blower1994}.  We also used the variance reduction technique of
+\autocite{blower1994}.  We also used the variance reduction technique of
 running different interventions with the same parameter samples, i.e.,
@@
 compared, and this process is repeated for each of the 1000 sample
-sets of parameters \cite{shechter2006}.
+sets of parameters \autocite{shechter2006}.
 
@@
 percentiles.  We calculated partial rank correlation coefficients
-(PRCC) \cite{blower1994} to measure the independent effect of each
-non-vaccine parameter on model projections of global new HIV
-infections from 2015 to 2035 (\autoref{PRCCs}).
-
-\begin{figure}
-  \centering
-  \includegraphics{../Codes/plots/prcc.pdf}
-  \caption{Sensitivity of global infections averted from 2015 to 2035
-    to model parameters.  Left is the sensitivity of infections
-    averted by 95--95--95, relative to status quo.  Right is the
-    sensitivity of vaccination with status quo levels of diagnosis and
-    treatment, relative to status quo.  Sensitivity is measured by the
-    partial rank correlation coefficient (PRCC).}
-  \label{PRCCs}
-\end{figure}
+(PRCC) \autocite{blower1994} to measure the independent effect of
+each non-vaccine parameter on model projections of global new HIV
+infections from 2015 to 2035
+(\hyperref[PRCCs]{Extended Data Fig.~\ref*{PRCCs}}).
 
@@
 coverage (50\%, 90\%), speed of rollout (10\% coverage per year), and
-first year of availability (2025; Figure 4). The vaccine scenario
+first year of availability (2025; Fig.~4). The vaccine scenario
 analysis was done using the modes from the parameter distributions,
@@
 \item[Beta-PERT] $\BetaPERT(a, b, c)$ is the Beta-PERT probability
-  distribution \cite{malcom1959} with minimum $a$, mode $b$, and
+  distribution \autocite{malcom1959} with minimum $a$, mode $b$, and
   maximum $c$.  It has density function
@@
   \end{equation}
-  and $B(v, w)$ is the standard beta function \cite[\S 6.2]{davis1972}.
+  and $B(v, w)$ is the standard beta function \autocite[\S 6.2]{davis1972}.
   We used the standard value of $\lambda = 4$.
@@
 
-\clearpage
-\newpage
-\vspace*{3in}
-\section{Global, regional, and per-country effectiveness}
-\newpage
-\input{../Codes/plots/effectiveness_all/all}
-
 \end{document}

### 2016-10-20 Documents/supplementary_information.tex
More tweaks.

@@
 \externaldocument{extended_data_fig_2}
+\externaldocument{extended_data_fig_3}
 
@@
 
-Our model has 8 HIV states (\autoref{model_diag}): susceptible to HIV
-infection ($S$ is the number of people susceptible), vaccinated
-against HIV ($R$), acute HIV infection ($A$), undiagnosed HIV
-infection ($U$), diagnosed but untreated HIV infection ($D$), treated
-without viral suppression ($T$), viral suppression ($V$), and having
-AIDS ($W$).  Viral suppression is defined as a viral load of less than
-1000 viral RNA copies per mL of blood.  Viral suppression not only
-extends survival but also dramatically reduces transmission
+Our model has 8 HIV states
+(\hyperref[model_diag]{Extended Data Figs.~\ref*{model_diag}}):
+susceptible to HIV infection ($S$ is the number of people
+susceptible), vaccinated against HIV ($R$), acute HIV infection ($A$),
+undiagnosed HIV infection ($U$), diagnosed but untreated HIV infection
+($D$), treated without viral suppression ($T$), viral suppression
+($V$), and having AIDS ($W$).  Viral suppression is defined as a viral
+load of less than 1000 viral RNA copies per mL of blood.  Viral
+suppression not only extends survival but also dramatically reduces
+transmission
 \autocite{vernazza2000, ioannidis2001, attia2009, May2014-gp}.
@@
   Figs.~\ref*{effectiveness_Global}}--\ref{effectiveness_Western_Europe}).
-
-\begin{figure}
-  \centering
-  \input{diagram}
-  \caption{Model diagram.}
-  \label{model_diag}
-\end{figure}
 

### 2016-11-19 Documents/supplementary_information.tex
A few tweaks.

@@
 
-\usepackage[font={sf}, labelfont={bf},
-            labelsep=space, singlelinecheck=off]{caption}
+\usepackage[font={sf},
+            labelfont={bf},
+            labelsep=space,
+            singlelinecheck=off]{caption}
 \usepackage[font={sf}]{floatrow}
@@
 \renewcommand{\thesection}{S\arabic{section}}
+\newcommand{\sectionname}{Section}
+\renewcommand{\sectionautorefname}{\sectionname}
 \renewcommand{\figurename}{Supplementary Fig.}
@@
   Dryden Hall, Corvallis, OR, 97331-4801, USA,
-  \href{mailto:jan.medlock@oregonstate.edu}{\texttt{jan.medlock@oregonstate.edu}}}
+  \href{mailto:jan.medlock@oregonstate.edu}
+  {\texttt{jan.medlock@oregonstate.edu}}}
 \author{Abhishek Pandey} \author{Alyssa S.~Parpia} \author{Amber Tang}
@@
 
-We developed a country-level continuous-time, compartmental model that
+We developed a country-level continuous-time mathematical model that
 divides people aged $15$\;y and older into non-overlapping HIV states.
-We chose to consider only these ages because they are the vast
-majority of global PLHIV \autocite{UNICEF}, 93\% in 2014; because
-population-level HIV estimates and demographic data are often
-stratified into ages $15$--$49$; and to capture the continuing burden
-of infections in people ages $50$ and older.
+We focus on this age group because it accounts for the vast majority
+of global PLHIV \autocite{UNICEF}, 93\% in 2014; because
+population-level HIV estimates and demographic data are typically only
+estimated for ages $15$--$49$; and to capture the continuing burden of
+infections in people ages $50$ and older.
 
-The background mortality rate ($\mu$) in each of the
-127 countries was collected from published estimates
-\autocite{World_Development_Indicators2013-ee}.  The recruitment rate
-($\kappa$) into the age $15\;\text{y}$ and older group was set by the
-difference between the country's population growth rate
-\autocite{WorldBankpg} and its background mortality rate
-\autocite{World_Development_Indicators2013-ee}, as would be true if the
-population was at its stable age structure.
-
-Our model has 8 HIV states
-(\hyperref[model_diag]{Extended Data Figs.~\ref*{model_diag}}):
+Our model has 8 HIV states (Extended Data Fig.~\ref*{model_diag}):
 susceptible to HIV infection ($S$ is the number of people
@@
 \autocite{vernazza2000, ioannidis2001, attia2009, May2014-gp}.
-Transitions between model states are governed by a series of
+
+Transitions between model states are governed by a system of
 differential equations parametrized using values found in other
@@
 of incidence and prevalence (\autoref{model_param}).  The model is
-deterministic, but uncertainty in the parameters is treated by running
-the model 1000 times with samples from the parameter distributions
-(\autoref{uncertainty}) and summarizing the model outcomes using the
-median, 1st and 3rd quartiles (i.e., 25th and 75th percentiles), and
-5th and 95th percentiles.  Each country was modeled separately
-(\hyperref[effectiveness_Afghanistan]{Extended Data
-  Figs.~\ref*{effectiveness_Afghanistan}}--\ref{effectiveness_Zimbabwe})
+deterministic, but uncertainty in the parameters was treated by
+running the model 1000 times with samples from the parameter
+distributions (\autoref{uncertainty}) and summarizing the model
+outcomes using the median and percentiles.  Each country was modeled
+separately (Extended Data
+Figs.~\ref*{effectiveness_Afghanistan}--\ref*{effectiveness_Zimbabwe})
 and the country simulations were aggregated to calculate global and
-regional outcomes
-(\hyperref[effectiveness_Global]{Extended Data
-  Figs.~\ref*{effectiveness_Global}}--\ref{effectiveness_Western_Europe}).
+regional outcomes (Extended Data
+Figs.~\ref*{effectiveness_Global}--\ref*{effectiveness_Western_Europe}).
+
+The background mortality rate ($\mu$) in each of the 127 countries was
+collected from published estimates
+\autocite{World_Development_Indicators2013-ee}.  The recruitment rate
+($\kappa$) into the age $15\;\text{y}$ and older group was set by the
+difference between the country's population growth rate
+\autocite{WorldBankpg} and its background mortality rate
+\autocite{World_Development_Indicators2013-ee}, as would be true if
+the population was at its stable age structure.  (More on these data
+sources is in \autoref{data_sources}.)
 
@@
       \hline
+      \vspace*{-2.5em}
     \end{tabularx}
     \caption{Model parameters. $\Triangular$, $\Uniform$, and
-      $\BetaPERT$ are sampling distributions: see
-      \autoref{uncertainty} for a full description.  For vaccine
-      efficacy, $50\%$ was the baseline, and $30\%$ and $70\%$ were
-      also used in a scenario analysis.}
+      $\BetaPERT$ are sampling distributions (\autoref{uncertainty}).
+      For vaccine efficacy, $50\%$ was the baseline, and $30\%$ and
+      $70\%$ were also used in a scenario analysis.}
     \label{model_param}
@@
 People susceptible to HIV ($S$) progress to acute infection ($A$)
-according to the force of infection ($\lambda$,
-eq.~\eqref{force_of_infection}), which depends on the HIV transmission
-rate, estimated from the country-specific incidence and prevalence
-data (\autoref{model_fitting}), adjusted for the current number of
-acutely infected, untreated or ineffectively treated, and viral
-suppression PLHIV.  Acute infection is characterized by high viral
-loads and lasts an average of 2.90 [95\% confidence interval 1.23,
-6.00]\;months \autocite{Hollingsworth2008-iy}.  (We converted these
-durations to rates like $1 / 2.90\;\text{month$^{-1}$} \approx
+according to the force of infection ($\lambda$), which depends on the
+HIV transmission rate, estimated from the country-specific incidence
+and prevalence data (\autoref{model_fitting}), adjusted for the
+current number of acutely infected, untreated or ineffectively
+treated, and viral suppression PLHIV.  Acute infection is
+characterized by high viral loads and lasts an average of 2.90 [95\%
+confidence interval 1.23, 6.00]\;months
+\autocite{Hollingsworth2008-iy}.  (We converted these durations to
+rates like $1 / 2.90\;\text{month$^{-1}$} \approx
 4.14\;\text{y$^{-1}$}$ and set the parameter using random samples from
@@
 occurs after between 8 months and 2 years on treatment
-\autocite{Currie2009-yz}.  Disengagement from treatment moves people from
-treated ($T$) and viral suppression ($V$) at the rate $\psi$,
+\autocite{Currie2009-yz}.  Disengagement from treatment moves people
+from treated ($T$) and viral suppression ($V$) at the rate $\psi$,
 dependent on the current level of viral suppression and the country's
@@
 develop AIDS (compartment $W$) after an average duration of 10.4 years
-\autocite{Morgan2002-cq}, i.e., with transition rate
+\autocite{Morgan2002-cq}, i.e. with transition rate
 $\sigma = 0.1064\;\text{y$^{-1}$}$.  People who have achieved viral
@@
 \end{equation}
-sexually active population size $N = S + R + A + U + D + T + V$.  We
-assumed that people with AIDS ($W$) are too sick to be sexually
+and sexually active population size $N = S + R + A + U + D + T + V$.
+We assumed that people with AIDS ($W$) are too sick to be sexually
 active.
@@
 
-The parametrized differential equations were solved numerically
-\autocite[see][]{medlock2016-git} and four effectiveness outcomes were
-computed from the solutions.
+The parametrized differential equations were solved numerically using
+the LSODA routine \autocite{odepack, scipy, medlock2016-git} and four
+effectiveness outcomes were computed from the solutions.
 \begin{description}
@@
 the desired level of viral suppression because achieving viral
-suppression seems to depend on the time on treatment (i.e.,
+suppression seems to depend on the time on treatment (i.e.
 $1 / \gamma$), while relapse rates are difficult to estimate.
@@
 (Supplementary Table 3) and incidence (Supplementary Table 4)
-estimates for ages 15--49, spanning from as early as 1990 to 2015,
-were primarily obtained from the AIDSinfo database produced by UNAIDS
-\autocite{Unaids2016-an}. Other sources included UNAIDS Country
-Progress Reports \autocite{Unaids2016-am} published from 2012 to 2016
-and AIDS Data Hub \autocite{AIDSdatahub-fg}, which compiles data from
-UNAIDS, UNICEF, WHO, and the Asian Development Bank. These sources
-were also used to inform the initial conditions for the model: the
-number of people diagnosed with HIV, the number on ART, and the number
-who have viral suppression or have been retained on treatment for at
-least 12 months (Supplementary Table 5). Where estimates or data were
-not available from these sources, alternative resources such as
-peer-reviewed journal articles and country health ministry reports
-were consulted.  See Supplementary Tables 2--5 for full information on
-the sources used for each country.  These source tables are also
-available in the public source-code repository
+estimates for ages 15--49, spanning from as early as 1990 for some
+countries to 2015, were primarily obtained from the AIDSinfo database
+produced by UNAIDS \autocite{Unaids2016-an}. Other sources included
+UNAIDS Country Progress Reports \autocite{Unaids2016-am} published
+from 2012 to 2016 and AIDS Data Hub \autocite{AIDSdatahub-fg}, which
+compiles data from UNAIDS, UNICEF, WHO, and the Asian Development
+Bank. These sources were also used to inform the initial conditions
+for the model: the number of people diagnosed with HIV, the number on
+ART, and the number who have viral suppression or have been retained
+on treatment for at least 12 months (Supplementary Table 5). Where
+estimates or data were not available from these sources, alternative
+resources such as peer-reviewed journal articles and country health
+ministry reports were consulted.  See Supplementary Tables 2--5 for
+full information on the sources used for each country.  These source
+tables are also available in the public source-code repository
 \autocite{medlock2016-git}.
@@
 
-A few countries—e.g., Bulgaria, Timor-Leste, and Yemen—are currently
+A few countries—e.g. Bulgaria, Timor-Leste, and Yemen—are currently
 estimated by UNAIDS to have low HIV prevalence but relatively high
@@
 \autocite{blower1994}.  We also used the variance reduction technique of
-running different interventions with the same parameter samples, i.e.,
+running different interventions with the same parameter samples, i.e.
 one set of sample parameter values is drawn, status quo and
@@
 The model outcomes were summarized using the median, 1st and 3rd
-quartiles (i.e., 25th and 75th percentiles), and 5th and 95th
+quartiles (i.e. 25th and 75th percentiles), and 5th and 95th
 percentiles.  We calculated partial rank correlation coefficients
-(PRCC) \autocite{blower1994} to measure the independent effect of
-each non-vaccine parameter on model projections of global new HIV
-infections from 2015 to 2035
-(\hyperref[PRCCs]{Extended Data Fig.~\ref*{PRCCs}}).
+(PRCC) \autocite{blower1994} to measure the independent effect of each
+non-vaccine parameter on model projections of global new HIV
+infections from 2015 to 2035 (Extended Data Fig.~\ref*{PRCCs}).
 
@@
   \end{equation}
-  and $B(v, w)$ is the standard beta function \autocite[\S 6.2]{davis1972}.
+  and $B(v, w)$ is the standard beta function \autocite{davis1972}.
+  % \cite[\S6.2]{davis1972}
   We used the standard value of $\lambda = 4$.

### 2016-11-19 Codes/plots/common.py

@@ -63,7 +63,6 @@ width_1column = 89 * 0.039370079 # inches
 width_2column = 183 * 0.039370079 # inches
 
 fontdict = {'family': 'sans-serif', 'size': 7}
-fontdict_part = {'size': 9, 'weight': 'bold'}
 matplotlib.rc('font', **fontdict)
 matplotlib.rc('figure', titlesize = fontdict['size'] + 1)
 matplotlib.rc('axes', titlesize = fontdict['size'] + 1,

### 2016-11-19 Documents/supplementary_information.tex
Tweaked a bit.

@@
 
+We developed a country-level mathematical model of HIV transmission
+and progression that stratifies HIV infection into acute, chronic
+undiagnosed, chronic diagnosed, chronic treated, chronic virally
+suppressed, and AIDS, along with uninfected unvaccinated and
+vaccinated people (\autoref{model} \&
+\hyperref[model_diag]{Extended Data Fig.~\ref*{model_diag}}).
+Simulations of our country-level model project the number of people in
+each HIV stratum from 2015 to 2035, from which statistics such as
+prevalence and incidence were calculated.  Model transition rates were
+adjusted dynamically to meet intervention goals for diagnosis,
+treatment, viral suppression, and vaccination coverage
+(\autoref{targets}).  Data and estimates from many sources were used
+to parametrize the model (\autoref{data_sources}).  Country-specific
+transmission rates were fitted to historical estimates of the
+trajectories of incidence and prevalence, spanning from as early as
+1990 for some countries (\autoref{model_fitting}). For every scenario
+of intervention combinations, we conducted 1000 model simulations,
+sampling values of model parameters from empirical distributions for
+each simulation, and summarized the results with median and
+percentiles (\autoref{uncertainty}).
+
 The model simulation and analysis tools, written in Python, are
@@
 \autocite{vernazza2000, ioannidis2001, attia2009, May2014-gp}.
+Simulations of our model project the number of people in each HIV
+stratum from 2015 to 2035.
 
@@
 
-The parametrized differential equations were solved numerically using
-the LSODA routine \autocite{odepack, scipy, medlock2016-git} and four
-effectiveness outcomes were computed from the solutions.
+The parametrized differential equations were solved numerically from
+year 2015 to year 2035 using the LSODA routine
+\autocite{odepack, scipy, medlock2016-git} and four effectiveness
+outcomes were computed from the solutions.
 \begin{description}

### 2016-11-20 Documents/supplementary_information.tex
Tweaks

@@
 \addbibresource{supplementary_information.bib}
+
+% For Nature, no page numbers.
+\pagestyle{empty}
+\usepackage{etoolbox}
+\apptocmd{\maketitle}{\thispagestyle{empty}}{}{}
 
@@
 divides people aged $15$\;y and older into non-overlapping HIV states.
-We focus on this age group because it accounts for the vast majority
+We focused on this age group because it accounts for the vast majority
 of global PLHIV \autocite{UNICEF}, 93\% in 2014; because
@@
 estimated for ages $15$--$49$; and to capture the continuing burden of
-infections in people ages $50$ and older.
-
-Our model has 8 HIV states (Extended Data Fig.~\ref*{model_diag}):
-susceptible to HIV infection ($S$ is the number of people
-susceptible), vaccinated against HIV ($R$), acute HIV infection ($A$),
-undiagnosed HIV infection ($U$), diagnosed but untreated HIV infection
-($D$), treated without viral suppression ($T$), viral suppression
-($V$), and having AIDS ($W$).  Viral suppression is defined as a viral
-load of less than 1000 viral RNA copies per mL of blood.  Viral
-suppression not only extends survival but also dramatically reduces
-transmission
+infections in people ages $50$ and older.  Our model has 8 HIV states
+(Extended Data Fig.~\ref*{model_diag}): susceptible to HIV infection
+($S$ is the number of people susceptible), vaccinated against HIV
+($R$), acute HIV infection ($A$), undiagnosed HIV infection ($U$),
+diagnosed but untreated HIV infection ($D$), treated without viral
+suppression ($T$), viral suppression ($V$), and having AIDS ($W$).
+Viral suppression is defined as a viral load of less than 1000 viral
+RNA copies per mL of blood.  Viral suppression not only extends
+survival but also dramatically reduces transmission
 \autocite{vernazza2000, ioannidis2001, attia2009, May2014-gp}.

### 2016-11-20 Documents/supplementary_information.tex
Switch from biblatex/biber to bibtex so I can offset the reference numbers.

@@
 
-\usepackage[style=nature]{biblatex}
-\addbibresource{supplementary_information.bib}
+% \usepackage[style=nature]{biblatex}
+% \addbibresource{supplementary_information.bib}
+\usepackage[sort&compress]{natbib}
+\usepackage{hypernat}
+\citestyle{nature}
+
+% For Nature, add 27 to reference numbers to start after
+% last number in manuscript.
+\usepackage{etoolbox}
+\makeatletter
+\apptocmd{\thebibliography}{\global\c@NAT@ctr 27\relax}{}{}
+\makeatother
 
@@
 The model simulation and analysis tools, written in Python, are
-publicly available \autocite{medlock2016-git}.
+publicly available\cite{medlock2016-git}.
 
@@
 We focused on this age group because it accounts for the vast majority
-of global PLHIV \autocite{UNICEF}, 93\% in 2014; because
-population-level HIV estimates and demographic data are typically only
-estimated for ages $15$--$49$; and to capture the continuing burden of
-infections in people ages $50$ and older.  Our model has 8 HIV states
-(Extended Data Fig.~\ref*{model_diag}): susceptible to HIV infection
-($S$ is the number of people susceptible), vaccinated against HIV
-($R$), acute HIV infection ($A$), undiagnosed HIV infection ($U$),
-diagnosed but untreated HIV infection ($D$), treated without viral
-suppression ($T$), viral suppression ($V$), and having AIDS ($W$).
-Viral suppression is defined as a viral load of less than 1000 viral
-RNA copies per mL of blood.  Viral suppression not only extends
-survival but also dramatically reduces transmission
-\autocite{vernazza2000, ioannidis2001, attia2009, May2014-gp}.
+of global PLHIV\cite{UNICEF}, 93\% in 2014; because population-level
+HIV estimates and demographic data are typically only estimated for
+ages $15$--$49$; and to capture the continuing burden of infections in
+people ages $50$ and older.  Our model has 8 HIV states (Extended Data
+Fig.~\ref*{model_diag}): susceptible to HIV infection ($S$ is the
+number of people susceptible), vaccinated against HIV ($R$), acute HIV
+infection ($A$), undiagnosed HIV infection ($U$), diagnosed but
+untreated HIV infection ($D$), treated without viral suppression
+($T$), viral suppression ($V$), and having AIDS ($W$).  Viral
+suppression is defined as a viral load of less than 1000 viral RNA
+copies per mL of blood.  Viral suppression not only extends survival
+but also dramatically reduces
+transmission\cite{vernazza2000, ioannidis2001, attia2009, May2014-gp}.
 Simulations of our model project the number of people in each HIV
@@
 The background mortality rate ($\mu$) in each of the 127 countries was
-collected from published estimates
-\autocite{World_Development_Indicators2013-ee}.  The recruitment rate
-($\kappa$) into the age $15\;\text{y}$ and older group was set by the
-difference between the country's population growth rate
-\autocite{WorldBankpg} and its background mortality rate
-\autocite{World_Development_Indicators2013-ee}, as would be true if
+collected from published
+estimates\cite{World_Development_Indicators2013-ee}.  The recruitment
+rate ($\kappa$) into the age $15\;\text{y}$ and older group was set by
+the difference between the country's population growth
+rate\cite{WorldBankpg} and its background mortality
+rate\cite{World_Development_Indicators2013-ee}, as would be true if
 the population was at its stable age structure.  (More on these data
@@
       & Country specific, Supplementary Table 2
-      & \autocite{World_Development_Indicators2013-ee} \\
+      & \cite{World_Development_Indicators2013-ee} \\
       $\kappa$ & Recruitment rate
       & Country specific, Supplementary Table 2
-      & \autocite{World_Development_Indicators2013-ee, WorldBankpg} \\
+      & \cite{World_Development_Indicators2013-ee, WorldBankpg} \\
       $\delta$	& Rate of leaving acute infection
       & $\Triangular$(2, 4.14, 9.6)\;y$^{-1}$
-      & \autocite{Hollingsworth2008-iy} \\
+      & \cite{Hollingsworth2008-iy} \\
       $\sigma$	& Rate of developing AIDS without viral suppression
-      & 0.1064\;y$^{-1}$ & \autocite{Morgan2002-cq} \\
+      & 0.1064\;y$^{-1}$ & \cite{Morgan2002-cq} \\
       $\theta$ & Rate of developing AIDS with viral suppression
@@
       & $\Uniform$(0.5, 1.5)\;y$^{-1}$
-      & \autocite{Currie2009-yz} \\
+      & \cite{Currie2009-yz} \\
       $\nu$ & Death rate from AIDS & 0.5\;y$^{-1}$
-      & \autocite{Morgan2002-cq} \\
+      & \cite{Morgan2002-cq} \\
       $\rho$ & Vaccine efficacy & 50\%\,[30\%, 70\%] & --- \\
@@
       & $\Uniform$(5, 8)\;y
-      & \autocite{Samji2013-kf, Unaids2014-ue} \\
+      & \cite{Samji2013-kf, Unaids2014-ue} \\
       $\tau_{A}$ & Transmissibility during acute phase
       & $\Triangular$(0.0039, 0.0082, 0.0150)
-      & \autocite{Wawer2005-us, Skarbinski2015-ni}\\
+      & \cite{Wawer2005-us, Skarbinski2015-ni}\\
       $\tau_{U}$ & Transmissibility after acute phase
       & $\Triangular$(0.00077, 0.0014, 0.00251)
-      & \autocite{Hughes2012-so} \\
+      & \cite{Hughes2012-so} \\
       $\varepsilon$ & Relative transmissibility with
       viral suppression & $\BetaPERT$(0.08, 0.002, 0.57)
-      & \autocite{Donnell2010-xo, attia_2009, wilson_2012, jia_2013,
+      & \cite{Donnell2010-xo, attia_2009, wilson_2012, jia_2013,
         rodger_2016} \\
       $n$ & Coital acts per year & $\Uniform$(96, 108)
-      & \autocite{Wawer2005-us, Abdool_Karim2010-cm}\\
+      & \cite{Wawer2005-us, Abdool_Karim2010-cm}\\
       $\alpha$ & Diagnosis rate & See eq.~(\ref{diagnosis_rate}) & --- \\
@@
 characterized by high viral loads and lasts an average of 2.90 [95\%
-confidence interval 1.23, 6.00]\;months
-\autocite{Hollingsworth2008-iy}.  (We converted these durations to
-rates like $1 / 2.90\;\text{month$^{-1}$} \approx
-4.14\;\text{y$^{-1}$}$ and set the parameter using random samples from
+confidence interval 1.23, 6.00]\;months\cite{Hollingsworth2008-iy}.
+(We converted these durations to rates like
+$1 / 2.90\;\text{month$^{-1}$} \approx 4.14\;\text{y$^{-1}$}$ and set
+the parameter using random samples from
 $\Triangular(2, 4.14, 9.6)\;\text{y$^{-1}$}$ to capture the
@@
 $\Uniform(0.5, 1.5)\;\text{y$^{-1}$}$, that is, viral suppression
-occurs after between 8 months and 2 years on treatment
-\autocite{Currie2009-yz}.  Disengagement from treatment moves people
-from treated ($T$) and viral suppression ($V$) at the rate $\psi$,
-dependent on the current level of viral suppression and the country's
-target (\autoref{targets}), back to the diagnosed class ($D$).
+occurs after between 8 months and 2 years on
+treatment\cite{Currie2009-yz}.  Disengagement from treatment moves
+people from treated ($T$) and viral suppression ($V$) at the rate
+$\psi$, dependent on the current level of viral suppression and the
+country's target (\autoref{targets}), back to the diagnosed class
+($D$).
 
 PLHIV without viral suppression (compartments $U$, $D$, and $T$)
-develop AIDS (compartment $W$) after an average duration of 10.4 years
-\autocite{Morgan2002-cq}, i.e. with transition rate
+develop AIDS (compartment $W$) after an average duration of 10.4
+years\cite{Morgan2002-cq}, i.e. with transition rate
 $\sigma = 0.1064\;\text{y$^{-1}$}$.  People who have achieved viral
@@
 without viral suppression.  People with viral suppression are
-estimated to live $5$--$8$\;y shorter lives than the non-HIV infected
-\autocite{Samji2013-kf, Unaids2014-ue}, which we quantified by
+estimated to live $5$--$8$\;y shorter lives than the non-HIV
+infected\cite{Samji2013-kf, Unaids2014-ue}, which we quantified by
 randomly sampling the parameter $\omega$ from
@@
 transmissibility during the acute phase, we sampled $\tau_A$ from
-$\Triangular$(0.0039, 0.0082, 0.0150)
-\autocite{Wawer2005-us, Skarbinski2015-ni}, whereas, for transmissibility
-for unsuppressed people, we sampled $\tau_U$ from
-$\Triangular(0.00077, 0.0014, 0.00251)$ \autocite{Hughes2012-so}.  The
+$\Triangular(0.0039, 0.0082, 0.0150)$\cite{Wawer2005-us,
+  Skarbinski2015-ni},
+whereas, for transmissibility for unsuppressed people, we sampled
+$\tau_U$ from
+$\Triangular(0.00077, 0.0014, 0.00251)$\cite{Hughes2012-so}.  The
 transmissibility of people with viral suppression relative to those
 without suppression has been estimated at 0.08 (95\% confidence
-interval 0.002, 0.57) \autocite{Donnell2010-xo}: due to the extremely long
+interval 0.002, 0.57)\cite{Donnell2010-xo}: due to the extremely long
 left tail, we chose to sample the relative transmissibility
@@
 description of $\BetaPERT(a, b, c)$.)  The annual number of coital
-acts $n$ was sampled from $\Uniform(96, 108)$
-\autocite{Wawer2005-us, Abdool_Karim2010-cm}.  The country-specific
-transmission rate $\eta$ was derived from UNAIDS estimates of each
-country's longitudinal HIV prevalence and incidence
+acts $n$ was sampled from
+$\Uniform(96, 108)$\cite{Wawer2005-us, Abdool_Karim2010-cm}.  The
+country-specific transmission rate $\eta$ was derived from UNAIDS
+estimates of each country's longitudinal HIV prevalence and incidence
 (\autoref{model_fitting}).
@@
 The parametrized differential equations were solved numerically from
-year 2015 to year 2035 using the LSODA routine
-\autocite{odepack, scipy, medlock2016-git} and four effectiveness
-outcomes were computed from the solutions.
+year 2015 to year 2035 using the LSODA routine\cite{odepack, scipy,
+  medlock2016-git} and four effectiveness outcomes were computed from
+the solutions.
 \begin{description}
@@
 parametrize our model.  Demographic data, including population growth
-rate \autocite{WorldBankpg}, death rate
-\autocite{World_Development_Indicators2013-ee}, and number of people
-aged 15--49 years \autocite{The_World_Bank2016-fd} were obtained from
-the World Bank (Supplementary Table 2). Longitudinal HIV prevalence
+rate\cite{WorldBankpg}, death
+rate\cite{World_Development_Indicators2013-ee}, and number of people
+aged 15--49 years\cite{The_World_Bank2016-fd} were obtained from the
+World Bank (Supplementary Table 2). Longitudinal HIV prevalence
 (Supplementary Table 3) and incidence (Supplementary Table 4)
@@
 countries to 2015, were primarily obtained from the AIDSinfo database
-produced by UNAIDS \autocite{Unaids2016-an}. Other sources included
-UNAIDS Country Progress Reports \autocite{Unaids2016-am} published
-from 2012 to 2016 and AIDS Data Hub \autocite{AIDSdatahub-fg}, which
-compiles data from UNAIDS, UNICEF, WHO, and the Asian Development
-Bank. These sources were also used to inform the initial conditions
-for the model: the number of people diagnosed with HIV, the number on
-ART, and the number who have viral suppression or have been retained
-on treatment for at least 12 months (Supplementary Table 5). Where
-estimates or data were not available from these sources, alternative
-resources such as peer-reviewed journal articles and country health
-ministry reports were consulted.  See Supplementary Tables 2--5 for
-full information on the sources used for each country.  These source
-tables are also available in the public source-code repository
-\autocite{medlock2016-git}.
+produced by UNAIDS\cite{Unaids2016-an}. Other sources included UNAIDS
+Country Progress Reports\cite{Unaids2016-am} published from 2012 to
+2016 and AIDS Data Hub\cite{AIDSdatahub-fg}, which compiles data from
+UNAIDS, UNICEF, WHO, and the Asian Development Bank. These sources
+were also used to inform the initial conditions for the model: the
+number of people diagnosed with HIV, the number on ART, and the number
+who have viral suppression or have been retained on treatment for at
+least 12 months (Supplementary Table 5). Where estimates or data were
+not available from these sources, alternative resources such as
+peer-reviewed journal articles and country health ministry reports
+were consulted.  See Supplementary Tables 2--5 for full information on
+the sources used for each country.  These source tables are also
+available in the public source-code repository\cite{medlock2016-git}.
 
@@
 incidence (Supplementary Tables 3 and 4), and published estimates of
-transmissibility
-\autocite{Wawer2005-us,Donnell2010-xo,Hughes2012-so,Skarbinski2015-ni},
+transmissibility\cite{Wawer2005-us, Donnell2010-xo, Hughes2012-so,
+  Skarbinski2015-ni},
 we derived an average country-specific transmission rate, which then
@@
 $\mu$ and $\sigma^2$ of the lognormal distribution we used the
-exponentially weighted mean and variance \autocite{holt2004} over time
+exponentially weighted mean and variance\cite{holt2004} over time
 (with half-life 1\;y) of $\log \beta(t)$ for the year 2015.  That is,
@@
 distribution of the transmission rate (\autoref{model_fitting}). The
-parameters were sampled using Latin hypercube sampling
-\autocite{blower1994}.  We also used the variance reduction technique of
-running different interventions with the same parameter samples, i.e.
-one set of sample parameter values is drawn, status quo and
-intervention scenarios are all run with those sample values and
+parameters were sampled using Latin hypercube
+sampling\cite{blower1994}.  We also used the variance reduction
+technique of running different interventions with the same parameter
+samples, i.e.  one set of sample parameter values is drawn, status quo
+and intervention scenarios are all run with those sample values and
 compared, and this process is repeated for each of the 1000 sample
-sets of parameters \autocite{shechter2006}.
+sets of parameters\cite{shechter2006}.
 
@@
 percentiles.  We calculated partial rank correlation coefficients
-(PRCC) \autocite{blower1994} to measure the independent effect of each
+(PRCC)\cite{blower1994} to measure the independent effect of each
 non-vaccine parameter on model projections of global new HIV
@@
 \item[Beta-PERT] $\BetaPERT(a, b, c)$ is the Beta-PERT probability
-  distribution \autocite{malcom1959} with minimum $a$, mode $b$, and
+  distribution\cite{malcom1959} with minimum $a$, mode $b$, and
   maximum $c$.  It has density function
@@
   \end{equation}
-  and $B(v, w)$ is the standard beta function \autocite{davis1972}.
+  and $B(v, w)$ is the standard beta function\cite{davis1972}.
   % \cite[\S6.2]{davis1972}
@@
 
-\printbibliography
+% \printbibliography
+\bibliography{supplementary_information}
+\bibliographystyle{naturemag}
 

### 2016-11-30 Documents/supplementary_information.tex
Tweak graphics import.
Merged Alison's edits.

@@
   {\texttt{jan.medlock@oregonstate.edu}}}
-\author{Abhishek Pandey} \author{Alyssa S.~Parpia} \author{Amber Tang}
-\author{Laura A.~Skrip} \author{Alison P.~Galvani}
+\author{Abhishek Pandey}
+\author{Alyssa S.~Parpia}
+\author{Amber Tang}
+\author{Laura A.~Skrip}
+\author{Alison P.~Galvani}
 \affil{Center for Infectious Disease Modeling and Analysis, Yale
@@
 
-We developed a country-level mathematical model of HIV transmission
-and progression that stratifies HIV infection into acute, chronic
-undiagnosed, chronic diagnosed, chronic treated, chronic virally
-suppressed, and AIDS, along with uninfected unvaccinated and
-vaccinated people (\autoref{model} \&
-\hyperref[model_diag]{Extended Data Fig.~\ref*{model_diag}}).
-Simulations of our country-level model project the number of people in
-each HIV stratum from 2015 to 2035, from which statistics such as
-prevalence and incidence were calculated.  Model transition rates were
-adjusted dynamically to meet intervention goals for diagnosis,
-treatment, viral suppression, and vaccination coverage
-(\autoref{targets}).  Data and estimates from many sources were used
-to parametrize the model (\autoref{data_sources}).  Country-specific
-transmission rates were fitted to historical estimates of the
-trajectories of incidence and prevalence, spanning from as early as
-1990 for some countries (\autoref{model_fitting}). For every scenario
-of intervention combinations, we conducted 1000 model simulations,
-sampling values of model parameters from empirical distributions for
-each simulation, and summarized the results with median and
-percentiles (\autoref{uncertainty}).
+We developed a mathematical model of HIV transmission and progression
+that stratifies HIV infection into acute, chronic undiagnosed, chronic
+diagnosed, chronic treated, chronic virally suppressed, and AIDS,
+along with uninfected unvaccinated and vaccinated people
+(\autoref{model} \&
+\hyperref[model_diag]{Extended Data Fig.~\ref*{model_diag}}), tailored
+to each of 127 countries.  Simulations of our model project the number
+of people in each HIV stratum from 2015 to 2035, from which statistics
+such as prevalence and incidence were calculated.  To evaluate the
+impact of the 90--90--90 and 95--95--95 UNAIDS goals, model transition
+rates were adjusted dynamically to meet intervention goals for
+diagnosis, treatment, viral suppression, and vaccination coverage
+(\autoref{targets}).  Data and estimates from many sources, including
+The World Bank and UNAIDS, were used to parametrize the model
+(\autoref{data_sources}).  Country-specific transmission rates were
+fitted to estimates of the historical trajectories of incidence and
+prevalence, spanning from as early as 1990 for some countries
+(\autoref{model_fitting}). For every scenario of intervention
+combinations, we conducted 1000 model simulations, sampling values of
+model parameters from empirical distributions for each simulation, and
+reported the results with median and percentiles
+(\autoref{uncertainty}).
 
 The model simulation and analysis tools, written in Python, are
-publicly available\cite{medlock2016-git}.
+publicly available.\cite{medlock2016-git}
 
-\section{Mathematical model}
+\section{Model structure}
 \label{model}
 
-We developed a country-level continuous-time mathematical model that
-divides people aged $15$\;y and older into non-overlapping HIV states.
-We focused on this age group because it accounts for the vast majority
-of global PLHIV\cite{UNICEF}, 93\% in 2014; because population-level
-HIV estimates and demographic data are typically only estimated for
-ages $15$--$49$; and to capture the continuing burden of infections in
+Within each country, our model divides people aged $15$\;years and
+older into non-overlapping HIV states.  We focused on this age group
+because it accounts for the vast majority of global
+PLHIV,\cite{UNICEF} 93\% in 2014; because population-level HIV
+estimates and demographic data are typically only estimated for ages
+$15$--$49$; and to capture the continuing burden of infections in
 people ages $50$ and older.  Our model has 8 HIV states (Extended Data
@@
 untreated HIV infection ($D$), treated without viral suppression
-($T$), viral suppression ($V$), and having AIDS ($W$).  Viral
-suppression is defined as a viral load of less than 1000 viral RNA
-copies per mL of blood.  Viral suppression not only extends survival
-but also dramatically reduces
-transmission\cite{vernazza2000, ioannidis2001, attia2009, May2014-gp}.
-Simulations of our model project the number of people in each HIV
-stratum from 2015 to 2035.
+($T$), viral suppression ($V$), and having AIDS ($W$).
 
@@
 
-The background mortality rate ($\mu$) in each of the 127 countries was
-collected from published
-estimates\cite{World_Development_Indicators2013-ee}.  The recruitment
-rate ($\kappa$) into the age $15\;\text{y}$ and older group was set by
-the difference between the country's population growth
-rate\cite{WorldBankpg} and its background mortality
-rate\cite{World_Development_Indicators2013-ee}, as would be true if
-the population was at its stable age structure.  (More on these data
-sources is in \autoref{data_sources}.)
-
 \begin{table}
@@
       \hline
-      & Definition & Value & Reference \\
+      & Definition & Value & References \\
       \hline
@@
       & \cite{World_Development_Indicators2013-ee, WorldBankpg} \\
-      $\delta$	& Rate of leaving acute infection
+      $\delta$	& Rate of progression from acute infection
       & $\Triangular$(2, 4.14, 9.6)\;y$^{-1}$
@@
       $\rho$ & Vaccine efficacy & 50\%\,[30\%, 70\%] & --- \\
-      $\omega$	& Reduction in lifetime with viral suppression
+      $\omega$	& Reduction in life expectancy with viral suppression
       & $\Uniform$(5, 8)\;y
@@
       & \cite{Hughes2012-so} \\
-      $\varepsilon$ & Relative transmissibility with
+      $\epsilon$ & Relative transmissibility with
       viral suppression & $\BetaPERT$(0.08, 0.002, 0.57)
@@
       For vaccine efficacy, $50\%$ was the baseline, and $30\%$ and
-      $70\%$ were also used in a scenario analysis.}
+      $70\%$ were also assessed in sensitivity analysis.}
     \label{model_param}
@@
 
-People susceptible to HIV ($S$) progress to acute infection ($A$)
+People susceptible to HIV ($S$) are at risk of becoming infected
 according to the force of infection ($\lambda$), which depends on the
@@
 current number of acutely infected, untreated or ineffectively
-treated, and viral suppression PLHIV.  Acute infection is
-characterized by high viral loads and lasts an average of 2.90 [95\%
-confidence interval 1.23, 6.00]\;months\cite{Hollingsworth2008-iy}.
-(We converted these durations to rates like
-$1 / 2.90\;\text{month$^{-1}$} \approx 4.14\;\text{y$^{-1}$}$ and set
-the parameter using random samples from
+treated, and virally suppressed PLHIV.  Upon infection, people
+transition into acute infection ($A$), characterized by high viral
+loads for an average of 2.90 [95\% confidence interval 1.23,
+6.00]\;months.\cite{Hollingsworth2008-iy}  (We converted these
+durations to rates like $1 / 2.90\;\text{month$^{-1}$} \approx
+4.14\;\text{y$^{-1}$}$ and set the parameter using random samples from
 $\Triangular(2, 4.14, 9.6)\;\text{y$^{-1}$}$ to capture the
 uncertainty in its value.  See \autoref{uncertainty} for the
-definition of $\Triangular(a, b, c)$ and other distributions.)  We
-assumed that people remain undiagnosed during their acute-infection
-phase. After acute infection, people move into the chronic undiagnosed
-class ($U$).  People in the undiagnosed class will be diagnosed at the
-rate $\alpha$, which is determined by the country's current diagnosis
-level and its diagnosis target (\autoref{targets}).  Diagnosed people
-($D$) transition to the treated compartment ($T$) upon starting ART at
-the rate $\phi$, dependent on the country's current treatment level
-and its treatment target (\autoref{targets}).  After some time,
-treated people then transition to the viral-suppression class ($V$),
-at the rate $\gamma$.  We took $\gamma$ as a random sample from
-$\Uniform(0.5, 1.5)\;\text{y$^{-1}$}$, that is, viral suppression
-occurs after between 8 months and 2 years on
-treatment\cite{Currie2009-yz}.  Disengagement from treatment moves
-people from treated ($T$) and viral suppression ($V$) at the rate
-$\psi$, dependent on the current level of viral suppression and the
-country's target (\autoref{targets}), back to the diagnosed class
-($D$).
+definition of $\Triangular(a, b, c)$ and other distributions.)  Acute
+infection progresses into the chronic undiagnosed class ($U$), from
+which diagnosis occurs at the rate $\alpha$, which is determined by
+the country's current diagnosis level and its diagnosis target under
+the different scenarios (\autoref{targets}).  Upon diagnosis, people
+transition into the diagnosed class ($D$).  From the diagnosed class,
+people transition to the treated compartment ($T$) upon starting ART
+at the rate $\phi$, dependent on the country's current treatment level
+and its treatment target (\autoref{targets}).  Treated people
+transition to the viral suppression ($V$) at the rate $\gamma$,
+sampled from $\Uniform(0.5, 1.5)\;\text{y$^{-1}$}$: thus, viral
+suppression occurs after between 8 months and 2 years on
+treatment.\cite{Currie2009-yz}  Disengagement from treatment moves
+people from treated ($T$) and viral suppression ($V$) back to the
+diagnosed class ($D$) at the rate $\psi$, dependent on the current
+level of viral suppression and the country's target
+(\autoref{targets}).
 
@@
 develop AIDS (compartment $W$) after an average duration of 10.4
-years\cite{Morgan2002-cq}, i.e. with transition rate
-$\sigma = 0.1064\;\text{y$^{-1}$}$.  People who have achieved viral
-suppression ($V$) develop AIDS at rate $\theta$, slower than PLHIV
-without viral suppression.  People with viral suppression are
-estimated to live $5$--$8$\;y shorter lives than the non-HIV
-infected\cite{Samji2013-kf, Unaids2014-ue}, which we quantified by
-randomly sampling the parameter $\omega$ from
-$\Uniform(5, 8)\;\text{y}$.  Assuming no relapse to untreated, the
-duration of viral suppression is
+years,\cite{Morgan2002-cq} i.e.~with transition rate
+$\sigma = 0.1064\;\text{y$^{-1}$}$.  Viral suppression greatly reduces
+the rate of progression to AIDS ($\theta$) and improves longevity,
+such that life expectancy is only $5$--$8$\;y shorter than average
+country-specific life expectancy.\cite{Samji2013-kf, Unaids2014-ue}
+This reduction in life expectancy was quantified by randomly sampling
+the parameter $\omega$ from $\Uniform(5, 8)\;\text{y}$. Thus, in the
+absence of relapse to untreated, the duration of viral suppression is
 \begin{equation}
@@
 \end{equation}
-The term to the left of the equals sign is the time until leaving
-viral suppression by either progression to AIDS (at rate $\theta$) or
-background mortality (at rate $\mu$).  The term to the right of the
-equals sign is the lifespan of the non-HIV infected, minus the
-reduction in life due to having HIV with viral suppression, minus the
-duration of the AIDS stage.  Solving for $\theta$ gives the rate of
-progression to AIDS with viral suppression as
+The left-hand side of the equation is the time until leaving viral
+suppression by either progression to AIDS (at rate $\theta$) or
+background mortality (at rate $\mu$).  The right-hand side of the
+equation is the life expectancy of uninfected people, minus the
+reduction in life expectancy attributable to virally suppressed HIV
+infection, minus the duration of the AIDS stage.  Solving for $\theta$
+gives the rate of progression to AIDS from viral suppression,
 \begin{equation}
@@
 
-In scenarios with vaccine, susceptible people are vaccinated at rate
-$\zeta$, depending on the country's current vaccination coverage and
-its coverage target (\autoref{targets}), transitioning into the
-vaccinated compartment ($R$), where the vaccine reduces their force of
-infection by the efficacy factor $\rho$.  We took the base-case
-efficacy to be $50\%$ and varied it to $30\%$ and $70\%$ in analyzing
-vaccination scenarios (\autoref{uncertainty}).  We did not model
+In the vaccination scenarios, susceptible people are vaccinated at
+rate $\zeta$, depending on the country's current vaccination coverage
+and its coverage target (\autoref{targets}), transitioning into the
+vaccinated compartment ($R$).  The force of infection for vaccinated
+people is reduced by the efficacy factor $\rho$.  We took the
+base-case efficacy to be $50\%$, but varied it to $30\%$ and $70\%$ in
+sensitivity analysis (\autoref{uncertainty}).  We did not model
 specific vaccine dose regime, such that implicit in our efficacy
@@
 
+The background mortality rate ($\mu$) in each of the 127 countries was
+collected from published
+estimates.\cite{World_Development_Indicators2013-ee} The recruitment
+rate ($\kappa$) into the age $15\;\text{y}$ and older group was set by
+the difference between the country's population growth
+rate\cite{WorldBankpg} and its background mortality
+rate,\cite{World_Development_Indicators2013-ee} as would be true if
+the population was at its stable age structure.  (More on these data
+sources is in \autoref{data_sources}.)
+
 We also added differential equations to track the cumulative number of
-new infections ($Y$) and AIDS deaths ($Z$) over the model period.
+new infections ($Y$) and AIDS deaths ($Z$) over the simulation period.
 
@@
   \lambda =
-  \frac{\eta \big[\beta_A A + \beta_U (U + D + T) + \beta_V V\big]}{N},
+  \frac{\xi \big[\beta_A A + \beta_U (U + D + T) + \beta_V V\big]}{N},
 \end{equation}
@@
 
-The relative transmission rates of acute, unsuppressed, and suppressed
-infected people are
+The relative transmission rates (per unit time), $\beta$, from acute
+($A$), unsuppressed ($U$ and $T$), and suppressed infected ($V$)
+people are respectively
 \begin{equation}
@@
     \\
-    \beta_V &= 1 - (1 - \varepsilon \tau_U)^n,
+    \beta_V &= 1 - (1 - \epsilon \tau_U)^n,
   \end{split}
 \end{equation}
-where the $\tau$'s are the relative transmissibilities of people with
-acute ($A$), unsuppressed ($U$ and $T$), and suppressed ($V$)
-infections, $n$ is the annual number of coital acts, and $\varepsilon$
-is the relative transmissibility with viral suppression.  For
-transmissibility during the acute phase, we sampled $\tau_A$ from
-$\Triangular(0.0039, 0.0082, 0.0150)$\cite{Wawer2005-us,
-  Skarbinski2015-ni},
-whereas, for transmissibility for unsuppressed people, we sampled
-$\tau_U$ from
-$\Triangular(0.00077, 0.0014, 0.00251)$\cite{Hughes2012-so}.  The
-transmissibility of people with viral suppression relative to those
-without suppression has been estimated at 0.08 (95\% confidence
-interval 0.002, 0.57)\cite{Donnell2010-xo}: due to the extremely long
-left tail, we chose to sample the relative transmissibility
-$\varepsilon$ from $\BetaPERT(0.08, 0.002, 0.57)$ rather than a
-$\Triangular$ distribution.  (See \autoref{uncertainty} for a full
-description of $\BetaPERT(a, b, c)$.)  The annual number of coital
-acts $n$ was sampled from
-$\Uniform(96, 108)$\cite{Wawer2005-us, Abdool_Karim2010-cm}.  The
-country-specific transmission rate $\eta$ was derived from UNAIDS
-estimates of each country's longitudinal HIV prevalence and incidence
-(\autoref{model_fitting}).
+where the $\tau$'s are the relative transmissibilities per coital act,
+$n$ is the annual number of coital acts, and $\epsilon$ is the
+relative transmissibility per coital act with viral suppression.  For
+transmissibility per coital act during the acute phase, we sampled
+$\tau_A$ from
+$\Triangular(0.0039, 0.0082,
+0.0150)$.\cite{Wawer2005-us,
+  Skarbinski2015-ni}
+Transmissibility per coital act for unsuppressed people, $\tau_U$, was
+sampled from
+$\Triangular(0.00077, 0.0014, 0.00251)$.\cite{Hughes2012-so} The
+transmissibility per coital act of people with viral suppression
+relative to those without suppression has been estimated at 0.08 (95\%
+confidence interval 0.002, 0.57).\cite{Donnell2010-xo} Due to the
+extremely long left tail of this confidence interval, we sampled the
+relative transmissibility per coital act $\epsilon$ from
+$\BetaPERT(0.08, 0.002, 0.57)$ rather than a $\Triangular$
+distribution.  (See \autoref{uncertainty} for a full description of
+$\BetaPERT(a, b, c)$.)  The annual number of coital acts per person
+$n$ was sampled from $\Uniform(96, 108)$ based on survey
+studies.\cite{Wawer2005-us, Abdool_Karim2010-cm}  The country-specific
+transmission rate $\xi$ was derived from country-specific longitudinal
+trends in HIV prevalence and incidence, primarily from UNAIDS
+estimates (\autoref{model_fitting}).
 
-For year 2015, estimates of the number of people aged 15--49 years,
-$M(2015)$; the prevalence, $p_I(2015)$; the proportion diagnosed,
-$p_D(2015)$; the proportion treated, $p_T(2015)$; and proportion with
-viral suppression, $p_V(2015)$ were used to initialize the model
+The model was initiated with country-specific estimates from 2015 of
+the number of people aged 15--49 years, $M(2015)$; the prevalence,
+$p_I(2015)$; the proportion diagnosed, $p_D(2015)$; the proportion
+treated, $p_T(2015)$; and proportion with viral suppression,
+$p_V(2015)$ were used to initialize the model
 (\autoref{data_sources}).  Although the initial population used ages
 15--49 due to the availability of published estimates, model
-projections allowed for analysis of infected people aging beyond age
-50.  Due to a lack of published estimates of acute infections, and
-since the acute phase is so much shorter than the other stages, we
-assumed that initially there were no acute infections.  Due to a lack
-of comprehensive estimates of the number of people with AIDS in each
-country, we assumed that the proportion of diagnosed, untreated people
-($D + W$) who have AIDS ($W$) in year 2015 was
+projections allowed for analysis of infected people aging beyond 50
+years old.  Due to a lack of published estimates of the number of
+acute infections, and since the acute phase is so much shorter than
+the other stages, we assumed that initially there were no acute
+infections.  Due to a lack of comprehensive estimates of the number of
+people with AIDS in each country, we assumed that the proportion of
+diagnosed, untreated people ($D + W$) who have AIDS ($W$) in year 2015
+was
 \begin{equation}
@@
 have AIDS ($W$) in the absence of treatment and background mortality.
-The number initially vaccinated was set to 0.  The initial cumulative
-number of new infections and AIDS deaths were set to 0.  Thus, the
+Simulations were initiated with no vaccination.  The cumulative number
+of new infections and AIDS deaths were initially set to 0.  Thus, the
 model initial conditions are
@@
 The parametrized differential equations were solved numerically from
-year 2015 to year 2035 using the LSODA routine\cite{odepack, scipy,
-  medlock2016-git} and four effectiveness outcomes were computed from
-the solutions.
-\begin{description}
-\item[New infections] New infections from 2015 to time $t$ are given
-  by $Y(t)$.
+2015 to 2035 using the LSODA
+routine\cite{odepack, scipy, medlock2016-git} and four effectiveness
+outcomes were computed from the solutions.
+\begin{description}[labelsep=0.6ex]
+\item[Cumulative new infections] from 2015 to time $t$ was given by
+  $Y(t)$.
 
-\item[Per-capita incidence] At each solution time point, the
-  per-capita incidence was calculated as
+\item[Per-capita incidence] at each solution time was calculated as
   \begin{equation}
@@
   \end{equation}
-  is the total population size at time $t$.  The per-capita incidence
-  at the first time point was undefined.
+  is the total population size at time $t$.  (The per-capita incidence
+  at the first time point was undefined.)
 
-\item[PLHIV] At each solution time point, PLHIV was given by
+\item[PLHIV] at each solution time was given by
   \begin{equation}
@@
 
-\item[AIDS-related deaths] AIDS-related deaths from 2015 to time $t$
-  are given by $Z(t)$.
+\item[Cumulative AIDS-related deaths] from 2015 to time $t$ was given
+  by $Z(t)$.
 
@@
 
-The current proportion of PLHIV who know their diagnosis is
+The current proportion of PLHIV who have been diagnosed is
 \begin{equation}
   p_D(t) = \frac{D(t) + T(t) + V(t) + W(t)}
-  {A(t) + U(t) + D(t) + T(t) + V(t) + W(t)},
+  {A(t) + U(t) + D(t) + T(t) + V(t) + W(t)}.
 \end{equation}
-and the desired target for the current level of diagnosis is
-$p_D^*(t)$.  For the rate of new diagnosis, we used the function
+The timing and levels of diagnosis under evaluation, whether
+maintaining status quo or increasing to UNAIDS targets, are given by
+the target $p_D^*(t)$.  (See below.)  To achieve this target, we
+adjusted the diagnosis rate over time according to the function
 \begin{equation}
@@
 \end{equation}
-Like the rate of new diagnosis, the rate of enrolling new people in
-treatment is
+Like the diagnosis rate, the rate of treatment initiation is
 \begin{equation}
@@
 relapses ($\psi(t) > 0$) when the current level of viral suppression
-is at or above target.  We chose to vary the relapse rate to achieve
-the desired level of viral suppression because achieving viral
-suppression seems to depend on the time on treatment (i.e.
-$1 / \gamma$), while relapse rates are difficult to estimate.
+is at or above target.  We varied the relapse rate to achieve the
+target level of viral suppression because achieving viral suppression
+depends on the time on treatment\cite{Currie2009-yz}
+(i.e.~$1 / \gamma$).
 
@@
 \end{equation}
-with $\zeta_{\max} = 1$, allowing vaccination ($\zeta(t) > 0$) when
-the current vaccine coverage level is below the target
-($p_R^*(t) > p_R(t)$) and stopping vaccination ($\zeta(t) = 0$) when
-the current vaccine coverage is at or above target.
+with $\zeta_{\max} = 1$, vaccinating people ($\zeta(t) > 0$) when the
+current vaccine coverage level is below the target
+($p_R^*(t) > p_R(t)$).
 
@@
 proportion treated ($p_T$), and the proportion with viral suppression ($p_V$).
-\begin{description}
-\item[Status quo] The status quo target is for the proportions $p_D$,
-  $p_T$, and $p_V$ to remain fixed at their initial levels
-  (Supplementary Table 5) going forward. That is,
+\begin{description}[labelsep=0.6ex]
+\item[Status quo] is maintenance of the proportions $p_D$, $p_T$, and
+  $p_V$ at their initial levels going forward.  That is,
   \begin{equation}
@@
 
-\item[UNAIDS 90--90--90] The UNAIDS 90--90--90 target is for $p_D$,
-  $p_T$, and $p_V$ to all be raised to $90\%$ by 2020.  We implemented
-  this target as linear increases from the 2015 levels, each up to
-  $90\%$ in 2020, and constant at $90\%$ from 2020 to 2035, except if
-  an initial level is above $90\%$ then it remains constant from 2015
-  to 2035 so that meeting the UNAIDS target does not worsen any aspect
-  of the treatment cascade.  That is,
+\item[UNAIDS 90--90--90] was implemented as linearly increasing $p_D$,
+  $p_T$, and $p_V$ from their 2015 levels, each up to $90\%$ by 2020,
+  and then maintained at $90\%$ from 2020 to 2035.  However, if an
+  initial level exceeds $90\%$, it is maintained at its higher level
+  so that meeting the 90--90--90 goal does not worsen any aspect of
+  the treatment cascade.  That is,
   \begin{equation}
@@
         \\
-        p_V(2015) & \text{if $p_V(2015) \geq 0.9$}.
+        p_V(2015) & \text{if $p_V(2015) \geq 0.9$},
       \end{cases}
@@
 
-\item[UNAIDS 95--95--95] The UNAIDS 95--95--95 target is to achieve
-  90--90--90 by 2020 and then for $p_D$, $p_T$, and $p_V$ to all be
-  raised to $95\%$ by 2030.  We implemented this target as for
-  90--90--90 from 2015 to 2020, and then linear increases from the
-  2020 levels up to $95\%$ in 2030, again with the exception that if
-  an initial level is above $95\%$ then it remains constant from 2015
-  to 2035.  That is,
+\item[UNAIDS 95--95--95] is to achieve 90--90--90 by 2020, and then
+  for $p_D$, $p_T$, and $p_V$ to all be raised to $95\%$ by 2030.  We
+  implemented this target as for 90--90--90 from 2015 to 2020, and
+  then as linear increases from the 2020 levels up to $95\%$ in 2030,
+  again with the exception that if an initial level is above $95\%$
+  then it remains constant from 2015 to 2035.  That is,
   \begin{equation}
@@
 
-For vaccination, we assume that rollout begins in year $t_V = 2020$
-(or $t_V = 2025$ in vaccine scenario analysis, \autoref{uncertainty}),
-that rollout linearly increases the proportion of the non-infected
-population covered from 0\% by $r_V = 25\%$ per year (or $r_V = 10\%$
-per year) up to $c_V = 70\%$ (or $c_V = 50\%$ or $c_V = 90\%$) and
-staying constant thereafter.  Thus, the vaccination target is
+For vaccination, we assume in our base case that rollout begins in
+year $t_V = 2020$ (or $t_V = 2025$ in vaccine scenario analysis,
+\autoref{uncertainty}), with the proportion of susceptible people
+becoming vaccinated increasing from 0\% by $r_V = 25\%$ per year (or
+$r_V = 10\%$ per year) up to $c_V = 70\%$ (or $c_V = 50\%$ or
+$c_V = 90\%$), after which the vaccination coverage remains constant.
+Thus, the target for vaccination coverage at time $t$ is
 \begin{equation}
@@
 
-Target strategies were one of the three diagnosis and treatment
-targets (status quo, 90--90--90, or 95--95--95), combined with either
-no vaccination ($p_R^*(t) = 0$) or vaccination at some level of
+We simulated each of the 3 diagnosis and treatment targets (status
+quo, 90--90--90, or 95--95--95) with and without vaccination.  In
+sensitivity analysis (\autoref{uncertainty}), we varied vaccine
 efficacy, ultimate coverage, start date of rollout, and speed of
@@
 
-For 127 countries, we found sufficient published estimates and data to
-parametrize our model.  Demographic data, including population growth
-rate\cite{WorldBankpg}, death
-rate\cite{World_Development_Indicators2013-ee}, and number of people
+We found sufficient published estimates and data to parametrize our
+model for 127 countries.  Demographic data, including population
+growth rate,\cite{WorldBankpg} death
+rate,\cite{World_Development_Indicators2013-ee} and number of people
 aged 15--49 years\cite{The_World_Bank2016-fd} were obtained from the
@@
 countries to 2015, were primarily obtained from the AIDSinfo database
-produced by UNAIDS\cite{Unaids2016-an}. Other sources included UNAIDS
+produced by UNAIDS.\cite{Unaids2016-an} Other sources included UNAIDS
 Country Progress Reports\cite{Unaids2016-am} published from 2012 to
-2016 and AIDS Data Hub\cite{AIDSdatahub-fg}, which compiles data from
+2016 and AIDS Data Hub,\cite{AIDSdatahub-fg} which compiles data from
 UNAIDS, UNICEF, WHO, and the Asian Development Bank.  These sources
-were also used to inform the initial conditions for the model: the
-number of people diagnosed with HIV, the number on ART, and the number
-who have viral suppression or have been retained on treatment for at
-least 12 months (Supplementary Table 5). Where estimates or data were
-not available from these sources, alternative resources such as
-peer-reviewed journal articles and country health ministry reports
-were consulted.  See Supplementary Tables 2--5 for full information on
-the sources used for each country.  These source tables are also
-available in the public source-code repository\cite{medlock2016-git}.
+were also used to inform the initial conditions for the model
+regarding the number of people diagnosed with HIV, the number on ART,
+and the number who have viral suppression or have been retained on
+treatment for at least 12 months (Supplementary Table 5).  Where data
+or estimates were not available from these sources, alternative
+resources such as peer-reviewed journal articles and country health
+ministry reports were consulted.  Full information on the sources used
+for each country is provided in Supplementary Tables 2--5.  These
+source tables are also available in our public source-code
+repository.\cite{medlock2016-git}
 
@@
 
-Using available historical country-level estimates of prevalence and
+We tailored our model to each of the 127 countries separately.  Using
+available historical country-specific estimates of prevalence and
 incidence (Supplementary Tables 3 and 4), and published estimates of
-transmissibility\cite{Wawer2005-us, Donnell2010-xo, Hughes2012-so,
-  Skarbinski2015-ni},
-we derived an average country-specific transmission rate, which then
-informs the acute, unsuppressed, and suppressed transmission rates.
-This calibration method provided a recent estimate of country-specific
-transmission, while using historical data to smooth out short-term
-variations.
+transmissibility per coital
+act,\cite{Wawer2005-us, Donnell2010-xo, Hughes2012-so,
+  Skarbinski2015-ni}
+we derived an average country-specific transmission rate, taking into
+account the differential contributions from the proportions of acute,
+unsuppressed, and suppressed of the infected population in each
+country.  Using historical data to smooth out short-term variations,
+our calibration method provided estimates of current country-specific
+transmission, as detailed below.
 
-For each country, we first derived time-dependent rates of HIV
-transmission for each of the available points in the historical
-estimates of prevalence and incidence.  The calculation involved
-approximating the simplified force of infection
+We first derived country-specific rates of HIV transmission,
+$\beta(t)$, for each of the available points in the historical
+estimates of prevalence and incidence.  Approximating the model
+force of infection \eqref{force_of_infection} by
 \begin{align}
@@
   \begin{split}
-    \lambda(t) &= \frac{\eta \left[\beta_{A} A(t)
+    \lambda(t) &= \frac{\xi \left[\beta_{A} A(t)
         + \beta_{U} \big(U(t) + D(t) + T(t)\big) +
@@
 transmission risk among acute, unsuppressed, suppressed, and AIDS
-classes, and $I = A + U + D + T + V + W$ is the total number of PLHIV.
-Therefore, the per-capita incidence is
+classes, and $I = A + U + D + T + V + W$ is the total number of PLHIV,
+gives the per-capita incidence as
 \begin{equation}
@@
 exponentially weighted mean and variance\cite{holt2004} over time
-(with half-life 1\;y) of $\log \beta(t)$ for the year 2015.  That is,
+(with half-life 1\;year) of $\log \beta(t)$ for the year 2015.  That
+is,
 \begin{equation}
@@
 \end{equation}
-A half-life of 1\;y means that the estimate of the transmission rate
+For this exponentially weighted mean and variance over time, a
+half-life of 1 year means that the estimate of the transmission rate
 from year $i$ is weighted half as much as the estimate from year
 $i + 1$, a quarter as much as the estimate from year $i + 2$, and so
-on.  This approach captured the recent country-level transmission
-behavior while still allowing for the use of less-recent estimates to
-smooth short-term variations (\autoref{transmission_rate}).
+on.  This approach captured the recent country-specific transmission
+behavior while simultaneously allowing the use of historical estimates
+to smooth short-term variations (\autoref{transmission_rate}).
 
@@
 
-For each of the 1000 model parameter samples, the country-level
+For each of the 1000 simulations per scenario, the country-specific
 aggregate transmission rate $\bar{\beta}$ was sampled from
 $\Lognormal(\mu, \sigma^2)$ with the parameters given by
-eqs.~\eqref{lognormal_params}, and samples were also drawn for the
-transmissibilities for acute and unsuppressed infected people,
-$\tau_A$ and $\tau_U$; the transmission reduction by suppression,
-$\varepsilon$; and the annual number of coital acts, $n$
-(\autoref{model}).  From the latter samples, the relative transmission
-rates for the acute phase ($\beta_A$), for unsuppressed chronic
-infections ($\beta_U$), and for chronic infections with viral
-suppression ($\beta_V$) were calculated by eqs.~\eqref{betas}.  The
-sample value of the country-level transmission rate was then computed
-by
+eqs.~\eqref{lognormal_params}. Samples were also drawn for the
+transmissibilities per coital act of acute and virally unsuppressed
+infected people, $\tau_A$ and $\tau_U$; the transmission reduction due
+to viral suppression, $\epsilon$; and the average annual number of
+coital acts per person, $n$ (\autoref{model}).  From these samples,
+the relative transmission rates for the acute phase ($\beta_A$), for
+unsuppressed chronic infections ($\beta_U$), and for chronic
+infections with viral suppression ($\beta_V$) were calculated by
+eqs.~\eqref{betas}.  For each sample parameter set, the
+country-specific transmission rate was then computed by
 \begin{equation}
   \label{eta}
-  \eta = \frac{\bar{\beta} I(2015)}{
+  \xi = \frac{\bar{\beta} I(2015)}{
     \beta_A A(2015) + \beta_U \big(U(2015) + D(2015) + T(2015)\big)
@@
 derived by rearranging eq.~\eqref{foi}, and uses the model initial
-conditions eq.~\eqref{initial_conditions}.  This estimate of $\eta$ is
+conditions eq.~\eqref{initial_conditions}.  This estimate of $\xi$ is
 derived for the 2015 estimates of the proportion of PLHIV divided
 among acute infections; undiagnosed, diagnosed, or treated infections;
-and virally suppressed infections.  Using the estimate of $\eta$ in
-projections for future times, when these proportions may change, may
-introduce bias.
+and virally suppressed infections.
 
-A few countries—e.g. Bulgaria, Timor-Leste, and Yemen—are currently
+A few countries—e.g.~Bulgaria, Timor-Leste, and Yemen—are currently
 estimated by UNAIDS to have low HIV prevalence but relatively high
-incidence, resulting in large estimated transmission rates, leading to
-rapid projected growth of their HIV epidemics by 2035. The apparent
-low prevalence and high incidence may, at least in part, be due to the
-resolution in UNAIDS estimates (0.1\% for prevalence, 0.01\% for
-annual per-capita incidence).  Results for such countries should be
-considered in light of this limitation.
+incidence, resulting in large estimated transmission rates and, thus,
+rapid projected growth of their HIV epidemics. The apparent low
+prevalence and high incidence may be an artifact of the resolution in
+UNAIDS estimates (0.1\% for prevalence, 0.01\% for annual per-capita
+incidence).  Results for these countries should be considered in light
+of this limitation.
 
-\section{Uncertainty analysis}
+\section{Sensitivity and uncertainty analysis}
 \label{uncertainty}
 
-Projections were generated for each country through model simulations
-using 1000 random samples from published parameter distributions
-(\autoref{model_param}) and the country-specific estimated
-distribution of the transmission rate (\autoref{model_fitting}). The
-parameters were sampled using Latin hypercube
-sampling\cite{blower1994}.  We also used the variance reduction
-technique of running different interventions with the same parameter
-samples, i.e.  one set of sample parameter values is drawn, status quo
-and intervention scenarios are all run with those sample values and
-compared, and this process is repeated for each of the 1000 sample
-sets of parameters\cite{shechter2006}.
+Latin hypercube sampling\cite{blower1994} was used to draw parameter
+samples from published parameter distributions (\autoref{model_param})
+and the country-specific estimated distribution of the transmission
+rate (\autoref{model_fitting}) 1000 times for each country.
+Projections were then generated by running the model simulations with
+these parameter sets.  To compare interventions, as well as status quo
+projections, we implemented the variance-reduction technique of using
+the same set of sample parameter values for all interventions,
+repeating this process for each of the 1000 simulations in every
+country.\cite{shechter2006}  We report the median, 1st and 3rd
+quartiles (i.e.~25th and 75th percentiles), and 5th and 95th
+percentiles for each model outcome.  We also calculated partial rank
+correlation coefficients (PRCC)\cite{blower1994} to measure the
+independent effect of each non-vaccine parameter on model projections
+of global HIV incidence from 2015 to 2035 (Extended Data
+Fig.~\ref*{PRCCs}).
 
-The model outcomes were summarized using the median, 1st and 3rd
-quartiles (i.e. 25th and 75th percentiles), and 5th and 95th
-percentiles.  We calculated partial rank correlation coefficients
-(PRCC)\cite{blower1994} to measure the independent effect of each
-non-vaccine parameter on model projections of global new HIV
-infections from 2015 to 2035 (Extended Data Fig.~\ref*{PRCCs}).
-
-Given that vaccine parameters have not yet been quantified, we
-restricted the number of unknowns by keeping vaccine efficacy constant
-over time.  This assumption is based on proposed vaccine regimens that
-include boosters for sustaining immunogenicity.  We chose plausible
-baseline values for the included vaccine parameters (efficacy 50\%,
-ultimate coverage 70\%, speed of rollout 25\% per year, year vaccine
-is first available 2020) and examined uncertainty by simulating 6
-additional vaccine scenarios, varying efficacy (30\%, 70\%), ultimate
-coverage (50\%, 90\%), speed of rollout (10\% coverage per year), and
-first year of availability (2025; Fig.~4). The vaccine scenario
-analysis was done using the modes from the parameter distributions,
-not samples from these distributions, to reduce the computation time.
-
-We used several probability distributions to quantify the parameters.
-\begin{description}
-\item[Uniform] $\Uniform(a, b)$ is the uniform random variable with
-  minimum $a$ and maximum $b$, which has density function
+We used several probability distributions to capture the uncertainty
+in the parameters.  (See \autoref{model} for more on each parameter.)
+\begin{description}[labelsep=0.6ex]
+\item[Uniform] was used for parameters where only a broad range was
+  indicated in the literature.  $\Uniform(a, b)$, with minimum $a$ and
+  maximum $b$, has density function
   \begin{equation}
@@
 
-\item [Triangular] $\Triangular(a, b, c)$ is the triangular random
-  variable distribution with minimum $a$, mode $b$, and maximum $c$.
-  It has density function
+\item [Triangular] was used for parameters where maximum-likelihood
+  estimates and confidence intervals (or similar) were available.
+  $\Triangular(a, b, c)$, with minimum $a$, mode $b$, and maximum $c$,
+  has density function
   \begin{equation}
@@
 
-\item[Beta-PERT] $\BetaPERT(a, b, c)$ is the Beta-PERT probability
+\item[Beta-PERT] was used for the efficacy of viral suppression at
+  reducing transmission, $\epsilon$, because the confidence interval
+  had an extremely long right tail\cite{Donnell2010-xo}, which would
+  strongly skew the mean and median of a Triangular distribution to
+  the right.  $\BetaPERT(a, b, c)$, the Beta-PERT probability
   distribution\cite{malcom1959} with minimum $a$, mode $b$, and
-  maximum $c$.  It has density function
+  maximum $c$, has density function
   \begin{equation}
@@
   \end{equation}
-  and $B(v, w)$ is the standard beta function\cite{davis1972}.
+  and $B(v, w)$ is the standard beta function.\cite{davis1972}
   % \cite[\S6.2]{davis1972}
@@
 
-\item[Lognormal] $\Lognormal(\mu, \sigma^2)$ is the lognormal random
-  variable, which has density function
+\item[Lognormal] was used for the country-specific aggregate
+  transmission rates, $\bar{\beta}$.  $\Lognormal(\mu, \sigma^2)$
+  has density function
   \begin{equation}
@@
 
+Based on proposed vaccine regimens that include boosters for
+sustaining immunogenicity\cite{gray_2016}, we made the simplifying
+assumption that vaccine efficacy remains constant over time. We chose
+plausible baseline values for efficacy (50\%), ultimate coverage
+(70\%), speed of rollout (25\% per year), and date of rollout
+initiation (2020). We examined sensitivity and uncertainty by
+simulating 6 additional vaccine scenarios, varying efficacy (30\%,
+70\%), ultimate coverage (50\%, 90\%), speed of rollout (10\% coverage
+per year), and date of rollout initiation (2025; Fig.~4). The vaccine
+scenario analysis was done using the modes from the parameter
+distributions, not samples from these distributions, to reduce the
+computation time.
+
 % \printbibliography

### 2016-11-30 Documents/supplementary_information.tex
Stop trying to hyperlink to external document.

@@
 along with uninfected unvaccinated and vaccinated people
-(\autoref{model} \&
-\hyperref[model_diag]{Extended Data Fig.~\ref*{model_diag}}), tailored
-to each of 127 countries.  Simulations of our model project the number
-of people in each HIV stratum from 2015 to 2035, from which statistics
+(\autoref{model} \& Extended Data Fig.~\ref*{model_diag}), tailored to
+each of 127 countries.  Simulations of our model project the number of
+people in each HIV stratum from 2015 to 2035, from which statistics
 such as prevalence and incidence were calculated.  To evaluate the

### 2016-12-13 Documents/supporting_information.tex
Initial changes for PNAS.

--- 2016-11-30 Documents/supplementary_information.tex
@@
 % \usepackage[style=nature]{biblatex}
-% \addbibresource{supplementary_information.bib}
-\usepackage[sort&compress]{natbib}
+% \addbibresource{supporting_information.bib}
+\usepackage[numbers, round, comma, sort&compress]{natbib}
 \usepackage{hypernat}
-\citestyle{nature}
-
-% For Nature, add 27 to reference numbers to start after
-% last number in manuscript.
-\usepackage{etoolbox}
-\makeatletter
-\apptocmd{\thebibliography}{\global\c@NAT@ctr 27\relax}{}{}
-\makeatother
-
-% For Nature, no page numbers.
-\pagestyle{empty}
-\usepackage{etoolbox}
-\apptocmd{\maketitle}{\thispagestyle{empty}}{}{}
 
@@
 \renewcommand{\sectionautorefname}{\sectionname}
-\renewcommand{\figurename}{Supplementary Fig.}
-\renewcommand{\figureautorefname}{\figurename}
-\renewcommand{\tablename}{Supplementary Table}
-\renewcommand{\tableautorefname}{\tablename}
+\renewcommand{\thefigure}{S\arabic{figure}}
+\renewcommand{\thetable}{S\arabic{table}}
 
-\title{Supplementary Methods for\\
+\title{Supporting Information for\\
   \emph{Effectiveness of UNAIDS targets and HIV vaccination across 127
@@
       $\mu$ & Background death rate
-      & Country specific, Supplementary Table 2
+      & Country specific, Data Table 2
       & \cite{World_Development_Indicators2013-ee} \\
       $\kappa$ & Recruitment rate
-      & Country specific, Supplementary Table 2
+      & Country specific, Data Table 2
       & \cite{World_Development_Indicators2013-ee, WorldBankpg} \\
@@
 PLHIV, and HIV-related deaths were calculated from the aggregates.
-(See Supplementary Table 6 for the definitions of UNAIDS regions.)
+(See Data Table 6 for the definitions of UNAIDS regions.)
 
@@
 aged 15--49 years\cite{The_World_Bank2016-fd} were obtained from the
-World Bank (Supplementary Table 2). Longitudinal HIV prevalence
-(Supplementary Table 3) and incidence (Supplementary Table 4)
+World Bank (Data Table 2). Longitudinal HIV prevalence
+(Data Table 3) and incidence (Data Table 4)
 estimates for ages 15--49, spanning from as early as 1990 for some
@@
 and the number who have viral suppression or have been retained on
-treatment for at least 12 months (Supplementary Table 5).  Where data
+treatment for at least 12 months (Data Table 5).  Where data
 or estimates were not available from these sources, alternative
@@
 ministry reports were consulted.  Full information on the sources used
-for each country is provided in Supplementary Tables 2--5.  These
+for each country is provided in Data Tables 2--5.  These
 source tables are also available in our public source-code
@@
 available historical country-specific estimates of prevalence and
-incidence (Supplementary Tables 3 and 4), and published estimates of
+incidence (Data Tables 3 \& 4), and published estimates of
 transmissibility per coital
@@
 % \printbibliography
-\bibliography{supplementary_information}
-\bibliographystyle{naturemag}
+\bibliography{supporting_information}
+\bibliographystyle{pnas2011}
 

### 2016-12-13 Documents/supporting_information.tex
More work on PNAS submission.

@@
 \usepackage{amsmath}
-\usepackage{graphicx}
+\usepackage{graphics}
 \usepackage{tikz}
 
+% Tweak spacing of descriptions.
 \usepackage{enumitem}
-\setlist{topsep=1ex}
+\setlist[description]{topsep=1ex, labelsep=0.6ex}
 
-\usepackage[font={sf},
-            labelfont={bf},
-            labelsep=space,
+% Tweak captions.
+\usepackage[font=sf,
+            labelfont=bf,
+            labelsep=period,
             singlelinecheck=off]{caption}
-\usepackage[font={sf}]{floatrow}
+
+% Make float text and math sans serif.
+\usepackage[font=sf]{floatrow}
+\usepackage{sansmath}
+\usepackage{etoolbox}
+\AtBeginEnvironment{table}{\sansmath}
+\AtBeginEnvironment{figure}{\sansmath}
+\floatsetup[table]{capposition=top,  % Table captions on top.
+                   justification=justified}  % Don't center by default.
+
+% Nice formatting for \textwidth tables.
 \usepackage{tabularx}
 
-\usepackage[blocks]{authblk}
-\renewcommand{\Authsep}{, }
-\renewcommand{\Authand}{ \& }
-\renewcommand{\Authands}{, }
+\usepackage[noblocks]{authblk}
 \renewcommand{\Affilfont}{\small}
@@
 \usepackage{hypernat}
+% PNAS style: no brackets in reference list.
+\makeatletter 
+\renewcommand\@biblabel[1]{#1.} 
+\makeatother
+
+% PNAS style: square brackets around equation labels and all in
+% boldface, boldface equation number in references.
+\usepackage{mathtools}
+\newtagform{brackets}{\bf[}{]}
+\usetagform{brackets}
+\renewcommand{\eqref}[1]{\textbf{\ref{#1}}}
+
+\renewcommand{\thesection}{S\arabic{section}}
+\renewcommand{\thefigure}{S\arabic{figure}}
+\renewcommand{\thetable}{S\arabic{table}}
+\newcommand{\sectionname}{Section}
+\renewcommand{\sectionautorefname}{\sectionname}
+\renewcommand{\figurename}{Fig.}
+\renewcommand{\figureautorefname}{\figurename}
 
@@
 \externaldocument{extended_data_fig_1}
-\externaldocument{extended_data_fig_2}
-\externaldocument{extended_data_fig_3}
 
-\newcommand{\comment}[1]{\textbf{[#1]}}
 \newcommand{\md}{\mathrm{d}}
-\newcommand{\mT}{\mathrm{T}}
-\renewcommand{\vec}[1]{\mathbf{#1}}
-\newcommand{\mat}[1]{\mathbf{#1}}
-\newcommand{\me}{\mathrm{e}}
 \DeclareMathOperator{\Uniform}{Uniform}
@@
 
-\renewcommand{\thesection}{S\arabic{section}}
-\newcommand{\sectionname}{Section}
-\renewcommand{\sectionautorefname}{\sectionname}
-\renewcommand{\thefigure}{S\arabic{figure}}
-\renewcommand{\thetable}{S\arabic{table}}
-
 \title{Supporting Information for\\
@@
 
-\author{Jan Medlock}
-\affil{Department of Biomedical Sciences, Oregon State University, 106
-  Dryden Hall, Corvallis, OR, 97331-4801, USA,
-  \href{mailto:jan.medlock@oregonstate.edu}
-  {\texttt{jan.medlock@oregonstate.edu}}}
-\author{Abhishek Pandey}
-\author{Alyssa S.~Parpia}
-\author{Amber Tang}
-\author{Laura A.~Skrip}
-\author{Alison P.~Galvani}
-\affil{Center for Infectious Disease Modeling and Analysis, Yale
-  School of Public Health, 135 College Street, New Haven, USA}
+\author[a,1]{Jan Medlock}
+\affil[a]{Department of Biomedical Sciences,
+  Oregon State University,
+  106 Dryden Hall,
+  Corvallis, OR 97331-4801,
+  USA}
+\author[b]{Abhishek Pandey}
+\author[b]{Alyssa S.~Parpia}
+\author[b]{Amber Tang}
+\author[b]{Laura A.~Skrip}
+\author[b]{Alison P.~Galvani}
+\affil[b]{Center for Infectious Disease Modeling and Analysis,
+  Yale School of Public Health,
+  135 College Street,
+  New Haven, CT 06510-2483,
+  USA}
+\affil[1]{To whom correspondence should be addressed.
+  Email: \href{mailto:jan.medlock@oregonstate.edu}
+  {\texttt{jan.medlock@oregonstate.edu}}.}
 
@@
 along with uninfected unvaccinated and vaccinated people
-(\autoref{model} \& Extended Data Fig.~\ref*{model_diag}), tailored to
+(\autoref{model} \& \autoref{model_diag}), tailored to
 each of 127 countries.  Simulations of our model project the number of
@@
 
+\begin{figure}
+  \centering
+  \input{diagram}
+  \caption{Model diagram.}
+  \label{model_diag}
+\end{figure}
+
 The model simulation and analysis tools, written in Python, are
-publicly available.\cite{medlock2016-git}
+publicly available \cite{medlock2016-git}.
 
@@
 older into non-overlapping HIV states.  We focused on this age group
-because it accounts for the vast majority of global
-PLHIV,\cite{UNICEF} 93\% in 2014; because population-level HIV
-estimates and demographic data are typically only estimated for ages
-$15$--$49$; and to capture the continuing burden of infections in
-people ages $50$ and older.  Our model has 8 HIV states (Extended Data
-Fig.~\ref*{model_diag}): susceptible to HIV infection ($S$ is the
-number of people susceptible), vaccinated against HIV ($R$), acute HIV
-infection ($A$), undiagnosed HIV infection ($U$), diagnosed but
-untreated HIV infection ($D$), treated without viral suppression
-($T$), viral suppression ($V$), and having AIDS ($W$).
+because it accounts for the vast majority of global PLHIV
+\cite{UNICEF}, 93\% in 2014; because population-level HIV estimates
+and demographic data are typically only estimated for ages $15$--$49$;
+and to capture the continuing burden of infections in people ages $50$
+and older.  Our model has 8 HIV states (\autoref{model_diag}):
+susceptible to HIV infection ($S$ is the number of people
+susceptible), vaccinated against HIV ($R$), acute HIV infection ($A$),
+undiagnosed HIV infection ($U$), diagnosed but untreated HIV infection
+($D$), treated without viral suppression ($T$), viral suppression
+($V$), and having AIDS ($W$).
 
@@
 \begin{table}
-  \begin{center}
+  \caption{Model parameters.}
+  \label{model_param}
   \begin{tabularx}{\textwidth}{lXlll}
     \hline
-      & Definition & Value & References \\
-      \hline
+    & Definition & Value & References
+    \\ \hline
     $\mu$ & Background death rate
-      & Country specific, Data Table 2
-      & \cite{World_Development_Indicators2013-ee} \\
+    & Country specific, Data Set 2
+    & \cite{World_Development_Indicators2013-ee}
+    \\
     $\kappa$ & Recruitment rate
-      & Country specific, Data Table 2
-      & \cite{World_Development_Indicators2013-ee, WorldBankpg} \\
+    & Country specific, Data Set 2
+    & \cite{World_Development_Indicators2013-ee, WorldBankpg}
+    \\
     $\delta$ & Rate of progression from acute infection
-      & $\Triangular$(2, 4.14, 9.6)\;y$^{-1}$
-      & \cite{Hollingsworth2008-iy} \\
+    & $\Triangular(2, 4.14, 9.6)\;\text{y$^{-1}$}$
+    & \cite{Hollingsworth2008-iy}
+    \\
     $\sigma$ & Rate of developing AIDS without viral suppression
-      & 0.1064\;y$^{-1}$ & \cite{Morgan2002-cq} \\
+    & $0.1064\;\text{y$^{-1}$}$ & \cite{Morgan2002-cq}
+    \\
     $\theta$ & Rate of developing AIDS with viral suppression
-      & Eq.~(\ref{theta}) & --- \\
+    & Eq.~\eqref{theta} & ---
+    \\
     $\gamma$ & Rate of viral suppression
-      & $\Uniform$(0.5, 1.5)\;y$^{-1}$
-      & \cite{Currie2009-yz} \\
-      $\nu$ & Death rate from AIDS & 0.5\;y$^{-1}$
-      & \cite{Morgan2002-cq} \\
-      $\rho$ & Vaccine efficacy & 50\%\,[30\%, 70\%] & --- \\
+    & $\Uniform(0.5, 1.5)\;\text{y$^{-1}$}$
+    & \cite{Currie2009-yz}
+    \\
+    $\nu$ & Death rate from AIDS & $0.5\;\text{y$^{-1}$}$
+    & \cite{Morgan2002-cq}
+    \\
+    $\rho$ & Vaccine efficacy & 50\%\,[30\%, 70\%] & ---
+    \\
     $\omega$ & Reduction in life expectancy with viral suppression
-      & $\Uniform$(5, 8)\;y
-      & \cite{Samji2013-kf, Unaids2014-ue} \\
-      $\tau_{A}$ & Transmissibility during acute phase
-      & $\Triangular$(0.0039, 0.0082, 0.0150)
-      & \cite{Wawer2005-us, Skarbinski2015-ni}\\
-      $\tau_{U}$ & Transmissibility after acute phase
-      & $\Triangular$(0.00077, 0.0014, 0.00251)
-      & \cite{Hughes2012-so} \\
-      $\epsilon$ & Relative transmissibility with
-      viral suppression & $\BetaPERT$(0.08, 0.002, 0.57)
+    & $\Uniform(5, 8)\;\text{y}$
+    & \cite{Samji2013-kf, Unaids2014-ue}
+    \\
+    $\tau_{A}$ & Transmissibility per coital act during acute phase
+    & $\Triangular(0.0039, 0.0082, 0.0150)$
+    & \cite{Wawer2005-us, Skarbinski2015-ni}
+    \\
+    $\tau_{U}$ & Transmissibility per coital act after acute phase
+    & $\Triangular(0.00077, 0.0014, 0.00251)$
+    & \cite{Hughes2012-so}
+    \\
+    $\epsilon$ & Relative transmissibility per coital act with
+    viral suppression & $\BetaPERT(0.08, 0.002, 0.57)$
     & \cite{Donnell2010-xo, attia_2009, wilson_2012, jia_2013,
-        rodger_2016} \\
-      $n$ & Coital acts per year & $\Uniform$(96, 108)
-      & \cite{Wawer2005-us, Abdool_Karim2010-cm}\\
-      $\alpha$ & Diagnosis rate & See eq.~(\ref{diagnosis_rate}) & --- \\
-      $\phi$ & Treatment rate & See eq.~(\ref{treatment_rate}) & --- \\
-      $\psi$ & Rate of relapse to untreated & See eq.~(\ref{relapse_rate})
-      & --- \\
-      $\zeta$ & Vaccination rate & See eq.~(\ref{vaccination_rate}) & --- \\
-      \hline
-      \vspace*{-2.5em}
+      rodger_2016}
+    \\
+    $n$ & Coital acts per year & $\Uniform(96, 108)$
+    & \cite{Wawer2005-us, Abdool_Karim2010-cm}
+    \\
+    $\alpha$ & Diagnosis rate & Eq.~\eqref{diagnosis_rate} & ---
+    \\
+    $\phi$ & Treatment rate & Eq.~\eqref{treatment_rate} & ---
+    \\
+    $\psi$ & Rate of relapse to untreated & Eq.~\eqref{relapse_rate} & ---
+    \\
+    $\zeta$ & Vaccination rate & Eq.~\eqref{vaccination_rate} & ---
+    \\ \hline
   \end{tabularx}
-    \caption{Model parameters. $\Triangular$, $\Uniform$, and
-      $\BetaPERT$ are sampling distributions (\autoref{uncertainty}).
-      For vaccine efficacy, $50\%$ was the baseline, and $30\%$ and
-      $70\%$ were also assessed in sensitivity analysis.}
-    \label{model_param}
-  \end{center}
+  \\[5pt]
+  $\Triangular$, $\Uniform$, and $\BetaPERT$ are sampling
+  distributions (\autoref{uncertainty}).
+  \\
+  For vaccine efficacy, $50\%$ was the baseline, and $30\%$ and $70\%$
+  were also assessed in sensitivity analysis.
 \end{table}
@@
 loads for an average of 2.90 [95\% confidence interval 1.23,
-6.00]\;months.\cite{Hollingsworth2008-iy}  (We converted these
+6.00]\;months \cite{Hollingsworth2008-iy}.  (We converted these
 durations to rates like $1 / 2.90\;\text{month$^{-1}$} \approx
@@
 suppression occurs after between 8 months and 2 years on
-treatment.\cite{Currie2009-yz}  Disengagement from treatment moves
+treatment \cite{Currie2009-yz}.  Disengagement from treatment moves
 people from treated ($T$) and viral suppression ($V$) back to the
@@
 develop AIDS (compartment $W$) after an average duration of 10.4
-years,\cite{Morgan2002-cq} i.e.~with transition rate
+years \cite{Morgan2002-cq}, i.e.~with transition rate
 $\sigma = 0.1064\;\text{y$^{-1}$}$.  Viral suppression greatly reduces
@@
 such that life expectancy is only $5$--$8$\;y shorter than average
-country-specific life expectancy.\cite{Samji2013-kf, Unaids2014-ue}
+country-specific life expectancy \cite{Samji2013-kf, Unaids2014-ue}.
 This reduction in life expectancy was quantified by randomly sampling
@@
 collected from published
-estimates.\cite{World_Development_Indicators2013-ee} The recruitment
+estimates \cite{World_Development_Indicators2013-ee}.  The recruitment
 rate ($\kappa$) into the age $15\;\text{y}$ and older group was set by
 the difference between the country's population growth
-rate\cite{WorldBankpg} and its background mortality
-rate,\cite{World_Development_Indicators2013-ee} as would be true if
+rate \cite{WorldBankpg} and its background mortality
+rate \cite{World_Development_Indicators2013-ee}, as would be true if
 the population was at its stable age structure.  (More on these data
@@
 $\Triangular(0.0039, 0.0082,
-0.0150)$.\cite{Wawer2005-us,
-  Skarbinski2015-ni}
+0.0150)$ \cite{Wawer2005-us,
+  Skarbinski2015-ni}.
 Transmissibility per coital act for unsuppressed people, $\tau_U$, was
 sampled from
-$\Triangular(0.00077, 0.0014, 0.00251)$.\cite{Hughes2012-so} The
+$\Triangular(0.00077, 0.0014, 0.00251)$ \cite{Hughes2012-so}.  The
 transmissibility per coital act of people with viral suppression
 relative to those without suppression has been estimated at 0.08 (95\%
-confidence interval 0.002, 0.57).\cite{Donnell2010-xo} Due to the
+confidence interval 0.002, 0.57) \cite{Donnell2010-xo}.  Due to the
 extremely long left tail of this confidence interval, we sampled the
@@
 $n$ was sampled from $\Uniform(96, 108)$ based on survey
-studies.\cite{Wawer2005-us, Abdool_Karim2010-cm}  The country-specific
+studies \cite{Wawer2005-us, Abdool_Karim2010-cm}.  The country-specific
 transmission rate $\xi$ was derived from country-specific longitudinal
@@
 2015 to 2035 using the LSODA
-routine\cite{odepack, scipy, medlock2016-git} and four effectiveness
+routine \cite{odepack, scipy, medlock2016-git} and four effectiveness
 outcomes were computed from the solutions.
-\begin{description}[labelsep=0.6ex]
+\begin{description}
 \item[Cumulative new infections] from 2015 to time $t$ was given by
@@
 PLHIV, and HIV-related deaths were calculated from the aggregates.
-(See Data Table 6 for the definitions of UNAIDS regions.)
+(See Data Set 6 for the definitions of UNAIDS regions.)
 
@@
 target level of viral suppression because achieving viral suppression
-depends on the time on treatment\cite{Currie2009-yz}
-(i.e.~$1 / \gamma$).
+depends on the time on treatment \cite{Currie2009-yz}.
 
@@
 proportion treated ($p_T$), and the proportion with viral suppression ($p_V$).
-\begin{description}[labelsep=0.6ex]
+\begin{description}
 \item[Status quo] is maintenance of the proportions $p_D$, $p_T$, and
@@
 model for 127 countries.  Demographic data, including population
-growth rate,\cite{WorldBankpg} death
-rate,\cite{World_Development_Indicators2013-ee} and number of people
-aged 15--49 years\cite{The_World_Bank2016-fd} were obtained from the
-World Bank (Data Table 2). Longitudinal HIV prevalence
-(Data Table 3) and incidence (Data Table 4)
+growth rate \cite{WorldBankpg}, death
+rate \cite{World_Development_Indicators2013-ee}, and number of people
+aged 15--49 years \cite{The_World_Bank2016-fd} were obtained from the
+World Bank (Data Set 2). Longitudinal HIV prevalence
+(Data Set 3) and incidence (Data Set 4)
 estimates for ages 15--49, spanning from as early as 1990 for some
 countries to 2015, were primarily obtained from the AIDSinfo database
-produced by UNAIDS.\cite{Unaids2016-an} Other sources included UNAIDS
-Country Progress Reports\cite{Unaids2016-am} published from 2012 to
-2016 and AIDS Data Hub,\cite{AIDSdatahub-fg} which compiles data from
+produced by UNAIDS \cite{Unaids2016-an}. Other sources included UNAIDS
+Country Progress Reports \cite{Unaids2016-am} published from 2012 to
+2016 and AIDS Data Hub \cite{AIDSdatahub-fg}, which compiles data from
 UNAIDS, UNICEF, WHO, and the Asian Development Bank.  These sources
@@
 and the number who have viral suppression or have been retained on
-treatment for at least 12 months (Data Table 5).  Where data
+treatment for at least 12 months (Data Set 5).  Where data
 or estimates were not available from these sources, alternative
@@
 ministry reports were consulted.  Full information on the sources used
-for each country is provided in Data Tables 2--5.  These
+for each country is provided in Data Sets 2--5.  These
 source tables are also available in our public source-code
-repository.\cite{medlock2016-git}
+repository \cite{medlock2016-git}.
 
@@
 available historical country-specific estimates of prevalence and
-incidence (Data Tables 3 \& 4), and published estimates of
+incidence (Data Sets 3 \& 4), and published estimates of
 transmissibility per coital
-act,\cite{Wawer2005-us, Donnell2010-xo, Hughes2012-so,
-  Skarbinski2015-ni}
+act \cite{Wawer2005-us, Donnell2010-xo, Hughes2012-so,
+  Skarbinski2015-ni},
 we derived an average country-specific transmission rate, taking into
@@
 $\mu$ and $\sigma^2$ of the lognormal distribution we used the
-exponentially weighted mean and variance\cite{holt2004} over time
+exponentially weighted mean and variance \cite{holt2004} over time
 (with half-life 1\;year) of $\log \beta(t)$ for the year 2015.  That
@@
 \begin{figure}
-  \centering
+  \begin{center}
     \includegraphics{../Codes/plots/transmission_rate.pdf}
+  \end{center}
   \caption{Country-specific distributions of transmission rate,
@@
 
-Latin hypercube sampling\cite{blower1994} was used to draw parameter
+Latin hypercube sampling \cite{blower1994} was used to draw parameter
 samples from published parameter distributions (\autoref{model_param})
@@
 repeating this process for each of the 1000 simulations in every
-country.\cite{shechter2006}  We report the median, 1st and 3rd
+country \cite{shechter2006}.  We report the median, 1st and 3rd
 quartiles (i.e.~25th and 75th percentiles), and 5th and 95th
 percentiles for each model outcome.  We also calculated partial rank
-correlation coefficients (PRCC)\cite{blower1994} to measure the
+correlation coefficients (PRCC) \cite{blower1994} to measure the
 independent effect of each non-vaccine parameter on model projections
-of global HIV incidence from 2015 to 2035 (Extended Data
-Fig.~\ref*{PRCCs}).
+of global HIV incidence from 2015 to 2035 (\autoref{PRCCs}).
+
+\begin{figure}
+   \centering
+   \includegraphics{../Codes/plots/prcc.pdf}
+   \caption{Sensitivity of global HIV incidence from 2015 to 2035 to
+     model parameters.  Left is the sensitivity of infections averted
+     by 95--95--95, relative to status quo.  Right is the sensitivity
+     of vaccination with status quo levels of diagnosis and treatment,
+     relative to status quo.  Sensitivity is measured by the partial
+     rank correlation coefficient (PRCC).}
+   \label{PRCCs}
+\end{figure}
 
@@
 in the parameters.  (See \autoref{model} for more on each parameter.)
-\begin{description}[labelsep=0.6ex]
+\begin{description}
 \item[Uniform] was used for parameters where only a broad range was
@@
   reducing transmission, $\epsilon$, because the confidence interval
-  had an extremely long right tail\cite{Donnell2010-xo}, which would
+  had an extremely long right tail \cite{Donnell2010-xo}, which would
   strongly skew the mean and median of a Triangular distribution to
   the right.  $\BetaPERT(a, b, c)$, the Beta-PERT probability
-  distribution\cite{malcom1959} with minimum $a$, mode $b$, and
+  distribution \cite{malcom1959} with minimum $a$, mode $b$, and
   maximum $c$, has density function
@@
   \end{equation}
-  and $B(v, w)$ is the standard beta function.\cite{davis1972}
-  % \cite[\S6.2]{davis1972}
+  and $B(v, w)$ is the standard beta function
+  \cite[\S6.2]{davis1972}.
   We used the standard value of $\lambda = 4$.
@@
 Based on proposed vaccine regimens that include boosters for
-sustaining immunogenicity\cite{gray_2016}, we made the simplifying
+sustaining immunogenicity \cite{gray_2016}, we made the simplifying
 assumption that vaccine efficacy remains constant over time. We chose

### 2016-12-15 Documents/supporting_information.tex
More changes for PNAS.

@@
 
-\usepackage[utf8]{inputenc}
-\usepackage{microtype}
+\usepackage{common}
+
 \usepackage{geometry}
@@
 \usepackage{amsmath}
-\usepackage{graphics}
 \usepackage{tikz}
@@
 
-% Tweak captions.
-\usepackage[font=sf,
-            labelfont=bf,
-            labelsep=period,
-            singlelinecheck=off]{caption}
-
-% Make float text and math sans serif.
-\usepackage[font=sf]{floatrow}
-\usepackage{sansmath}
-\usepackage{etoolbox}
-\AtBeginEnvironment{table}{\sansmath}
-\AtBeginEnvironment{figure}{\sansmath}
-\floatsetup[table]{capposition=top,  % Table captions on top.
-                   justification=justified}  % Don't center by default.
-
 % Nice formatting for \textwidth tables.
@@
 \renewcommand{\Affilfont}{\small}
-
-\usepackage[pdfborder={0 0 0}]{hyperref}
 
@@
 
-\title{Supporting Information for\\
+\title{Supporting information for\\
   \emph{Effectiveness of UNAIDS targets and HIV vaccination across 127
@@
   106 Dryden Hall,
-  Corvallis, OR 97331-4801,
-  USA}
+  Corvallis, OR 97331-4801}
 \author[b]{Abhishek Pandey}
@@
   135 College Street,
-  New Haven, CT 06510-2483,
-  USA}
+  New Haven, CT 06510-2483}
 \affil[1]{To whom correspondence should be addressed.
@@
   \begin{center}
-    \includegraphics{../Codes/plots/transmission_rate.pdf}
+    \input{../Codes/plots/transmission_rate.pgf}
   \end{center}
@@
    \centering
-   \includegraphics{../Codes/plots/prcc.pdf}
+   \input{../Codes/plots/prcc.pgf}
    \caption{Sensitivity of global HIV incidence from 2015 to 2035 to
@@
 \bibliography{supporting_information}
-\bibliographystyle{pnas2011}
+\bibliographystyle{pnas-new}
 

### 2016-12-15 Codes/plots/common.py

@@ -57,12 +57,21 @@ country_labels_short = {
 
 matplotlib.rc('mathtext', fontset = 'stixsans')
 
-# Science style
-# Nature style
-width_1column = 89 * 0.039370079 # inches
-width_2column = 183 * 0.039370079 # inches
+# Use Type 1 fonts instead of Type 3.
+matplotlib.rc('pdf', fonttype = 42)
+matplotlib.rc('ps', fonttype = 42)
 
-fontdict = {'family': 'sans-serif', 'size': 7}
+
+# PNAS style
+width_1column = 20.5 / 6    # inches
+width_1_5column = 27 / 6    # inches
+width_2column = 42.125 / 6  # inches
+height_max = 54 / 6         # inches
+
+
+fontdict = {'family': 'sans-serif',
+            'sans-serif': 'Latin Modern Sans',
+            'size': 7}
 matplotlib.rc('font', **fontdict)
 matplotlib.rc('figure', titlesize = fontdict['size'] + 1)
 matplotlib.rc('axes', titlesize = fontdict['size'] + 1,
@@ -493,21 +502,13 @@ def savefig(fig, filename, title = None, **kwargs):
 
     if filename.endswith('.pdf'):
         fig.savefig(filename, **kwargs)
-        pdfoptimize(filename)
+        # pdfoptimize(filename)
         pdf_add_info(filename, **info)
-    elif filename.endswith('.png'):
-        if ('dpi' not in kwargs):
-            kwargs['dpi'] = 600
+    elif filename.endswith('.pgf'):
         fig.savefig(filename, **kwargs)
-        # Use PIL etc to set metadata.
-        image_add_info(filename, **info)
-    elif (filename.endswith('.tiff') or filename.endswith('.tif')):
-        if ('dpi' not in kwargs):
-            kwargs['dpi'] = 600
-        fig.savefig(filename, **kwargs)
-        # Use PIL etc to set metadata.
-        image_add_info(filename, **info)
     else:
+        if ('dpi' not in kwargs):
+            kwargs['dpi'] = 600
         fig.savefig(filename, **kwargs)
         # Use PIL etc to set metadata.
         image_add_info(filename, **info)

### 2016-12-15 Codes/plots/effectiveness.py

@@ -37,7 +37,7 @@ def _plot_cell(ax, results, country, targets, stat,
                scale = None, units = None,
                country_label = None, stat_label = None,
                colors = None, alpha = 0.35,
-               jitter = 0.6):
+               jitter = 0.6, plotevery = 1):
     if colors is None:
         colors = seaborn.color_palette()
 
@@ -76,7 +76,9 @@ def _plot_cell(ax, results, country, targets, stat,
         except tables.NoSuchNodeError:
             pass
         else:
-            l = ax.plot(common.t, numpy.asarray(v['median']) / info.scale,
+            t = common.t[ : : plotevery]
+            y = numpy.asarray(v['median'])[ : : plotevery] / info.scale
+            l = ax.plot(t, y,
                         label = common.get_target_label(target),
                         color = colors[i],
                         alpha = alpha0,
@@ -95,9 +97,9 @@ def _plot_cell(ax, results, country, targets, stat,
                 #             alpha = alpha0,
                 #             zorder = 2)
                 # Shade interior of CI, with low alpha.
-                ax.fill_between(common.t,
-                                numpy.asarray(CI[0]) / info.scale,
-                                numpy.asarray(CI[1]) / info.scale,
+                y1 = numpy.asarray(CI[0])[ : : plotevery] / info.scale
+                y2 = numpy.asarray(CI[1])[ : : plotevery] / info.scale
+                ax.fill_between(t, y1, y2,
                                 facecolor = colors[i],
                                 linewidth = 0,
                                 alpha = alpha)

### 2016-12-15 Codes/plots/effectiveness_all.py

@@ -7,7 +7,6 @@ import os.path
 import sys
 
 from matplotlib import pyplot
-from matplotlib.backends import backend_pdf
 
 sys.path.append(os.path.dirname(__file__))  # For Sphinx.
 import common
@@ -20,7 +19,7 @@ import model
 template = r'''
 \begin{{figure}}[H]
   \centering
-  \includegraphics{{{figfile:}}}
+  \input{{{figfile:}}}
   \caption{{{region_or_country:} model outcomes under the different
     diagnosis, treatment, and vaccination scenarios.  Central curves
     show the medians over model runs with 1000 samples from parameter
@@ -34,16 +33,17 @@ template = r'''
 '''
 
 
-def plot_all(**kwargs):
+def plot_all(plotevery = 10, **kwargs):
     path = common.get_filebase()
     with model.results.samples.stats.open_() as results:
         for region_or_country in common.all_regions_and_countries:
             print(region_or_country)
             fig = effectiveness._plot_one(results,
                                           region_or_country,
+                                          plotevery = plotevery,
                                           **kwargs)
             filebase = os.path.join(path, region_or_country.replace(' ', '_'))
-            filename = '{}.pdf'.format(filebase)
+            filename = '{}.pgf'.format(filebase)
             label = common.get_country_label(region_or_country)
             common.savefig(fig, filename,
                            title = '{} effectiveness'.format(label))
@@ -58,7 +58,7 @@ def combine(prefix = '../Codes/plots'):
         for region_or_country in common.all_regions_and_countries:
             filebase = region_or_country.replace(' ', '_')
             filename = os.path.join(prefix, path,
-                                    '{}.pdf'.format(filebase))
+                                    '{}.pgf'.format(filebase))
             filename = os.path.normpath(filename)
             label = common.get_country_label(region_or_country)
             if isfirst:

### 2016-12-15 Codes/plots/prcc.py

@@ -131,6 +131,7 @@ def tornados():
     fig.tight_layout(h_pad = 0, w_pad = 1)
 
     common.savefig(fig, '{}.pdf'.format(common.get_filebase()), title = 'PRCC')
+    common.savefig(fig, '{}.pgf'.format(common.get_filebase()), title = 'PRCC')
     common.savefig(fig, '{}.png'.format(common.get_filebase()), title = 'PRCC')
 
 

### 2016-12-15 Codes/plots/transmission_rate.py

@@ -56,7 +56,7 @@ def plot_transmission_rates(countries, fig = None,
     ax.xaxis.set_major_locator(ticker.MultipleLocator(0.05))
     ax.set_ylim(-1.5, n + 0.5)
     ax.set_yticks(range(n))
-    yticklabels = (common.get_country_label(c, short = True)
+    yticklabels = (common.get_country_label(c, short = True).replace('&', '\&')
                    for c in reversed(countries))
     ax.set_yticklabels(yticklabels, size = 5)
     ax.grid(False, axis = 'y')
@@ -76,6 +76,7 @@ def plot_transmission_rates(countries, fig = None,
     fig.tight_layout(pad = 0)
     if savefig:
         common.savefig(fig, '{}.pdf'.format(common.get_filebase()))
+        common.savefig(fig, '{}.pgf'.format(common.get_filebase()))
         common.savefig(fig, '{}.png'.format(common.get_filebase()))
     return fig, ax
 

### 2016-12-15 drive_upload.py

@@ -3,7 +3,7 @@
 Upload figures etc to Google Drive.
 '''
 
-import os.path
+import os
 import sys
 import time
 
@@ -11,22 +11,6 @@ sys.path.append('Codes')
 import drive
 
 
-files = (
-    'Documents/supplementary_information.pdf',
-    'Documents/diagram_standalone.pdf',
-    'Documents/diagram_standalone.png',
-    'Codes/plots/effectiveness.pdf',
-    'Codes/plots/effectiveness.png',
-    'Codes/plots/effectiveness_regions.pdf',
-    'Codes/plots/effectiveness_regions.png',
-    'Codes/plots/infections_averted_map.pdf',
-    'Codes/plots/infections_averted_map.png',
-    'Codes/plots/initial_prevalence_map.pdf',
-    'Codes/plots/initial_prevalence_map.png',
-    'Codes/plots/vaccine_scenarios.pdf',
-    'Codes/plots/vaccine_scenarios.png',
-)
-       
 # 'Effectiveness of HIV vaccine files' folder
 folderId = '0B_53qFSHU3XKNjc0d3lTV2s4cWM'
 
@@ -38,8 +22,7 @@ if __name__ == '__main__':
             time.sleep(1)
         else:
             first = False
-        for f in files:
-            try:
-                d.upload_if_newer(f)
-            except FileNotFoundError:
-                print('{}: file not found locally.'.format(f))
+        for (dirpath, dirnames, filenames) in os.walk('upload',
+                                                      followlinks = True):
+            for f in filenames:
+                d.upload_if_newer(os.path.join(dirpath, f))

### 2016-12-15 generate_samples.py
Big directory rename, plus more PNAS changes.

@@ -1,0 +1,13 @@
+#!/usr/bin/python3
+'''
+Generate parameter samples to use for simulations.
+'''
+
+import model
+
+
+nsamples = 1000
+
+
+if __name__ == '__main__':
+    model.samples.generate(nsamples)

### 2016-12-15 model/__init__.py

@@ -1,0 +1,14 @@
+'''
+HIV 90-90-90 & optimization model.
+'''
+
+from . import datasheet
+from . import multicountry
+from . import multisim
+# from . import optimization
+from . import parameters
+from . import regions
+from . import results
+from . import samples
+from . import simulation
+from . import targets

### 2016-12-15 model/container.py

@@ -1,0 +1,51 @@
+import collections
+
+import numpy
+
+
+class Container(collections.abc.MutableMapping):
+    '''
+    A simple class to hold attributes with an interface like
+    :class:`collections.OrderedDict`.
+    '''
+
+    _keys = tuple()
+
+    def __getitem__(self, k):
+        return getattr(self, k)
+
+    def __setitem__(self, k, v):
+        return setattr(self, k, v)
+
+    def __delitem__(self, k):
+        return delattr(self, k)
+
+    def __iter__(self):
+        return iter(self._keys)
+
+    def __len__(self):
+        return len(self._keys)
+
+    def to_records(self):
+        names, arrays = zip(*self.items())
+        return numpy.rec.fromarrays(arrays, names = names)
+
+
+class DefaultOrderedDict(collections.OrderedDict):
+    '''
+    The combination of :class:`collections.OrderedDict` and
+    :class:`collections.defaultdict`.
+    '''
+    def __init__(self, default_factory):
+        super().__init__()
+        self.default_factory = default_factory
+
+    def __getitem__(self, key):
+        try:
+            return super().__getitem__(key)
+        except KeyError:
+            return self.__missing__(key)
+
+    def __missing__(self, key):
+        self[key] = value = self.default_factory()
+        return value

### 2016-12-15 model/effectiveness.py

@@ -1,0 +1,58 @@
+'''
+Compute effectiveness.
+
+For disability weights :math:`\mathbf{w}`
+and state variables :math:`\mathbf{y}(t)`,
+DALYs are
+
+.. math:: D = \int_0^{t_\mathrm{end}} \mathbf{w}^{\mathrm{T}}
+          \mathbf{y}(t)\;\mathrm{d} t,
+
+and QALYs are
+
+.. math:: Q = \int_0^{t_\mathrm{end}}
+          (\mathbf{1} - \mathbf{w})^{\mathrm{T}}
+          \mathbf{y}(t)\;\mathrm{d} t,
+
+so DALYs and QALYs are related by
+
+.. math:: Q = \int_0^{t_\mathrm{end}} \mathbf{1}^{\mathrm{T}}
+          \mathbf{y}(t)\;\mathrm{d} t - D.
+'''
+
+import unittest
+
+import numpy
+from scipy import integrate
+
+
+def QALYs(simulation):
+    # A component of Sphinx chokes on the '@'.
+    # QALYs_rate = (simulation.state[:, : -1]
+    #               @ simulation.parameters.QALY_rates_per_person)
+    QALYs_rate = numpy.dot(simulation.state[:, : -1],
+                           simulation.parameters.QALY_rates_per_person)
+    return integrate.simps(QALYs_rate, simulation.t)
+
+
+def DALYs(simulation):
+    # A component of Sphinx chokes on the '@'.
+    # DALYs_rate = (simulation.state[:, : -1]
+    #               @ simulation.parameters.DALY_rates_per_person)
+    DALYs_rate = numpy.dot(simulation.state[:, : -1],
+                           simulation.parameters.DALY_rates_per_person)
+    return integrate.simps(DALYs_rate, simulation.t)
+
+
+class TestDALYsQALYs(unittest.TestCase):
+    def test_DALYs_QALYs(self):
+        from .parameters import Parameters
+        from .simulation import Simulation
+        from . import targets
+        country = 'Nigeria'
+        parameters = Parameters(country).mode()
+        simulation = Simulation(parameters, targets.UNAIDS90())
+        self.assertTrue(numpy.isclose(
+            integrate.simps(simulation.alive + simulation.dead, simulation.t)
+            - simulation.DALYs,
+            simulation.QALYs))

### 2016-12-15 model/multicountry.py

@@ -1,0 +1,105 @@
+'''
+Aggregate multi-country (e.g. Global or regional) results.
+'''
+
+import numpy
+
+from . import container
+from . import datasheet
+from . import incidence
+from . import multicountry
+from . import parameters
+from . import regions
+
+
+class MultiCountry(container.Container):
+    '''
+    Class to hold the results of multiple countries,
+    e.g. Global or regional.
+    '''
+    _keys = ('AIDS', 'alive', 'dead', 'infected', 'new_infections')
+
+    def __init__(self, data):
+        # self.t = None
+        self.t = numpy.linspace(
+            2015, 2035,
+            20 * 120 + 1)
+        for k in self.keys():
+            setattr(self, k, 0)
+
+        for (c, v) in data.items():
+            if self.t is None:
+                self.t = v.t
+            for k in self.keys():
+                # Do self.k += v.k
+                setattr(self, k,
+                        getattr(self, k) + numpy.asarray(getattr(v, k)))
+            try:
+                v.flush() # Free memory
+            except AttributeError:
+                pass
+
+    @property
+    def prevalence(self):
+        return self.infected / self.alive
+
+    @property
+    def incidence(self):
+        return incidence.compute(self.t, self.new_infections)
+
+    @property
+    def incidence_per_capita(self):
+        return self.incidence / numpy.asarray(self.alive)
+
+
+class Global(multicountry.MultiCountry):
+    '''
+    Class to hold global results.
+
+    The aggregated simulation results are scaled so that the model
+    current statistics match UNAIDS current estimates.
+    '''
+    global_alive = 7.2e9
+    global_prevalence = 0.008  # CI (0.007, 0.009), UNAIDS 2014
+    global_infected = 36.9e6  # CI (34.3e6, 41.4e6), UNAIDS 2014
+    global_incidence = 2e6  # CI (1.9e6, 2.2e6), UNAIDS 2014
+    global_annual_AIDS_deaths = 1.2e6  # CI (0.98e6, 1.6e6), UNAIDS 2014
+
+    def __init__(self, data):
+        super().__init__(data)
+        self._normalize()
+
+    def _normalize(self):
+        scale_alive = self.global_alive / self.alive[..., 0]
+        self.alive *= scale_alive[..., numpy.newaxis]
+
+        scale_infected = self.global_infected / self.infected[..., 0]
+        self.infected *= scale_infected[..., numpy.newaxis]
[…]

### 2016-12-15 model/optimization/effectiveness.py

@@ -1,0 +1,13 @@
+'''
+Find target values that maximize the benefit for fixed cost.
+
+The idea here is to make graphs of optimal incremental effectiveness
+for many levels of cost.  Lines from the origin with slope
+1 DALY / GDP per capita and 1 / 3 DALY / GDP per capita define the
+thresholds.
+
+Perhaps an upper bound for cost is
+DALYs_basecase * 3 * GDP per capita per DALYs.
+
+.. todo:: Not implemented.
+'''

### 2016-12-15 model/picklefile.py

@@ -1,0 +1,15 @@
+'''
+A :mod:`pickle` interface using files instead of descriptors.
+'''
+
+import pickle
+
+
+def load(filename):
+    with open(filename, 'rb') as fd:
+        return pickle.load(fd)
+
+
+def dump(obj, filename):
+    with open(filename, 'wb') as fd:
+        return pickle.dump(obj, fd)

### 2016-12-15 model/proportions.py

@@ -1,0 +1,51 @@
+'''
+Compute proportions diagnosed, treated, viral suppressed, and vaccinated.
+'''
+
+import warnings
+
+import numpy
+
+from . import container
+from . import ODEs
+
+
+def _safe_divide(a, b, fill_value = 0):
+    '''
+    Return a / b,
+    unless b == a == 0, then return 0.
+    '''
+    # Ignore divide-by-zero warnings.
+    with warnings.catch_warnings():
+        warnings.filterwarnings('ignore',
+                                module = 'numpy',
+                                message = ('divide by zero encountered in '
+                                           'true_divide'))
+        return numpy.where((a == 0) & (b == 0), 0, numpy.divide(a, b))
+
+class Proportions(container.Container):
+    '''
+    Get the proportions diagnosed, treated, viral suppressed, and vaccinated
+    from the current number of people in the model compartments.
+    '''
+
+    _keys = ('diagnosed', 'treated', 'suppressed', 'vaccinated')
+
+    def __init__(self, state):
+        S, Q, A, U, D, T, V, W, Z, R = ODEs.split_state(state)
+
+        # (D + T + V + W) / (A + U + D + T + V + W)
+        self.diagnosed = _safe_divide(D + T + V + W,
+                                      A + U + D + T + V + W)
+
+        # (T + V + W) / (D + T + V + W)
+        self.treated = _safe_divide(T + V + W,
+                                    D + T + V + W)
+
+        # V / (T + V)
+        self.suppressed = _safe_divide(V,
+                                       T + V)
+
+        # Q / (S + Q)
+        self.vaccinated = _safe_divide(Q,
+                                       S + Q)

### 2016-12-15 model/regions.py

@@ -1,0 +1,69 @@
+'''
+Countries by region.
+'''
+
+from . import datasheet
+
+
+regions = {
+    'Global':
+    datasheet.get_country_list(),
+
+    'East and Southern Africa':
+    ['Angola', 'Botswana', 'Burundi', 'Eritrea', 'Ethiopia', 'Kenya',
+     'Lesotho', 'Madagascar', 'Malawi', 'Mozambique', 'Namibia', 'Rwanda',
+     'Somalia', 'South Africa', 'South Sudan', 'Swaziland', 'Uganda',
+     'Zambia', 'Zimbabwe'],
+
+    'West and Central Africa':
+    ['Benin', 'Burkina Faso', 'Cameroon', 'Cape Verde',
+     'Central African Republic', 'Democratic Republic of the Congo',
+     'Equatorial Guinea', 'Gabon', 'Gambia', 'Ghana', 'Guinea',
+     'Ivory Coast', 'Liberia', 'Mali', 'Mauritania', 'Niger', 'Nigeria',
+     'Senegal', 'Sierra Leone', 'Republic of Congo', 'Togo'],
+
+    'Middle East and North Africa':
+    ['Afghanistan', 'Algeria', 'Egypt', 'Iran', 'Lebanon', 'Morocco',
+     'Sudan', 'Tunisia', 'Yemen'],
+
+    'Asia Pacific':
+    ['Australia', 'Bangladesh', 'Bhutan', 'Cambodia', 'China', 'East Timor',
+     'India', 'Indonesia', 'Laos', 'Malaysia', 'Mongolia', 'Myanmar',
+     'Nepal', 'New Zealand', 'Papua New Guinea', 'Philippines', 'Sri Lanka',
+     'Thailand', 'Vietnam'],
+
+    'Eastern Europe and Central Asia':
+    ['Belarus', 'Bulgaria', 'Kazakhstan', 'Kyrgystan', 'Moldova', 'Russia',
+     'Tajikistan', 'Ukraine', 'Uzbekistan'],
+
+    'Western Europe':
+    ['Austria', 'Belgium', 'Denmark', 'Estonia', 'France', 'Greece',
+     'Italy', 'Spain', 'Sweden', 'Switzerland', 'United Kingdom'],
+
+    'North America':
+    ['Canada', 'United States of America'],
+
+    'Caribbean':
+    ['Barbados', 'Cuba', 'Dominican Republic', 'Haiti', 'Jamaica',
[…]

### 2016-12-15 model/results/common.py

@@ -1,0 +1,8 @@
+'''
+Common definitions.
+'''
+
+import os.path
+
+resultsdir = os.path.join(os.path.dirname(os.path.abspath(__file__)),
+                          '../../results')

### 2016-12-15 model/results/samples/results.py

@@ -1,0 +1,177 @@
+'''
+Store and retrieve results from simulations with parameter samples.
+
+.. todo:: Use HDF instead of pickle.  HDF can do random access instead
+          of reading the whole file, so all the complicated caching
+          I'm doing could hopefully be removed.
+'''
+
+import collections
+import os
+
+from .. import common
+from ... import datasheet
+from ... import multicountry
+from ... import picklefile
+from ... import regions
+
+
+def get_path(country_or_region, target):
+    if isinstance(target, type):
+        # It's a class.
+        target = target()
+    if target is not None:
+        path = os.path.join(common.resultsdir,
+                            country_or_region,
+                            '{}.pkl'.format(str(target)))
+    else:
+        path = os.path.join(common.resultsdir,
+                            country_or_region)
+    return path
+
+
+def exists(country_or_region, target):
+    resultsfile = get_path(country_or_region, target)
+    return os.path.exists(resultsfile)
+
+
+class Results:
+    '''
+    Class to load the data on demand.
+    '''
+    def __init__(self, country_or_region, target):
+        self._country_or_region = country_or_region
+        # Convert to string in case its an instance.
+        self._target = str(target)
+
+        if (not self.exists) and regions.is_country(self._country_or_region):
+            raise FileNotFoundError("'{}', '{}' not found!".format(
+                self._country_or_region, self._target))
+        self._data = None
+
+    def __enter__(self):
+        return self
+
+    def __exit__(self, type_, value, tb):
+        pass
+
+    def _load_data(self):
+        if regions.is_region(self._country_or_region) and (not self.exists):
+            print('Building {}, {}...'.format(self._country_or_region,
+                                              self._target))
+            self._build_regional()
+        else:
+            print('Loading data for {}, {}...'.format(self._country_or_region,
+                                                      self._target))
+            self._data = picklefile.load(self.path)
+            if regions.is_country(self._country_or_region):
+                self.correct_ni()
+
+    def _build_regional(self):
+        countries = regions.regions[self._country_or_region]
+        # Use an OrderedDict so that the countries' Results._load_data()
+        # are called in order later by multicountry.MultiCountry().
+        data = collections.OrderedDict()
+        for country in sorted(countries):
+            try:
+                data[country] = open_(country, self._target)
[…]

### 2016-12-15 model/samples.py

@@ -1,0 +1,26 @@
+'''
+Generate, save and load parameter samples.
+'''
+
+import os.path
+
+import numpy
+
+from . import parameters
+
+
+samplesfile = os.path.join(os.path.dirname(os.path.abspath(__file__)),
+                           '../samples.npy')
+
+
+def load():
+    samples = numpy.load(samplesfile)
+    # print('Loaded {} samples.'.format(len(samples)))
+    return samples
+
+
+def generate(nsamples):
+    samples = parameters.Parameters.generate_samples(nsamples)
+    print('Generated {} samples.'.format(len(samples)))
+    numpy.save(samplesfile, samples)
+    return samples

### 2016-12-15 model/simulation.py

@@ -1,0 +1,242 @@
+'''
+Simulation of the HIV model.
+'''
+
+import copy
+import warnings
+
+import numpy
+from scipy import integrate
+
+from . import container
+# from . import cost
+from . import effectiveness
+from . import incidence
+# from . import net_benefit
+from . import ODEs
+from . import plot
+from . import proportions
+
+
+class Simulation(container.Container):
+    '''
+    A class to hold the simulation information.
+
+    `integrator` is a
+    :class:`scipy.integrate.ode` integrator---``'lsoda'``,
+    ``'vode'``, ``'dopri5'``, ``'dop853'``---or
+    ``'odeint'`` to use :func:`scipy.integrate.odeint`.
+
+    .. todo:: Only store .state, and compute 'susceptible' etc from that,
+              or use pandas.DataFrames or numpy.records or similar for
+              handling the attributes.
+              Implement dumping and loading that to/from an npy file.
+              Implement moving that to Multisims, too.
+    '''
+
+    _keys = ['susceptible', 'vaccinated', 'acute', 'undiagnosed',
+             'diagnosed', 'treated', 'viral_suppression',
+             'AIDS', 'dead', 'new_infections']
+
+    _alive = ('susceptible', 'vaccinated', 'acute', 'undiagnosed',
+              'diagnosed', 'treated', 'viral_suppression', 'AIDS')
+
+    _infected = ('acute', 'undiagnosed', 'diagnosed', 'treated',
+                 'viral_suppression', 'AIDS')
+
+    def __init__(self, parameters, targets,
+                 t_start = 2015, t_end = 2035,
+                 pts_per_year = 120, # = 10 per month
+                 integrator = 'odeint',
+                 _use_log = True,
+                 **kwargs):
+        self.parameters = parameters
+        self.country = self.parameters.country
+        self.targets = targets
+        self.pts_per_year = pts_per_year
+        self.integrator = integrator
+        self._use_log = _use_log
+        self.kwargs = kwargs
+
+        if len(self.kwargs) > 0:
+            self.parameters = copy.copy(self.parameters)
+            for (k, v) in self.kwargs.items():
+                setattr(self.parameters, k, v)
+
+        self.t = numpy.linspace(
+            t_start, t_end,
+            numpy.abs(t_end - t_start) * self.pts_per_year + 1)
+
+        self.simulate()
+
+    def simulate(self):
[…]

### 2016-12-15 model/targets.py

@@ -1,0 +1,297 @@
+'''
+Get the current target values for diagnosis, treatment, viral suppression,
+and vaccination from the overall target goals.
+'''
+
+import numpy
+
+from . import container
+from . import control_rates
+from . import proportions
+
+
+class TargetZero:
+    '''
+    Fixed at 0.
+    '''
+    def __call__(self, initial_proportion, t):
+        return numpy.zeros_like(t, dtype = float)
+
+
+class TargetStatusQuo:
+    '''
+    Fixed at the `initial_proportion`.
+    '''
+    def __call__(self, initial_proportion, t):
+        return initial_proportion * numpy.ones_like(t, dtype = float)
+
+
+class TargetLinear:
+    '''
+    Linearly go from the `initial_proportion` to
+    `max(target_value, initial_proportion)` between `time_to_start` and
+    `time_to_target`.  Stay fixed at initial proportion before
+    `time_to_start` and fixed at `target_value` after `time_to_target`.
+    '''
+    def __init__(self, target_value, time_to_start, time_to_target):
+        self.target_value = target_value
+        self.time_to_start = time_to_start
+        self.time_to_target = time_to_target
+
+    def __call__(self, initial_proportion, t):
+        target_value_ = max(self.target_value, initial_proportion)
+        amount_implemented = numpy.where(
+            t < self.time_to_start, 0,
+            numpy.where(
+                t < self.time_to_target,
+                (t - self.time_to_start)
+                / (self.time_to_target - self.time_to_start),
+                1))
+        return (initial_proportion
+                + (target_value_ - initial_proportion) * amount_implemented)
+
+class Target90(TargetLinear):
+    '''
+    Linearly go from the `initial_proportion` to the
+    `target_value = max(90%, initial_proportion)` between 2015 and
+    2020.  Stay fixed at `initial_proportion` before
+    2015 and fixed at the `target_value` after 2020.
+    '''
+    target_value = 0.9
+    time_to_start = 2015
+    time_to_target = 2020
+
+    def __init__(self):
+        pass
+
+
+class Target95:
+    '''
+    Linearly go from the `initial_proportion` to
+    `target_value_0 = max(90%, initial_proportion)` between 2015 and
+    2020, then linearly go to
+    `target_value_1 = max(95%, initial_proportion)` between 2020 and 2030.
+    Stay fixed at `initial_proportion` before 2015 and fixed at
+    `target_value_1` after 2030.
+    '''
[…]

### 2016-12-15 model/transmission_rate.py

@@ -1,0 +1,135 @@
+'''
+Estimate the gross transmission rate from incidence and prevalence data.
+'''
+
+import numpy
+from scipy import stats
+import pandas
+
+
+def estimate_vs_time(parameters):
+    r'''
+    Estimate the transmission rate at each time.
+
+    The per-capita incidence is
+
+    .. math:: i(t) = \lambda(t) \frac{S(t)}{N(t)}
+              = \beta \frac{I(t)}{N(t)} \frac{S(t)}{N(t)},
+
+    assuming no differences in transmission between acute, unsuppressed,
+    suppressed and AIDS classes (i.e. :math:`I = A + U + D + V + W`).
+
+    If :math:`p = \frac{I}{N}` is the prevalence,
+
+    .. math:: i(t) = \beta p(t) (1 - p(t)).
+
+    Rearranging gives
+
+    .. math:: \beta(t) = \frac{i(t)}{p(t) (1 - p(t))}.
+    '''
+    # Interpolate in case of any missing data.
+    prevalence = parameters.prevalence.interpolate(method = 'index')
+    incidence = parameters.incidence_per_capita.interpolate(method = 'index')
+    transmission_rates_vs_time = incidence / prevalence / (1 - prevalence)
+    # Remove nan entries.
+    return transmission_rates_vs_time.dropna()
+
+
+def estimate(parameters, halflife = 1):
+    '''
+    Estimate the transmission rate at each time,
+    then build a lognormal random variable using exponentially
+    weighted statistics from the result.
+    '''
+    transmission_rates_vs_time = estimate_vs_time(parameters)
+    if len(transmission_rates_vs_time) > 0:
+        # Assuming transmission_rates_vs_time are lognormal(mu, sigma),
+        # mu and sigma are the mean and stdev of
+        # log(transmission_rates_vs_time).
+        trt_log = transmission_rates_vs_time.apply(numpy.log)
+
+        # Get the exponentially weighted mean and stdev at the last
+        # time point.
+        if hasattr(trt_log, 'ewm'):
+            # pandas 0.18 syntax.
+            ew = trt_log.ewm(halflife = halflife)
+            mu = ew.mean().iloc[-1]
+            # The default, bias = False, seems to be ddof = 1.
+            sigma = ew.std().iloc[-1]
+        else:
+            # pandas 0.17 syntax.
+            mu = pandas.ewma(trt_log, halflife = halflife).iloc[-1]
[…]

### 2016-12-15 plots/common.py

@@ -1,0 +1,514 @@
+'''
+Common plotting settings etc.
+'''
+
+import collections
+import copy
+import inspect
+import operator
+import os
+import subprocess
+import sys
+import tempfile
+import time
+import unicodedata
+
+import matplotlib
+from matplotlib import cm
+from matplotlib import colors
+from matplotlib import ticker
+from matplotlib.backends import backend_pdf
+from matplotlib.backends import backend_cairo
+import numpy
+from PIL import Image
+
+sys.path.append(os.path.dirname(__file__))  # For Sphinx.
+# import seaborn
+import seaborn_quiet as seaborn
+sys.path.append('..')
+import model
+
+
+author = 'Jan Medlock et al'
+
+
+countries_to_plot = ('Global',
+                     'India',
+                     'Rwanda',
+                     'South Africa',
+                     'Swaziland',
+                     'United States of America')
+
+
+country_labels_short = {
+    'Bolivia (Plurinational State of)': 'Bolivia',
+    'Democratic Republic of the Congo': 'DR Congo',
+    'Iran (Islamic Republic of)': 'Iran',
+    "Lao People's Democratic Republic": 'Laos',
+    'Republic of Moldova': 'Moldova',
+    'Russian Federation': 'Russia',
+    'Trinidad and Tobago': 'Trinidad & Tobago',
+    'United States of America': 'United States',
+    'United Kingdom of Great Britain and Northern Ireland': 'United Kingdom',
+    'United Republic of Tanzania': 'Tanzania',
+    'Venezuela (Bolivarian Republic of)': 'Venezuela',
+}
+
+
+matplotlib.rc('mathtext', fontset = 'stixsans')
+
+# Use Type 1 fonts instead of Type 3.
+matplotlib.rc('pdf', fonttype = 42)
+matplotlib.rc('ps', fonttype = 42)
+
+
+# PNAS style
+width_1column = 20.5 / 6    # inches
+width_1_5column = 27 / 6    # inches
+width_2column = 42.125 / 6  # inches
+height_max = 54 / 6         # inches
+
+
+fontdict = {'family': 'sans-serif',
+            'sans-serif': 'Latin Modern Sans',
+            'size': 7}
+matplotlib.rc('font', **fontdict)
+matplotlib.rc('figure', titlesize = fontdict['size'] + 1)
+matplotlib.rc('axes', titlesize = fontdict['size'] + 1,
+              labelsize = fontdict['size'] + 1)
[…]

### 2016-12-15 plots/differences.py

@@ -1,0 +1,228 @@
+#!/usr/bin/python3
+'''
+Plot differences for samples from uncertainty analysis.
+
+.. todo:: Clean up.
+'''
+
+import operator
+import os.path
+import sys
+
+from matplotlib import colorbar
+from matplotlib import colors
+from matplotlib import gridspec
+from matplotlib import pyplot
+from matplotlib import ticker
+from matplotlib.backends import backend_pdf
+import numpy
+import tables
+
+sys.path.append(os.path.dirname(__file__))  # For Sphinx.
+import common
+# import seaborn
+import seaborn_quiet as seaborn
+sys.path.append('..')
+import model
+
+
+# Pairs (baseline, baseline + vaccine)
+targets = [model.targets.all_[i : i + 2]
+           for i in range(0, len(model.targets.all_), 2)]
+
+
+def _get_plot_info(results, country, targs, stat):
+    scale = None
+    percent = False
+    units = ''
+
+    if stat == 'infected':
+        label = 'PLHIV'
+        scale = 1e6
+    elif stat == 'prevalence':
+        label = 'Prevelance'
+        percent = True
+    elif stat == 'incidence_per_capita':
+        label = 'Incidence\n(per M per y)'
+        scale = 1e-6
+        units = ''
+    elif stat == 'AIDS':
+        label = 'AIDS'
+    elif stat == 'dead':
+        label = 'HIV-Related\nDeaths'
+    else:
+        raise ValueError("Unknown stat '{}'".format(stat))
+    
+    v_base = numpy.asarray(getattr(results['/{}/{}'.format(country, targs[0])],
+                                   stat))
+    v_intv = numpy.asarray(getattr(results['/{}/{}'.format(country, targs[1])],
+                                   stat))
+
+    data = v_base - v_intv
+    # data = (v_base - v_intv) / v_base
+
+    if percent:
+        scale = 1 / 100
+        units = '%%'
+    elif scale is None:
+        vmax = numpy.max(data)
+        if vmax > 1e6:
+            scale = 1e6
+            units = 'M'
+        elif vmax > 1e3:
+            scale = 1e3
+            units = 'k'
+        else:
+            scale = 1
+            units = ''
+
+    return (data, label, scale, units)
+
+
+def _plot_cell(ax, results, country, targs, stat,
+               country_label = None,
+               attr_label = None):
+    '''
[…]

### 2016-12-15 plots/effectiveness.py

@@ -1,0 +1,246 @@
+#!/usr/bin/python3
+'''
+Plot the effectiveness of interventions.
+'''
+
+import os.path
+import sys
+
+from matplotlib import lines
+from matplotlib import pyplot
+from matplotlib import ticker
+import numpy
+import tables
+
+sys.path.append(os.path.dirname(__file__))  # For Sphinx.
+import common
+# import seaborn
+import seaborn_quiet as seaborn
+sys.path.append('..')
+import model
+
+
+alpha0 = 0.9
+
+
+def _set_clip_on(obj, val):
+    if obj is not None:
+        try:
+            obj.set_clip_on(val)
+        except AttributeError:
+            for x in obj:
+                _set_clip_on(x, val)
+
+
+def _plot_cell(ax, results, country, targets, stat,
+               confidence_level, ci_bar,
+               scale = None, units = None,
+               country_label = None, stat_label = None,
+               colors = None, alpha = 0.35,
+               jitter = 0.6, plotevery = 1):
+    if colors is None:
+        colors = seaborn.color_palette()
+
+    CIkey = 'CI{:g}'.format(100 * confidence_level)
+    CIBkey = 'CI{:g}'.format(100 * ci_bar)
+
+    info = common.get_stat_info(stat)
+
+    # Allow scaling across rows in _plot_one().
+    if scale is not None:
+        info.scale = scale
+    if units is not None:
+        info.units = units
+    data = []
+    for target in targets:
+        try:
+            v = results[country][str(target)][stat]
+        except tables.NoSuchNodeError:
+            pass
+        else:
+            # Store the largest one.
+            if ci_bar > 0:
+                data.append(v[CIBkey])
+            elif confidence_level > 0:
+                data.append(v[CIkey])
+            else:
+                data.append(v['median'])
+    if info.scale is None:
+        info.autoscale(data)
+    if info.units is None:
+        info.autounits(data)
+
+    for (i, target) in enumerate(targets):
+        try:
+            v = results[country][str(target)][stat]
+        except tables.NoSuchNodeError:
+            pass
+        else:
+            t = common.t[ : : plotevery]
+            y = numpy.asarray(v['median'])[ : : plotevery] / info.scale
+            l = ax.plot(t, y,
+                        label = common.get_target_label(target),
+                        color = colors[i],
+                        alpha = alpha0,
+                        zorder = 2)
+
+            if confidence_level > 0:
+                CI = v[CIkey]
+                # Draw borders of CI with high alpha,
[…]

### 2016-12-15 plots/effectiveness_all.py

@@ -1,0 +1,76 @@
+#!/usr/bin/python3
+'''
+Plot the effectiveness of interventions in all countries.
+'''
+
+import os.path
+import sys
+
+from matplotlib import pyplot
+
+sys.path.append(os.path.dirname(__file__))  # For Sphinx.
+import common
+import effectiveness
+sys.path.append('..')
+import model
+
+
+# [H] requires \usepackage{float}
+template = r'''
+\begin{{figure}}[H]
+  \centering
+  \input{{{figfile:}}}
+  \caption{{{region_or_country:} model outcomes under the different
+    diagnosis, treatment, and vaccination scenarios.  Central curves
+    show the medians over model runs with 1000 samples from parameter
+    distributions, shaded regions show the 1st and 3rd quartiles
+    (i.e.~25th and 75th percentiles), and vertical bars to the right of
+    each axis show the 5th and 95th percentiles at the end time, 2035.
+    Regional and global outcomes were aggregated from the country-level
+    model outcomes.}}
+  \label{{effectiveness_{base:}}}
+\end{{figure}}
+'''
+
+
+def plot_all(plotevery = 10, **kwargs):
+    path = common.get_filebase()
+    with model.results.samples.stats.open_() as results:
+        for region_or_country in common.all_regions_and_countries:
+            print(region_or_country)
+            fig = effectiveness._plot_one(results,
+                                          region_or_country,
+                                          plotevery = plotevery,
+                                          **kwargs)
+            filebase = os.path.join(path, region_or_country.replace(' ', '_'))
+            filename = '{}.pgf'.format(filebase)
+            label = common.get_country_label(region_or_country)
+            common.savefig(fig, filename,
+                           title = '{} effectiveness'.format(label))
+            pyplot.close(fig)
+
+
+def combine(prefix = '../Codes/plots'):
+    path = common.get_filebase()
+    outfile = os.path.join(path, 'all.tex')
+    with open(outfile, 'w') as fd:
+        isfirst = True
+        for region_or_country in common.all_regions_and_countries:
+            filebase = region_or_country.replace(' ', '_')
+            filename = os.path.join(prefix, path,
+                                    '{}.pgf'.format(filebase))
+            filename = os.path.normpath(filename)
+            label = common.get_country_label(region_or_country)
+            if isfirst:
+                isfirst = False
+            else:
+                fd.write('\n')
+            fd.write(template[1 : ].format(
+                figfile = filename,
[…]

### 2016-12-15 plots/effectiveness_regions.py

@@ -1,0 +1,163 @@
+#!/usr/bin/python3
+'''
+Plot the effectiveness of interventions by region.
+'''
+
+import itertools
+import os.path
+import sys
+
+from matplotlib import pyplot
+from matplotlib import patches
+from matplotlib import ticker
+import numpy
+import pandas
+import tables
+
+sys.path.append(os.path.dirname(__file__))  # For Sphinx.
+import common
+# import seaborn
+import seaborn_quiet as seaborn
+sys.path.append('..')
+import model
+
+
+effectiveness_measures = ['new_infections', 'infected']
+
+regions = model.regions.all_
+if 'Global' in regions:
+    regions.remove('Global')
+
+targets = model.targets.all_
+
+region_labels = {
+    'Global': 'Global',
+    'Asia Pacific': 'Asia\n& The\nPacific',
+    'Caribbean': 'The\nCarribean',
+    'East and Southern Africa': 'Eastern &\nSouthern\nAfrica',
+    'Eastern Europe and Central Asia': 'Eastern\nEurope &\nCentral Asia',
+    'Latin America': 'Latin\nAmerica',
+    'Middle East and North Africa': 'Middle\nEast &\nNorth Africa',
+    'North America': 'North\nAmerica',
+    'West and Central Africa': 'West &\nCentral\nAfrica',
+    'Western Europe': 'Western &\nCentral\nEurope'
+}
+
+
+def _plot_stat(ax, results, regions, stat, confidence_level, **kwargs):
+    CIkey = 'CI{:g}'.format(100 * confidence_level)
+
+    info = common.get_stat_info(stat)
+
+    idx = ['median', 'CIlower', 'CIupper']
+    data = pandas.Panel(items = regions,
+                        major_axis = targets,
+                        minor_axis = idx,
+                        dtype = float)
+    for region, target in itertools.product(regions, targets):
+        try:
+            v = results[region][target][stat]
+        except tables.NoSuchNodeError:
+            pass
+        else:
+            # At the end time.
+            data.loc[region, target, 'median'] = v['median'][..., -1]
+            data.loc[region, target, ['CIlower', 'CIupper']] = v[CIkey][..., -1]
+
+    if info.scale is None:
+        info.autoscale(data.max().max())
+
+    colors = seaborn.color_palette()
+
+    pad = 0.2
+    width = (1 - pad) / len(targets)
+    for (i, target) in enumerate(targets):
+        median = data.loc[:, target, 'median'].values
[…]

### 2016-12-15 plots/infections_averted_map.py

@@ -1,0 +1,131 @@
+#!/usr/bin/python3
+'''
+Make maps of the infections averted at different times.
+'''
+
+import os.path
+import sys
+
+from matplotlib import colors as mcolors
+from matplotlib import pyplot
+from matplotlib import ticker
+import numpy
+import pandas
+import tables
+
+sys.path.append(os.path.dirname(__file__))
+import common
+import mapplot
+sys.path.append('..')
+import model
+
+
+baseline = model.targets.StatusQuo()
+interventions = (
+    model.targets.UNAIDS95(),
+    model.targets.Vaccine(treatment_targets = model.targets.StatusQuo()),
+    model.targets.Vaccine(treatment_targets = model.targets.UNAIDS95()))
+
+baseline = str(baseline)
+interventions = list(map(str, interventions))
+
+time = 2035
+
+scale = 0.01
+title = 'Infections Averted (Compared to {})'.format(
+    baseline)
+vmin = 0.1 / scale
+vmax = 0.9 / scale
+norm = mcolors.Normalize(vmin = vmin, vmax = vmax)
+cmap = 'plasma_r'
+label_coords = (-130, -30)
+height = 0.28
+pad = 0.02
+cpad = 0.05
+aspect = 1.45
+
+
+def plot(infections_averted):
+    countries = infections_averted.index
+    interventions = infections_averted.columns
+
+    fig = pyplot.figure(figsize = (common.width_1_5column, 6))
+    nrows = len(interventions)
+    for (i, intv) in enumerate(interventions):
+        if i <  nrows - 1:
+            h = height
+            b = 1 - height - (height + pad) * i
+        else:
+            h = 1 - (height + pad) * (nrows - 1)
+            b = 0
+
+        m = mapplot.Basemap(rect = (0, b, 1, h),
+                            anchor = (0.5, 1))
+
+        mappable = m.choropleth(
+            countries,
+            infections_averted.loc[:, intv] / scale,
+            cmap = cmap,
+            norm = norm,
+            vmin = vmin,
+            vmax = vmax)
+
+        label = common.get_target_label(intv)
+        label = label.replace('_', ' ').replace('+', '\n+')
+        X, Y = label_coords
+        m.text_coords(
+            X, Y, label,
+            fontdict = dict(size = pyplot.rcParams['font.size'] + 3,
+                            weight = 'bold'),
+            horizontalalignment = 'center',
+            verticalalignment = 'center')
+
+    cbar = fig.colorbar(mappable,
[…]

### 2016-12-15 plots/infections_per_capita_averted_map.py

@@ -1,0 +1,148 @@
+#!/usr/bin/python3
+'''
+Make maps of the infections averted at different times.
+
+.. todo:: This uses :func:`model.results.samples.open_` because `alive`
+          is not in :func:`model.results.samples.h5.open_` at the moment.
+'''
+
+import os.path
+import sys
+
+from matplotlib import colors as mcolors
+from matplotlib import pyplot
+from matplotlib import ticker
+import numpy
+import pandas
+from scipy import integrate
+import tables
+
+sys.path.append(os.path.dirname(__file__))
+import common
+import mapplot
+sys.path.append('..')
+import model
+
+
+baseline = model.targets.StatusQuo()
+interventions = (
+    model.targets.UNAIDS95(),
+    model.targets.Vaccine(treatment_targets = model.targets.StatusQuo()),
+    model.targets.Vaccine(treatment_targets = model.targets.UNAIDS95()))
+
+baseline = str(baseline)
+interventions = list(map(str, interventions))
+
+time = 2035
+
+scale = 1e-3
+title = 'Infections per 1000 Averted (Compared to {})'.format(baseline)
+vmin = 0.0025 / scale
+vmax = 0.25 / scale
+norm = mcolors.LogNorm(vmin = vmin, vmax = vmax)
+cmap = common.cmap_scaled('magma_r', vmax = 0.85)
+label_coords = (-130, -30)
+height = 0.28
+pad = 0.035
+cpad = 0.05
+aspect = 1.45
+
+
+def plot(infections_per_capita_averted):
+    countries = infections_per_capita_averted.index
+    interventions = infections_per_capita_averted.columns
+
+    fig = pyplot.figure()
+    nrows = len(interventions)
+    for (i, intv) in enumerate(interventions):
+        if i <  nrows - 1:
+            h = height
+            b = 1 - height - (height + pad) * i
+        else:
+            h = 1 - (height + pad) * (nrows - 1)
+            b = 0
+
+        m = mapplot.Basemap(rect = (0, b, 1, h),
+                            anchor = (0.5, 1))
+
+        mappable = m.choropleth(
+            countries,
+            infections_per_capita_averted.loc[:, intv] / scale,
+            cmap = cmap,
+            norm = norm,
+            vmin = vmin,
+            vmax = vmax)
+
+        label = common.get_target_label(intv)
+        label = label.replace('_', ' ').replace('+', '\n+')
+        X, Y = label_coords
+        m.text_coords(X, Y, label,
[…]

### 2016-12-15 plots/initial_prevalence_map.py

@@ -1,0 +1,70 @@
+#!/usr/bin/python3
+'''
+Map the initial proportion of the population with HIV.
+'''
+
+import os.path
+import sys
+
+from matplotlib import colors
+from matplotlib import pyplot
+from matplotlib import ticker
+import numpy
+import pandas
+
+sys.path.append(os.path.dirname(__file__))  # For Sphinx.
+import common
+import mapplot
+sys.path.append('..')
+import model
+
+
+def _main():
+    data = model.datasheet.InitialConditions.get_all()
+
+    countries = data.columns
+
+    nHIV = data.iloc[1 :].sum(0)
+    n = data.sum(0)
+    prevalence = nHIV / n
+    for (k, v) in prevalence.items():
+        print('{}: {:g}%'.format(k, 100 * v))
+
+    # vmin = prevalence.min()
+    # vmax = prevalence.max()
+    vmin = 0.0005
+    vmax = 0.25
+
+    cmap = 'YlOrRd'
+    norm = colors.LogNorm
+    ticks = ticker.LogLocator(10, [1, 2.5, 5])
+    fig = pyplot.figure(figsize = (common.width_2column, 3))
+    m = mapplot.Basemap()
+    m.choropleth(countries, 100 * prevalence,
+                 cmap = cmap,
+                 norm = norm(vmin = 100 * vmin,
+                             vmax = 100 * vmax),
+                 vmin = 100 * vmin,
+                 vmax = 100 * vmax)
+    cbar = m.colorbar(label = '2015 HIV Prevalence',
+                      format = '%g%%',
+                      ticks = ticks)
+
+    ticklabels = cbar.ax.get_xticklabels()
+    if prevalence.min() < vmin:
+        ticklabels[0].set_text(r'$\leq\!$' + ticklabels[0].get_text())
+    if prevalence.max() > vmax:
+        ticklabels[-1].set_text(r'$\geq\!$' + ticklabels[-1].get_text())
+    cbar.ax.set_xticklabels(ticklabels)
+    cbar.ax.tick_params(labelsize = pyplot.rcParams['font.size'])
+
+    m.tighten(aspect_adjustment = 1.35)
+
+    common.savefig(m.fig, '{}.pdf'.format(common.get_filebase()))
+    common.savefig(m.fig, '{}.png'.format(common.get_filebase()))
+
+    m.show()
+
+
+if __name__ == '__main__':
+    _main()

### 2016-12-15 plots/mapplot/__init__.py

@@ -1,0 +1,5 @@
+'''
+Make nice graphs on maps.
+'''
+
+from .basemap import *

### 2016-12-15 plots/mapplot/basemap.py

@@ -1,0 +1,693 @@
+'''
+Make nice graphs on maps.
+'''
+
+from collections import abc
+import itertools
+import os.path
+import sys
+
+from matplotlib import animation
+from matplotlib import cm
+from matplotlib import patches
+from matplotlib import pyplot
+import numpy
+import shapely.geometry
+import shapely.ops
+
+# import cartopy
+sys.path.append(os.path.dirname(__file__))  # For Sphinx
+import cartopy_quiet as cartopy
+
+sys.path.append('..')
+# import seaborn
+import seaborn_quiet as seaborn
+
+from . import locators
+
+
+# Change cartopy cache from ~/.local/share
+# to a subdirectory so it'll go in Google Drive.
+cartopy.config['data_dir'] = os.path.join(
+    os.path.dirname(os.path.abspath(__file__)),
+    '_cartopy')
+
+
+_east_hemis = shapely.geometry.box(180, -90, 0, 90)
+_west_hemis = shapely.geometry.box(-180, -90, 0, 90)
+
+
+def _in_west_hemis(p):
+    return p.intersects(_west_hemis)
+
+
+def _in_east_hemis(p):
+    return p.intersects(_east_hemis)
+
+
+def _wrap_line(line, direction):
+    '''
+    Move a line that has some points on one side of ±180 longitude
+    to entirely one side or the other.
+    '''
+    if direction.lower() == 'east':
+        shift = [360, 0]
+    elif direction.lower() == 'west':
+        shift = [-360, 0]
+    else:
+        raise ValueError("Unknown direction '{}'!".format(direction))
+    return numpy.asarray(line.coords) + shift
+
+
+def _wrap_polygon(poly, direction):
+    '''
+    Move a polygon that has some points on one side of ±180 longitude
+    to entirely one side or the other.
+    '''
+    e = _wrap_line(poly.exterior, direction)
+    i = list(map(_wrap_line, poly.interiors, direction))
+    return shapely.geometry.Polygon(e, i)
+
+
+class Basemap:
+    def __init__(self,
+                 extent = (-180, 180, -60, 85),
+                 rect = (0, 0, 1, 1),
+                 central_longitude = 11,
+                 fig = None,
+                 *args, **kwargs):
+        '''
+        Set up the basic map.
+        extent is the map limits in longitude and latitude.
+        rect is the shape of plot in (0, 1) coordinates.
+        '''
+
+        self.fig = fig or pyplot.gcf()
+        proj = cartopy.crs.PlateCarree(
[…]

### 2016-12-15 plots/mapplot/cmap.py

@@ -1,0 +1,96 @@
+'''
+Helper functions for dealing with :mod:`matplotlib.cm` colormaps.
+'''
+
+import collections
+
+from matplotlib import colors as mcolors
+
+
+def _get_linear_transform(a, b):
+    '''
+    Map [a, b] to [0, 1].
+    '''
+    
+    def f(x):
+        '''
+        Map [a, b] to [0, 1].
+        '''
+        return (x - a) / (b - a)
+
+    return f
+
+
+class _CDict(collections.OrderedDict):
+    '''
+    An object to hold the data for a colormap.
+    '''
+    def __init__(self):
+        super().__init__()
+        self['red'] = []
+        self['green'] = []
+        self['blue'] = []
+
+    def append(self, x0, c0, c1):
+        for (i, k) in enumerate(self):
+            self[k].append((x0, c0[i], c1[i]))
+
+    def get_cmap(self, name):
+        return mcolors.LinearSegmentedColormap(name, self)
+
+
+def combine(clist):
+    '''
+    Combine multiple colormaps into one.
+
+    Takes a list of (x0, x1, cmap) elements
+    where cmap is the colormap to use in between x0 and x1.
+
+    The x0 and x1 values must be non-decreasing.
+    '''
+    a = clist[0][0]
+    b = clist[-1][1]
+    f = _get_linear_transform(a, b)
+
+    cdict = _CDict()
+
+    for (x0, x1, cmap) in clist:
+        def g(y):
+            '''
+            Map [0, 1] to [x0, x1].
+            '''
+            return y * (x1 - x0) + x0
+
+        for (k, v) in cmap._segmentdata.items():
+            for (y, c0, c1) in v:
+                cdict[k].append((f(g(y)), c0, c1))
+
+    return cdict.get_cmap('combined')
+        
+        
+def build(clist):
+    '''
+    Build a colormap from a list of colors and the points where they change.
+
+    The list should have elements
+    (x0, x1, c0, c1)
+    where c0 starts at x0 and transitions linearly to c1 at x1.
+
+    The x0 and x1 values must be non-decreasing.
+    '''
+    a = clist[0][0]
+    b = clist[-1][1]
+    f = _get_linear_transform(a, b)
+
+    cdict = _CDict()
+
+    c0 = None
+    for (x1, x2, c1, c2) in clist:
+        if c0 is None:
+            cdict.append(x1, c1, c1)
+        else:
[…]

### 2016-12-15 plots/prcc.py

@@ -1,0 +1,148 @@
+#!/usr/bin/python3
+'''
+Calculate PRCCs and make tornado plots.
+
+.. todo:: Clean up similarity with sensitivity.py.
+'''
+
+import os.path
+import sys
+
+from matplotlib import pyplot
+from matplotlib import ticker
+import numpy
+from scipy import interpolate
+
+sys.path.append(os.path.dirname(__file__))  # cwd for Sphinx.
+import common
+import stats
+# import seaborn
+import seaborn_quiet as seaborn
+sys.path.append('..')
+import model
+
+
+def get_outcome_samples(results, country, targets, stat, times):
+    x, y =  (numpy.asarray(getattr(results[country][str(target)], stat))
+             for target in targets)
+    z = x - y
+    interp = interpolate.interp1d(common.t, z, axis = -1)
+    outcome_samples = interp(times)
+    return outcome_samples
+
+
+def tornado(ax, results, country, targets, outcome, t, parameter_samples,
+            colors, parameter_names = None, errorbars = False):
+    outcome_samples = get_outcome_samples(results, country, targets,
+                                          outcome, t)
+
+    n = numpy.shape(parameter_samples)[-1]
+
+    if parameter_names is None:
+        parameter_names = ['parameter[{}]'.format(i) for i in range(n)]
+
+    rho = stats.prcc(parameter_samples, outcome_samples)
+    CI = stats.prcc_CI(rho, len(outcome_samples))
+    xerr = numpy.row_stack((rho - CI[:, 0], CI[:, 1] - rho))
+
+    ix = numpy.argsort(numpy.abs(rho))
+
+    labels = [parameter_names[i] for i in ix]
+    c = [colors[l] for l in labels]
+
+    h = range(n)
+    if errorbars:
+        kwds = dict(xerr = xerr[:, ix],
+                    error_kw = dict(ecolor = 'black',
+                                    elinewidth = 1.5,
+                                    capthick = 1.5,
+                                    capsize = 5,
+                                    alpha = 0.9))
+    else:
+        kwds = dict()
+
+    patches = ax.barh(h, rho[ix],
+                      height = 1, left = 0,
+                      align = 'center',
+                      color = c,
+                      edgecolor = c,
+                      **kwds)
+        
+    ax.xaxis.set_major_formatter(ticker.StrMethodFormatter('{x:g}'))
[…]

### 2016-12-15 plots/stats.py

@@ -1,0 +1,63 @@
+'''
+Calculate PRCCs, etc.
+'''
+
+import numpy
+import scipy.stats
+
+
+def rankdata(X, axis = 0):
+    return numpy.apply_along_axis(scipy.stats.rankdata, axis, X)
+
+
+def cc(X, y):
+    result = (scipy.stats.pearsonr(y, x) for x in X.T)
+    rho, p = zip(*result)
+    return rho, p
+
+
+def rcc(X, y):
+    result = (scipy.stats.spearmanr(y, x) for x in X.T)
+    rho, p = zip(*result)
+    return rho, p
+
+
+def get_residuals(Z, b):
+    # Add a column of ones for intercept term.
+    A = numpy.column_stack((numpy.ones_like(Z[..., 0]), Z))
+    result = numpy.linalg.lstsq(A, b)
+    coefs = result[0]
+    # residuals = b - A @ coefs  # Stupid Sphinx bug.
+    residuals = b - numpy.dot(A, coefs)
+    return residuals
+
+
+def pcc(X, y):
+    n = numpy.shape(X)[-1]
+
+    rho = numpy.empty(n)
+    for i in range(n):
+        # Separate ith column from other columns.
+        mask = numpy.array([j == i for j in range(n)])
+        x = numpy.squeeze(X[..., mask])
+        Z = X[..., ~mask]
+        x_res = get_residuals(Z, x)
+        y_res = get_residuals(Z, y)
+        rho[i], _ = scipy.stats.pearsonr(x_res, y_res)
+    return rho
+
+
+def prcc(X, y):
+    return pcc(rankdata(X), rankdata(y))
+
+
+def pcc_CI(rho, N, alpha = 0.05):
+    p = 1
+    z = numpy.arctanh(rho)
+    z_crit = scipy.stats.norm.ppf([alpha / 2, 1 - alpha / 2])
+    z_CI = z[..., numpy.newaxis] + z_crit / numpy.sqrt(N - p - 3)
+    return numpy.tanh(z_CI)
+
+
+def prcc_CI(rho, N, alpha = 0.05):
+    return pcc_CI(rho, N, alpha = alpha)

### 2016-12-15 plots/table_format.py

@@ -1,0 +1,112 @@
+#!/usr/bin/python3
+'''
+Make a LaTeX-formatted table from the simulation output.
+'''
+
+import locale
+import os.path
+import sys
+
+import numpy
+import pandas
+
+sys.path.append(os.path.dirname(__file__))  # For Sphinx.
+import common
+
+
+country_label_replacements = {'United States of America': 'United States',
+                              'Democratic Republic of the Congo': 'DR Congo',
+                              'Bolivia (Plurinational State of)': 'Bolivia',
+                              'Iran (Islamic Republic of)': 'Iran',
+                              "Lao People's Democratic Republic": 'Laos',
+                              'Republic of Moldova': 'Moldova',
+                              'Venezuela (Bolivarian Republic of)': 'Venezuela'
+}
+
+
+def _format_number(x):
+    if not numpy.isnan(x):
+        return locale.format('%d', x, grouping = True)
+    else:
+        return '------'
+
+
+def _format_target(t):
+    return t.replace('%', '\%').replace('_', ' ')
+
+
+def normalize(c):
+    x = common.get_country_label(c)
+    y = country_label_replacements.get(x, x)
+    return y
+
+if __name__ == '__main__':
+    locale.setlocale(locale.LC_NUMERIC, 'en_US.utf8')
+
+    df = pandas.read_csv('table.csv',
+                         index_col = [0, 1],
+                         header = [0, 1, 2])
+
+    countries = common.all_regions_and_countries
+
+    targets = df.index.levels[1]
+
+    with open('table_sub.tex', 'w') as fd:
+        colfmt = 'r@{ [\\,}r@{, }r@{\\,] }'
+        fd.write('\\begin{{tabu}}{{ll|[3pt]{}|[1.5pt]{}|[1.5pt]{}|[3pt]{}|[1.5pt]{}|[1.5pt]{}|[3pt]}}'.format(
+            *(6 * (colfmt, ))))
+
+        fd.write('\\tabucline[3pt]{3-}\n')
+        fd.write('\\multicolumn{2}{l|[3pt]}{} & ')
+        fd.write('\\multicolumn{9}{c|[3pt]}{\\textbf{As of 2025}} & ')
+        fd.write('\\multicolumn{9}{c|[3pt]}{\\textbf{As of 2035}}\n')
[…]

### 2016-12-15 plots/transmission_rate.py

@@ -1,0 +1,262 @@
+#!/usr/bin/python3
+'''
+Make a PDF with a page of transmission plots for each country.
+'''
+
+import itertools
+import os.path
+import sys
+
+import joblib
+from matplotlib.backends import backend_pdf
+from matplotlib import pyplot
+from matplotlib import ticker
+import numpy
+import pandas
+
+sys.path.append(os.path.dirname(__file__))  # For Sphinx.
+import common
+sys.path.append('..')
+import model
+from model import transmission_rate
+
+# import seaborn
+import seaborn_quiet as seaborn
+
+
+def plot_transmission_rates(countries, fig = None,
+                            quantile_level = 0.01,
+                            scale = 0.8,
+                            savefig = True):
+    if fig is None:
+        fig = pyplot.figure(figsize = (8.5, 11))
+    with seaborn.axes_style('whitegrid'):
+        ax = fig.add_subplot(1, 1, 1)
+        seaborn.despine(ax = ax, top = True, bottom = True)
+        n = len(countries)
+        colors = seaborn.color_palette('husl', n)
+        for (i, country) in enumerate(countries):
+            # Plot from top instead of bottom.
+            j = n - 1 - i
+            parameters = model.parameters.Parameters(country)
+            rv = transmission_rate.estimate(parameters)
+            a, b = rv.ppf([quantile_level / 2, 1 - quantile_level / 2])
+            x = numpy.linspace(a, b, 101)
+            y = rv.pdf(x) / n * scale
+            ax.fill_between(x, j + y, j - y,
+                            linewidth = 0,
+                            facecolor = colors[i],
+                            alpha = 0.7)
+            ax.scatter(rv.mode, j,
+                       marker = '|', s = 30, linewidth = 1,
+                       color = 'black')
+    ax.xaxis.set_tick_params(labelsize = pyplot.rcParams['font.size'])
+    ax.set_xlabel('Transmission rate (per year)')
+    ax.set_xlim(0, 0.5001)
+    ax.xaxis.set_major_locator(ticker.MultipleLocator(0.05))
+    ax.set_ylim(-1.5, n + 0.5)
+    ax.set_yticks(range(n))
+    yticklabels = (common.get_country_label(c, short = True).replace('&', '\&')
+                   for c in reversed(countries))
+    ax.set_yticklabels(yticklabels, size = 5)
+    ax.grid(False, axis = 'y')
[…]

### 2016-12-15 plots/vaccine_scenarios.py

@@ -1,0 +1,229 @@
+#!/usr/bin/python3
+'''
+Using the modes of the parameter distributions,
+make plots for sensitivity to vaccine parameters.
+'''
+
+import operator
+import os.path
+import sys
+
+from matplotlib import lines
+from matplotlib import pyplot
+from matplotlib import ticker
+from matplotlib.backends import backend_pdf
+import numpy
+import tables
+
+sys.path.append(os.path.dirname(__file__))  # For Sphinx.
+import common
+# import seaborn
+import seaborn_quiet as seaborn
+sys.path.append('..')
+import model
+
+
+ix = [0, 1, 2, 3, 5, 9]
+colors = ['black'] + [common.colors_paired[i] for i in ix]
+
+
+def _get_args(target):
+    i = target.find('(')
+    return target[i + 1 : -1].split(', ')
+
+
+def get_target_label(treatment_target, target):
+    baseline = model.targets.Vaccine(treatment_targets = treatment_target)
+    args_baseline = _get_args(str(baseline))
+    args = _get_args(target)
+    diff = []
+    for i in range(len(args)):
+        if args[i] != args_baseline[i]:
+            fancy = args[i].replace('_', ' ').replace('=', ' = ')
+            fancy = fancy.replace('time to start', 'start date')
+            if fancy.startswith('time to fifty percent'):
+                i = fancy.find('=')
+                t = float(fancy[i + 2 : -1])
+                fancy = 'scale-up = {:g}% y$^{{-1}}$'.format(50 / t)
+            i = fancy.find('=')
+            pre = fancy[ : i - 1]
+            post = fancy[i + 2 : ]
+            fancy = post + ' ' + pre
+            diff.append(fancy.capitalize())
+    retval = ', '.join(diff)
+    if retval == '':
+        return 'Baseline'
+    else:
+        return retval
+
+
+def _get_targets(treatment_target):
+    return [str(t) for t in model.targets.vaccine_scenarios
+            if hasattr(t, '_treatment_targets')
+            and (str(t._treatment_targets) == str(treatment_target))]
+
+
+def _get_kwds(label):
+    if label == 'Baseline':
+        return dict(zorder = 2,
+                    alpha = 1,
+                    linestyle = 'dotted')
+    else:
+        return dict(zorder = 1,
+                    alpha = 0.9,
+                    linestyle = 'solid')
+
+
+def _plot_cell(ax, results, country, treatment_target, stat,
+               country_label = None,
[…]

### 2016-12-15 run_modes.py

@@ -1,0 +1,76 @@
+#!/usr/bin/python3
+'''
+Using the modes of the parameter distributions,
+run simulations.
+
+.. todo:: Update to use hdf5 well and save Simulation.keys().
+'''
+
+import joblib
+import tables
+
+import model
+
+
+stats_to_save = ['infected', 'incidence', 'prevalence',
+                 'incidence_per_capita', 'AIDS', 'dead',
+                 'new_infections', 'alive']
+
+
+def _run_one(country, targets = None):
+    if targets is None:
+        targets = model.targets.all_
+    parameters = model.parameters.Parameters(country)
+    parameter_values = parameters.mode()
+    results = joblib.Parallel(n_jobs = -1)(
+        joblib.delayed(model.simulation.Simulation)(parameter_values,
+                                                    target)
+        for target in targets)
+    retval = {}
+    for (target, r) in zip(targets, results):
+        retval[str(target)] = r
+    return retval
+
+
+def _build_regionals(results, targets = None):
+    if targets is None:
+        targets = model.targets.all_
+
+    countries = list(results.keys())
+    for region in model.regions.all_:
+        if region in countries:
+            countries.remove(region)
+
+    for target in targets:
+        val = {country: results[country][str(target)] for country in countries}
+        for region in model.regions.all_:
+            if region == 'Global':
+                mc = model.multicountry.Global(val)
+            else:
+                val_ = {c: val[c] for c in val.keys()
+                        if c in model.regions.regions[region]}
+                mc = model.multicountry.MultiCountry(val_)
+            for s in stats_to_save:
+                v = getattr(mc, s)
+                model.h5._dump_val(results, '/{}/{}'.format(region, target),
+                                   s, v)
+
+
+def _run_all(targets = None):
+    countries = model.datasheet.get_country_list()
+    results = model.results.modes.open_(mode = 'a')
+    for country in countries:
+        if country not in results:
+            print(country)
+            r = _run_one(country, targets = targets)
+            for (t, v) in r.items():
+                for s in stats_to_save:
+                    x = getattr(v, s)
+                    model.h5._dump_val(results, '/{}/{}'.format(country, t),
+                                       s, x)
+    _build_regionals(results, targets = targets)
+    return results
+
+
+if __name__ == '__main__':
+    results = _run_all()

### 2016-12-15 run_samples.py

@@ -1,0 +1,44 @@
+#!/usr/bin/python3
+'''
+Run simulations with parameter samples.
+'''
+
+import model
+
+
+countries = model.datasheet.get_country_list()
+# Move these to the front.
+countries_to_plot = ['United States of America',
+                     'South Africa',
+                     'Uganda',
+                     'Nigeria',
+                     'India',
+                     'Rwanda']
+for c in countries_to_plot:
+    countries.remove(c)
+countries = countries_to_plot + countries
+
+
+def _run_country(country, target, samples):
+    print('Running {}, {!s}.'.format(country, target))
+
+    parametersamples = model.parameters.Sample.from_samples(country,
+                                                            samples)
+
+    multisim = model.multisim.MultiSim(parametersamples, target)
+
+    return multisim
+
+
+def _main():
+    samples = model.samples.load()
+
+    for country in countries:
+        for target in model.targets.all_:
+            if not model.results.samples.exists(country, target):
+                results = _run_country(country, target, samples)
+                model.results.samples.dump(country, target, results)
+
+
+if __name__ == '__main__':
+    _main()

### 2016-12-15 run_vaccine_scenarios.py

@@ -1,0 +1,76 @@
+#!/usr/bin/python3
+'''
+Using the modes of the parameter distributions,
+run simulations for the different vaccine sensitivity scenarios.
+
+.. todo:: Update to use hdf5 well and save Simulation.keys().
+'''
+
+import joblib
+import tables
+
+import model
+
+
+stats_to_save = ['infected', 'incidence', 'prevalence',
+                 'incidence_per_capita', 'AIDS', 'dead',
+                 'new_infections', 'alive']
+
+
+def _run_one(country, targets = None):
+    if targets is None:
+        targets = model.targets.vaccine_scenarios
+    parameters = model.parameters.Parameters(country)
+    parameter_values = parameters.mode()
+    results = joblib.Parallel(n_jobs = -1)(
+        joblib.delayed(model.simulation.Simulation)(parameter_values,
+                                                    target)
+        for target in targets)
+    retval = {}
+    for (target, r) in zip(targets, results):
+        retval[str(target)] = r
+    return retval
+
+
+def _build_regionals(results, targets = None):
+    if targets is None:
+        targets = model.targets.vaccine_scenarios
+
+    countries = list(results.keys())
+    for region in model.regions.all_:
+        if region in countries:
+            countries.remove(region)
+
+    for target in targets:
+        val = {country: results[country][str(target)] for country in countries}
+        for region in model.regions.all_:
+            if region == 'Global':
+                mc = model.multicountry.Global(val)
+            else:
+                val_ = {c: val[c] for c in val.keys()
+                        if c in model.regions.regions[region]}
+                mc = model.multicountry.MultiCountry(val_)
+            for s in stats_to_save:
+                v = getattr(mc, s)
+                model.h5._dump_val(results, '/{}/{}'.format(region, target),
+                                   s, v)
+
+
+def _run_all(targets = None):
+    countries = model.datasheet.get_country_list()
+    results = model.results.modes.open_vaccine_scenarios(mode = 'a')
+    for country in countries:
+        if country not in results:
+            print(country)
+            r = _run_one(country, targets = targets)
+            for (t, v) in r.items():
+                for s in stats_to_save:
+                    x = getattr(v, s)
+                    model.h5._dump_val(results, '/{}/{}'.format(country, t),
+                                       s, x)
+    _build_regionals(results, targets = targets)
+    return results
+
+
+if __name__ == '__main__':
+    results = _run_all()

### 2016-12-15 samples_patch.py

@@ -1,0 +1,52 @@
+#!/usr/bin/python3
+'''
+Patch samples.h5.
+'''
+
+import warnings
+
+import numpy
+import tables
+
+
+filters = tables.Filters(complevel = 4,
+                         complib = 'zlib',
+                         shuffle = True,
+                         fletcher32 = True)
+
+def _main():
+    patch = tables.open_file('samples_patch.h5')
+    h5file = tables.open_file('results/samples.h5', mode = 'a', filters = filters)
+
+    def are_equal(x, y):
+        # Handle NaNs.
+        X = numpy.ma.masked_invalid(x)
+        Y = numpy.ma.masked_invalid(x)
+        return (X == Y).all()
+
+
+    with warnings.catch_warnings():
+        warnings.filterwarnings('ignore',
+                                category = tables.NaturalNameWarning)
+        for leaf in patch.walk_nodes(classname = 'Leaf'):
+            if leaf._v_pathname in h5file:
+                arr = h5file.get_node(leaf._v_parent._v_pathname, leaf._v_name)
+                if are_equal(leaf, arr):
+                    print('Skipping {}: identical in both files.'.format(
+                        leaf._v_pathname))
+                else:
+                    print('Updating {}.'.format(leaf._v_pathname))
+                    # arr[:] = leaf[:]
+            else:
+                print('Adding {}.'.format(leaf._v_pathname))
+                h5file.create_carray(leaf._v_parent._v_pathname, leaf._v_name,
+                                     obj = leaf[:],
+                                     createparents = True)
+
+
+    patch.close()
+    h5file.close()
+
+
+if __name__ == '__main__':
+    _main()

### 2016-12-15 tests/compare.py

@@ -1,0 +1,25 @@
+#!/usr/bin/python3
+'''
+Run the 90-90-90 policies for one country.
+'''
+
+import sys
+
+sys.path.append('..')
+import model
+
+
+def _main(parallel = True):
+    country = 'South Africa'
+    parameters = model.parameters.Parameters(country).mode()
+    targets = [model.targets.StatusQuo(), model.targets.UNAIDS90()]
+    results = {}
+    for target in targets:
+        target_ = str(target)
+        results[target_] = model.simulation.Simulation(parameters, target)
+        print('{}: {:g} DALYs'.format(target_, results[target_].DALYs))
+    return results
+
+
+if __name__ == '__main__':
+    results = _main()

### 2016-12-15 tests/modes_example.py

@@ -1,0 +1,47 @@
+#!/usr/bin/python3
+'''
+Example script of accessing results from runs with the modes of
+the parameter distributions.
+'''
+
+import sys
+
+from matplotlib import pyplot
+
+sys.path.append('..')
+import model
+
+# import seaborn
+sys.path.append('../plots')
+import seaborn_quiet as seaborn
+
+
+if __name__ == '__main__':
+    with model.results.modes.open_() as results:
+        # The data look like results[country][target][stat]
+
+        countries = results.keys()
+        print('countries =', countries)
+
+        country = 'South Africa'
+        targets = results[country].keys()
+        print('targets =', targets)
+
+        target = targets[5]
+        stats = results[country][target].keys()
+        print('stats =', stats)
+
+        # You need '[:]' or '.read()' at the end to get the actual values.
+        print('prevalence =', results[country][target]['prevalence'][:])
+
+        # Again, you need '[:]' or '.read()' at the end to get the
+        # actual values.
+        stat = 'infected'
+        print(stat, '=', results[country][target][stat][:])
+
+        t = results[country][target]['t']
+        x = results[country][target][stat]
+        pyplot.plot(t, x, label = country)
+        pyplot.ylabel(stat.capitalize())
+        pyplot.legend(loc = 'upper right', frameon = False)
+        pyplot.show()

### 2016-12-15 tests/profile_.py

@@ -1,0 +1,23 @@
+#!/usr/bin/python3
+'''
+Profile :mod:`model.simulation`.
+'''
+
+
+import cProfile
+import sys
+
+sys.path.append('..')
+import model
+
+
+def _main():
+    country = 'South Africa'
+    targets = model.targets.Vaccine()
+    parameters = model.parameters.Parameters(country).mode()
+    simulation = model.simulation.Simulation(parameters, targets)
+    return simulation
+
+
+if __name__ == '__main__':
+    cProfile.run('_main()', sort = 'tottime')

### 2016-12-15 tests/samples_cache.py

@@ -1,0 +1,24 @@
+#!/usr/bin/python3
+'''
+Test :mod:`model.results.sample_cache`.
+'''
+
+
+import sys
+
+import numpy
+
+sys.path.append('..')
+import model
+
+
+if __name__ == '__main__':
+    country = 'South Africa'
+    target = 'Status Quo'
+    attr = 'new_infections'
+
+    with model.results.samples.Cache() as cache:
+        ccache = cache[country]
+        ctcache = ccache[target]
+        val = getattr(ctcache, attr)
+        print(numpy.shape(val))

### 2016-12-15 tests/samples_stats_example.py

@@ -1,0 +1,66 @@
+#!/usr/bin/python3
+'''
+Example script of accessing results from runs with the samples of
+the parameter distributions.
+'''
+
+import sys
+
+from matplotlib import pyplot
+import numpy
+
+sys.path.append('..')
+import model
+
+# import seaborn
+sys.path.append('../plots')
+import seaborn_quiet as seaborn
+
+
+if __name__ == '__main__':
+    with model.results.samples.stats.open_() as results:
+        countries = results.keys()
+        print('countries =', countries)
+
+        country = 'South Africa'
+        cgroup = results[country]
+        targets = cgroup.keys()
+        print('targets =', targets)
+
+        target = 'Status Quo'
+        ctgroup = cgroup[target]
+        outcomes = ctgroup.keys()
+        print('outcomes =', outcomes)
+
+        outcome = 'infected'
+        ctogroup = ctgroup[outcome]
+        stats = ctogroup.keys()
+        print('stats =', stats)
+
+        stat = 'CI50'
+        value = ctogroup[stat]
+        print(stat, '=', value[:])
+
+        zmax = len(stats)
+        # I forgot to put 't' in the file...
+        t = numpy.linspace(2015, 2035, 20 * 120 + 1)
+        # You can also use '.' to access values.
+        pyplot.plot(t, ctogroup['median'],
+                    label = 'median', color = 'black',
+                    zorder = zmax)
+
+        CIs = sorted([s for s in stats if s.startswith('CI')])
+        colors = seaborn.color_palette()
+        for (i, CI) in enumerate(CIs):
+            value = ctogroup[CI]
+            label = '{}% CI'.format(CI[2 : ])
+            pyplot.fill_between(t, value[0], value[1],
+                                label = label,
+                                facecolor = colors[i],
+                                linewidth = 0,
+                                zorder = zmax - 1 - i)
+
+        pyplot.ylabel(outcome.replace('_', ' ').title())
+        pyplot.title(country)
+        pyplot.legend(loc = 'upper left', frameon = False)
+        pyplot.show()

### 2016-12-15 tests/targets.py

@@ -1,0 +1,27 @@
+#!/usr/bin/python3
+'''
+Test :mod:`model.targets`.
+'''
+
+import sys
+
+import numpy
+
+sys.path.append('..')
+import model
+
+
+def _print_container(c):
+    print('\n'.join('{} = {}'.format(k, v)
+                    for (k, v) in c.items()))
+
+
+if __name__ == '__main__':
+    parameters = model.parameters.Parameters('South Africa')
+    targets = model.targets.Vaccine()
+    times = [2015, 2020, 2021, 2022, 2023, 2025, 2030]
+    target_values = targets(parameters, times)
+    _print_container(target_values)
+    state = numpy.vstack(len(times) * (parameters.mode().initial_conditions, ))
+    control_rates = target_values.control_rates(state)
+    _print_container(control_rates)

### 2016-12-15 docs/cover_letter.tex
Big directory rename, plus more PNAS changes.

--- 2016-10-19 Documents/cover_letter.tex
@@
-\documentclass{jpmletter}
+\documentclass[12pt]{jpmletter}
 
@@
 
-    \opening{Dear Editorial Board of Nature,}
+    \opening{Dear Editorial Board,}
 
@@
     targets and HIV vaccination across 127 countries,'' which we are
-    submitting to \textit{Nature} as a Letter.
+    submitting to \textit{PNAS}.
 
@@
 
-    We believe our letter will be approximately 4 pages when
-    formatted.
-
     Thank you for your consideration. We look forward to hearing from

### 2016-12-15 docs/supporting_information.tex
Big directory rename, plus more PNAS changes.

--- 2016-12-15 Documents/supporting_information.tex
@@
 
-\usepackage{xr}
-\externaldocument{extended_data_fig_1}
-
 \newcommand{\md}{\mathrm{d}}
@@
 \DeclareMathOperator{\BetaPERT}{Beta-PERT}
+\DeclareMathOperator{\Beta}{B}
 
@@
 along with uninfected unvaccinated and vaccinated people
-(\autoref{model} \& \autoref{model_diag}), tailored to
-each of 127 countries.  Simulations of our model project the number of
-people in each HIV stratum from 2015 to 2035, from which statistics
-such as prevalence and incidence were calculated.  To evaluate the
-impact of the 90--90--90 and 95--95--95 UNAIDS goals, model transition
-rates were adjusted dynamically to meet intervention goals for
-diagnosis, treatment, viral suppression, and vaccination coverage
+(\autoref{model} \& \autoref{model_diag}), tailored to each of 127
+countries.  Simulations of our model project the number of people in
+each HIV stratum from 2015 to 2035, from which statistics such as
+prevalence and incidence were calculated.  To evaluate the impact of
+the 90--90--90 and 95--95--95 UNAIDS goals, model transition rates
+were adjusted dynamically to meet intervention goals for diagnosis,
+treatment, viral suppression, and vaccination coverage
 (\autoref{targets}).  Data and estimates from many sources, including
@@
 reported the results with median and percentiles
-(\autoref{uncertainty}).
+(\autoref{uncertainty}).  The effectiveness of the UNAIDS goals and
+vaccination was estimated for each of the 127 countries and aggregated
+by region and globally (\autoref{effectiveness_all_plots}).
 
@@
 outcomes using the median and percentiles.  Each country was modeled
-separately (Extended Data
-Figs.~\ref*{effectiveness_Afghanistan}--\ref*{effectiveness_Zimbabwe})
+separately
+(\hyperref[effectiveness_Afghanistan]{Figs.~\ref*{effectiveness_Afghanistan}}--\ref{effectiveness_Zimbabwe})
 and the country simulations were aggregated to calculate global and
-regional outcomes (Extended Data
-Figs.~\ref*{effectiveness_Global}--\ref*{effectiveness_Western_Europe}).
+regional outcomes
+(\hyperref[effectiveness_Global]{Figs.~\ref*{effectiveness_Global}}--\ref*{effectiveness_Western_Europe}).
 
@@
   \begin{center}
-    \input{../Codes/plots/transmission_rate.pgf}
+    \input{../src/plots/transmission_rate.pgf}
   \end{center}
@@
     $\bar{\beta}$, calculated based on UNAIDS historical estimates of
-    country prevalence and incidence.  See \autoref{model_fitting}.}
+    country prevalence and incidence.  The colored shapes are the
+    sampling distributions and the black bars are the modes of these
+    distributions.  See \autoref{model_fitting}.}
   \label{transmission_rate}
@@
    \centering
-   \input{../Codes/plots/prcc.pgf}
+   \input{../src/plots/prcc.pgf}
    \caption{Sensitivity of global HIV incidence from 2015 to 2035 to
@@
     \begin{cases}
-      \frac{(x - a)^{v - 1} (c - x)^{w - 1}}{(c - a)^{v + w - 2} B(v, w)}
+      \frac{(x - a)^{v - 1} (c - x)^{w - 1}}{(c - a)^{v + w - 2} \Beta(v, w)}
       & \text{if $a \leq x \leq c$,}
@@
   \end{equation}
-  and $B(v, w)$ is the standard beta function
+  and $\Beta(v, w)$ is the standard beta function
   \cite[\S6.2]{davis1972}.
@@
 
+\newpage
+\vspace*{3in}
+\section{Global, regional, and per-country effectiveness}
+\label{effectiveness_all_plots}
+\newpage
+
+\input{../src/plots/effectiveness_all/all}
+
 \end{document}

### 2016-12-15 drive_download.py

@@ -7,8 +7,9 @@ import drive
 
 xlsx_mime = 'application/vnd.openxmlformats-officedocument.spreadsheetml.sheet'
 files = (
-    {'filename': 'data_sheet',
-     'mimeType': xlsx_mime},
+    dict(filename = 'data_sheet',
+         mimeType = xlsx_mime,
+         path = 'src'),
 )
        
 

### 2016-12-15 src/plots/effectiveness.py

@@ -137,7 +137,7 @@ def _make_legend(fig, **kwargs):
 
 
 def _plot_one(results, country, confidence_level = 0.5, ci_bar = 0.9,
-              figsize = (5.95, 6.4), **kwargs):
+              figsize = (8.5 * 0.7, 6.5), **kwargs):
     nrows = len(common.effectiveness_measures)
     ncols = int(numpy.ceil(len(model.targets.all_) / 2))
     fig, axes = pyplot.subplots(nrows, ncols,
@@ -209,7 +209,7 @@ def plot_some(confidence_level = 0, ci_bar = 0, **kwargs):
             ncols = len(common.countries_to_plot)
             nrows = len(common.effectiveness_measures)
             fig, axes = pyplot.subplots(nrows, ncols,
-                                        figsize = (common.width_2column, 4),
+                                        figsize = (common.width_1_5column, 4),
                                         sharex = 'all', sharey = 'none')
             for (col, country) in enumerate(common.countries_to_plot):
                 for (row, stat) in enumerate(common.effectiveness_measures):

### 2016-12-15 src/plots/effectiveness_regions.py

@@ -140,7 +140,8 @@ def plot(confidence_level = 0.5, **kwargs):
         with seaborn.color_palette(common.colors_paired):
             with seaborn.axes_style('darkgrid'):
                 fig, axes = pyplot.subplots(nrows, ncols,
-                                            figsize = (common.width_2column, 4),
+                                            figsize = (common.width_1_5column,
+                                                       4),
                                             sharex = 'col', sharey = 'none')
                 for (ax, stat) in zip(axes, effectiveness_measures):
                     _plot_stat(ax, results, regions_sorted, stat,

### 2016-12-15 src/plots/infections_averted_map.py

@@ -49,7 +49,7 @@ def plot(infections_averted):
     countries = infections_averted.index
     interventions = infections_averted.columns
 
-    fig = pyplot.figure(figsize = (common.width_2column, 6))
+    fig = pyplot.figure(figsize = (common.width_1_5column, 6))
     nrows = len(interventions)
     for (i, intv) in enumerate(interventions):
         if i <  nrows - 1:
@@ -94,9 +94,9 @@ def plot(infections_averted):
 
     ticklabels = cbar.ax.get_xticklabels()
     if infections_averted.min().min() < vmin * scale:
-        ticklabels[0].set_text('≤' + ticklabels[0].get_text())
+        ticklabels[0].set_text(r'$\leq\!$' + ticklabels[0].get_text())
     if infections_averted.max().max() > vmax * scale:
-        ticklabels[-1].set_text('≥' + ticklabels[-1].get_text())
+        ticklabels[-1].set_text(r'$\geq\!$' + ticklabels[-1].get_text())
     cbar.ax.set_xticklabels(ticklabels)
     cbar.ax.tick_params(labelsize = pyplot.rcParams['font.size'])
 

### 2016-12-15 src/plots/initial_prevalence_map.py

@@ -52,9 +52,9 @@ def _main():
 
     ticklabels = cbar.ax.get_xticklabels()
     if prevalence.min() < vmin:
-        ticklabels[0].set_text('≤' + ticklabels[0].get_text())
+        ticklabels[0].set_text(r'$\leq\!$' + ticklabels[0].get_text())
     if prevalence.max() > vmax:
-        ticklabels[-1].set_text('≥' + ticklabels[-1].get_text())
+        ticklabels[-1].set_text(r'$\geq\!$' + ticklabels[-1].get_text())
     cbar.ax.set_xticklabels(ticklabels)
     cbar.ax.tick_params(labelsize = pyplot.rcParams['font.size'])
 

### 2016-12-15 src/plots/vaccine_scenarios.py

@@ -193,7 +193,7 @@ def plot_some(treatment_target = model.targets.StatusQuo()):
             nrows = len(common.effectiveness_measures)
             legend_height_ratio = 0.35
             fig, axes = pyplot.subplots(nrows, ncols,
-                                        figsize = (common.width_2column, 4),
+                                        figsize = (common.width_1_5column, 4),
                                         sharex = 'all', sharey = 'none')
             for (col, country) in enumerate(common.countries_to_plot):
                 for (row, stat) in enumerate(common.effectiveness_measures):

### 2016-12-15 docs/figs.tex
More tweaks for PNAS.

\documentclass{article}

\usepackage{common}

\usepackage[textwidth=505.5bp]{geometry}

\usepackage{graphics}

\renewcommand{\figurename}{Fig.}

\begin{document}

\begin{figure}
  \centering
  \includegraphics{../src/plots/infections_averted_map.pdf}
  \caption{Infections averted between 2015 and 2035, compared to
    maintaining status quo diagnosis, treatment, and viral
    suppression, by the UNAIDS 95–95–95 target (top); rollout of
    vaccination in 2020 while maintaining status quo levels of
    diagnosis, treatment, and viral suppression (middle); and the
    UNAIDS 95–95–95 target combined with 2020 vaccination rollout
    (bottom). Predictions are medians over 1000 model simulations in
    which parameter values were sampled from data-driven
    distributions. See Figs. S4–S140 for projections and uncertainty
    estimation globally, by region, and by country.}
\end{figure}

\begin{figure}
  \centering
  \includegraphics{../src/plots/effectiveness.pdf}
  \caption{Effectiveness of HIV interventions globally (left column)
    and for selected countries in terms of cumulative incidence (top
    row), annual incidence per million population (2nd row), PLHIV
    (3rd row), and cumulative HIV mortality (bottom row). Predictions
    are medians over 1000 model simulations in which parameter values
    were sampled from data-driven distributions. See Figs. S4–S140 for
    median and uncertainty estimates of effectiveness of HIV
    interventions for all 127 countries.}
\end{figure}

\begin{figure}
  \centering
  \includegraphics{../src/plots/effectiveness_regions.pdf}
  \caption{Effectiveness of HIV interventions for UNAIDS regions in
    terms of cumulative incidence from 2015 to 2035 (top) and number
    of PLHIV in 2035 (bottom). Medians (colored bars) and 1st and 3rd
    quartiles (black error bars) were generated from 1000 model
    simulations in which parameter values were sampled from
    data-driven distributions. See Figs. S4–S140 for median and
    uncertainty estimates of the effectiveness of HIV interventions
    for UNAIDS regions.}
\end{figure}

\begin{figure}
  \centering
  \includegraphics{../src/plots/vaccine_scenarios.pdf}
  \caption{Scenario analysis for vaccination under six strategies,
    globally (left column) and for selected countries (remaining
    columns), with variation in vaccine efficacy, ultimate coverage,
    initiation date of vaccination rollout, and rate of
    scale-up. Vaccine scenario projections are generated from
    simulations parametrized with modal values.}
\end{figure}

\end{document}

### 2016-12-15 plots/effectiveness.py
More tweaks for PNAS.

@@ -227,7 +227,10 @@ def plot_some(confidence_level = 0, ci_bar = 0, **kwargs):
 
                     ax.xaxis.set_tick_params(labelsize = 5)
                     ax.yaxis.set_major_locator(ticker.MaxNLocator(nbins = 4))
-                    ax.title.set_verticalalignment('bottom')
+                    if country_label is not None:
+                        t = ax.set_title(ax.get_title().replace(' ', '\n'),
+                                         va = 'center')
+                        t.set_y(1.07)
 
             _make_legend(fig)
 

### 2017-01-31 docs/response.tex
Added response to PNAS reviews.

\documentclass[12pt]{jpmletter}

\newcommand{\section}[1]{\textbf{#1}\\}
\newenvironment{original}{\it}{}
\usepackage[rightmargin=0pt]{quoting}

\begin{document}
  \begin{letter}{}

    \opening{Dear Editor,}

    Thank you very much for the opportunity to re-submit our
    manuscript entitled ``Effectiveness of UNAIDS targets and HIV
    vaccination across 127 countries''. We are grateful for the
    thoughtfulness of the reviews and the appreciation for the
    timeliness and potential impactfulness of our paper. As detailed
    below, we have revised the manuscript to address the reviewers’
    suggestions and questions. The reviewers’ comments have been most
    helpful in strengthening our manuscript.

    Thank you for your consideration. We look forward to hearing from
    you.

    \closing{Sincerely,}

    \newpage

    \section{Editor's Remarks to Author}
    \begin{original}
      This paper provides important insights into the impact of
      a partially protective HIV vaccine of the trajectory of the HIV
      pandemic in various regions of the world. The authors should
      make the minor revisions associated with the comments of
      reviewers \#1 and \#3.
    \end{original}

    Thank you for your feedback regarding our manuscript. As detailed
    in our point-by-point response, we have addressed the revisions
    requested.

    \section{Reviewer \#1}
    \begin{original}
      Suitable Quality?: Yes\\
      Sufficient General Interest?: Yes\\
      Conclusions Justified?: Yes\\
      Clearly Written?: No\\
      Procedures Described?: Yes\\
      Supplemental Material Warranted?: Yes

      This is an exciting manuscript that demonstrates the power of a
      partially protective vaccine to have an important impact on
      HIV/AIDS incidence and the number of people living with HIV
      (PLHIV), especially when used in programs of vaccine-linked
      chemotherapy with ART.
    \end{original}

    Thank you for your appreciation of our work.

    \begin{original}
      1–4. I found the manuscript challenging to read, in part
      because so much information had to be compressed in the brief
      report template used by PNAS. But also because I did not think
      it was well organized—too often the manuscript lapsed into a
      series of unrelated facts. Possibly some organization with
      subheadings might help, if that's acceptable—similar to the
      Global Burden of Disease capstone papers published in the
      Lancet. For example, it would be been helpful to have brief
      paragraphs to look at the impact of vaccination on each of the
      major regions of the world. Doing so would help address some
      interesting features of the model. For example, for the
      incidence data it was not clear to me why the impact of the
      vaccine is so much greater in African countries than in India,
      also for PLHIV. Dividing by region might also be instructive in
      terms of where we need to consider introducing or rolling out
      the vaccine first.
    \end{original}

    Thank you for the helpful suggestion of subheadings which we have
    implemented to distinguish global, regional, and country-level
    model projections and agree have clarified the organization of our
    results. We have also added the following sentences in the
    regional projections section:
    \begin{quoting}
      The UNAIDS targets based on antiviral treatment affect the
      number of PLHIV by prolonging survival (which increases PLHIV
      compared to status quo) and by reducing transmission (which
      decreases PLHIV). By contrast, vaccination averts new
      infections, reducing PLHIV without the concomitant improvement
      in survival. This transmission reduction achieved by vaccination
      is greater in African regions that have a high incidence,
      including Swaziland, Uganda, and South Africa, than in Asian
      countries with lower incidence, such as India (Figure 2).
    \end{quoting}

    \begin{original}
      5. It was not clear how long it would take to vaccinate
      a fully immunized individual, and the optimal age group. It
      would have helped to have a brief summary of the vaccine's
      target product profile (TPP).
    \end{original}

    Following this suggestion as well as the details provided for
    inclusion by Reviewer 3, we added a description of the target
    product profile from the HVTN 100/702 trials and expanded the
    description of the most recent vaccine candidate in the context of
    its predecessor:
    \begin{quoting}
      The Phase III RV144 trial in Thailand demonstrated efficacies of
      60.5\% after 1 year and of 31.2\% after 3.5 years among
      participants aged 18 to 30 years, with vaccine doses
      administered at weeks 0, 4, 12, and 24. Preliminary results of
      the HVTN 100 candidate in South Africa, which builds on RV144,
      evidence a more robust immune response than its predecessor in
      participants aged 18 to 40 (Gray et al. 2016). Given the safety
      and immunogenicity demonstrated by HVTN 100, the HVTN 702 study
      was initiated in November 2016 to determine HIV vaccine efficacy
      in 14 sites across South Africa  (First New HIV Vaccine Efficacy
      Study ...). The trial is enrolling 18 to 35 year olds with
      vaccination scheduled at months 0, 1, 3, 6, and 12. Additional
      advances in HIV vaccine research have included candidates based
      on adenovirus serotype vectors (Baden et al. 2016). Motivated by
      strong pre-clinical scientific underpinnings, three phase I/II
      trials have been initiated as part of the Ad26/MVA/trimer gp140
      program and an efficacy study is planned for later in
      2017. Furthermore, investigation into the prophylactic potential
      of broadly acting neutralizing antibodies has provided
      preliminary evidence into enhanced viral clearance (Fauci 2016).
    \end{quoting}

    \begin{original}
      6. Finally I thought it might be helpful to briefly discuss the
      implications of other partially protective vaccines. More and
      more we're seeing new vaccines come online, which do not have
      the high levels of protection we associate with say measles
      vaccine. For example, in addition to HIV, there's the next
      generation TB, malaria, and other parasite vaccines—increasingly
      such vaccines will not replace existing drug therapies but
      instead will be used alongside them—sometimes called
      ``vaccine-linked chemotherapy''. The analysis here emphasizes
      why and how vaccine-linked chemotherapy can be successfully
      modeled and applied and that should be mentioned.
    \end{original}

    Thank you for this excellent suggestion. In the second paragraph
    of the introduction, we have added:
    \begin{quoting}
      At the frontier of vaccinology for many diseases, including
      malaria, TB, hookworm, dengue and HIV, is the development of
      partially efficacious vaccines (Evans et al. 2016; Efficacy and
      safety of RTS,S/AS01 mal...; Hotez et al. 2013). In cases where
      such vaccines may not alone be sufficient to eliminate a given
      disease, they may nonetheless be an component of disease control
      in combination with drug therapies. Here we specifically
      evaluate such vaccine-linked chemotherapy approaches (Hotez
      2011) in the context of HIV.  Impending opportunities for
      widespread availability warrants evaluation of the impact of
      packaged interventions, such as vaccine-linked chemotherapy, to
      guide operational policy decisions.
    \end{quoting}

    In the discussion we have also added:
    \begin{quoting}
      Our findings and modeling approaches may have conceptual
      applicability beyond HIV in exemplifying the added benefits of
      partially protective vaccines for other diseases implemented in
      conjunction with drug therapies. In general, rather than
      expecting vaccines with perfect efficacy to replace existing
      drug therapies, it is important to appreciate that a
      multifaceted strategy that includes partially protective
      vaccines may nonetheless be necessary to achieve elimination, as
      we demonstrated for HIV.
    \end{quoting}

    \section{Reviewer \#2}
    \begin{original}
      Suitable Quality?: Yes \\
      Sufficient General Interest?: Yes \\
      Conclusions Justified?: Yes \\
      Clearly Written?: Yes \\
      Procedures Described?: Yes \\
      Supplemental Material Warranted?: Yes

      As I am not a mathematical modeler, my thoughts on this article
      relate to its overall message and presentation to an audience
      interested in HIV prevention and vaccine effectiveness in
      general.

      The bottom line is I like this article for it illustrates some
      interesting issues about a partially effective vaccine, its
      effect on incidence and how it can work synergistically with HIV
      treatment programs such as test and treat. This
      fact/illustration is the most provocative part of the paper and
      in my opinion could be highlighted a bit more, by making the US
      graphs a bit more present in the paper. For example, Figure
      S11—elevate that to a panel to Figure 3, perhaps with Eastern
      and Southern Africa (Figure S7) to show the similarities in
      shape/concept. The paper is well written. The importance of the
      concept is high.
    \end{original}

    Thank you for your comments. We agree that the impact of a
    partially effective vaccine alone or in combination with treatment
    is a provocative contribution to the discussion around HIV vaccine
    development. Elevating supplementary figures to the main text
    would further highlight the effects across different settings, yet
    we are concerned that the addition of panels―while keeping with
    the PNAS formatting requirements―would jeopardize the
    discernibility of Figure 3. Moreover, HIV in North America (Figure
    S11) is dominated by HIV in the United States, which is in Figure
    2. To draw attention to the trends in the US graphs, we now
    include references to Figures S8 and S11 in the regional
    projections section.

    In the discussion, we have also added the following text to
    underscore the synergy of HIV vaccination with other complementary
    approaches:
    \begin{quoting}
      Our findings and modeling approaches may have conceptual
      applicability beyond HIV in exemplifying the added benefits of
      partially protective vaccines for other diseases implemented in
      conjunction with drug therapies. In general, rather than
      expecting vaccines with perfect efficacy to replace existing
      drug therapies, it is important to appreciate that a
      multifaceted strategy that includes partially protective
      vaccines may nonetheless be necessary to achieve elimination, as
      we demonstrated for HIV.
    \end{quoting}

    \section{Reviewer \#3}
    \begin{original}
      Suitable Quality?: Yes\\
      Sufficient General Interest?: Yes\\
      Conclusions Justified?: Yes\\
      Clearly Written?: Yes\\
      Procedures Described?: Yes\\
      Supplemental Material Warranted?: Yes

      Medlock and colleagues describe an infectious disease modeling
      approach to evaluating the impact of HIV vaccines of varying
      degrees of efficacy and global coverage to the global HIV
      pandemic. The paper is concise and well written. The conclusions
      are within the scope of stated limitations of the approach. This
      paper will be of much interest to the field and will be cited by
      many in the HIV vaccine field. Coming at a time of growing
      HIV/AIDS complacency, it's timing couldn't be better. Attention
      to the points below would strengthen the manuscript.

      1. The authors should add a sentence or two describing other HIV
      prevention modalities, such as adult medical male circumcision,
      PrEP, antibody mediated protection, and treatment as prevention,
      that will likely join an effective HIV vaccine as tools to
      mitigate HIV transmission.
    \end{original}

    We have added the following to the discussion section:
    \begin{quoting}
      The vaccination and treatment as prevention considered here
      would be complementary to other HIV prevention modalities, such
      as adult medical male circumcision (Bailey et al. 2007),
      pre-exposure prophylaxis (PrEP) (Walensky et al. 2012) and
      antibody-mediated protection (Byrareddy et al. 2014). The
      combination of these interventions is likely to have synergistic
      effects on mitigating HIV transmission.
    \end{quoting}

    \begin{original}
      2. While HVTN 100 was an important study, and the final safety
      and immunogenicity study of ALVAC vCP2348 + gp120 bivalent C
      that led to the decision to launch the HVTN 702 HIV vaccine
      efficacy study, it is the latter study that is more relevant to
      the authors' thesis. HVTN 702 started in mid-November 2016; it
      was highlighted in many 01 December 2016 World AIDS Day
      announcements. This is the first HIV efficacy study to launch in
      seven years and builds on the success of the only HIV vaccine
      efficacy study that showed efficacy, RV 144, which the authors
      cite, but they need to connect HVTN 702 to RV 144 and HVTN 100
      to complete the historical and scientific context.
    \end{original}

    Thank you for this important context.  We have provided more
    context to connect the RV 144, HVTN 100, and the HVTN 702 trials,
    as suggested, in the introduction:
    \begin{quoting}
      The Phase III RV144 trial in Thailand demonstrated efficacies of
      60.5\% after 1 year and of 31.2\% after 3.5 years among
      participants aged 18 to 30 years, with vaccine doses
      administered at weeks 0, 4, 12, and 24. Preliminary results of
      the HVTN 100 candidate in South Africa, which builds on RV144,
      evidence a more robust immune response than its predecessor in
      participants aged 18 to 40 (Gray et al. 2016). Given the safety
      and immunogenicity demonstrated by HVTN 100, the HVTN 702 study
      was initiated in November 2016 to determine HIV vaccine efficacy
      in 14 sites across South Africa (First New HIV Vaccine Efficacy
      Study ...). The trial is enrolling 18 to 35 year olds with
      vaccination scheduled at months 0, 1, 3, 6, and 12.
    \end{quoting}

    \begin{original}
      3. While HIV vaccine development based on ALVAC + gp120 products
      are mentioned in the manuscript, the other major effort in the
      field, the Ad26/MVA/trimer gp140 program is not. This should be
      corrected. The Ad26 program has strong pre-clinical scientific
      underpinnings that have supported advancement into phase I/II
      studies with a first phase IIb efficacy study planned for summer
      2017. While the authors do note that protein immunogens designed
      to elicit broad and potent neutralizing antibody against the
      HIV-1 envelope protein are being explored, they are in much
      earlier clinical development than either the ALVAC + gp120 or
      Ad26 programs.
    \end{original}

    We have revised the introduction to reference both efforts
    involving broadly neutralizing antibodies and contributions to
    date of the Ad26/MVA/trimer gp140 program:
    \begin{quoting}
      Additional advances in HIV vaccine research have included
      candidates based on adenovirus serotype vectors. Motivated by
      strong pre-clinical scientific underpinnings, three phase I/II
      trials have been initiated as part of the Ad26/MVA/trimer gp140
      program and an efficacy study is planned for later in
      2017. Furthermore, investigation into the prophylactic potential
      of broadly acting neutralizing antibodies has provided
      preliminary evidence into enhanced viral clearance through
      immunotherapy.
    \end{quoting}

    \begin{original}
      4. Lines 54–55: International interest in HIV vaccines is
      codified by national HIV vaccine plans published by the
      governments of a number of countries (U.S., Canada, Thailand,
      Nigeria, etc). The fact that national governments have embraced
      HIV vaccine as part of national efforts to control HIV/AIDS is
      significant as it reveals that governments are reacting to the
      data in papers that the authors have cited such as refs 18 \&
      19. Those governments will read this paper with much interest.
    \end{original}

    Thank you for your comments supporting the usefulness of our
    manuscript. We are indeed hopeful that our study can contribute to
    support the efforts for HIV vaccine development and deployment. We
    added following in our significance statement:
    \begin{quoting}
      At a time when governments around the world are recognizing the
      role of vaccination in HIV/AIDS control efforts, our study
      provides country-specific impact of a partially effective HIV
      vaccine and illustrates its importance in elimination of HIV
      transmission globally.
    \end{quoting}

  \end{letter}

\end{document}

### 2017-01-31 docs/response.tex
Updated response letter.

@@
 \newenvironment{original}{\it}{}
-\usepackage[rightmargin=0pt]{quoting}
+\usepackage[rightmargin=0pt, vskip=0pt]{quoting}
 
@@
     Thank you very much for the opportunity to re-submit our
-    manuscript entitled ``Effectiveness of UNAIDS targets and HIV
+    manuscript ``Effectiveness of UNAIDS targets and HIV
     vaccination across 127 countries''. We are grateful for the
@@
 
-    Thank you for the helpful suggestion of subheadings which we have
-    implemented to distinguish global, regional, and country-level
-    model projections and agree have clarified the organization of our
-    results. We have also added the following sentences in the
+    Thank you for the helpful suggestion of subheadings to clarify the
+    organization of our results: we added subheadings to distinguish
+    global, regional, country-level model projections, along with
+    uncertainty analysis of vaccine characteristics and sensitivity
+    analysis.  We have also added the following sentences in the
     regional projections section:
@@
       infections, reducing PLHIV without the concomitant improvement
-      in survival. This transmission reduction achieved by vaccination
-      is greater in African regions that have a high incidence,
-      including Swaziland, Uganda, and South Africa, than in Asian
-      countries with lower incidence, such as India (Figure 2).
+      in survival.  This transmission reduction achieved by
+      vaccination is greater in African regions that have a high
+      incidence, including Swaziland, Uganda, and South Africa, than
+      in Asian countries with lower incidence, such as India (Figure
+      2).
     \end{quoting}
@@
     Following this suggestion as well as the details provided for
-    inclusion by Reviewer 3, we added a description of the target
+    inclusion by Reviewer \#3, we added a description of the target
     product profile from the HVTN 100/702 trials and expanded the
@@
     \begin{quoting}
-      The Phase III RV144 trial in Thailand demonstrated efficacies of
-      60.5\% after 1 year and of 31.2\% after 3.5 years among
-      participants aged 18 to 30 years, with vaccine doses
-      administered at weeks 0, 4, 12, and 24. Preliminary results of
-      the HVTN 100 candidate in South Africa, which builds on RV144,
-      evidence a more robust immune response than its predecessor in
-      participants aged 18 to 40 (Gray et al. 2016). Given the safety
-      and immunogenicity demonstrated by HVTN 100, the HVTN 702 study
-      was initiated in November 2016 to determine HIV vaccine efficacy
-      in 14 sites across South Africa  (First New HIV Vaccine Efficacy
-      Study ...). The trial is enrolling 18 to 35 year olds with
-      vaccination scheduled at months 0, 1, 3, 6, and 12. Additional
-      advances in HIV vaccine research have included candidates based
-      on adenovirus serotype vectors (Baden et al. 2016). Motivated by
-      strong pre-clinical scientific underpinnings, three phase I/II
-      trials have been initiated as part of the Ad26/MVA/trimer gp140
-      program and an efficacy study is planned for later in
-      2017. Furthermore, investigation into the prophylactic potential
-      of broadly acting neutralizing antibodies has provided
-      preliminary evidence into enhanced viral clearance (Fauci 2016).
+      For example, the phase III RV144 trial in Thailand of an
+      ALVAC-HIV/gp120 regimen demonstrated efficacies of 60.5\% after
+      1 year and of 31.2\% after 3.5 years among participants aged 18
+      to 30 years, with vaccine doses administered at weeks 0, 4, 12,
+      and 24 (XX). Results of the HVTN 100 trial in South Africa,
+      which used an updated ALVAC-HIV/gp120 regimen, showed a more
+      robust immune response than RV144 in participants aged 18 to 40
+      (XX).  Given the safety and immunogenicity demonstrated by HVTN
+      100, the HVTN 702 study was initiated in November 2016 to
+      determine HIV vaccine efficacy in 14 sites across South Africa
+      (XX). The trial is enrolling 18 to 35 year olds with vaccination
+      scheduled at months 0, 1, 3, 6, and 12.  Other advances in
+      research on HIV vaccines have included candidates based on
+      adenovirus vectors (XX).  Motivated by strong pre-clinical
+      scientific underpinnings, three phase I/II trials have been
+      initiated as part of the Ad26/MVA/trimer gp140 program and an
+      efficacy study is planned for later in 2017 (XX).  In addition,
+      investigation into the prophylactic potential of broadly acting
+      neutralizing antibodies has provided preliminary evidence for
+      enhanced viral clearance through immunotherapy (XX).
     \end{quoting}
@@
     \begin{quoting}
-      At the frontier of vaccinology for many diseases, including
-      malaria, TB, hookworm, dengue and HIV, is the development of
-      partially efficacious vaccines (Evans et al. 2016; Efficacy and
-      safety of RTS,S/AS01 mal...; Hotez et al. 2013). In cases where
-      such vaccines may not alone be sufficient to eliminate a given
-      disease, they may nonetheless be an component of disease control
-      in combination with drug therapies. Here we specifically
-      evaluate such vaccine-linked chemotherapy approaches (Hotez
-      2011) in the context of HIV.  Impending opportunities for
-      widespread availability warrants evaluation of the impact of
-      packaged interventions, such as vaccine-linked chemotherapy, to
-      guide operational policy decisions.
+      Likewise, at the frontier of vaccinology for myriad other
+      diseases, including malaria, TB, hookworm, and dengue, is the
+      development of partially efficacious vaccines (XX). In cases
+      where vaccines may not alone be sufficient for disease
+      elimination, they may nonetheless be a component of disease
+      control in combination with drug therapies. Here we evaluate
+      such vaccine-linked chemotherapy approaches (XX) for HIV.
     \end{quoting}
@@
       Our findings and modeling approaches may have conceptual
-      applicability beyond HIV in exemplifying the added benefits of
-      partially protective vaccines for other diseases implemented in
-      conjunction with drug therapies. In general, rather than
-      expecting vaccines with perfect efficacy to replace existing
-      drug therapies, it is important to appreciate that a
-      multifaceted strategy that includes partially protective
-      vaccines may nonetheless be necessary to achieve elimination, as
-      we demonstrated for HIV.
+      applicability beyond HIV by showing the added benefits of
+      partially protective vaccines for other diseases when
+      implemented in conjunction with drug therapies. In general,
+      rather than expecting vaccines with perfect efficacy to replace
+      existing drug therapies, a multifaceted strategy that includes
+      partially protective vaccines may nonetheless be necessary to
+      achieve elimination, as we demonstrated for HIV.
     \end{quoting}
@@
     would further highlight the effects across different settings, yet
-    we are concerned that the addition of panels―while keeping with
-    the PNAS formatting requirements―would jeopardize the
-    discernibility of Figure 3. Moreover, HIV in North America (Figure
-    S11) is dominated by HIV in the United States, which is in Figure
-    2. To draw attention to the trends in the US graphs, we now
-    include references to Figures S8 and S11 in the regional
-    projections section.
-
-    In the discussion, we have also added the following text to
-    underscore the synergy of HIV vaccination with other complementary
+    we are concerned that the addition of panels would jeopardize the
+    discernibility of Figure 3. Instead, to draw attention to the
+    regional trends in the US graphs, we now include references to
+    Figures S8 \& S11 in the regional projections section. In the
+    Discussion, we have also added the following text to underscore
+    the synergy of HIV vaccination with other complementary
     approaches:
@@
     \begin{quoting}
-      The vaccination and treatment as prevention considered here
-      would be complementary to other HIV prevention modalities, such
-      as adult medical male circumcision (Bailey et al. 2007),
-      pre-exposure prophylaxis (PrEP) (Walensky et al. 2012) and
-      antibody-mediated protection (Byrareddy et al. 2014). The
-      combination of these interventions is likely to have synergistic
-      effects on mitigating HIV transmission.
+      The vaccination and treatment as prevention approaches
+      considered here would be complementary to other HIV prevention
+      modalities, such as adult medical male circumcision (XX),
+      pre-exposure prophylaxis (PrEP, XX) and antibody-mediated
+      protection (XX). The combination of these interventions is
+      likely to have synergistic effects on mitigating HIV
+      transmission.
     \end{quoting}
@@
     \begin{quoting}
-      The Phase III RV144 trial in Thailand demonstrated efficacies of
-      60.5\% after 1 year and of 31.2\% after 3.5 years among
-      participants aged 18 to 30 years, with vaccine doses
-      administered at weeks 0, 4, 12, and 24. Preliminary results of
-      the HVTN 100 candidate in South Africa, which builds on RV144,
-      evidence a more robust immune response than its predecessor in
-      participants aged 18 to 40 (Gray et al. 2016). Given the safety
-      and immunogenicity demonstrated by HVTN 100, the HVTN 702 study
-      was initiated in November 2016 to determine HIV vaccine efficacy
-      in 14 sites across South Africa (First New HIV Vaccine Efficacy
-      Study ...). The trial is enrolling 18 to 35 year olds with
-      vaccination scheduled at months 0, 1, 3, 6, and 12.
+      For example, the phase III RV144 trial in Thailand of an
+      ALVAC-HIV/gp120 regimen demonstrated efficacies of 60.5\% after
+      1 year and of 31.2\% after 3.5 years among participants aged 18
+      to 30 years, with vaccine doses administered at weeks 0, 4, 12,
+      and 24 (XX). Results of the HVTN 100 trial in South Africa,
+      which used an updated ALVAC-HIV/gp120 regimen, showed a more
+      robust immune response than RV144 in participants aged 18 to 40
+      (XX).  Given the safety and immunogenicity demonstrated by HVTN
+      100, the HVTN 702 study was initiated in November 2016 to
+      determine HIV vaccine efficacy in 14 sites across South Africa
+      (XX). The trial is enrolling 18 to 35 year olds with vaccination
+      scheduled at months 0, 1, 3, 6, and 12.
     \end{quoting}
@@
     \begin{quoting}
-      Additional advances in HIV vaccine research have included
-      candidates based on adenovirus serotype vectors. Motivated by
-      strong pre-clinical scientific underpinnings, three phase I/II
+      Other advances in HIV vaccine research have included candidates
+      based on adenovirus vectors (XX). Motivated by strong
+      pre-clinical scientific underpinnings (XX), three phase I/II
       trials have been initiated as part of the Ad26/MVA/trimer gp140
-      program and an efficacy study is planned for later in
-      2017. Furthermore, investigation into the prophylactic potential
+      program and an efficacy study is planned for later in 2017
+      (XX). In addition, investigation into the prophylactic potential
       of broadly acting neutralizing antibodies has provided
-      preliminary evidence into enhanced viral clearance through
-      immunotherapy.
+      preliminary evidence for enhanced viral clearance through
+      immunotherapy (XX).
     \end{quoting}
@@
     \begin{quoting}
-      At a time when governments around the world are recognizing the
-      role of vaccination in HIV/AIDS control efforts, our study
-      provides country-specific impact of a partially effective HIV
-      vaccine and illustrates its importance in elimination of HIV
-      transmission globally.
+      Upon the advent of international partnerships to conduct HIV
+      vaccine trials and in anticipation of including vaccination in
+      HIV/AIDS control programs, our study provides country-specific
+      impacts of a partially effective HIV vaccine and demonstrates
+      its importance to the elimination of HIV transmission globally.
     \end{quoting}

### 2017-02-03 docs/response.tex
Tweak for submission.

@@
       to 30 years, with vaccine doses administered at weeks 0, 4, 12,
-      and 24 (XX). Results of the HVTN 100 trial in South Africa,
+      and 24 (9). Results of the HVTN 100 trial in South Africa,
       which used an updated ALVAC-HIV/gp120 regimen, showed a more
       robust immune response than RV144 in participants aged 18 to 40
-      (XX).  Given the safety and immunogenicity demonstrated by HVTN
+      (10).  Given the safety and immunogenicity demonstrated by HVTN
       100, the HVTN 702 study was initiated in November 2016 to
       determine HIV vaccine efficacy in 14 sites across South Africa
-      (XX). The trial is enrolling 18 to 35 year olds with vaccination
-      scheduled at months 0, 1, 3, 6, and 12.  Other advances in
+      (11). The trial is enrolling 18 to 35 year olds with vaccination
+      scheduled at months 0, 1, 3, 6, and 12 (12).  Other advances in
       research on HIV vaccines have included candidates based on
-      adenovirus vectors (XX).  Motivated by strong pre-clinical
-      scientific underpinnings, three phase I/II trials have been
+      adenovirus vectors (13).  Motivated by strong pre-clinical
+      scientific underpinnings (14), three phase I/II trials have been
       initiated as part of the Ad26/MVA/trimer gp140 program and an
-      efficacy study is planned for later in 2017 (XX).  In addition,
+      efficacy study is planned for later in 2017 (15).  In addition,
       investigation into the prophylactic potential of broadly acting
       neutralizing antibodies has provided preliminary evidence for
-      enhanced viral clearance through immunotherapy (XX).
+      enhanced viral clearance through immunotherapy (16).
     \end{quoting}
@@
       diseases, including malaria, TB, hookworm, and dengue, is the
-      development of partially efficacious vaccines (XX). In cases
+      development of partially efficacious vaccines (17--19). In cases
       where vaccines may not alone be sufficient for disease
@@
       control in combination with drug therapies. Here we evaluate
-      such vaccine-linked chemotherapy approaches (XX) for HIV.
+      such vaccine-linked chemotherapy approaches (20) for HIV.
     \end{quoting}
@@
       considered here would be complementary to other HIV prevention
-      modalities, such as adult medical male circumcision (XX),
-      pre-exposure prophylaxis (PrEP, XX) and antibody-mediated
-      protection (XX). The combination of these interventions is
+      modalities, such as adult medical male circumcision (31),
+      pre-exposure prophylaxis (PrEP, 32) and antibody-mediated
+      protection (33). The combination of these interventions is
       likely to have synergistic effects on mitigating HIV
@@
       to 30 years, with vaccine doses administered at weeks 0, 4, 12,
-      and 24 (XX). Results of the HVTN 100 trial in South Africa,
+      and 24 (9). Results of the HVTN 100 trial in South Africa,
       which used an updated ALVAC-HIV/gp120 regimen, showed a more
       robust immune response than RV144 in participants aged 18 to 40
-      (XX).  Given the safety and immunogenicity demonstrated by HVTN
+      (10).  Given the safety and immunogenicity demonstrated by HVTN
       100, the HVTN 702 study was initiated in November 2016 to
       determine HIV vaccine efficacy in 14 sites across South Africa
-      (XX). The trial is enrolling 18 to 35 year olds with vaccination
-      scheduled at months 0, 1, 3, 6, and 12.
+      (11). The trial is enrolling 18 to 35 year olds with vaccination
+      scheduled at months 0, 1, 3, 6, and 12 (12).
     \end{quoting}
@@
       Other advances in HIV vaccine research have included candidates
-      based on adenovirus vectors (XX). Motivated by strong
-      pre-clinical scientific underpinnings (XX), three phase I/II
+      based on adenovirus vectors (13). Motivated by strong
+      pre-clinical scientific underpinnings (14), three phase I/II
       trials have been initiated as part of the Ad26/MVA/trimer gp140
       program and an efficacy study is planned for later in 2017
-      (XX). In addition, investigation into the prophylactic potential
+      (15). In addition, investigation into the prophylactic potential
       of broadly acting neutralizing antibodies has provided
       preliminary evidence for enhanced viral clearance through
-      immunotherapy (XX).
+      immunotherapy (16).
     \end{quoting}

### 2017-02-06 docs/cover_letter.tex
Tweak.
Reorganize directories like master.

--- 2016-08-22 Documents/cover_letter.tex
@@
     targets and HIV vaccination across 127 countries,'' which we are
-    submitting to Science as a Report.
+    submitting to \textit{Science} as a Report.
 

### 2017-02-06 build_percentiles.py
Reorganize directories like master.

@@ -1,0 +1,68 @@
+#!/usr/bin/python3
+'''
+Update the cache of percentiles from the runs with parameter distributions.
+'''
+
+import itertools
+import warnings
+
+import numpy
+import tables
+
+import model
+
+
+regions_and_countries = model.regions.all_ + model.datasheet.get_country_list()
+
+targets = model.target.all_
+
+_stats_to_dump = ['new_infections', 'infected', 'incidence_per_capita',
+                  'AIDS', 'dead']
+
+CI_levels = ['median', 50, 80, 90, 95, 99]
+
+
+def _main():
+    with model.results.samples.stats.open_(mode = 'a') as h5file:
+        for (region_or_country, target) in itertools.product(
+                regions_and_countries, targets):
+            target = str(target)
+            results_exist = model.results.samples.exists(region_or_country,
+                                                         target)
+            stats_exist = '/{}/{}'.format(region_or_country, target) in h5file
+            if results_exist and (not stats_exist):
+                print('{}, {}'.format(region_or_country, target))
+                with model.results.samples.open_(region_or_country,
+                                                 target) as results:
+                    with warnings.catch_warnings():
+                        warnings.filterwarnings(
+                            'ignore',
+                            category = tables.NaturalNameWarning)
+                        # For NaNs.
+                        warnings.filterwarnings(
+                            'ignore',
+                            category = RuntimeWarning)
+                        rtgroup = h5file.create_group(
+                            '/{}'.format(region_or_country),
+                            target,
+                            createparents = True)
+                        for stat in _stats_to_dump:
+                            vals = getattr(results, stat)
+                            rtsgroup = h5file.create_group(rtgroup,
+                                                           stat)
+                            for lev in CI_levels:
+                                if lev == 'median':
+                                    obj = numpy.median(vals, axis = 0)
+                                    name = 'median'
+                                else:
+                                    obj = numpy.percentile(vals,
+                                                           [50 - lev / 2,
+                                                            50 + lev / 2],
+                                                           axis = 0)
+                                    name = 'CI{}'.format(lev)
+                                h5file.create_carray(rtsgroup, name,
+                                                     obj = obj)
+
+
+if __name__ == '__main__':
+    _main()

### 2017-02-06 docs/conf.py

@@ -1,0 +1,316 @@
+# -*- coding: utf-8 -*-
+#
+# 90-90-90 documentation build configuration file, created by
+# sphinx-quickstart on Wed Mar  2 11:37:36 2016.
+#
+# This file is execfile()d with the current directory set to its
+# containing dir.
+#
+# Note that not all possible configuration values are present in this
+# autogenerated file.
+#
+# All configuration values have a default; values that are commented out
+# serve to show the default.
+
+import sys
+import os
+
+# If extensions (or modules to document with autodoc) are in another directory,
+# add these directories to sys.path here. If the directory is relative to the
+# documentation root, use os.path.abspath to make it absolute, like shown here.
+#sys.path.insert(0, os.path.abspath('.'))
+sys.path.insert(0, os.path.abspath('..'))
+
+# -- General configuration ------------------------------------------------
+
+# If your documentation needs a minimal Sphinx version, state it here.
+#needs_sphinx = '1.0'
+
+# Add any Sphinx extension module names here, as strings. They can be
+# extensions coming with Sphinx (named 'sphinx.ext.*') or your custom
+# ones.
+extensions = [
+    'sphinx.ext.autodoc',
+    # 'sphinx.ext.doctest',
+    'sphinx.ext.intersphinx',
+    'sphinx.ext.todo',
+    'sphinx.ext.coverage',
+    'sphinx.ext.mathjax',
+    'sphinx.ext.ifconfig',
+    'sphinx.ext.viewcode',
+]
+
+# Add any paths that contain templates here, relative to this directory.
+templates_path = ['_templates']
+
+# The suffix(es) of source filenames.
+# You can specify multiple suffix as a list of string:
+# source_suffix = ['.rst', '.md']
+source_suffix = '.rst'
+
+# The encoding of source files.
+#source_encoding = 'utf-8-sig'
+
+# The master toctree document.
+master_doc = 'index'
+
+# General information about the project.
+project = u'90-90-90'
+author = u'Meagan Fitzpatrick, Alison Galvani, Jan Medlock, Abhishek Pandey, Alyssa Parpia'
+copyright = u'2015–2016: ' + author
+
+# The version info for the project you're documenting, acts as replacement for
+# |version| and |release|, also used in various other places throughout the
+# built documents.
+#
+# The short X.Y version.
+# version = u'1'
+import subprocess
+import shlex
+cmd = shlex.split('git describe --tags --always')
[…]

### 2017-02-06 drive/__init__.py

@@ -1,0 +1,5 @@
+'''
+Transfer files to and from Google Drive.
+'''
+
+from .driver import *

### 2017-02-06 drive_download.py

@@ -1,0 +1,22 @@
+#!/usr/bin/python3
+'''
+Download files from Google Drive.
+'''
+
+import drive
+
+xlsx_mime = 'application/vnd.openxmlformats-officedocument.spreadsheetml.sheet'
+files = (
+    {'filename': 'data_sheet',
+     'mimeType': xlsx_mime},
+)
+       
+
+# 90-90-90/Codes
+folderId = '0B5E-ra0QvBe-bjlVWGVzREgwbTg'
+
+
+if __name__ == '__main__':
+    with drive.Driver(parent = folderId) as d:
+        for f in files:
+            d.export_if_newer(**f)

### 2017-02-06 model/control_rates.py

@@ -1,0 +1,119 @@
+'''
+Compute the value of the control rates.
+'''
+
+import numpy
+
+from . import proportions
+
+
+class ControlRatesMax:
+    '''
+    Maximum control rates.
+    '''
+    diagnosis = 1
+    treatment = 10
+    nonadherence = 1
+    vaccination = 1
+
+
+def ramp(x, tol = 0.001):
+    r'''
+    Piecewise linear
+
+    .. math:: f(x) =
+              \begin{cases}
+              0 & \text{if $x \leq 0$},
+              \\
+              \frac{x}{\epsilon} & \text{if $0 \leq x \leq \epsilon$},
+              \\
+              1 & \text{if $x \geq \epsilon$},
+              \end{cases}
+
+    where :math:`\epsilon` is `tol`.
+    '''
+    return numpy.clip(x / tol, 0, 1)
+
+
+def get(t, state, target, parameters):
+    r'''
+    Calculate control rates from the current proportions diagnosed, etc.
+
+    Rates for diagnosis, treatment, nonadherence, & vaccination
+    are piecewise constant.
+
+    The diagnosis rate is:
+
+    .. math:: r_{\text{diagnosis}} =
+              \begin{cases}
+              R_{\text{diagnosis}}
+              &
+              \text{if $p_{\text{diagnosed}} < T_{\text{diagnosed}}(t)$},
+              \\
+              0 & \text{otherwise}.
+              \end{cases}
+
+    The treatment rate is
+
+    .. math:: r_{\text{treatment}} =
+              \begin{cases}
+              R_{\text{treatment}}
+              &
+              \text{if $p_{\text{treated}} < T_{\text{treated}}(t)$},
+              \\
+              0 & \text{otherwise}.
+              \end{cases}
+
+    The nonadherence rate is
+
+    .. math:: r_{\text{nonadherence}} =
+              \begin{cases}
+              0 &
+              \text{if $p_{\text{suppressed}} < T_{\text{suppressed}}(t)$},
+              \\
+              R_{\text{nonadherence}} & \text{otherwise}.
+              \end{cases}
+
+    The vaccination rate is
+
+    .. math:: r_{\text{vaccination}} =
+              \begin{cases}
+              R_{\text{vaccination}} &
+              \text{if $p_{\text{vaccinated}} < T_{\text{vaccinated}}(t)$},
+              \\
+              R_{\text{vaccination}} & \text{otherwise}.
+              \end{cases}
+
+    The :math:`R`'s are :class:`ControlRatesMax`.
+
[…]

### 2017-02-06 model/datasheet.py

@@ -1,0 +1,532 @@
+'''
+Load data from the datafile.
+
+.. todo:: Report which countries have been updated when there's
+          a new version of the datasheet.
+'''
+
+import collections.abc
+import itertools
+import os.path
+import sys
+
+import joblib
+import numpy
+import pandas
+
+datafile = '../data_sheet.xlsx'
+# It's relative to this module file,
+# not files that might import it.
+datapath = os.path.join(os.path.dirname(__file__), datafile)
+
+
+def isyear(x):
+    try:
+        return (1900 < x < 2100)
+    except TypeError:
+        return False
+
+
+class Sheet:
+    # By default, don't allow a country to have no data.
+    allow_missing = False
+
+    @classmethod
+    def clean(cls, sheet):
+        '''
+        Drop junk rows at end of sheet.
+        '''
+        return sheet.iloc[: len(cls.parameter_names)].copy()
+
+    @classmethod
+    def get_index(cls, sheet):
+        return cls.parameter_names
+
+    @classmethod
+    def get_all(cls, wb = None):
+        '''
+        Read data for all countries from the Excel file.
+        '''
+        if wb is None:
+            wb = pandas.ExcelFile(datapath)
+        sheet_ = wb.parse(cls.sheetname, index_col = 0)
+        sheet = cls.clean(sheet_)
+        sheet.index = cls.get_index(sheet)
+        return sheet
+
+    @classmethod
+    def get_data_name(cls):
+        '''
+        The class name lower cased, and with any inner capital letters
+        replaced by '_' followed by the lower-cased letter.
+        '''
+        name = cls.__name__
+        if len(name) > 0:
+            name = name[0].lower() + name[1 : ]
+            i = 1
+            while (i < len(name)):
+                if name[i].isupper():
+                    rep = '_' + name[i].lower() + name[i + 1 : ]
+                    name = name[ : i] + rep
+                    i += 1  # Since we added the '_'
+                i += 1
+        return name
+
+    @classmethod
+    def get_empty(cls):
+        return pandas.Series(index = cls.parameter_names)
+
+    @classmethod
+    def get_country_data(cls, country, wb = None, allow_missing = None):
+        '''
+        `allow_missing = None` uses the class default.
+        '''
+        if allow_missing is None:
+            allow_missing = cls.allow_missing
+        sheet = cls.get_all(wb = wb)
+        try:
+            data = sheet[country]
+        except KeyError:
+            if allow_missing:
+                data = cls.get_empty()
[…]

### 2017-02-06 model/effectiveness.py

@@ -1,0 +1,51 @@
+'''
+Compute effectiveness.
+
+For disability weights :math:`\mathbf{w}`
+and state variables :math:`\mathbf{y}(t)`,
+DALYs are
+
+.. math:: D = \int_0^{t_\mathrm{end}} \mathbf{w}^{\mathrm{T}}
+          \mathbf{y}(t)\;\mathrm{d} t,
+
+and QALYs are
+
+.. math:: Q = \int_0^{t_\mathrm{end}}
+          (\mathbf{1} - \mathbf{w})^{\mathrm{T}}
+          \mathbf{y}(t)\;\mathrm{d} t,
+
+so DALYs and QALYs are related by
+
+.. math:: Q = \int_0^{t_\mathrm{end}} \mathbf{1}^{\mathrm{T}}
+          \mathbf{y}(t)\;\mathrm{d} t - D.
+'''
+
+import unittest
+
+import numpy
+from scipy import integrate
+
+from . import simulation
+
+
+def QALYs(sim):
+    QALYs_rate = sim.state @ sim.parameters.QALY_rates_per_person
+    return integrate.simps(QALYs_rate, simulation.t)
+
+
+def DALYs(sim):
+    DALYs_rate = sim.state @ sim.parameters.DALY_rates_per_person
+    return integrate.simps(DALYs_rate, simulation.t)
+
+
+class TestDALYsQALYs(unittest.TestCase):
+    def test_DALYs_QALYs(self):
+        from . import parameters
+        from . import target
+        country = 'Nigeria'
+        params = parameters.Parameters(country).mode()
+        targ = target.UNAIDS90()
+        sim = simulation.Simulation(params, targ)
+        self.assertTrue(numpy.isclose(
+            integrate.simps(sim.alive + sim.dead, simulation.t) - sim.DALYs,
+            sim.QALYs))

### 2017-02-06 model/incidence.py

@@ -1,0 +1,18 @@
+'''
+Compute the incidence.
+'''
+
+import numpy
+
+from . import simulation
+
+
+def compute(new_infections):
+    incidence = (numpy.diff(numpy.asarray(new_infections))
+                 / numpy.diff(simulation.t))
+    # Put NaNs in the first column to make it align with t.
+    if numpy.ndim(new_infections) == 1:
+        pad = numpy.nan
+    else:
+        pad = numpy.nan * numpy.ones(numpy.shape(new_infections)[: -1] + (1, ))
+    return numpy.hstack((pad, incidence))

### 2017-02-06 model/plot.py

@@ -1,0 +1,69 @@
+'''
+Make plots.
+'''
+
+from matplotlib import pyplot
+from matplotlib import ticker
+
+# import seaborn
+import os.path
+import sys
+sys.path.append(os.path.join(os.path.dirname(__file__), '../plots'))
+import seaborn_quiet as seaborn
+
+from . import ODEs
+from . import simulation
+
+
+def simulation_(sim, show = True):
+    '''
+    Plot a :class:`model.simulation.Simulation`.
+    '''
+
+    (fig0, ax0) = pyplot.subplots(2, 1)
+
+    for (pn, tn) in zip(sim.proportions.dtype.names,
+                        sim.target_values.dtype.names):
+        pv = getattr(sim.proportions, pn)
+        tv = getattr(sim.target_values, tn)
+        l = ax0[0].plot(simulation.t, pv, label = pn)
+        ax0[0].plot(simulation.t, tv, color = l[0].get_color(),
+                    linestyle = ':')
+    ax0[0].legend(loc = 'lower right')
+
+    for n in sim.control_rates.dtype.names:
+        v = getattr(sim.control_rates, n)
+        ax0[1].plot(simulation.t, v, label = '{} rate'.format(n))
+    ax0[1].legend(loc = 'upper right')
+
+    (fig1, ax1) = pyplot.subplots()
+
+    colors = seaborn.color_palette('husl', len(ODEs.variables))
+    for (n, c) in zip(ODEs.variables, colors):
+        v = getattr(sim, n)
+        ax1.semilogy(simulation.t, v, color = c, label = n)
+    ax1.legend(loc = 'lower right')
+
+    (fig2, ax2) = pyplot.subplots()
+
+    diagnosed = (sim.diagnosed
+                 + sim.treated
+                 + sim.viral_suppression
+                 + sim.AIDS)
+    treated =  (sim.treated
+                + sim.viral_suppression)
+    ax2.plot(simulation.t, sim.infected, label = 'PLHIV')
+    ax2.plot(simulation.t, diagnosed, label = 'diagnosed')
+    ax2.plot(simulation.t, treated, label = 'treated')
+    ax2.plot(simulation.t, sim.viral_suppression, label = 'suppressed')
+    ax2.legend(loc = 'upper right')
+
+    (fig3, ax3) = pyplot.subplots()
+
+    ax3.plot(simulation.t, 100 * sim.prevalence, label = 'prevalence')
[…]

### 2017-02-06 model/proportions.py

@@ -1,0 +1,53 @@
+'''
+Compute proportions diagnosed, treated, viral suppressed, and vaccinated.
+'''
+
+import warnings
+
+import numpy
+
+from . import ODEs
+
+
+def _safe_divide(a, b, fill_value = 0):
+    '''
+    Return a / b,
+    unless b == a == 0, then return 0.
+    '''
+    # Ignore divide-by-zero warnings.
+    with warnings.catch_warnings():
+        warnings.filterwarnings('ignore',
+                                module = 'numpy',
+                                message = ('divide by zero encountered in '
+                                           'true_divide'))
+        return numpy.where((a == 0) & (b == 0), 0, numpy.divide(a, b))
+
+
+def get(state):
+    '''
+    Get the proportions diagnosed, treated, viral suppressed, and vaccinated
+    from the current number of people in the model compartments.
+    '''
+
+    S, Q, A, U, D, T, V, W, Z, R = ODEs.split_state(state)
+
+    names = []
+    arrays = []
+
+    names.append('diagnosed')
+    # (D + T + V + W) / (A + U + D + T + V + W)
+    arrays.append(_safe_divide(D + T + V + W, A + U + D + T + V + W))
+
+    names.append('treated')
+    # (T + V + W) / (D + T + V + W)
+    arrays.append(_safe_divide(T + V + W, D + T + V + W))
+
+    names.append('suppressed')
+    # V / (T + V)
+    arrays.append(_safe_divide(V, T + V))
+
+    names.append('vaccinated')
+    # Q / (S + Q)
+    arrays.append(_safe_divide(Q, S + Q))
+
+    return numpy.rec.fromarrays(arrays, names = names)

### 2017-02-06 model/test.py

@@ -1,0 +1,41 @@
+'''
+Tests.
+'''
+
+import unittest
+
+# Import tests from other modules.
+# These get automatically run without any further code.
+# from .cost import TestRelativeCostOfEffort
+from .effectiveness import TestDALYsQALYs
+
+
+# class TestCE(unittest.TestCase):
+#     '''
+#     Tests of statsistics from a run of the simulation with
+#     precomputed values.
+#     '''
+#     country = 'Nigeria'
+#     # Precomputed values.
+#     stats = dict(# cost = 44373373515.342896,
+#                  DALYs = 25118516.824676983,
+#                  QALYs = 2201334748.7090836,
+#                  # incremental_cost = 32324197633.36628,
+#                  incremental_DALYs = 23269279.560440436,
+#                  incremental_QALYs = 27464382.193239689,
+#                  ICER_DALYs = 0.43365824620362664,
+#                  ICER_QALYs = 0.36741823987165301)
+#
+#     def test_stats(self):
+#         import numpy
+#         from .parameters import Parameters
+#         from .simulation import Simulation
+#         from . import targets
+#         parameters = Parameters(self.country).mode()
+#         simulation = Simulation(parameters, targets.UNAIDS90())
+#         for (i, kv) in enumerate(self.stats.items()):
+#             k, v = kv
+#             with self.subTest(i = i):
+#                 actual = getattr(simulation, k)
+#                 msg = '{}: Expected {}.  Got {}.'.format(k, v, actual)
+#                 self.assertTrue(numpy.isclose(actual, v), msg)

### 2017-02-06 plots/differences.py

@@ -1,0 +1,226 @@
+#!/usr/bin/python3
+'''
+Plot differences for samples from uncertainty analysis.
+
+.. todo:: Clean up.
+'''
+
+import operator
+import os.path
+import sys
+
+from matplotlib import colorbar
+from matplotlib import colors
+from matplotlib import gridspec
+from matplotlib import pyplot
+from matplotlib import ticker
+from matplotlib.backends import backend_pdf
+import numpy
+import tables
+
+sys.path.append(os.path.dirname(__file__))  # For Sphinx.
+import common
+# import seaborn
+import seaborn_quiet as seaborn
+sys.path.append('..')
+import model
+
+
+# Pairs (baseline, baseline + vaccine)
+targets = [model.target.all_[i : i + 2]
+           for i in range(0, len(model.target.all_), 2)]
+
+
+def _get_plot_info(results, country, targs, stat):
+    scale = None
+    percent = False
+    units = ''
+
+    if stat == 'infected':
+        label = 'PLHIV'
+        scale = 1e6
+    elif stat == 'prevalence':
+        label = 'Prevelance'
+        percent = True
+    elif stat == 'incidence_per_capita':
+        label = 'Incidence\n(per M per y)'
+        scale = 1e-6
+        units = ''
+    elif stat == 'AIDS':
+        label = 'AIDS'
+    elif stat == 'dead':
+        label = 'HIV-Related\nDeaths'
+    else:
+        raise ValueError("Unknown stat '{}'".format(stat))
+    
+    v_base = numpy.asarray(getattr(results['/{}/{}'.format(country, targs[0])],
+                                   stat))
+    v_intv = numpy.asarray(getattr(results['/{}/{}'.format(country, targs[1])],
+                                   stat))
+
+    data = v_base - v_intv
+    # data = (v_base - v_intv) / v_base
+
+    if percent:
+        scale = 1 / 100
+        units = '%%'
+    elif scale is None:
+        vmax = numpy.max(data)
+        if vmax > 1e6:
+            scale = 1e6
+            units = 'M'
+        elif vmax > 1e3:
+            scale = 1e3
+            units = 'k'
+        else:
+            scale = 1
+            units = ''
+
+    return (data, label, scale, units)
+
+
+def _plot_cell(ax, results, country, targs, stat,
+               country_label = None,
+               attr_label = None):
+    '''
+    .. todo:: Do a better job with making the lower ylim 0.
[…]

### 2017-02-06 plots/drive_upload.py

@@ -1,0 +1,45 @@
+#!/usr/bin/python3
+'''
+Upload figures etc to Google Drive.
+'''
+
+import os.path
+import sys
+import time
+
+sys.path.append('..')
+import drive
+
+
+files = (
+    '../../Documents/supplementary_text.pdf',
+    '../../Documents/diagram_standalone.pdf',
+    '../../Documents/diagram_standalone.png',
+    'effectiveness.pdf',
+    'effectiveness.png',
+    'effectiveness_regions.pdf',
+    'effectiveness_regions.png',
+    'infections_averted_map.pdf',
+    'infections_averted_map.png',
+    'initial_prevalence_map.pdf',
+    'initial_prevalence_map.png',
+    'vaccine_scenarios.pdf',
+    'vaccine_scenarios.png',
+)
+       
+# 'Effectiveness of HIV vaccine files' folder
+folderId = '0B_53qFSHU3XKNjc0d3lTV2s4cWM'
+
+
+if __name__ == '__main__':
+    first = True
+    with drive.Driver(parent = folderId) as d:
+        if not first:
+            time.sleep(1)
+        else:
+            first = False
+        for f in files:
+            try:
+                d.upload_if_newer(f)
+            except FileNotFoundError:
+                print('{}: file not found locally.'.format(f))

### 2017-02-06 plots/effectiveness_modes.py

@@ -1,0 +1,205 @@
+#!/usr/bin/python3
+'''
+Using the modes of the parameter distributions,
+make simulation plots.
+'''
+
+import os.path
+import sys
+
+from matplotlib import lines
+from matplotlib import pyplot
+from matplotlib.backends import backend_pdf
+import numpy
+import tables
+
+sys.path.append(os.path.dirname(__file__))  # For Sphinx.
+import common
+# import seaborn
+import seaborn_quiet as seaborn
+sys.path.append('..')
+import model
+
+
+alpha0 = 0.9
+
+
+def _plot_cell(ax, results, parameters, country, stat,
+               plot_hist = True,
+               country_label = None,
+               country_label_short = True,
+               stat_label = 'ylabel'):
+    '''
+    Plot one axes of simulation and historical data figure.
+    '''
+    info = common.get_stat_info(stat)
+
+    data = []
+    for target in model.targets.all_:
+        try:
+            v = results[country][str(target)][stat]
+        except tables.NoSuchNodeError:
+            v = None
+        data.append(v)
+    if info.scale is None:
+        info.autoscale(data)
+    if info.units is None:
+        info.autounits(data)
+
+    if plot_hist and (parameters is not None):
+        data_hist = common.data_hist_getter[stat](parameters)
+        if data_hist is not None:
+            data_hist = data_hist.dropna()
+            if len(data_hist) > 0:
+                ax.plot(data_hist.index, data_hist / info.scale,
+                        label = 'Historical data',
+                        zorder = 2,
+                        **common.historical_data_style)
+
+    for target in model.targets.all_:
+        try:
+            v = results[country][str(target)][stat]
+        except tables.NoSuchNodeError:
+            # Pop a style.
+            next(ax._get_lines.prop_cycler)
+        else:
+            ax.plot(common.t, numpy.asarray(v) / info.scale,
+                    label = common.get_target_label(target),
+                    alpha = alpha0,
+                    zorder = 1)
+
+            # Make a dotted line connecting the end of the historical data
+            # and the begining of the simulation.
+            if (plot_hist and (parameters is not None)
+                and (data_hist is not None) and (len(data_hist) > 0)):
+                # Drop NaNs at the beginning of incidence.
+                t = numpy.compress(numpy.isfinite(v), common.t)
+                w = numpy.compress(numpy.isfinite(v), v)
+                t = [data_hist.index[-1], t[0]]
[…]

### 2017-02-06 plots/effectiveness_regions.py

@@ -1,0 +1,162 @@
+#!/usr/bin/python3
+'''
+Plot the effectiveness of interventions by region.
+'''
+
+import itertools
+import os.path
+import sys
+
+from matplotlib import pyplot
+from matplotlib import patches
+from matplotlib import ticker
+import numpy
+import pandas
+import tables
+
+sys.path.append(os.path.dirname(__file__))  # For Sphinx.
+import common
+# import seaborn
+import seaborn_quiet as seaborn
+sys.path.append('..')
+import model
+
+
+effectiveness_measures = ['new_infections', 'infected']
+
+regions = model.regions.all_
+if 'Global' in regions:
+    regions.remove('Global')
+
+targets = model.target.all_
+
+region_labels = {
+    'Global': 'Global',
+    'Asia Pacific': 'Asia\n& The\nPacific',
+    'Caribbean': 'The\nCarribean',
+    'East and Southern Africa': 'Eastern &\nSouthern\nAfrica',
+    'Eastern Europe and Central Asia': 'Eastern\nEurope &\nCentral Asia',
+    'Latin America': 'Latin\nAmerica',
+    'Middle East and North Africa': 'Middle\nEast &\nNorth Africa',
+    'North America': 'North\nAmerica',
+    'West and Central Africa': 'West &\nCentral\nAfrica',
+    'Western Europe': 'Western &\nCentral\nEurope'
+}
+
+
+def _plot_stat(ax, results, regions, stat, confidence_level, **kwargs):
+    CIkey = 'CI{:g}'.format(100 * confidence_level)
+
+    info = common.get_stat_info(stat)
+
+    idx = ['median', 'CIlower', 'CIupper']
+    data = pandas.Panel(items = regions,
+                        major_axis = targets,
+                        minor_axis = idx,
+                        dtype = float)
+    for region, target in itertools.product(regions, targets):
+        try:
+            v = results[region][target][stat]
+        except tables.NoSuchNodeError:
+            pass
+        else:
+            # At the end time.
+            data.loc[region, target, 'median'] = v['median'][..., -1]
+            data.loc[region, target, ['CIlower', 'CIupper']] = v[CIkey][..., -1]
+
+    if info.scale is None:
+        info.autoscale(data.max().max())
+
+    colors = seaborn.color_palette()
+
+    pad = 0.2
+    width = (1 - pad) / len(targets)
+    for (i, target) in enumerate(targets):
[…]

### 2017-02-06 plots/infections_per_capita_averted_map.py

@@ -1,0 +1,148 @@
+#!/usr/bin/python3
+'''
+Make maps of the infections averted at different times.
+
+.. todo:: This uses :func:`model.results.samples.open_` because `alive`
+          is not in :func:`model.results.samples.h5.open_` at the moment.
+'''
+
+import os.path
+import sys
+
+from matplotlib import colors as mcolors
+from matplotlib import pyplot
+from matplotlib import ticker
+import numpy
+import pandas
+from scipy import integrate
+import tables
+
+sys.path.append(os.path.dirname(__file__))
+import common
+import mapplot
+sys.path.append('..')
+import model
+
+
+baseline = model.targets.StatusQuo()
+interventions = (
+    model.targets.UNAIDS95(),
+    model.targets.Vaccine(treatment_target = model.targets.StatusQuo()),
+    model.targets.Vaccine(treatment_target = model.targets.UNAIDS95()))
+
+baseline = str(baseline)
+interventions = list(map(str, interventions))
+
+time = 2035
+
+scale = 1e-3
+title = 'Infections per 1000 Averted (Compared to {})'.format(baseline)
+vmin = 0.0025 / scale
+vmax = 0.25 / scale
+norm = mcolors.LogNorm(vmin = vmin, vmax = vmax)
+cmap = common.cmap_scaled('magma_r', vmax = 0.85)
+label_coords = (-130, -30)
+height = 0.28
+pad = 0.035
+cpad = 0.05
+aspect = 1.45
+
+
+def plot(infections_per_capita_averted):
+    countries = infections_per_capita_averted.index
+    interventions = infections_per_capita_averted.columns
+
+    fig = pyplot.figure()
+    nrows = len(interventions)
+    for (i, intv) in enumerate(interventions):
+        if i <  nrows - 1:
+            h = height
+            b = 1 - height - (height + pad) * i
+        else:
+            h = 1 - (height + pad) * (nrows - 1)
+            b = 0
+
+        m = mapplot.Basemap(rect = (0, b, 1, h),
+                            anchor = (0.5, 1))
+
+        mappable = m.choropleth(
+            countries,
+            infections_per_capita_averted.loc[:, intv] / scale,
+            cmap = cmap,
+            norm = norm,
+            vmin = vmin,
+            vmax = vmax)
+
+        label = common.get_target_label(intv)
+        label = label.replace('_', ' ').replace('+', '\n+')
+        X, Y = label_coords
+        m.text_coords(X, Y, label,
[…]

### 2017-02-06 plots/initial_prevalence_map.py

@@ -1,0 +1,70 @@
+#!/usr/bin/python3
+'''
+Map the initial proportion of the population with HIV.
+'''
+
+import os.path
+import sys
+
+from matplotlib import colors
+from matplotlib import pyplot
+from matplotlib import ticker
+import numpy
+import pandas
+
+sys.path.append(os.path.dirname(__file__))  # For Sphinx.
+import common
+import mapplot
+sys.path.append('..')
+import model
+
+
+def _main():
+    data = model.datasheet.InitialConditions.get_all()
+
+    countries = data.columns
+
+    nHIV = data.iloc[1 :].sum(0)
+    n = data.sum(0)
+    prevalence = nHIV / n
+    for (k, v) in prevalence.items():
+        print('{}: {:g}%'.format(k, 100 * v))
+
+    # vmin = prevalence.min()
+    # vmax = prevalence.max()
+    vmin = 0.0005
+    vmax = 0.25
+
+    cmap = 'YlOrRd'
+    norm = colors.LogNorm
+    ticks = ticker.LogLocator(10, [1, 2.5, 5])
+    fig = pyplot.figure(figsize = (common.width_2column, 3))
+    m = mapplot.Basemap()
+    m.choropleth(countries, 100 * prevalence,
+                 cmap = cmap,
+                 norm = norm(vmin = 100 * vmin,
+                             vmax = 100 * vmax),
+                 vmin = 100 * vmin,
+                 vmax = 100 * vmax)
+    cbar = m.colorbar(label = '2015 HIV Prevalence',
+                      format = '%g%%',
+                      ticks = ticks)
+
+    ticklabels = cbar.ax.get_xticklabels()
+    if prevalence.min() < vmin:
+        ticklabels[0].set_text('≤' + ticklabels[0].get_text())
+    if prevalence.max() > vmax:
+        ticklabels[-1].set_text('≥' + ticklabels[-1].get_text())
+    cbar.ax.set_xticklabels(ticklabels)
+    cbar.ax.tick_params(labelsize = pyplot.rcParams['font.size'])
+
+    m.tighten(aspect_adjustment = 1.35)
+
+    common.savefig(m.fig, '{}.pdf'.format(common.get_filebase()))
+    common.savefig(m.fig, '{}.png'.format(common.get_filebase()))
+
+    m.show()
+
+
+if __name__ == '__main__':
+    _main()

### 2017-02-06 plots/initial_proportions_map.py

@@ -1,0 +1,91 @@
+#!/usr/bin/python3
+'''
+Map the initial proportions diagnosed, treated, and viral suppressed.
+'''
+
+import os.path
+import sys
+
+import pandas
+
+sys.path.append(os.path.dirname(__file__))  # For Sphinx.
+import common
+sys.path.append('..')
+import model
+import mapplot
+
+
+def _main():
+    data = model.datasheet.InitialConditions.get_all()
+
+    countries = data.columns
+
+    # People with HIV.
+    nHIV = data.iloc[1 :].sum(0)
+    pHIV = nHIV / data.sum(0)
+
+
+    ###############################
+    # Non-overlapping proportions #
+    # I.e. should sum to 1.       #
+    ###############################
+    p = pandas.DataFrame(index = countries)
+    p['undiagnosed'] = data.loc[['A', 'U']].sum(0) / nHIV
+    p['diagnosed'] = data.loc['D'] / nHIV
+    p['treated'] = data.loc['T'] / nHIV
+    p['suppressed'] = data.loc['V'] / nHIV
+
+
+    ##############################################################
+    # Proportions of people with HIV with the different statuses #
+    # I.e. the treatment cascade.                                #
+    # These overlap: treated people are also diagnosed, etc.     #
+    ##############################################################
+    p_overlapping = pandas.DataFrame(index = countries)
+    p_overlapping['all'] = 1
+    p_overlapping['diagnosed'] \
+        = p[['diagnosed', 'treated', 'suppressed']].sum(1)
+    p_overlapping['treated'] = p[['treated', 'suppressed']].sum(1)
+    p_overlapping['suppressed'] = p['suppressed']
+
+
+    # Easy-to-read colors.
+    cp = mapplot.seaborn.color_palette('Set1')
+    colors = (cp[0], cp[1], cp[4], cp[2])
+
+    m = mapplot.Basemap()
+
+    m.barhs(countries, p_overlapping,
+            widthscale = 4.5, heightscale = 1.5, color = colors)
+
+    # Legend
+    X, Y = (-155, -30)
+    m.rectangle_coords(X - 5.5, Y - 7, 78, 14,
+                       facecolor = 'white', linewidth = 0.1)
+    m.barh_coords(X, Y, [1, 0.9, 0.9 ** 2, 0.9 ** 3],
+                  widthscale = 2 * 4.5, heightscale = 2 * 1.5,
+                  color = colors)
[…]

### 2017-02-06 plots/mapplot/cartopy_quiet.py

@@ -1,0 +1,11 @@
+'''
+Silence warnings from :mod:`matplotlib` that are triggered by :mod:`cartopy`.
+'''
+
+import warnings
+warnings.filterwarnings('ignore',
+                        module = 'matplotlib',
+                        message = ('get_axes has been deprecated in mpl 1.5, '
+                                   'please use the\naxes property.  '
+                                   'A removal date has not been set.'))
+from cartopy import *

### 2017-02-06 plots/mapplot/locators.py

@@ -1,0 +1,85 @@
+'''
+Locators to get the coordinates of a country.
+'''
+
+import numpy
+
+# import cartopy
+import os.path
+import sys
+sys.path.append(os.path.dirname(__file__))  # For Sphinx
+import cartopy_quiet as cartopy
+
+
+class _Locator:
+    '''
+    Abstract base class for locators.
+    '''
+
+    crs = cartopy.crs.PlateCarree()
+
+    def get_locations(self, countries):
+        '''
+        Do many calls to :meth:`get_location` and stack results.
+        '''
+
+        coords = numpy.vstack(map(self.get_location, countries)).T
+        return coords
+    
+
+class GeocodeLocator(_Locator):
+    '''
+    Use :class:`geopy.geocoders.Nominatim` to get country coordinates.
+    '''
+
+    crs = cartopy.crs.PlateCarree()
+
+    translations = {'United Republic of Tanzania': 'Tanzania'}
+
+    def __init__(self, *args, **kwargs):
+        import geopy
+
+        from . import _shelve
+
+        self.geolocator = geopy.geocoders.Nominatim(*args, **kwargs)
+
+        # cache geolocator lookups to disk for speed.
+        self.get_location = _shelve.shelved(self.get_location)
+
+    def get_location(self, country):
+        country = self.translations.get(country, country)
+        location = self.geolocator.geocode(dict(country = country))
+        if location is None:
+            raise ValueError('Couldn\'t find country "{}".'.format(country))
+        return location.longitude, location.latitude
+
+
+class CentroidLocator(_Locator):
+    '''
+    Use the centroid from the country map borders to get country coordinates.
+    '''
+
+    _equalarea_crs = cartopy.crs.AlbersEqualArea()
+    def __init__(self, borders):
+        self.borders = borders
+
+        try:
+            geom = next(self.borders.geometries())
+        except StopIteration:
+            self.crs = None
+        else:
+            self.crs = geom.crs
+
+    def get_location(self, country):
+        border = self.borders[country]
+
+        centroids = []
+        areas = []
+        for g in border.geometries():
+            centroids.append(g.centroid.xy)
+            areas.append(
+                self._equalarea_crs.project_geometry(g, border.crs).area)
+
+        centroid = numpy.average(centroids, weights = areas,
+                                 axis = 0).squeeze()
+        return centroid

### 2017-02-06 plots/sensitivity.py

@@ -1,0 +1,251 @@
+#!/usr/bin/python3
+'''
+Plot correlation between samples and outcomes.
+
+.. todo:: Clean up similarity with prcc.py.
+'''
+
+import os.path
+import sys
+
+from matplotlib import pyplot
+from matplotlib import ticker
+import numpy
+from scipy import interpolate
+
+sys.path.append(os.path.dirname(__file__))  # cwd for Sphinx.
+import common
+import stats
+# import seaborn
+import seaborn_quiet as seaborn
+sys.path.append('..')
+import model
+
+
+def get_outcome_samples(results, country, targets, stat, times):
+    x, y =  (numpy.asarray(getattr(results['/{}/{}'.format(country, t)], stat))
+             for t in targets)
+    z = x - y
+    interp = interpolate.interp1d(common.t, z, axis = -1)
+    outcome_samples = interp(times)
+    return outcome_samples
+
+
+def plot_ranks(X, y, outcome, parameter_names = None, alpha = 0.7,
+               size = 2, colors = None):
+    m = numpy.shape(X)[0]
+    n = numpy.shape(X)[-1]
+
+    X = (stats.rankdata(X) - 1) / (m - 1)
+    y = (stats.rankdata(y) - 1) / (m - 1)
+
+    if colors is None:
+        colors = seaborn.color_palette('Dark2', n)
+
+    fig, axes = pyplot.subplots(n, 2,
+                                sharex = 'col',
+                                sharey = 'col',
+                                figsize = (5.5, 11))
+    maxlim = 0
+    for (i, ax) in enumerate(axes):
+        mask = numpy.array([j == i for j in range(n)])
+        x = numpy.squeeze(X[..., mask])
+        Z = X[..., ~mask]
+
+        ax[0].scatter(x, y, color = colors[i], s = size, alpha = alpha)
+
+        x_res = stats.get_residuals(Z, x)
+        y_res = stats.get_residuals(Z, y)
+
+        ax[1].scatter(x_res, y_res, color = colors[i], s = size, alpha = alpha)
+
+        if i == n - 1:
+            ax[0].set_xlabel('rank\nparameter value')
+            ax[1].set_xlabel('residual rank\n parameter value')
+
+        if i == n // 2:
+            ax[0].set_ylabel('rank reduction in\n{}'.format(
+                outcome.replace('_', ' ')))
+            ax[1].set_ylabel('residual rank reduction in\n{}'.format(
[…]

### 2017-02-06 plots/transmission_rate.py

@@ -1,0 +1,261 @@
+#!/usr/bin/python3
+'''
+Make a PDF with a page of transmission plots for each country.
+'''
+
+import itertools
+import os.path
+import sys
+
+import joblib
+from matplotlib.backends import backend_pdf
+from matplotlib import pyplot
+from matplotlib import ticker
+import numpy
+import pandas
+
+sys.path.append(os.path.dirname(__file__))  # For Sphinx.
+import common
+sys.path.append('..')
+import model
+from model import transmission_rate
+
+# import seaborn
+import seaborn_quiet as seaborn
+
+
+def plot_transmission_rates(countries, fig = None,
+                            quantile_level = 0.01,
+                            scale = 0.8,
+                            savefig = True):
+    if fig is None:
+        fig = pyplot.figure(figsize = (8.5, 11))
+    with seaborn.axes_style('whitegrid'):
+        ax = fig.add_subplot(1, 1, 1)
+        seaborn.despine(ax = ax, top = True, bottom = True)
+        n = len(countries)
+        colors = seaborn.color_palette('husl', n)
+        for (i, country) in enumerate(countries):
+            # Plot from top instead of bottom.
+            j = n - 1 - i
+            parameters = model.parameters.Parameters(country)
+            rv = transmission_rate.estimate(parameters)
+            a, b = rv.ppf([quantile_level / 2, 1 - quantile_level / 2])
+            x = numpy.linspace(a, b, 101)
+            y = rv.pdf(x) / n * scale
+            ax.fill_between(x, j + y, j - y,
+                            linewidth = 0,
+                            facecolor = colors[i],
+                            alpha = 0.7)
+            ax.scatter(rv.mode, j,
+                       marker = '|', s = 30, linewidth = 1,
+                       color = 'black')
+    ax.xaxis.set_tick_params(labelsize = pyplot.rcParams['font.size'])
+    ax.set_xlabel('Transmission rate (per year)')
+    ax.set_xlim(0, 0.5001)
+    ax.xaxis.set_major_locator(ticker.MultipleLocator(0.05))
+    ax.set_ylim(-1.5, n + 0.5)
+    ax.set_yticks(range(n))
+    yticklabels = (common.get_country_short_name(c)
+                   for c in reversed(countries))
+    ax.set_yticklabels(yticklabels, size = 5)
+    ax.grid(False, axis = 'y')
+    # Alternate right-left alignment.
[…]

### 2017-02-06 run_samples.py

@@ -1,0 +1,44 @@
+#!/usr/bin/python3
+'''
+Run simulations with parameter samples.
+'''
+
+import model
+
+
+countries = model.datasheet.get_country_list()
+# Move these to the front.
+countries_to_plot = ['United States of America',
+                     'South Africa',
+                     'Uganda',
+                     'Nigeria',
+                     'India',
+                     'Rwanda']
+for c in countries_to_plot:
+    countries.remove(c)
+countries = countries_to_plot + countries
+
+
+def _run_country(country, target, samples):
+    print('Running {}, {!s}.'.format(country, target))
+
+    parametersamples = model.parameters.Sample.from_samples(country,
+                                                            samples)
+
+    multisim = model.multisim.MultiSim(parametersamples, target)
+
+    return multisim
+
+
+def _main():
+    samples = model.samples.load()
+
+    for country in countries:
+        for target in model.target.all_:
+            if not model.results.exists(country, target):
+                results = _run_country(country, target, samples)
+                model.results.dump(results)
+
+
+if __name__ == '__main__':
+    _main()

### 2017-02-06 run_vaccine_scenarios.py

@@ -1,0 +1,76 @@
+#!/usr/bin/python3
+'''
+Using the modes of the parameter distributions,
+run simulations for the different vaccine sensitivity scenarios.
+
+.. todo:: Update to use results.dump.
+'''
+
+import joblib
+import tables
+
+import model
+
+
+stats_to_save = ['infected', 'incidence', 'prevalence',
+                 'incidence_per_capita', 'AIDS', 'dead',
+                 'new_infections', 'alive']
+
+
+def _run_one(country, targets = None):
+    if targets is None:
+        targets = model.targets.vaccine_scenarios
+    parameters = model.parameters.Parameters(country)
+    parameter_values = parameters.mode()
+    results = joblib.Parallel(n_jobs = -1)(
+        joblib.delayed(model.simulation.Simulation)(parameter_values,
+                                                    target)
+        for target in targets)
+    retval = {}
+    for (target, r) in zip(targets, results):
+        retval[str(target)] = r
+    return retval
+
+
+def _build_regionals(results, targets = None):
+    if targets is None:
+        targets = model.targets.vaccine_scenarios
+
+    countries = list(results.keys())
+    for region in model.regions.all_:
+        if region in countries:
+            countries.remove(region)
+
+    for target in targets:
+        val = {country: results[country][str(target)] for country in countries}
+        for region in model.regions.all_:
+            if region == 'Global':
+                mc = model.multicountry.Global(val)
+            else:
+                val_ = {c: val[c] for c in val.keys()
+                        if c in model.regions.regions[region]}
+                mc = model.multicountry.MultiCountry(val_)
+            for s in stats_to_save:
+                v = getattr(mc, s)
+                model.h5._dump_val(results, '/{}/{}'.format(region, target),
+                                   s, v)
+
+
+def _run_all(targets = None):
+    countries = model.datasheet.get_country_list()
+    results = model.results.modes.open_vaccine_scenarios(mode = 'a')
+    for country in countries:
+        if country not in results:
+            print(country)
+            r = _run_one(country, targets = targets)
+            for (t, v) in r.items():
+                for s in stats_to_save:
+                    x = getattr(v, s)
+                    model.h5._dump_val(results, '/{}/{}'.format(country, t),
+                                       s, x)
+    _build_regionals(results, targets = targets)
+    return results
+
+
+if __name__ == '__main__':
+    results = _run_all()

### 2017-02-06 tests/datasheet.py

@@ -1,0 +1,37 @@
+#!/usr/bin/python3
+'''
+Test the loading of data from the datasheet using :mod:`model.datasheet`.
+'''
+
+import sys
+
+sys.path.append('..')
+import model
+
+
+def test_one(country):
+    '''
+    Test loading one country's data from the datasheet.
+    '''
+    parameters = model.parameters.Parameters(country).mode()
+
+    print(parameters)
+
+
+def test_all():
+    '''
+    Test loading all data from the datasheet.
+    '''
+    for country in model.datasheet.get_country_list():
+        print(country)
+        model.parameters.Parameters(country)
+
+
+def _main():
+    test_one('South Africa')
+    
+    test_all()
+
+
+if __name__ == '__main__':
+    _main()

### 2017-02-06 tests/global_.py

@@ -1,0 +1,101 @@
+#!/usr/bin/python3
+'''
+Test :mod:`model.global_`.
+
+This requires data from the simulation runs in the directory `./results`.
+'''
+
+import sys
+
+from matplotlib import pyplot
+from matplotlib import ticker
+from matplotlib.backends import backend_pdf
+import numpy
+
+# import seaborn
+sys.path.append('../plots')
+import seaborn_quiet as seaborn
+
+sys.path.append('..')
+import model
+
+
+countries_to_plot = ('Global', )
+
+
+def getstats(x):
+    avg = numpy.median(x, axis = 0)
+    CIlevel = 0.5
+    CI = numpy.percentile(x,
+                          [100 * CIlevel / 2, 100 * (1 - CIlevel / 2)],
+                          axis = 0)
+    # avg = numpy.mean(x, axis = 0)
+    # std = numpy.std(x, axis = 0, ddof = 1)
+    # CI = [avg + std, avg - std]
+    return (avg, CI)
+
+
+class PercentFormatter(ticker.ScalarFormatter):
+    def _set_format(self, vmin, vmax):
+        super()._set_format(vmin, vmax)
+        if self._usetex:
+            self.format = self.format[: -1] + '%%$'
+        elif self._useMathText:
+            self.format = self.format[: -2] + '%%}$'
+        else:
+            self.format += '%%'
+
+
+def plotcell(ax, results, attr):
+    percent = False
+    if attr == 'infected':
+        ylabel = 'People Living with HIV\n(M)'
+        scale = 1e6
+    elif attr == 'AIDS':
+        ylabel = 'People with AIDS\n(1000s)'
+        scale = 1e3
+    elif attr == 'incidence_per_capita':
+        ylabel = 'HIV Incidence\n(per M people per y)'
+        scale = 1e-6
+    elif attr == 'prevalence':
+        ylabel = 'HIV Prevelance\n'
+        percent = True
+    else:
+        raise ValueError("Unknown attr '{}'!".format(attr))
+
+    if percent:
+        scale = 1 / 100
+
+    t = results.t
+    x = getattr(results, attr)
+    avg, CI = getstats(x)
+    lines = ax.plot(t, avg / scale, label = target,
+                    zorder = 2)
+    ax.fill_between(t, CI[0] / scale, CI[1] / scale,
+                    color = lines[0].get_color(),
+                    alpha = 0.3)
+
[…]

### 2017-02-06 tests/logmodel.py

@@ -1,0 +1,48 @@
+#!/usr/bin/python3
+'''
+Test solving the log model :func:`model.ODEs.rhs_log`
+versus the non-log model :func:`model.ODEs.rhs`
+for correctness and speed.
+'''
+
+import sys
+import time
+
+import numpy
+
+sys.path.append('..')
+import model
+
+
+def _main():
+    country = 'South Africa'
+    target = model.target.UNAIDS90()
+
+    parameters = model.parameters.Parameters(country).mode()
+
+    time0 = time.time()
+    simulation = model.simulation.Simulation(parameters, target,
+                                             use_log = False)
+    time1 = time.time()
+    print('Non-log model took {} sec.'.format(time1 - time0))
+
+    time0 = time.time()
+    simulation_log = model.simulation.Simulation(parameters, target,
+                                                 use_log = True)
+    time1 = time.time()
+    print('Log model took {} sec.'.format(time1 - time0))
+
+
+    # Ignore differences in the initial conditions.
+    maxabserr = numpy.abs(simulation.state - simulation_log.state)[1 : ].max()
+    maxrelerr = numpy.ma.divide(
+        numpy.abs(simulation.state - simulation_log.state),
+        simulation.state).filled(0).max()
+
+    print('Max absolute error = {}'.format(maxabserr))
+    print('Max relative error = {}'.format(maxrelerr))
+
+
+
+if __name__ == '__main__':
+    _main()

### 2017-02-06 tests/profile_.py

@@ -1,0 +1,23 @@
+#!/usr/bin/python3
+'''
+Profile :mod:`model.simulation`.
+'''
+
+
+import cProfile
+import sys
+
+sys.path.append('..')
+import model
+
+
+def _main():
+    country = 'South Africa'
+    target = model.target.Vaccine()
+    parameters = model.parameters.Mode.from_country(country)
+    simulation = model.simulation.Simulation(parameters, target)
+    return simulation
+
+
+if __name__ == '__main__':
+    cProfile.run('_main()', sort = 'tottime')

### 2017-02-12 model/__init__.py
More merging...

@@ -1,10 +1,9 @@
 '''
-HIV 90-90-90 & optimization model.
+HIV 90-90-90 model.
 '''
 
 from . import datasheet
 from . import multicountry
-from . import optimization
 from . import parameters
 from . import regions
 from . import results

### 2017-02-12 model/parameters.py

@@ -12,13 +12,12 @@ from scipy import optimize
 from . import datasheet
 from . import latin_hypercube_sampling
 from . import R0
+from . import results
 from . import transmission_rate
 
 
-# nsamples = 1000
-nsamples = 2 # For testing.
-samplesfile = os.path.normpath(os.path.join(os.path.dirname(__file__),
-                                            '../samples.npy'))
+nsamples = 1000
+samplesfile = os.path.join(results.resultsdir, 'samples.pkl')
 
 
 def _get_samples():

### 2017-02-12 docs/supporting_information.tex
Fixed reference style for PNAS.
More merging...

@@
 
-% \usepackage[style=nature]{biblatex}
-% \addbibresource{supporting_information.bib}
 \usepackage[numbers, round, comma, sort&compress]{natbib}
@@
     $\mu$ & Background death rate
-    & Country specific, Data Set 2
+    & Country specific, Dataset 2
     & \cite{World_Development_Indicators2013-ee}
@@
     $\kappa$ & Recruitment rate
-    & Country specific, Data Set 2
+    & Country specific, Dataset 2
     & \cite{World_Development_Indicators2013-ee, WorldBankpg}
@@
 PLHIV, and HIV-related deaths were calculated from the aggregates.
-(See Data Set 6 for the definitions of UNAIDS regions.)
+(See Dataset 6 for the definitions of UNAIDS regions.)
 
@@
 aged 15--49 years \cite{The_World_Bank2016-fd} were obtained from the
-World Bank (Data Set 2). Longitudinal HIV prevalence
-(Data Set 3) and incidence (Data Set 4)
+World Bank (Dataset 2). Longitudinal HIV prevalence
+(Dataset 3) and incidence (Dataset 4)
 estimates for ages 15--49, spanning from as early as 1990 for some
@@
 and the number who have viral suppression or have been retained on
-treatment for at least 12 months (Data Set 5).  Where data
+treatment for at least 12 months (Dataset 5).  Where data
 or estimates were not available from these sources, alternative
@@
 ministry reports were consulted.  Full information on the sources used
-for each country is provided in Data Sets 2--5.  These
+for each country is provided in Datasets 2--5.  These
 source tables are also available in our public source-code
@@
 available historical country-specific estimates of prevalence and
-incidence (Data Sets 3 \& 4), and published estimates of
+incidence (Datasets 3 \& 4), and published estimates of
 transmissibility per coital
@@
 
-% \printbibliography
-\bibliography{supporting_information}
-\bibliographystyle{pnas-new}
+%\bibliography{\jobname}
+%\bibliographystyle{pnas-jm}
+% The reference list was hand editted!
+\input{\jobname.bbl}
 

### 2017-02-12 src/build_percentiles.py

@@ -1,68 +1,0 @@
-#!/usr/bin/python3
-'''
-Update the cache of percentiles from the runs with parameter distributions.
-'''
-
-import itertools
-import warnings
-
-import numpy
-import tables
-
-import model
-
-
-regions_and_countries = model.regions.all_ + model.datasheet.get_country_list()
-
-targets = model.target.all_
-
-_stats_to_dump = ['new_infections', 'infected', 'incidence_per_capita',
-                  'AIDS', 'dead']
-
-CI_levels = ['median', 50, 80, 90, 95, 99]
-
-
-def _main():
-    with model.results.samples.stats.open_(mode = 'a') as h5file:
-        for (region_or_country, target) in itertools.product(
-                regions_and_countries, targets):
-            target = str(target)
-            results_exist = model.results.samples.exists(region_or_country,
-                                                         target)
-            stats_exist = '/{}/{}'.format(region_or_country, target) in h5file
-            if results_exist and (not stats_exist):
-                print('{}, {}'.format(region_or_country, target))
-                with model.results.samples.open_(region_or_country,
-                                                 target) as results:
-                    with warnings.catch_warnings():
-                        warnings.filterwarnings(
-                            'ignore',
-                            category = tables.NaturalNameWarning)
-                        # For NaNs.
-                        warnings.filterwarnings(
-                            'ignore',
-                            category = RuntimeWarning)
-                        rtgroup = h5file.create_group(
-                            '/{}'.format(region_or_country),
-                            target,
-                            createparents = True)
-                        for stat in _stats_to_dump:
-                            vals = getattr(results, stat)
-                            rtsgroup = h5file.create_group(rtgroup,
-                                                           stat)
-                            for lev in CI_levels:
-                                if lev == 'median':
-                                    obj = numpy.median(vals, axis = 0)
-                                    name = 'median'
-                                else:
-                                    obj = numpy.percentile(vals,
-                                                           [50 - lev / 2,
-                                                            50 + lev / 2],
-                                                           axis = 0)
-                                    name = 'CI{}'.format(lev)
-                                h5file.create_carray(rtsgroup, name,
-                                                     obj = obj)
-
-
-if __name__ == '__main__':
-    _main()

### 2017-02-12 src/model/optimization/__init__.py

@@ -1,6 +1,0 @@
-'''
-Optimization of target levels.
-'''
-
-from . import effectiveness
-from . import net_benefit

### 2017-02-12 src/tests/global_.py

@@ -2,7 +2,7 @@
 '''
 Test :mod:`model.global_`.
 
-This requires data from the simulation runs in the directory `./sim_data`.
+This requires data from the simulation runs.
 '''
 
 import sys

### 2017-02-12 src/tests/net_benefit_maximize.py

@@ -1,39 +1,0 @@
-#!/usr/bin/python3
-'''
-Test the :mod:`model.optimization`.
-
-.. todo:: Not working.
-'''
-
-import sys
-
-sys.path.append('..')
-import model
-
-
-def _main(parallel = True, debug = True, **kwargs):
-    country = 'South Africa'
-
-    parameters = model.parameters.Mode.from_country(country)
-
-    # 0 is just cost.
-    # inf is just DALYs.
-    # Other values are multiples of per-capita GDP.
-    cost_effectiveness_threshold = 1
-
-    result = model.optimization.net_benefit.maximize(
-        parameters,
-        cost_effectiveness_threshold,
-        parallel = parallel,
-        debug = debug,
-        **kwargs)
-
-    targets, incremental_net_benefit = result
-
-    print('target values = {}'.format(targets))
-    print('incremental net benefit = {:g} DALYs'.format(
-        incremental_net_benefit))
-
-
-if __name__ == '__main__':
-    _main(nruns = 1)

### 2017-03-07 docs/supporting_information.tex
Fixed label for new region names.

@@
 regional outcomes
-(\hyperref[effectiveness_Global]{Figs.~\ref*{effectiveness_Global}}--\ref*{effectiveness_Western_Europe}).
+(\hyperref[effectiveness_Global]{Figs.~\ref*{effectiveness_Global}}--\ref*{effectiveness_Western_and_Central_Europe}).
 
